---
title: "Selection on within-individual variation in flowering time in Lathyrus vernus"
subtitle: "Data preparation"
author : "Alicia Valdés"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(tibble.width = Inf)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r load packages, include=FALSE}
library(tidyverse)
library(readxl)
library(lubridate)
library(moments)
library(RColorBrewer)
library(ggthemes)
library(ggridges)
```

```{r Define ggplot themes and palettes, include=FALSE}
my_theme <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(legend.position="none")+theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
my_theme_legend <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
myPalette <- colorRampPalette(brewer.pal(11, "YlOrRd"))
```

# Read data for individuals from Excel file

```{r}
data_ids_87 <- read_excel("data/edited/individual_characteristics.xlsx", 
                       sheet = "1987_editsAV")
data_ids_88 <- read_excel("data/edited/individual_characteristics.xlsx", 
                       sheet = "1988_editsAV")
data_ids_89 <- read_excel("data/edited/individual_characteristics.xlsx", 
                       sheet = "1989_editsAV")
```

# Read data for individual flowers from Excel files

```{r}
data_id_flowers_87 <- read_excel("data/edited/individual_flower_characteristics.xlsx", 
                       sheet = "1987")
data_id_flowers_88 <- read_excel("data/edited/individual_flower_characteristics.xlsx", 
                       sheet = "1988")
data_id_flowers_89 <- read_excel("data/edited/individual_flower_characteristics.xlsx", 
                       sheet = "1989")
data_Ind2_33_1989 <- read_excel("data/edited/individual_characteristics_Ind2_33_1989.xlsx",
                                sheet = "to_R")
```

```{r}
nrow(data_ids_87)
# 231 rows
nrow(data_ids_88)
# 169 rows
nrow(data_ids_89)
# 96 rows
```
# Error in 1989

Ind = 2:33 appears twice, there was a problem with this Ind, I will remove those two records and add a new record for Ind 2:33 with all moments that were recalculated in Excel.

```{r}
subset(data_ids_89,Ind=="2:33")
data_ids_89 <- data_ids_89 %>% filter(!(Ind=="2:33"))
data_ids_89 <- bind_rows(data_ids_89,data_Ind2_33_1989)
```

# Rename columns

```{r}
data_ids_87 <- data_ids_87 %>% 
  rename(number = ID, subplot = Subplot, id = Ind, avFD = `Mean (MFD)`,
         skew =  Skew, kurt = Kurtosis,LFD = `Max (LFD)`, FFD = `Min (FFD)`,
         dur = `Range (Duration)`, n_fl = `Flower N`, n_fr = Fruits, 
         fr_init = `Fruit init (fr/fl)`, n_seed = `Total seeds`, 
         n_preyed_seed = `Preyed seeds`, 
         fitness = `Intact seeds (fitness)`,
         imp_seed_preyed = Imputed,
         n_seed_per_fr = `Seeds per fruit`,
         prop_seed_preyed = `Proportion preyed`)
data_ids_88 <- data_ids_88 %>% 
  rename(number = ID, subplot = Subplot, id = Ind, avFD = `Mean (MFD)`,
         skew =  Skew, kurt = Kurtosis,LFD = `Max (LFD)`, FFD = `Min (FFD)`,
         dur = `Range (Duration)`, n_fl = `Flower N`, n_fr = Fruits, 
         fr_init = `Fruit init (fr/fl)`, n_seed = `Total seeds`, 
         n_preyed_seed = `Preyed seeds`, 
         fitness = `Intact seeds (fitness)`,
         imp_seed_preyed = Imputed,
         n_seed_per_fr = `Seeds per fruit`,
         prop_seed_preyed = `Proportion preyed`)
data_ids_89 <- data_ids_89 %>%
  rename(number = ID, subplot = Subplot, id = Ind, avFD = `Mean (MFD)`,
         skew =  Skew, kurt = Kurtosis,LFD = `Max (LFD)`, FFD = `Min (FFD)`,
         dur = `Range (Duration)`, n_fl = `Flower N`, n_fr = Fruits, 
         fr_init = `Fruit init (fr/fl)`, n_seed = `Total seeds`, 
         n_preyed_seed = `Preyed seeds`, 
         fitness = `Intact seeds (fitness)`,
         imp_seed_preyed = Imputed)
```

# Calculate number of seeds per fruit and proportion of seeds preyed in 1989

```{r}
data_ids_89 <- data_ids_89 %>%
  mutate(n_seed_per_fr = ifelse(n_fr==0, NA, n_seed / n_fr), 
         prop_seed_preyed = ifelse(n_seed==0, NA, n_preyed_seed / n_seed))
```

# Change column types

```{r}
data_ids_87 <- data_ids_87 %>% 
  mutate(imp_seed_preyed = as.factor(imp_seed_preyed))
data_ids_88 <- data_ids_88 %>% 
  mutate(imp_seed_preyed = as.factor(imp_seed_preyed))
data_ids_89 <- data_ids_89 %>% 
  mutate(imp_seed_preyed = as.factor(imp_seed_preyed))
# See if I keep integer values as "double"!
```

# Recalculate moments with individual flower data

## Data prep individual flower data

```{r}
data_id_flowers_87 <- data_id_flowers_87 %>%
  select(RUTA,GENET...2,`New Phenoadj based on intervals`) %>%
  mutate(id = paste(RUTA,GENET...2,sep=":"),
         opening_date = `New Phenoadj based on intervals`) %>%
  rename(subplot = RUTA, number = GENET...2) %>%
  select(-`New Phenoadj based on intervals`)
data_id_flowers_88 <- data_id_flowers_88 %>%
  select(RUTA...1,GENET...2,`New Phenoadj based on intervals`) %>%
  mutate(id = paste(RUTA...1,GENET...2,sep=":"),
         opening_date = `New Phenoadj based on intervals`) %>%
  rename(subplot = RUTA...1, number = GENET...2) %>%
  select(-`New Phenoadj based on intervals`) %>%
  filter(!(subplot==8|subplot==9))
data_id_flowers_89 <- data_id_flowers_89 %>%
  select(RUTA,GENET,`Corrected pheno`) %>%
  mutate(id = paste(RUTA,GENET,sep=":"),
         opening_date = `Corrected pheno`) %>%
  rename(subplot = RUTA, number = GENET) %>%
  select(-`Corrected pheno`)
```

See if the number of individuals in each subplot matches betwen individual data and individual flower data.

```{r}
data_ids_87%>%group_by(subplot)%>%summarise(n_indiv=n())
data_id_flowers_87%>%group_by(subplot)%>%summarise(n_indiv=n_distinct(id))
data_ids_88%>%group_by(subplot)%>%summarise(n_indiv=n())
data_id_flowers_88%>%group_by(subplot)%>%summarise(n_indiv=n_distinct(id))
data_ids_89%>%group_by(subplot)%>%summarise(n_indiv=n())
data_id_flowers_89%>%group_by(subplot)%>%summarise(n_indiv=n_distinct(id))
```

Yes, it matches.

See if the id values match between individual data and individual flower data.

```{r}
unique(anti_join(data_id_flowers_87, data_ids_87, by = "id")$id)
# Show values of id from data_id_flowers_87 that are not in data_ids_87
unique(anti_join(data_id_flowers_88, data_ids_88, by = "id")$id)
# Show values of id from data_id_flowers_88 that are not in data_ids_88
unique(anti_join(data_id_flowers_89, data_ids_89, by = "id")$id)
# Show values of id from data_id_flowers_89 that are not in data_ids_89
```

Yes, they match.

## Recalculate moments

I have recalculated all moments to check that everything matches with Johan's data for individuals (I might remove other moments later and keep only new versions of skewness and kurtosis).

```{r}
moments_87 <- data_id_flowers_87 %>%
  group_by(id) %>%
  summarise(avFD_a=mean(opening_date),FFD_a=min(opening_date),
            MFD_a=median(opening_date), # Calculate also median
            LFD_a=max(opening_date),SD_a=sd(opening_date),
            var_a=var(opening_date), # Calculate also variance
            skew_a=ifelse(n()>2,skewness(opening_date),NA),
            kurt_a=ifelse(n()>2,kurtosis(opening_date),NA),
            # Calculate skewness and kurtosis when n_fl>2
            dur_a=LFD_a-FFD_a) %>%
  mutate(year=as.factor(1987))
moments_88 <- data_id_flowers_88 %>%
  group_by(id) %>%
  summarise(avFD_a=mean(opening_date),FFD_a=min(opening_date),
            MFD_a=median(opening_date), # Calculate also median
            LFD_a=max(opening_date),SD_a=sd(opening_date),
            var_a=var(opening_date), # Calculate also variance
            skew_a=ifelse(n()>2,skewness(opening_date),NA),
            kurt_a=ifelse(n()>2,kurtosis(opening_date),NA),
            # Calculate skewness and kurtosis when n_fl>2
            dur_a=LFD_a-FFD_a) %>%  
  mutate(year=as.factor(1988))
moments_89 <- data_id_flowers_89 %>%
  group_by(id) %>%
  summarise(avFD_a=mean(opening_date),FFD_a=min(opening_date),
            MFD_a=median(opening_date), # Calculate also median
            LFD_a=max(opening_date),SD_a=sd(opening_date),
            var_a=var(opening_date), # Calculate also variance
            skew_a=ifelse(n()>2,skewness(opening_date),NA),
            kurt_a=ifelse(n()>2,kurtosis(opening_date),NA),
            # Calculate skewness and kurtosis when n_fl>2
            dur_a=LFD_a-FFD_a) %>%  
  mutate(year=as.factor(1989))
moments <- full_join(full_join(moments_87,moments_88),moments_89)
```

# Merge Johan's data for individuals for the 3 years

```{r}
data_ids_87 <- data_ids_87 %>%
  mutate(year = as.integer(1987))
data_ids_88 <- data_ids_88 %>%
  mutate(year = as.integer(1988))
data_ids_89 <- data_ids_89 %>%
  mutate(year = as.integer(1989))
data_ids <- full_join(full_join(data_ids_87,data_ids_88),data_ids_89)
data_ids <- data_ids %>% mutate(year = as.factor(year))
```

# Merge with my calculated moments

```{r}
data_ids <- full_join(data_ids, moments)
```

# Compare values of moments between Johan's calculations and mine

In how many ids are my calculations different from Johan's?

```{r}
nrow(data_ids %>% filter(!near(avFD_a,avFD)) %>%
       # Using near() to avoid small differences in decimals
       select(year,number,subplot,id,avFD,avFD_a))
# None after editing data
nrow(data_ids %>% filter(!near(FFD_a,FFD))%>%
       select(year,number,subplot,id,FFD,FFD_a))
# None after editing data
nrow(data_ids %>% filter(!near(LFD_a,LFD))%>%
       select(year,number,subplot,id,LFD,LFD_a))
# None after editing data
nrow(data_ids %>% filter(!near(SD_a,SD))%>%
       select(year,number,subplot,id,SD,SD_a))
# None after editing data
nrow(data_ids %>% filter(!near(skew_a,skew))%>%
       select(year,number,subplot,id,skew,skew_a))
# 415 rows are different
nrow(data_ids %>% filter(!near(kurt_a,kurt))%>%
       select(year,number,subplot,id,kurt,kurt_a))
# 377 rows are different
nrow(data_ids %>% filter(!near(dur_a,dur))%>%
       select(year,number,subplot,id,dur,dur_a))
# None after editing data
```

All moments have the same values except for skewness and kurtosis.

The skewness function that I used (from the moments package) calculates g1, the skewness of a sample based on the third moment of the data divided by the cube root of the second moment of the data, using the formula:

g1=(sum((X - mean(X))^3)/n)/(sum((X - mean(X))^2)/n)^(3/2)

This is the formula for sample skewness, also known as Pearson's moment coefficient of skewness.

Excel uses the adjusted Fisher–Pearson standardized moment coefficient G1:

G1=(sqrt(n()*(n()-1))/(n()-2))*g1

The kurtosis function that I used (from the moments package) calculates Pearson's measure of kurtosis:

n*(sum((X-mean(X))^4))/((sum((X-mean(X))^2)^2))

Excel uses:

((n*(n+1))/((n-1)*(n-2)*(n-3))*sum(((X-mean(X))/sd(X))^4))-((3*((n-1)^2))/((n-2)*(n-3)))


## Plots of skewness and kurtosis

```{r}
ggplot(data_ids,aes(x=skew,y=skew_a))+
  geom_vline(xintercept=0,linetype=2)+geom_hline(yintercept=0,linetype=2)+
  geom_point(shape=20,size=3,alpha=0.25,color="darkred")+
  xlab("Skewness (Excel)")+ylab("Skewness (R)")
```

```{r}
ggplot(data_ids,aes(x=kurt,y=kurt_a))+
  geom_point(shape=20,size=3,alpha=0.25,color="darkred")+
  xlab("Kurtosis (Excel)")+ylab("Kurtosis (R)")
```

```{r}
ggplot(data_ids,aes(x=skew,y=year,fill=year,color=year))+
  my_theme()+
  theme(panel.grid = element_line(color="grey",size=0.1,linetype=3))+
  labs(x="Skewness_Excel",y="Year")+
  geom_density_ridges(alpha=.5,scale=1,quantile_lines=TRUE,
                      quantile_fun=function(x,...)mean(x),size=0.75)
ggplot(data_ids,aes(x=skew_a,y=year,fill=year,color=year))+
  my_theme()+
  theme(panel.grid = element_line(color="grey",size=0.1,linetype=3))+
  labs(x="Skewness_R",y="Year")+
  geom_density_ridges(alpha=.5,scale=1,quantile_lines=TRUE,
                      quantile_fun=function(x,...)mean(x),size=0.75)
ggplot(data_ids,aes(x=kurt,y=year,fill=year,color=year))+
  my_theme()+
  theme(panel.grid = element_line(color="grey",size=0.1,linetype=3))+
  labs(x="Kurtosis_Excel",y="Year")+
  geom_density_ridges(alpha=.4,scale=1,quantile_lines=TRUE,
                      quantile_fun=function(x,...)mean(x),size=0.75)
ggplot(data_ids,aes(x=kurt_a,y=year,fill=year,color=year))+
  my_theme()+
  theme(panel.grid = element_line(color="grey",size=0.1,linetype=3))+
  labs(x="Kurtosis_R",y="Year")+
  geom_density_ridges(alpha=.4,scale=1,quantile_lines=TRUE,
                      quantile_fun=function(x,...)mean(x),size=0.75)
```

So far I will keep only my calculated moments

# Keep only my calculated moments

```{r}
data_ids<-data_ids%>%
  select(number,subplot,id,n_fl,n_fr,fr_init,n_seed,n_preyed_seed,
                 fitness,imp_seed_preyed,n_seed_per_fr,prop_seed_preyed,year,
                 avFD_a,FFD_a,MFD_a,LFD_a,SD_a,var_a,skew_a,kurt_a,dur_a)%>%
  rename_at(vars(ends_with("_a")), ~sub("_a","",.))
```

# Transform dates

The dates are given in terms of four- or five-day intervals after the first recording. Convert them to calendar dates, then to julian dates, and then to number of days after the vernal equinox.

First create a table with information on each date for each year.

```{r}
dates <- tibble(year = as.factor(
  c(rep("1987",10),rep("1988",10),rep("1989",10))),
                date_num = rep(1:10,3), # Date in numeric format given in data
                date_calendar = as.Date(
                  ifelse(year==1987, seq(as.Date("1987-05-18"), 
                                         by = 4, length.out = 10),
                         # 1987: Start 18 May, 4-day intervals
                         ifelse(year==1988, seq(as.Date("1988-05-15"),
                                                by = 5, length.out = 10),
                                # 1988: Start 15 May, 5-day intervals
                                seq(as.Date("1989-05-07"), 
                                    by = 5, length.out = 10))),
                  # 1989: Start 7 May, 5-day intervals
                  # Calendar date
                  origin = "1970-01-01"),
  date_julian = yday(date_calendar), # Julian date
  date_vernal = ifelse(year==1987,date_calendar-as.Date("1987-03-21"),
                       ifelse(year==1988,date_calendar-as.Date("1988-03-20"),
                              date_calendar-as.Date("1989-03-20")))) 
# Days after vernal equinox
# Data on vernal equinox dates from https://data.giss.nasa.gov/ar5/srvernal.html
```

Calculate, for each year, the intercept and slope of the relationship among date_num (x)
and date_vernal or date_calendar (y).

```{r}
dates <- dates %>%
  group_by(year) %>%
  mutate(date_intercept_v = ifelse(year==1987,min(date_vernal)-4,
                                 min(date_vernal)-5),
         date_intercept_c = as.Date(ifelse(year==1987,min(date_calendar)-4,
                                 min(date_calendar)-5),origin = "1970-01-01"),
         date_slope_v = (date_vernal-date_intercept_v)/date_num,
         date_slope_c = (date_calendar-date_intercept_c)/date_num)
dates_summary <- summarise(dates, 
                           date_intercept_v = mean(date_intercept_v),
                           date_intercept_c = mean(date_intercept_c),
                           date_slope_v = mean(date_slope_v),
                           date_slope_c = mean(date_slope_c))
```

Transform avFD, FFD, MFD and LFD to calendar dates (avFFD_c, FFD_c, MFD_c, LFD_c) and to days after vernal equinox (avFFD_v, FFD_v, MFD_v, LFD_v).

```{r}
data_ids <- data_ids %>% 
  left_join(dates_summary, by = c("year" = "year")) %>%
  mutate(avFD_c = date_slope_c * avFD + date_intercept_c,
         FFD_c = date_slope_c * FFD + date_intercept_c,
         MFD_c = date_slope_c * MFD + date_intercept_c,
         LFD_c = date_slope_c * LFD + date_intercept_c,
         avFD_v = date_slope_v * avFD + date_intercept_v,
         FFD_v = date_slope_v * FFD + date_intercept_v,
         MFD_v = date_slope_v * MFD + date_intercept_v,
         LFD_v = date_slope_v * LFD + date_intercept_v)
```

# Standardize traits and relativize fitness within years

```{r}
data_ids<-data_ids%>%
  group_by(year)%>%
  mutate(across(c(n_fl,avFD:dur), scale, .names = "{col}_std"))%>%
  mutate(across(c(n_fl_std:dur_std),as.vector))%>%
  mutate(fitness_rel = fitness / mean(fitness))%>%
  ungroup()
# When standardizing, we get the same result for FFD, MFD and LFD
# than for FFD_v, MFD_v and LFD_v, so I used the first
```

# Join individual flower data for the three years

```{r}
data_id_flowers<-rbind(data_id_flowers_87%>%
                         mutate(year=1987),
                       data_id_flowers_88%>%
                         mutate(year=1988),
                       data_id_flowers_89%>%
                         mutate(year=1989))%>%
  mutate(year=as.factor(year))%>%
  left_join(dates_summary, by = c("year" = "year")) %>%
  mutate(opening_date_c=date_slope_c*opening_date+date_intercept_c,
         opening_date_v=date_slope_v*opening_date+date_intercept_v,
         year=as.factor(year))
```


# Save clean data as .csv

```{r}
write_csv(data_ids,"data/clean/data_ids.csv")
write_csv(data_id_flowers,"data/clean/data_id_flowers.csv")
```

# Session info

```{r}
sessionInfo()
```

