---
title: "Selection on within-individual variation in flowering time in Lathyrus vernus"
subtitle: "Analyses of relationships between phenological traits and fruit initiation and pre-dispersal seed predation, and analyses of phenotypic selection on phenological traits"
author : "Alicia Valdés"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(tibble.width = Inf)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r load packages, include=FALSE}
library(tidyverse)
library(jtools)
library(ggeffects)
library(glmmTMB)
library(DHARMa)
library(RColorBrewer)
library(gridExtra)
library(ggthemes)
library(ggfortify)
```

```{r Define ggplot themes and palettes, include=FALSE}
my_theme <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(legend.position="none")+theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
my_theme_legend <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
myPalette <- colorRampPalette(brewer.pal(11, "YlOrRd"))
```

# Read clean data from .csv file

```{r}
data_ids <- read_csv("data/clean/data_ids.csv")
data_ids$imp_seed_preyed <- as.factor(data_ids$imp_seed_preyed)
data_ids$year <- as.factor(data_ids$year)
```

# FRUIT INITIATION

Using standardized traits and subplot as a random effect. One model per year.

## Average FD

### Models

```{r}
fr_init_avFD_87<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
fr_init_avFD_88<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
fr_init_avFD_89<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
fr_init_avFD_89_glm<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std,
                      subset(data_ids,year==1989),family="binomial")
summary(fr_init_avFD_87)
summary(fr_init_avFD_88)
summary(fr_init_avFD_89) 
# Only 3 subplots in 1989 - Use? Very similar result with a GLM
summary(fr_init_avFD_89_glm)
```

Fruit initiation significantly increases with earlier average FD in the three years.

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_fr_init_avFD_87 <- simulateResiduals(fittedModel = fr_init_avFD_87, n = 5000) 
sim_fr_init_avFD_88 <- simulateResiduals(fittedModel = fr_init_avFD_88, n = 5000) 
sim_fr_init_avFD_89 <- simulateResiduals(fittedModel = fr_init_avFD_89, n = 5000) 
sim_fr_init_avFD_89_glm <- simulateResiduals(fittedModel = fr_init_avFD_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_fr_init_avFD_87,quantreg=T) 
plot(sim_fr_init_avFD_88,quantreg=T)
plot(sim_fr_init_avFD_89,quantreg=T)
plot(sim_fr_init_avFD_89_glm,quantreg=T)
# probably OK 
```

```{r}
testDispersion(sim_fr_init_avFD_87) # OK
testDispersion(sim_fr_init_avFD_88) # OK
testDispersion(sim_fr_init_avFD_89) # OK
testDispersion(sim_fr_init_avFD_89_glm) # OK
```

## FFD

### Models

```{r}
fr_init_FFD_87<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~FFD_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
fr_init_FFD_88<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~FFD_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
fr_init_FFD_89<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~FFD_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
fr_init_FFD_89_glm<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~FFD_std,
                      subset(data_ids,year==1989),family="binomial")
summary(fr_init_FFD_87)
summary(fr_init_FFD_88)
summary(fr_init_FFD_89) 
# Only 3 subplots in 1989 - Use? Very similar result with a GLM
summary(fr_init_FFD_89_glm)
```

Fruit initiation significantly increases with earlier FFD in the three years.

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_fr_init_avFD_87 <- simulateResiduals(fittedModel = fr_init_avFD_87, n = 5000) 
sim_fr_init_avFD_88 <- simulateResiduals(fittedModel = fr_init_avFD_88, n = 5000) 
sim_fr_init_avFD_89 <- simulateResiduals(fittedModel = fr_init_avFD_89, n = 5000) 
sim_fr_init_avFD_89_glm <- simulateResiduals(fittedModel = fr_init_avFD_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_fr_init_avFD_87,quantreg=T) 
plot(sim_fr_init_avFD_88,quantreg=T)
plot(sim_fr_init_avFD_89,quantreg=T)
plot(sim_fr_init_avFD_89_glm,quantreg=T)
# probably OK 
```

```{r}
testDispersion(sim_fr_init_avFD_87) # OK
testDispersion(sim_fr_init_avFD_88) # OK
testDispersion(sim_fr_init_avFD_89) # OK
testDispersion(sim_fr_init_avFD_89_glm) # OK
```

```{r}
testZeroInflation(sim_fr_init_avFD_87) # OK
testZeroInflation(sim_fr_init_avFD_88) # OK
testZeroInflation(sim_fr_init_avFD_89) # OK
testZeroInflation(sim_fr_init_avFD_89_glm) # OK
```

## MFD

### Models

```{r}
fr_init_MFD_87<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~MFD_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
fr_init_MFD_88<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~MFD_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
fr_init_MFD_89<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~MFD_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
fr_init_MFD_89_glm<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~MFD_std,
                      subset(data_ids,year==1989),family="binomial")
summary(fr_init_MFD_87)
summary(fr_init_MFD_88)
summary(fr_init_MFD_89) 
# Only 3 subplots in 1989 - Use? Very similar result with a GLM
summary(fr_init_MFD_89_glm)
```

Fruit initiation significantly increases with earlier MFD in the three years.

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_fr_init_MFD_87 <- simulateResiduals(fittedModel = fr_init_MFD_87, n = 5000) 
sim_fr_init_MFD_88 <- simulateResiduals(fittedModel = fr_init_MFD_88, n = 5000) 
sim_fr_init_MFD_89 <- simulateResiduals(fittedModel = fr_init_MFD_89, n = 5000) 
sim_fr_init_MFD_89_glm <- simulateResiduals(fittedModel = fr_init_MFD_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_fr_init_MFD_87,quantreg=T) 
plot(sim_fr_init_MFD_88,quantreg=T)
plot(sim_fr_init_MFD_89,quantreg=T)
plot(sim_fr_init_MFD_89_glm,quantreg=T)
# probably OK 
```

```{r}
testDispersion(sim_fr_init_MFD_87) # OK
testDispersion(sim_fr_init_MFD_88) # OK
testDispersion(sim_fr_init_MFD_89) # OK
testDispersion(sim_fr_init_MFD_89_glm) # OK
```

## LFD

### Models

```{r}
fr_init_LFD_87<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~LFD_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
fr_init_LFD_88<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~LFD_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
fr_init_LFD_89<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~LFD_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
fr_init_LFD_89_glm<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~LFD_std,
                      subset(data_ids,year==1989),family="binomial")
summary(fr_init_LFD_87)
summary(fr_init_LFD_88)
summary(fr_init_LFD_89) 
# Only 3 subplots in 1989 - Use? Very similar result with a GLM
summary(fr_init_LFD_89_glm)
```

Fruit initiation significantly increases with earlier LFD only in 1988.

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_fr_init_LFD_87 <- simulateResiduals(fittedModel = fr_init_LFD_87, n = 5000) 
sim_fr_init_LFD_88 <- simulateResiduals(fittedModel = fr_init_LFD_88, n = 5000) 
sim_fr_init_LFD_89 <- simulateResiduals(fittedModel = fr_init_LFD_89, n = 5000) 
sim_fr_init_LFD_89_glm <- simulateResiduals(fittedModel = fr_init_LFD_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_fr_init_LFD_87,quantreg=T) 
plot(sim_fr_init_LFD_88,quantreg=T)
plot(sim_fr_init_LFD_89,quantreg=T)
plot(sim_fr_init_LFD_89_glm,quantreg=T)
# probably OK 
```

```{r}
testDispersion(sim_fr_init_LFD_87) # OK
testDispersion(sim_fr_init_LFD_88) # OK
testDispersion(sim_fr_init_LFD_89) # OK
testDispersion(sim_fr_init_LFD_89_glm) # OK
```

## Duration

### Models

```{r}
fr_init_dur_87<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~dur_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
fr_init_dur_88<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~dur_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
fr_init_dur_89<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~dur_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
fr_init_dur_89_glm<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~dur_std,
                      subset(data_ids,year==1989),family="binomial")
summary(fr_init_dur_87)
summary(fr_init_dur_88)
summary(fr_init_dur_89) 
# Only 3 subplots in 1989 - Use? Very similar result with a GLM
summary(fr_init_dur_89_glm)
```

Fruit initiation significantly increases with longer duration of flowering only in 1989.

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_fr_init_dur_87 <- simulateResiduals(fittedModel = fr_init_dur_87, n = 5000) 
sim_fr_init_dur_88 <- simulateResiduals(fittedModel = fr_init_dur_88, n = 5000) 
sim_fr_init_dur_89 <- simulateResiduals(fittedModel = fr_init_dur_89, n = 5000) 
sim_fr_init_dur_89_glm <- simulateResiduals(fittedModel = fr_init_dur_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_fr_init_dur_87,quantreg=T) 
plot(sim_fr_init_dur_88,quantreg=T)
plot(sim_fr_init_dur_89,quantreg=T)
plot(sim_fr_init_dur_89_glm,quantreg=T)
# probably OK 
```

```{r}
testDispersion(sim_fr_init_dur_87) # OK
testDispersion(sim_fr_init_dur_88) # OK
testDispersion(sim_fr_init_dur_89) # OK
testDispersion(sim_fr_init_dur_89_glm) # OK
```

## SD

### Models

```{r}
fr_init_SD_87<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~SD_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
fr_init_SD_88<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~SD_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
fr_init_SD_89<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~SD_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
fr_init_SD_89_glm<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~SD_std,
                      subset(data_ids,year==1989),family="binomial")
summary(fr_init_SD_87)
summary(fr_init_SD_88)
summary(fr_init_SD_89) 
# Only 3 subplots in 1989 - Use? Very similar result with a GLM
summary(fr_init_SD_89_glm)
```

Fruit initiation significantly increases with higher SD of FD only in 1989.

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_fr_init_SD_87 <- simulateResiduals(fittedModel = fr_init_SD_87, n = 5000) 
sim_fr_init_SD_88 <- simulateResiduals(fittedModel = fr_init_SD_88, n = 5000) 
sim_fr_init_SD_89 <- simulateResiduals(fittedModel = fr_init_SD_89, n = 5000) 
sim_fr_init_SD_89_glm <- simulateResiduals(fittedModel = fr_init_SD_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_fr_init_SD_87,quantreg=T) 
plot(sim_fr_init_SD_88,quantreg=T)
plot(sim_fr_init_SD_89,quantreg=T)
plot(sim_fr_init_SD_89_glm,quantreg=T)
# probably OK 
```

```{r}
testDispersion(sim_fr_init_SD_87) # OK
testDispersion(sim_fr_init_SD_88) # OK
testDispersion(sim_fr_init_SD_89) # OK
testDispersion(sim_fr_init_SD_89_glm) # OK
```

## Variance

### Models

```{r}
fr_init_var_87<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
fr_init_var_88<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
fr_init_var_89<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
fr_init_var_89_glm<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std,
                      subset(data_ids,year==1989),family="binomial")
summary(fr_init_var_87)
summary(fr_init_var_88)
summary(fr_init_var_89) 
# Only 3 subplots in 1989 - Use? Very similar result with a GLM
summary(fr_init_var_89_glm)
```

Fruit initiation significantly increases with higher variance of FD in 1987 and 1989.

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_fr_init_var_87 <- simulateResiduals(fittedModel = fr_init_var_87, n = 5000) 
sim_fr_init_var_88 <- simulateResiduals(fittedModel = fr_init_var_88, n = 5000) 
sim_fr_init_var_89 <- simulateResiduals(fittedModel = fr_init_var_89, n = 5000) 
sim_fr_init_var_89_glm <- simulateResiduals(fittedModel = fr_init_var_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_fr_init_var_87,quantreg=T) 
plot(sim_fr_init_var_88,quantreg=T)
plot(sim_fr_init_var_89,quantreg=T)
plot(sim_fr_init_var_89_glm,quantreg=T)
# probably OK 
```

```{r}
testDispersion(sim_fr_init_var_87) # OK
testDispersion(sim_fr_init_var_88) # OK
testDispersion(sim_fr_init_var_89) # OK
testDispersion(sim_fr_init_var_89_glm) # OK
```

## Skewness

### Models

```{r}
fr_init_skew_87<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
fr_init_skew_88<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
fr_init_skew_89<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
fr_init_skew_89_glm<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std,
                      subset(data_ids,year==1989),family="binomial")
summary(fr_init_skew_87)
summary(fr_init_skew_88)
summary(fr_init_skew_89) 
# Only 3 subplots in 1989 - Use? Very similar result with a GLM
summary(fr_init_skew_89_glm)
```

Fruit initiation significantly increases with higher skewness of FD in 1987 and 1989 (meaning that in these years, a higher proportion of flowers developed to fruits when the distribution of flowering dates was positively skewed / right skewed - longer right tail of the distribution).

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_fr_init_skew_87 <- simulateResiduals(fittedModel = fr_init_skew_87, n = 5000) 
sim_fr_init_skew_88 <- simulateResiduals(fittedModel = fr_init_skew_88, n = 5000) 
sim_fr_init_skew_89 <- simulateResiduals(fittedModel = fr_init_skew_89, n = 5000) 
sim_fr_init_skew_89_glm <- simulateResiduals(fittedModel = fr_init_skew_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_fr_init_skew_87,quantreg=T) 
plot(sim_fr_init_skew_88,quantreg=T)
plot(sim_fr_init_skew_89,quantreg=T)
plot(sim_fr_init_skew_89_glm,quantreg=T)
# probably OK 
```

```{r}
testDispersion(sim_fr_init_skew_87) # OK
testDispersion(sim_fr_init_skew_88) # OK
testDispersion(sim_fr_init_skew_89) # OK
testDispersion(sim_fr_init_skew_89_glm) # OK
```

## Kurtosis

### Models

```{r}
fr_init_kurt_87<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
fr_init_kurt_88<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
fr_init_kurt_89<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
fr_init_kurt_89_glm<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std,
                      subset(data_ids,year==1989),family="binomial")
summary(fr_init_kurt_87)
summary(fr_init_kurt_88)
summary(fr_init_kurt_89) 
# Only 3 subplots in 1989 - Use? Very similar result with a GLM
summary(fr_init_kurt_89_glm)
```

Fruit initiation is not significantly related to kurtosis of FD in any of the three years.

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_fr_init_kurt_87 <- simulateResiduals(fittedModel = fr_init_kurt_87, n = 5000) 
sim_fr_init_kurt_88 <- simulateResiduals(fittedModel = fr_init_kurt_88, n = 5000) 
sim_fr_init_kurt_89 <- simulateResiduals(fittedModel = fr_init_kurt_89, n = 5000) 
sim_fr_init_kurt_89_glm <- simulateResiduals(fittedModel = fr_init_kurt_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_fr_init_kurt_87,quantreg=T) 
plot(sim_fr_init_kurt_88,quantreg=T)
plot(sim_fr_init_kurt_89,quantreg=T)
plot(sim_fr_init_kurt_89_glm,quantreg=T)
# probably OK 
```

```{r}
testDispersion(sim_fr_init_kurt_87) # OK
testDispersion(sim_fr_init_kurt_88) # OK
testDispersion(sim_fr_init_kurt_89) # OK
testDispersion(sim_fr_init_kurt_89_glm) # Significant
```

## Plots

Extract predictions from models

```{r}
pred_fr_init_avFD<-rbind(tibble(ggpredict(fr_init_avFD_87,
                                          terms=c("avFD_std [all]")))%>%
                           mutate(year=as.factor(1987)),
                         tibble(ggpredict(fr_init_avFD_88,
                                          terms=c("avFD_std [all]")))%>%
                           mutate(year=as.factor(1988)),
                         tibble(ggpredict(fr_init_avFD_89,
                                          terms=c("avFD_std [all]")))%>%
                           mutate(year=as.factor(1989)))
pred_fr_init_FFD<-rbind(tibble(ggpredict(fr_init_FFD_87,
                                         terms=c("FFD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(fr_init_FFD_88,
                                         terms=c("FFD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(fr_init_FFD_89,
                                         terms=c("FFD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_fr_init_MFD<-rbind(tibble(ggpredict(fr_init_MFD_87,
                                         terms=c("MFD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(fr_init_MFD_88,
                                         terms=c("MFD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(fr_init_MFD_89,
                                         terms=c("MFD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_fr_init_LFD<-rbind(tibble(ggpredict(fr_init_LFD_87,
                                         terms=c("LFD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(fr_init_LFD_88,
                                         terms=c("LFD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(fr_init_LFD_89,
                                         terms=c("LFD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_fr_init_dur<-rbind(tibble(ggpredict(fr_init_dur_87,
                                         terms=c("dur_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(fr_init_dur_88,
                                         terms=c("dur_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(fr_init_dur_89,
                                         terms=c("dur_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_fr_init_SD<-rbind(tibble(ggpredict(fr_init_SD_87,
                                         terms=c("SD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(fr_init_SD_88,
                                         terms=c("SD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(fr_init_SD_89,
                                         terms=c("SD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_fr_init_var<-rbind(tibble(ggpredict(fr_init_var_87,
                                         terms=c("var_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(fr_init_var_88,
                                         terms=c("var_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(fr_init_var_89,
                                         terms=c("var_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_fr_init_skew<-rbind(tibble(ggpredict(fr_init_skew_87,
                                         terms=c("skew_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(fr_init_skew_88,
                                         terms=c("skew_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(fr_init_skew_89,
                                         terms=c("skew_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_fr_init_kurt<-rbind(tibble(ggpredict(fr_init_kurt_87,
                                         terms=c("kurt_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(fr_init_kurt_88,
                                         terms=c("kurt_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(fr_init_kurt_89,
                                         terms=c("kurt_std [all]")))%>%
                          mutate(year=as.factor(1989)))
```

### Average FD, FFD, MFD, LFD

```{r fig.height=9, fig.width=6}
fr_init_1<-grid.arrange(
  # Average FD
  ggplot(data_ids,aes(x=avFD_std,y=fr_init))+geom_point(size=2,alpha=0.3)+
    geom_ribbon(data=pred_fr_init_avFD,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_fr_init_avFD,aes(x,predicted),linewidth=1,color="red")+
    facet_wrap(~year)+
    my_theme()+xlab("Average FD (standardized)")+ylab("Fruit initiation"),
  # FFD
  ggplot(data_ids,aes(x=FFD_std,y=fr_init))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_fr_init_FFD,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_fr_init_FFD,aes(x,predicted),linewidth=1,color="red")+
    facet_wrap(~year)+
    my_theme()+xlab("FFD (standardized)")+ylab("Fruit initiation"),
  # MFD
  ggplot(data_ids,aes(x=MFD_std,y=fr_init))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_fr_init_MFD,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_fr_init_MFD,aes(x,predicted),linewidth=1,color="red")+
    facet_wrap(~year)+
    my_theme()+xlab("MFD (standardized)")+ylab("Fruit initiation"),
  # LFD
  ggplot(data_ids,aes(x=LFD_std,y=fr_init))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_fr_init_LFD,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_fr_init_LFD,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("black","red","black"))+
    facet_wrap(~year)+
    my_theme()+xlab("LFD (standardized)")+ylab("Fruit initiation"),
  ncol=1)
ggsave(filename="output/figures/fr_init_1.tiff",plot=fr_init_1,
       width=20,height=25,units="cm",dpi=300)
```

### Duration, SD, variance

```{r fig.height=7, fig.width=6}
fr_init_2<-grid.arrange(
  # Duration
  ggplot(data_ids,aes(x=dur_std,y=fr_init))+geom_point(size=2,alpha=0.3)+
    geom_ribbon(data=pred_fr_init_dur,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_fr_init_dur,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("black","black","red"))+
    facet_wrap(~year)+
    my_theme()+
    xlab("Duration of flowering (standardized)")+ylab("Fruit initiation"),
  # SD
  ggplot(data_ids,aes(x=SD_std,y=fr_init))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_fr_init_SD,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_fr_init_SD,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("black","black","red"))+
    facet_wrap(~year)+
    my_theme()+xlab("SD of FD (standardized)")+ylab("Fruit initiation"),
  # Variance
  ggplot(data_ids,aes(x=var_std,y=fr_init))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_fr_init_var,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_fr_init_var,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("red","black","red"))+
    facet_wrap(~year)+
    my_theme()+xlab("Variance of FD (standardized)")+ylab("Fruit initiation"),
  ncol=1)
ggsave(filename="output/figures/fr_init_2.tiff",plot=fr_init_2,
       width=20,height=25,units="cm",dpi=300)
```

### Skewness, kurtosis

```{r fig.height=5, fig.width=6}
fr_init_3<-grid.arrange(
  # Skewness
  ggplot(data_ids,aes(x=skew_std,y=fr_init))+geom_point(size=2,alpha=0.3)+
    geom_ribbon(data=pred_fr_init_skew,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_fr_init_skew,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("red","black","red"))+
    facet_wrap(~year)+
    my_theme()+
    xlab("Skewness of FD (standardized)")+ylab("Fruit initiation"),
  # Kurtosis
  ggplot(data_ids,aes(x=kurt_std,y=fr_init))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_fr_init_kurt,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_fr_init_kurt,aes(x,predicted),linewidth=1)+
    facet_wrap(~year)+
    my_theme()+xlab("Kurtosis of FD (standardized)")+ylab("Fruit initiation"),
  ncol=1)
ggsave(filename="output/figures/fr_init_3.tiff",plot=fr_init_3,
       width=20,height=20,units="cm",dpi=300)
```

# PRE-DISPERSAL SEED PREDATION

Using standardized traits and subplot as a random effect. One model per year.

## Average FD

### Models

```{r}
seed_pred_avFD_87<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~avFD_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
seed_pred_avFD_88<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~avFD_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
seed_pred_avFD_89<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~avFD_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
seed_pred_avFD_89_glm<-glm(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~avFD_std,
                      subset(data_ids,year==1989),family="binomial")
summary(seed_pred_avFD_87)
summary(seed_pred_avFD_88)
summary(seed_pred_avFD_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(seed_pred_avFD_89_glm)
```

Seed predation significantly increases with earlier average FD in 1988.

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_seed_pred_avFD_87 <- simulateResiduals(fittedModel = seed_pred_avFD_87, n = 5000)
sim_seed_pred_avFD_88 <- simulateResiduals(fittedModel = seed_pred_avFD_88, n = 5000)
sim_seed_pred_avFD_89 <- simulateResiduals(fittedModel = seed_pred_avFD_89, n = 5000)
#sim_seed_pred_avFD_89_glm <- simulateResiduals(fittedModel = seed_pred_avFD_89_glm, n = 5000)
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_seed_pred_avFD_87,quantreg=T) 
plot(sim_seed_pred_avFD_88,quantreg=T)
plot(sim_seed_pred_avFD_89,quantreg=T)
#plot(sim_seed_pred_avFD_89_glm,quantreg=T)
# Problems?
```

```{r}
testDispersion(sim_seed_pred_avFD_87) # OK
testDispersion(sim_seed_pred_avFD_88) # OK
testDispersion(sim_seed_pred_avFD_89) # OK
#testDispersion(sim_seed_pred_avFD_89_glm) # OK
```

## FFD

### Models

```{r}
seed_pred_FFD_87<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~FFD_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
seed_pred_FFD_88<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~FFD_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
seed_pred_FFD_89<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~FFD_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
seed_pred_FFD_89_glm<-glm(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~FFD_std,
                      subset(data_ids,year==1989),family="binomial")
summary(seed_pred_FFD_87)
summary(seed_pred_FFD_88)
summary(seed_pred_FFD_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(seed_pred_FFD_89_glm)
```

Seed predation significantly increases with earlier FFD in 1988.

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_seed_pred_FFD_87 <- simulateResiduals(fittedModel = seed_pred_FFD_87, n = 5000) 
sim_seed_pred_FFD_88 <- simulateResiduals(fittedModel = seed_pred_FFD_88, n = 5000) 
sim_seed_pred_FFD_89 <- simulateResiduals(fittedModel = seed_pred_FFD_89, n = 5000) 
#sim_seed_pred_FFD_89_glm <- simulateResiduals(fittedModel = seed_pred_FFD_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_seed_pred_FFD_87,quantreg=T) 
plot(sim_seed_pred_FFD_88,quantreg=T)
plot(sim_seed_pred_FFD_89,quantreg=T)
#plot(sim_seed_pred_FFD_89_glm,quantreg=T)
# Problems?
```

```{r}
testDispersion(sim_seed_pred_FFD_87) # OK
testDispersion(sim_seed_pred_FFD_88) # OK
testDispersion(sim_seed_pred_FFD_89) # OK
#testDispersion(sim_seed_pred_FFD_89_glm) # OK
```

## MFD

### Models

```{r}
seed_pred_MFD_87<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~MFD_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
seed_pred_MFD_88<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~MFD_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
seed_pred_MFD_89<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~MFD_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
seed_pred_MFD_89_glm<-glm(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~MFD_std,
                      subset(data_ids,year==1989),family="binomial")
summary(seed_pred_MFD_87)
summary(seed_pred_MFD_88)
summary(seed_pred_MFD_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(seed_pred_MFD_89_glm)
```

Seed predation significantly increases with earlier MFD in 1988.

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_seed_pred_MFD_87 <- simulateResiduals(fittedModel = seed_pred_MFD_87, n = 5000) 
sim_seed_pred_MFD_88 <- simulateResiduals(fittedModel = seed_pred_MFD_88, n = 5000) 
sim_seed_pred_MFD_89 <- simulateResiduals(fittedModel = seed_pred_MFD_89, n = 5000) 
#im_seed_pred_MFD_89_glm <- simulateResiduals(fittedModel = seed_pred_MFD_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_seed_pred_MFD_87,quantreg=T) 
plot(sim_seed_pred_MFD_88,quantreg=T)
plot(sim_seed_pred_MFD_89,quantreg=T)
#plot(sim_seed_pred_MFD_89_glm,quantreg=T)
# Problems?
```

```{r}
testDispersion(sim_seed_pred_MFD_87) # OK
testDispersion(sim_seed_pred_MFD_88) # OK
testDispersion(sim_seed_pred_MFD_89) # OK
#testDispersion(sim_seed_pred_MFD_89_glm) # OK
```

## LFD

### Models

```{r}
seed_pred_LFD_87<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~LFD_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
seed_pred_LFD_88<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~LFD_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
seed_pred_LFD_89<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~LFD_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
seed_pred_LFD_89_glm<-glm(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~LFD_std,
                      subset(data_ids,year==1989),family="binomial")
summary(seed_pred_LFD_87)
summary(seed_pred_LFD_88)
summary(seed_pred_LFD_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(seed_pred_LFD_89_glm)
```

Seed predation significantly increases with later LFD in 1987.

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_seed_pred_LFD_87 <- simulateResiduals(fittedModel = seed_pred_LFD_87, n = 5000) 
sim_seed_pred_LFD_88 <- simulateResiduals(fittedModel = seed_pred_LFD_88, n = 5000) 
sim_seed_pred_LFD_89 <- simulateResiduals(fittedModel = seed_pred_LFD_89, n = 5000) 
#sim_seed_pred_LFD_89_glm <- simulateResiduals(fittedModel = seed_pred_LFD_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_seed_pred_LFD_87,quantreg=T) 
plot(sim_seed_pred_LFD_88,quantreg=T)
plot(sim_seed_pred_LFD_89,quantreg=T)
#plot(sim_seed_pred_LFD_89_glm,quantreg=T)
# Problems?
```

```{r}
testDispersion(sim_seed_pred_LFD_87) # OK
testDispersion(sim_seed_pred_LFD_88) # OK
testDispersion(sim_seed_pred_LFD_89) # OK
#testDispersion(sim_seed_pred_LFD_89_glm) # OK
```

## Duration

### Models

```{r}
seed_pred_dur_87<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~dur_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
seed_pred_dur_88<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~dur_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
seed_pred_dur_89<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~dur_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
seed_pred_dur_89_glm<-glm(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~dur_std,
                      subset(data_ids,year==1989),family="binomial")
summary(seed_pred_dur_87)
summary(seed_pred_dur_88)
summary(seed_pred_dur_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(seed_pred_dur_89_glm)
```

Seed predation significantly increases with longer duration of flowering in 1987 and 1988.

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_seed_pred_dur_87 <- simulateResiduals(fittedModel = seed_pred_dur_87, n = 5000) 
sim_seed_pred_dur_88 <- simulateResiduals(fittedModel = seed_pred_dur_88, n = 5000) 
sim_seed_pred_dur_89 <- simulateResiduals(fittedModel = seed_pred_dur_89, n = 5000) 
#sim_seed_pred_dur_89_glm <- simulateResiduals(fittedModel = seed_pred_dur_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_seed_pred_dur_87,quantreg=T) 
plot(sim_seed_pred_dur_88,quantreg=T)
plot(sim_seed_pred_dur_89,quantreg=T)
#plot(sim_seed_pred_dur_89_glm,quantreg=T)
# Problems?
```

```{r}
testDispersion(sim_seed_pred_dur_87) # OK
testDispersion(sim_seed_pred_dur_88) # OK
testDispersion(sim_seed_pred_dur_89) # OK
#testDispersion(sim_seed_pred_dur_89_glm) # OK
```

## SD

### Models

```{r}
seed_pred_SD_87<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~SD_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
seed_pred_SD_88<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~SD_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
seed_pred_SD_89<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~SD_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
seed_pred_SD_89_glm<-glm(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~SD_std,
                      subset(data_ids,year==1989),family="binomial")
summary(seed_pred_SD_87)
summary(seed_pred_SD_88)
summary(seed_pred_SD_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(seed_pred_SD_89_glm)
```

Seed predation significantly increases with SD of FD in 1987 and 1988.

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_seed_pred_SD_87 <- simulateResiduals(fittedModel = seed_pred_SD_87, n = 5000) 
sim_seed_pred_SD_88 <- simulateResiduals(fittedModel = seed_pred_SD_88, n = 5000) 
sim_seed_pred_SD_89 <- simulateResiduals(fittedModel = seed_pred_SD_89, n = 5000) 
#sim_seed_pred_SD_89_glm <- simulateResiduals(fittedModel = seed_pred_SD_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_seed_pred_SD_87,quantreg=T) 
plot(sim_seed_pred_SD_88,quantreg=T)
plot(sim_seed_pred_SD_89,quantreg=T)
#plot(sim_seed_pred_SD_89_glm,quantreg=T)
# Problems?
```

```{r}
testDispersion(sim_seed_pred_SD_87) # OK
testDispersion(sim_seed_pred_SD_88) # OK
testDispersion(sim_seed_pred_SD_89) # OK
#testDispersion(sim_seed_pred_SD_89_glm) # OK
```

## Variance

### Models

```{r}
seed_pred_var_87<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~var_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
seed_pred_var_88<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~var_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
seed_pred_var_89<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~var_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
seed_pred_var_89_glm<-glm(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~var_std,
                      subset(data_ids,year==1989),family="binomial")
summary(seed_pred_var_87)
summary(seed_pred_var_88)
summary(seed_pred_var_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(seed_pred_var_89_glm)
```

Seed predation significantly increases with variance of FD in 1988.

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_seed_pred_var_87 <- simulateResiduals(fittedModel = seed_pred_var_87, n = 5000) 
sim_seed_pred_var_88 <- simulateResiduals(fittedModel = seed_pred_var_88, n = 5000) 
sim_seed_pred_var_89 <- simulateResiduals(fittedModel = seed_pred_var_89, n = 5000) 
#sim_seed_pred_var_89_glm <- simulateResiduals(fittedModel = seed_pred_var_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_seed_pred_var_87,quantreg=T) 
plot(sim_seed_pred_var_88,quantreg=T)
plot(sim_seed_pred_var_89,quantreg=T)
#plot(sim_seed_pred_var_89_glm,quantreg=T)
# Problems?
```

```{r}
testDispersion(sim_seed_pred_var_87) # OK
testDispersion(sim_seed_pred_var_88) # OK
testDispersion(sim_seed_pred_var_89) # OK
#testDispersion(sim_seed_pred_var_89_glm) # OK
```

## Skewness

### Models

```{r}
seed_pred_skew_87<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~skew_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
seed_pred_skew_88<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~skew_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
seed_pred_skew_89<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~skew_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
seed_pred_skew_89_glm<-glm(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~skew_std,
                      subset(data_ids,year==1989),family="binomial")
summary(seed_pred_skew_87)
summary(seed_pred_skew_88)
summary(seed_pred_skew_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(seed_pred_skew_89_glm)
```

Seed predation significantly decreases with higher skewness of FD in 1989 (meaning that in this year, a lower proportion of seeds were predated when the distribution of flowering dates was positively skewed / right skewed - longer right tail of the distribution).

So higher skewness increases fruit initiation and reduces seed predation in this year - potential for selection for higher skewness?

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_seed_pred_skew_87 <- simulateResiduals(fittedModel = seed_pred_skew_87, n = 5000) 
sim_seed_pred_skew_88 <- simulateResiduals(fittedModel = seed_pred_skew_88, n = 5000) 
sim_seed_pred_skew_89 <- simulateResiduals(fittedModel = seed_pred_skew_89, n = 5000) 
#sim_seed_pred_skew_89_glm <- simulateResiduals(fittedModel = seed_pred_skew_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_seed_pred_skew_87,quantreg=T) 
plot(sim_seed_pred_skew_88,quantreg=T)
plot(sim_seed_pred_skew_89,quantreg=T)
#plot(sim_seed_pred_skew_89_glm,quantreg=T)
# Problems?
```

```{r}
testDispersion(sim_seed_pred_skew_87) # OK
testDispersion(sim_seed_pred_skew_88) # OK
testDispersion(sim_seed_pred_skew_89) # OK
#testDispersion(sim_seed_pred_skew_89_glm) # OK
```

## Kurtosis

### Models

```{r}
seed_pred_kurt_87<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~kurt_std+(1|subplot),
                      subset(data_ids,year==1987),family="binomial")
seed_pred_kurt_88<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~kurt_std+(1|subplot),
                      subset(data_ids,year==1988),family="binomial")
seed_pred_kurt_89<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~kurt_std+(1|subplot),
                      subset(data_ids,year==1989),family="binomial")
seed_pred_kurt_89_glm<-glm(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~kurt_std,
                      subset(data_ids,year==1989),family="binomial")
summary(seed_pred_kurt_87)
summary(seed_pred_kurt_88)
summary(seed_pred_kurt_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(seed_pred_kurt_89_glm)
```

Seed predation significantly increases with higher kurtosis of FD in 1987 (meaning that in this year, a higher proportion of seeds were predated when the distribution of flowering dates was more leptokurtic).

### Model diagnostics

Simulate residuals of the model:

```{r message=FALSE, warning=FALSE}
sim_seed_pred_kurt_87 <- simulateResiduals(fittedModel = seed_pred_kurt_87, n = 5000) 
sim_seed_pred_kurt_88 <- simulateResiduals(fittedModel = seed_pred_kurt_88, n = 5000) 
sim_seed_pred_kurt_89 <- simulateResiduals(fittedModel = seed_pred_kurt_89, n = 5000) 
#sim_seed_pred_kurt_89_glm <- simulateResiduals(fittedModel = seed_pred_kurt_89_glm, n = 5000) 
```

qq-plot  and plot of residuals vs. predicted:

```{r}
plot(sim_seed_pred_kurt_87,quantreg=T) 
plot(sim_seed_pred_kurt_88,quantreg=T)
plot(sim_seed_pred_kurt_89,quantreg=T)
#plot(sim_seed_pred_kurt_89_glm,quantreg=T)
# Problems?
```

```{r}
testDispersion(sim_seed_pred_kurt_87) # OK
testDispersion(sim_seed_pred_kurt_88) # OK
testDispersion(sim_seed_pred_kurt_89) # OK
#testDispersion(sim_seed_pred_kurt_89_glm) # OK
```

## Plots

Extract predictions from models

```{r}
pred_seed_pred_avFD<-rbind(tibble(ggpredict(seed_pred_avFD_87,
                                          terms=c("avFD_std [all]")))%>%
                           mutate(year=as.factor(1987)),
                         tibble(ggpredict(seed_pred_avFD_88,
                                          terms=c("avFD_std [all]")))%>%
                           mutate(year=as.factor(1988)),
                         tibble(ggpredict(seed_pred_avFD_89,
                                          terms=c("avFD_std [all]")))%>%
                           mutate(year=as.factor(1989)))
pred_seed_pred_FFD<-rbind(tibble(ggpredict(seed_pred_FFD_87,
                                         terms=c("FFD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(seed_pred_FFD_88,
                                         terms=c("FFD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(seed_pred_FFD_89,
                                         terms=c("FFD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_seed_pred_MFD<-rbind(tibble(ggpredict(seed_pred_MFD_87,
                                         terms=c("MFD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(seed_pred_MFD_88,
                                         terms=c("MFD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(seed_pred_MFD_89,
                                         terms=c("MFD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_seed_pred_LFD<-rbind(tibble(ggpredict(seed_pred_LFD_87,
                                         terms=c("LFD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(seed_pred_LFD_88,
                                         terms=c("LFD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(seed_pred_LFD_89,
                                         terms=c("LFD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_seed_pred_dur<-rbind(tibble(ggpredict(seed_pred_dur_87,
                                         terms=c("dur_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(seed_pred_dur_88,
                                         terms=c("dur_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(seed_pred_dur_89,
                                         terms=c("dur_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_seed_pred_SD<-rbind(tibble(ggpredict(seed_pred_SD_87,
                                         terms=c("SD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(seed_pred_SD_88,
                                         terms=c("SD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(seed_pred_SD_89,
                                         terms=c("SD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_seed_pred_var<-rbind(tibble(ggpredict(seed_pred_var_87,
                                         terms=c("var_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(seed_pred_var_88,
                                         terms=c("var_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(seed_pred_var_89,
                                         terms=c("var_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_seed_pred_skew<-rbind(tibble(ggpredict(seed_pred_skew_87,
                                         terms=c("skew_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(seed_pred_skew_88,
                                         terms=c("skew_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(seed_pred_skew_89,
                                         terms=c("skew_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_seed_pred_kurt<-rbind(tibble(ggpredict(seed_pred_kurt_87,
                                         terms=c("kurt_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(seed_pred_kurt_88,
                                         terms=c("kurt_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(seed_pred_kurt_89,
                                         terms=c("kurt_std [all]")))%>%
                          mutate(year=as.factor(1989)))
```

### Average FD, FFD, MFD, LFD

```{r fig.height=9, fig.width=6}
seed_pred_1<-grid.arrange(
  # Average FD
  ggplot(data_ids,aes(x=avFD_std,y=prop_seed_preyed))+geom_point(size=2,alpha=0.3)+
    geom_ribbon(data=pred_seed_pred_avFD,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_seed_pred_avFD,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("black","red","black"))+
    facet_wrap(~year)+
    my_theme()+xlab("Average FD (standardized)")+ylab("Seed predation"),
  # FFD
  ggplot(data_ids,aes(x=FFD_std,y=prop_seed_preyed))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_seed_pred_FFD,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_seed_pred_FFD,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("black","red","black"))+
    facet_wrap(~year)+
    my_theme()+xlab("FFD (standardized)")+ylab("Seed predation"),
  # MFD
  ggplot(data_ids,aes(x=MFD_std,y=prop_seed_preyed))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_seed_pred_MFD,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_seed_pred_MFD,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("black","red","black"))+
    facet_wrap(~year)+
    my_theme()+xlab("MFD (standardized)")+ylab("Seed predation"),
  # LFD
  ggplot(data_ids,aes(x=LFD_std,y=prop_seed_preyed))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_seed_pred_LFD,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_seed_pred_LFD,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("red","black","black"))+
    facet_wrap(~year)+
    my_theme()+xlab("LFD (standardized)")+ylab("Seed predation"),
  ncol=1)
ggsave(filename="output/figures/seed_pred_1.tiff",plot=seed_pred_1,
       width=20,height=25,units="cm",dpi=300)
```

### Duration, SD, variance

```{r fig.height=7, fig.width=6}
seed_pred_2<-grid.arrange(
  # Duration
  ggplot(data_ids,aes(x=dur_std,y=prop_seed_preyed))+geom_point(size=2,alpha=0.3)+
    geom_ribbon(data=pred_seed_pred_dur,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_seed_pred_dur,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("red","red","black"))+
    facet_wrap(~year)+
    my_theme()+
    xlab("Duration of flowering (standardized)")+ylab("Seed predation"),
  # SD
  ggplot(data_ids,aes(x=SD_std,y=prop_seed_preyed))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_seed_pred_SD,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_seed_pred_SD,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("red","red","black"))+
    facet_wrap(~year)+
    my_theme()+xlab("SD of FD (standardized)")+ylab("Seed predation"),
  # Variance
  ggplot(data_ids,aes(x=var_std,y=prop_seed_preyed))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_seed_pred_var,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_seed_pred_var,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("black","red","black"))+
    facet_wrap(~year)+
    my_theme()+xlab("Variance of FD (standardized)")+ylab("Seed predation"),
  ncol=1)
ggsave(filename="output/figures/seed_pred_2.tiff",plot=seed_pred_2,
       width=20,height=25,units="cm",dpi=300)
```

### Skewness, kurtosis

```{r fig.height=5, fig.width=6}
seed_pred_3<-grid.arrange(
  # Skewness
  ggplot(data_ids,aes(x=skew_std,y=prop_seed_preyed))+geom_point(size=2,alpha=0.3)+
    geom_ribbon(data=pred_seed_pred_skew,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_seed_pred_skew,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("black","black","red"))+
    facet_wrap(~year)+
    my_theme()+
    xlab("Skewness of FD (standardized)")+ylab("Seed predation"),
  # Kurtosis
  ggplot(data_ids,aes(x=kurt_std,y=prop_seed_preyed))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_seed_pred_kurt,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_seed_pred_kurt,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("red","black","black"))+
    facet_wrap(~year)+
    my_theme()+xlab("Kurtosis of FD (standardized)")+ylab("Seed predation"),
  ncol=1)
ggsave(filename="output/figures/seed_pred_3.tiff",plot=seed_pred_3,
       width=20,height=20,units="cm",dpi=300)
```

# PHENOTYPIC SELECTION

## Average FD

### Without n_fl

```{r}
sel_avFD_87<-glmmTMB(fitness_rel~avFD_std+(1|subplot),
                     subset(data_ids,year==1987))
sel_avFD_88<-glmmTMB(fitness_rel~avFD_std+(1|subplot),
                     subset(data_ids,year==1988))
sel_avFD_89<-glmmTMB(fitness_rel~avFD_std+(1|subplot),
                     subset(data_ids,year==1989))
sel_avFD_89_glm<-lm(fitness_rel~avFD_std,subset(data_ids,year==1989))
summary(sel_avFD_87)
summary(sel_avFD_88)
summary(sel_avFD_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_avFD_89_glm)
```

Selection for earlier average FD in 1987 and 1989.

#### BCA intervals

### With n_fl

```{r}
sel_avFD_87_nfl<-glmmTMB(fitness_rel~avFD_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1987))
sel_avFD_88_nfl<-glmmTMB(fitness_rel~avFD_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1988))
sel_avFD_89_nfl<-glmmTMB(fitness_rel~avFD_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1989))
sel_avFD_89_glm_nfl<-lm(fitness_rel~avFD_std+n_fl_std,
                        subset(data_ids,year==1989))
summary(sel_avFD_87_nfl)
summary(sel_avFD_88_nfl)
summary(sel_avFD_89_nfl) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_avFD_89_glm_nfl)
```

Selection for earlier average FD in 1987.

#### BCA intervals

## FFD

### Without n_fl

```{r}
sel_FFD_87<-glmmTMB(fitness_rel~FFD_std+(1|subplot),
                     subset(data_ids,year==1987))
sel_FFD_88<-glmmTMB(fitness_rel~FFD_std+(1|subplot),
                     subset(data_ids,year==1988))
sel_FFD_89<-glmmTMB(fitness_rel~FFD_std+(1|subplot),
                     subset(data_ids,year==1989))
sel_FFD_89_glm<-lm(fitness_rel~FFD_std,subset(data_ids,year==1989))
summary(sel_FFD_87)
summary(sel_FFD_88)
summary(sel_FFD_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_FFD_89_glm)
```

Selection for earlier FFD in all three years.

#### BCA intervals

### With n_fl

```{r}
sel_FFD_87_nfl<-glmmTMB(fitness_rel~FFD_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1987))
sel_FFD_88_nfl<-glmmTMB(fitness_rel~FFD_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1988))
sel_FFD_89_nfl<-glmmTMB(fitness_rel~FFD_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1989))
sel_FFD_89_glm_nfl<-lm(fitness_rel~FFD_std+n_fl_std,
                        subset(data_ids,year==1989))
summary(sel_FFD_87_nfl)
summary(sel_FFD_88_nfl)
summary(sel_FFD_89_nfl) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_FFD_89_glm_nfl)
```

Selection for earlier FFD in 1987.

#### BCA intervals

## MFD

### Without n_fl

```{r}
sel_MFD_87<-glmmTMB(fitness_rel~MFD_std+(1|subplot),
                     subset(data_ids,year==1987))
sel_MFD_88<-glmmTMB(fitness_rel~MFD_std+(1|subplot),
                     subset(data_ids,year==1988))
sel_MFD_89<-glmmTMB(fitness_rel~MFD_std+(1|subplot),
                     subset(data_ids,year==1989))
sel_MFD_89_glm<-lm(fitness_rel~MFD_std,subset(data_ids,year==1989))
summary(sel_MFD_87)
summary(sel_MFD_88)
summary(sel_MFD_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_MFD_89_glm)
```

Selection for earlier MFD in 1987 and 1989.

#### BCA intervals

### With n_fl

```{r}
sel_MFD_87_nfl<-glmmTMB(fitness_rel~MFD_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1987))
sel_MFD_88_nfl<-glmmTMB(fitness_rel~MFD_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1988))
sel_MFD_89_nfl<-glmmTMB(fitness_rel~MFD_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1989))
sel_MFD_89_glm_nfl<-lm(fitness_rel~MFD_std+n_fl_std,
                        subset(data_ids,year==1989))
summary(sel_MFD_87_nfl)
summary(sel_MFD_88_nfl)
summary(sel_MFD_89_nfl) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_MFD_89_glm_nfl)
```

Selection for earlier MFD in 1987.

#### BCA intervals

## LFD

### Without n_fl

```{r}
sel_LFD_87<-glmmTMB(fitness_rel~LFD_std+(1|subplot),
                     subset(data_ids,year==1987))
sel_LFD_88<-glmmTMB(fitness_rel~LFD_std+(1|subplot),
                     subset(data_ids,year==1988))
sel_LFD_89<-glmmTMB(fitness_rel~LFD_std+(1|subplot),
                     subset(data_ids,year==1989))
sel_LFD_89_glm<-lm(fitness_rel~LFD_std,subset(data_ids,year==1989))
summary(sel_LFD_87)
summary(sel_LFD_88)
summary(sel_LFD_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_LFD_89_glm)
```

Selection for later LFD in 1989.

#### BCA intervals

### With n_fl

```{r}
sel_LFD_87_nfl<-glmmTMB(fitness_rel~LFD_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1987))
sel_LFD_88_nfl<-glmmTMB(fitness_rel~LFD_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1988))
sel_LFD_89_nfl<-glmmTMB(fitness_rel~LFD_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1989))
sel_LFD_89_glm_nfl<-lm(fitness_rel~LFD_std+n_fl_std,
                        subset(data_ids,year==1989))
summary(sel_LFD_87_nfl)
summary(sel_LFD_88_nfl)
summary(sel_LFD_89_nfl) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_LFD_89_glm_nfl)
```

No selection for LFD in any of the three years.

#### BCA intervals

## Duration

### Without n_fl

```{r}
sel_dur_87<-glmmTMB(fitness_rel~dur_std+(1|subplot),
                     subset(data_ids,year==1987))
sel_dur_88<-glmmTMB(fitness_rel~dur_std+(1|subplot),
                     subset(data_ids,year==1988))
sel_dur_89<-glmmTMB(fitness_rel~dur_std+(1|subplot),
                     subset(data_ids,year==1989))
sel_dur_89_glm<-lm(fitness_rel~dur_std,subset(data_ids,year==1989))
summary(sel_dur_87)
summary(sel_dur_88)
summary(sel_dur_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_dur_89_glm)
```

Selection for longer duration of flowering in all three years.

#### BCA intervals

### With n_fl

```{r}
sel_dur_87_nfl<-glmmTMB(fitness_rel~dur_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1987))
sel_dur_88_nfl<-glmmTMB(fitness_rel~dur_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1988))
sel_dur_89_nfl<-glmmTMB(fitness_rel~dur_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1989))
sel_dur_89_glm_nfl<-lm(fitness_rel~dur_std+n_fl_std,
                        subset(data_ids,year==1989))
summary(sel_dur_87_nfl)
summary(sel_dur_88_nfl)
summary(sel_dur_89_nfl) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_dur_89_glm_nfl)
```

Selection for longer duration of flowering in 1987.

#### BCA intervals

## SD

### Without n_fl

```{r}
sel_SD_87<-glmmTMB(fitness_rel~SD_std+(1|subplot),
                     subset(data_ids,year==1987))
sel_SD_88<-glmmTMB(fitness_rel~SD_std+(1|subplot),
                     subset(data_ids,year==1988))
sel_SD_89<-glmmTMB(fitness_rel~SD_std+(1|subplot),
                     subset(data_ids,year==1989))
sel_SD_89_glm<-lm(fitness_rel~SD_std,subset(data_ids,year==1989))
summary(sel_SD_87)
summary(sel_SD_88)
summary(sel_SD_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_SD_89_glm)
```

Selection for higher SD of flowering in all three years.

#### BCA intervals

### With n_fl

```{r}
sel_SD_87_nfl<-glmmTMB(fitness_rel~SD_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1987))
sel_SD_88_nfl<-glmmTMB(fitness_rel~SD_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1988))
sel_SD_89_nfl<-glmmTMB(fitness_rel~SD_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1989))
sel_SD_89_glm_nfl<-lm(fitness_rel~SD_std+n_fl_std,
                        subset(data_ids,year==1989))
summary(sel_SD_87_nfl)
summary(sel_SD_88_nfl)
summary(sel_SD_89_nfl) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_SD_89_glm_nfl)
```

Selection for higher duration of flowering in 1987.

#### BCA intervals

## Variance

### Without n_fl

```{r}
sel_var_87<-glmmTMB(fitness_rel~var_std+(1|subplot),
                     subset(data_ids,year==1987))
sel_var_88<-glmmTMB(fitness_rel~var_std+(1|subplot),
                     subset(data_ids,year==1988))
sel_var_89<-glmmTMB(fitness_rel~var_std+(1|subplot),
                     subset(data_ids,year==1989))
sel_var_89_glm<-lm(fitness_rel~var_std,subset(data_ids,year==1989))
summary(sel_var_87)
summary(sel_var_88)
summary(sel_var_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_var_89_glm)
```

Selection for higher variance of flowering in all three years.

#### BCA intervals

### With n_fl

```{r}
sel_var_87_nfl<-glmmTMB(fitness_rel~var_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1987))
sel_var_88_nfl<-glmmTMB(fitness_rel~var_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1988))
sel_var_89_nfl<-glmmTMB(fitness_rel~var_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1989))
sel_var_89_glm_nfl<-lm(fitness_rel~var_std+n_fl_std,
                        subset(data_ids,year==1989))
summary(sel_var_87_nfl)
summary(sel_var_88_nfl)
summary(sel_var_89_nfl) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_var_89_glm_nfl)
```

Selection for higher variance of flowering in 1987.

#### BCA intervals

## Skewness

#### Without n_fl

```{r}
sel_skew_87<-glmmTMB(fitness_rel~skew_std+(1|subplot),
                     subset(data_ids,year==1987))
sel_skew_88<-glmmTMB(fitness_rel~skew_std+(1|subplot),
                     subset(data_ids,year==1988))
sel_skew_89<-glmmTMB(fitness_rel~skew_std+(1|subplot),
                     subset(data_ids,year==1989))
sel_skew_89_glm<-lm(fitness_rel~skew_std,subset(data_ids,year==1989))
summary(sel_skew_87)
summary(sel_skew_88)
summary(sel_skew_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_skew_89_glm)
```

Selection for higher skewness of FD in 1987 and 1989.

(Recall that fruit initiation significantly increased with higher skewness of FD in 1987 and 1989, and seed predation significantly decreased with higher skewness of FD in 1989).

##### BCA intervals

#### With n_fl

```{r}
sel_skew_87_nfl<-glmmTMB(fitness_rel~skew_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1987))
sel_skew_88_nfl<-glmmTMB(fitness_rel~skew_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1988))
sel_skew_89_nfl<-glmmTMB(fitness_rel~skew_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1989))
sel_skew_89_glm_nfl<-lm(fitness_rel~skew_std+n_fl_std,
                        subset(data_ids,year==1989))
summary(sel_skew_87_nfl)
summary(sel_skew_88_nfl)
summary(sel_skew_89_nfl) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_skew_89_glm_nfl)
```

Similar results as without n_fl: Selection for higher skewness of FD in 1987 and 1989.

##### BCA intervals

## Kurtosis

### Without n_fl

```{r}
sel_kurt_87<-glmmTMB(fitness_rel~kurt_std+(1|subplot),
                     subset(data_ids,year==1987))
sel_kurt_88<-glmmTMB(fitness_rel~kurt_std+(1|subplot),
                     subset(data_ids,year==1988))
sel_kurt_89<-glmmTMB(fitness_rel~kurt_std+(1|subplot),
                     subset(data_ids,year==1989))
sel_kurt_89_glm<-lm(fitness_rel~kurt_std,subset(data_ids,year==1989))
summary(sel_kurt_87)
summary(sel_kurt_88)
summary(sel_kurt_89) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_kurt_89_glm)
```

Selection for higher kurtosis of FD in 1987.

#### BCA intervals

### With n_fl

```{r}
sel_kurt_87_nfl<-glmmTMB(fitness_rel~kurt_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1987))
sel_kurt_88_nfl<-glmmTMB(fitness_rel~kurt_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1988))
sel_kurt_89_nfl<-glmmTMB(fitness_rel~kurt_std+n_fl_std+(1|subplot),
                         subset(data_ids,year==1989))
sel_kurt_89_glm_nfl<-lm(fitness_rel~kurt_std+n_fl_std,
                        subset(data_ids,year==1989))
summary(sel_kurt_87_nfl)
summary(sel_kurt_88_nfl)
summary(sel_kurt_89_nfl) 
# Only 3 subplots in 1989 - Use? Ssimilar result with a GLM
summary(sel_kurt_89_glm_nfl)
```

No selection for kurtosis of FD in any of the three years.

#### BCA intervals

## Plots

```{r}
pred_sel_avFD<-rbind(tibble(ggpredict(sel_avFD_87,
                                         terms=c("avFD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_avFD_88,
                                         terms=c("avFD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_avFD_89,
                                         terms=c("avFD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_avFD_nfl<-rbind(tibble(ggpredict(sel_avFD_87_nfl,
                                         terms=c("avFD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_avFD_88_nfl,
                                         terms=c("avFD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_avFD_89_nfl,
                                         terms=c("avFD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_FFD<-rbind(tibble(ggpredict(sel_FFD_87,
                                         terms=c("FFD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_FFD_88,
                                         terms=c("FFD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_FFD_89,
                                         terms=c("FFD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_FFD_nfl<-rbind(tibble(ggpredict(sel_FFD_87_nfl,
                                         terms=c("FFD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_FFD_88_nfl,
                                         terms=c("FFD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_FFD_89_nfl,
                                         terms=c("FFD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_MFD<-rbind(tibble(ggpredict(sel_MFD_87,
                                         terms=c("MFD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_MFD_88,
                                         terms=c("MFD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_MFD_89,
                                         terms=c("MFD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_MFD_nfl<-rbind(tibble(ggpredict(sel_MFD_87_nfl,
                                         terms=c("MFD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_MFD_88_nfl,
                                         terms=c("MFD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_MFD_89_nfl,
                                         terms=c("MFD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_LFD<-rbind(tibble(ggpredict(sel_LFD_87,
                                         terms=c("LFD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_LFD_88,
                                         terms=c("LFD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_LFD_89,
                                         terms=c("LFD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_LFD_nfl<-rbind(tibble(ggpredict(sel_LFD_87_nfl,
                                         terms=c("LFD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_LFD_88_nfl,
                                         terms=c("LFD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_LFD_89_nfl,
                                         terms=c("LFD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_dur<-rbind(tibble(ggpredict(sel_dur_87,
                                         terms=c("dur_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_dur_88,
                                         terms=c("dur_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_dur_89,
                                         terms=c("dur_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_dur_nfl<-rbind(tibble(ggpredict(sel_dur_87_nfl,
                                         terms=c("dur_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_dur_88_nfl,
                                         terms=c("dur_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_dur_89_nfl,
                                         terms=c("dur_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_SD<-rbind(tibble(ggpredict(sel_SD_87,
                                         terms=c("SD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_SD_88,
                                         terms=c("SD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_SD_89,
                                         terms=c("SD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_SD_nfl<-rbind(tibble(ggpredict(sel_SD_87_nfl,
                                         terms=c("SD_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_SD_88_nfl,
                                         terms=c("SD_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_SD_89_nfl,
                                         terms=c("SD_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_var<-rbind(tibble(ggpredict(sel_var_87,
                                         terms=c("var_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_var_88,
                                         terms=c("var_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_var_89,
                                         terms=c("var_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_var_nfl<-rbind(tibble(ggpredict(sel_var_87_nfl,
                                         terms=c("var_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_var_88_nfl,
                                         terms=c("var_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_var_89_nfl,
                                         terms=c("var_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_skew<-rbind(tibble(ggpredict(sel_skew_87,
                                         terms=c("skew_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_skew_88,
                                         terms=c("skew_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_skew_89,
                                         terms=c("skew_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_skew_nfl<-rbind(tibble(ggpredict(sel_skew_87_nfl,
                                         terms=c("skew_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_skew_88_nfl,
                                         terms=c("skew_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_skew_89_nfl,
                                         terms=c("skew_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_kurt<-rbind(tibble(ggpredict(sel_kurt_87,
                                         terms=c("kurt_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_kurt_88,
                                         terms=c("kurt_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_kurt_89,
                                         terms=c("kurt_std [all]")))%>%
                          mutate(year=as.factor(1989)))
pred_sel_kurt_nfl<-rbind(tibble(ggpredict(sel_kurt_87_nfl,
                                         terms=c("kurt_std [all]")))%>%
                          mutate(year=as.factor(1987)),
                        tibble(ggpredict(sel_kurt_88_nfl,
                                         terms=c("kurt_std [all]")))%>%
                          mutate(year=as.factor(1988)),
                        tibble(ggpredict(sel_kurt_89_nfl,
                                         terms=c("kurt_std [all]")))%>%
                          mutate(year=as.factor(1989)))
```

So far using predictions from models with n_fl.

### Average FD, FFD, MFD, LFD

```{r fig.height=9, fig.width=6}
phen_sel_1<-grid.arrange(
  # Average FD
  ggplot(data_ids,aes(x=avFD_std,y=fitness_rel))+geom_point(size=2,alpha=0.3)+
    geom_ribbon(data=pred_sel_avFD_nfl,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_sel_avFD_nfl,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("red","black","black"))+
    facet_wrap(~year)+
    my_theme()+xlab("Average FD (standardized)")+ylab("Relative fitness"),
  # FFD
  ggplot(data_ids,aes(x=FFD_std,y=fitness_rel))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_sel_FFD_nfl,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_sel_FFD_nfl,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("red","black","black"))+
    facet_wrap(~year)+
    my_theme()+xlab("FFD (standardized)")+ylab("Relative fitness"),
  # MFD
  ggplot(data_ids,aes(x=MFD_std,y=fitness_rel))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_sel_MFD_nfl,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_sel_MFD_nfl,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("red","black","black"))+
    facet_wrap(~year)+
    my_theme()+xlab("MFD (standardized)")+ylab("Relative fitness"),
  # LFD
  ggplot(data_ids,aes(x=LFD_std,y=fitness_rel))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_sel_LFD_nfl,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_sel_LFD_nfl,aes(x,predicted),linewidth=1)+
    facet_wrap(~year)+
    my_theme()+xlab("LFD (standardized)")+ylab("Relative fitness"),
  ncol=1)
ggsave(filename="output/figures/phen_sel_1.tiff",plot=phen_sel_1,
       width=20,height=25,units="cm",dpi=300)
```

### Duration, SD, variance

```{r fig.height=7, fig.width=6}
phen_sel_2<-grid.arrange(
  # Duration
  ggplot(data_ids,aes(x=dur_std,y=fitness_rel))+geom_point(size=2,alpha=0.3)+
    geom_ribbon(data=pred_sel_dur_nfl,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_sel_dur_nfl,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("red","black","black"))+
    facet_wrap(~year)+
    my_theme()+
    xlab("Duration of flowering (standardized)")+ylab("Relative fitness"),
  # SD
  ggplot(data_ids,aes(x=SD_std,y=fitness_rel))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_sel_SD_nfl,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_sel_SD_nfl,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("red","black","black"))+
    facet_wrap(~year)+
    my_theme()+xlab("SD of FD (standardized)")+ylab("Relative fitness"),
  # Variance
  ggplot(data_ids,aes(x=var_std,y=fitness_rel))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_sel_var_nfl,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_sel_var_nfl,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("red","black","black"))+
    facet_wrap(~year)+
    my_theme()+xlab("Variance of FD (standardized)")+ylab("Relative fitness"),
  ncol=1)
ggsave(filename="output/figures/phen_sel_2.tiff",plot=phen_sel_2,
       width=20,height=25,units="cm",dpi=300)
```

### Skewness, kurtosis

```{r fig.height=5, fig.width=6}
phen_sel_3<-grid.arrange(
  # Skewness
  ggplot(data_ids,aes(x=skew_std,y=fitness_rel))+geom_point(size=2,alpha=0.3)+
    geom_ribbon(data=pred_sel_skew_nfl,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_sel_skew_nfl,aes(x,predicted,color=year),linewidth=1)+
    scale_color_manual(values=c("red","black","red"))+
    facet_wrap(~year)+
    my_theme()+
    xlab("Skewness of FD (standardized)")+ylab("Relative fitness"),
  # Kurtosis
  ggplot(data_ids,aes(x=kurt_std,y=fitness_rel))+geom_point(size=2,alpha=0.3)+ 
    geom_ribbon(data=pred_sel_kurt_nfl,
                aes(x,predicted,ymin=conf.low,ymax=conf.high),alpha=0.3)+
    geom_line(data=pred_sel_kurt_nfl,aes(x,predicted),linewidth=1)+
    facet_wrap(~year)+
    my_theme()+xlab("Kurtosis of FD (standardized)")+ylab("Relative fitness"),
  ncol=1)
ggsave(filename="output/figures/phen_sel_3.tiff",plot=phen_sel_3,
       width=20,height=20,units="cm",dpi=300)
```

# Models with PCA axes of traits

Idea from Franks and Weis 2008 (J. Evol. Biol.)

Now using a global PCA with data for the three years together.
Separate PCAs for each year are a little different (but not much). See if we do that.

## Without n_fl 

### PCA

```{r}
data_ids_alltraits<-subset(data_ids,!is.na(avFD_std)&!is.na(FFD_std)&
                             !is.na(MFD_std)&!is.na(LFD_std)&!is.na(dur_std)&
                             !is.na(SD_std)&!is.na(var_std)&!is.na(skew_std)&
                             !is.na(kurt_std))
PCA_global<-prcomp(~avFD_std+FFD_std+MFD_std+LFD_std+dur_std+SD_std+var_std+
                 skew_std+kurt_std,data=data_ids_alltraits,center=T,scale=T)
autoplot(PCA_global,x=1,y=2,loadings=T,loadings.label=T,loadings.label.size=4,shape=F,
         label=F,loadings.label.repel=T)+
  geom_point(alpha=0.1,size=2)+my_theme()
autoplot(PCA_global,x=3,y=4,loadings=T,loadings.label=T,loadings.label.size=4,shape=F,
         label=F,loadings.label.repel=T)+
  geom_point(alpha=0.1,size=2)+my_theme()
PCA_global
summary(PCA_global)
data_ids_alltraits$PC1<-predict(PCA_global)[,1]
data_ids_alltraits$PC2<-predict(PCA_global)[,2]
data_ids_alltraits$PC3<-predict(PCA_global)[,3]
```
### Fruit initiation

```{r}
fr_init_PCA_87<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~PC1+PC2+PC3+(1|subplot),
                      subset(data_ids_alltraits,year==1987),family="binomial")
fr_init_PCA_88<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~PC1+PC2+PC3+(1|subplot),
                      subset(data_ids_alltraits,year==1988),family="binomial")
fr_init_PCA_89<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~PC1+PC2+PC3+(1|subplot),
                      subset(data_ids_alltraits,year==1989),family="binomial")
fr_init_PCA_89_glm<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~PC1+PC2+PC3,
                      subset(data_ids_alltraits,year==1989),family="binomial")
summary(fr_init_PCA_87)
summary(fr_init_PCA_88)
summary(fr_init_PCA_89) 
# Only 3 subplots in 1989 - Use? Very similar result with a GLM
summary(fr_init_PCA_89_glm)
```

### Seed predation

```{r}
seed_pred_PCA_87<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                                npr_seeds=round(n_seed)-round(n_preyed_seed))~
                            PC1+PC2+PC3+(1|subplot),
                          subset(data_ids_alltraits,year==1987),
                          family="binomial")
seed_pred_PCA_88<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                                npr_seeds=round(n_seed)-round(n_preyed_seed))~
                            PC1+PC2+PC3+(1|subplot),
                          subset(data_ids_alltraits,year==1988),
                          family="binomial")
seed_pred_PCA_89<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                                npr_seeds=round(n_seed)-round(n_preyed_seed))~
                            PC1+PC2+PC3+(1|subplot),
                          subset(data_ids_alltraits,year==1989),
                          family="binomial")
seed_pred_PCA_89_glm<-glm(cbind(pr_seeds=round(n_preyed_seed),
                                npr_seeds=round(n_seed)-round(n_preyed_seed))~
                            PC1+PC2+PC3,
                          subset(data_ids_alltraits,year==1989),
                          family="binomial")
summary(seed_pred_PCA_87)
summary(seed_pred_PCA_88)
summary(seed_pred_PCA_89) 
# Only 3 subplots in 1989 - Use? Very similar result with a GLM
summary(seed_pred_PCA_89_glm)
```

### Selection

```{r}
sel_PCA_87<-glmmTMB(fitness_rel~PC1+PC2+PC3+n_fl_std+(1|subplot),
                    subset(data_ids_alltraits,year==1987))
sel_PCA_88<-glmmTMB(fitness_rel~PC1+PC2+PC3+n_fl_std+(1|subplot),
                    subset(data_ids_alltraits,year==1988))
sel_PCA_89<-glmmTMB(fitness_rel~PC1+PC2+PC3+n_fl_std+(1|subplot),
                    subset(data_ids_alltraits,year==1989))
sel_PCA_89_glm<-lm(fitness_rel~PC1+PC2+PC3+n_fl_std,
                    subset(data_ids_alltraits,year==1989))
summary(sel_PCA_87)
summary(sel_PCA_88)
summary(sel_PCA_89)
# Only 3 subplots in 1989 - Use? Very similar result with a GLM
summary(sel_PCA_89_glm)
```


## With n_fl 

### PCA

```{r}
PCA_global_nfl<-prcomp(~avFD_std+FFD_std+MFD_std+LFD_std+dur_std+SD_std+var_std+
                 skew_std+kurt_std+n_fl_std,
                 data=data_ids_alltraits,center=T,scale=T)
autoplot(PCA_global_nfl,x=1,y=2,loadings=T,loadings.label=T,loadings.label.size=4,shape=F,
         label=F,loadings.label.repel=T)+
  geom_point(alpha=0.1,size=2)+my_theme()
autoplot(PCA_global_nfl,x=3,y=4,loadings=T,loadings.label=T,loadings.label.size=4,shape=F,
         label=F,loadings.label.repel=T)+
  geom_point(alpha=0.1,size=2)+my_theme()
PCA_global_nfl
summary(PCA_global_nfl)
data_ids_alltraits$PC1_nfl<-predict(PCA_global_nfl)[,1]
data_ids_alltraits$PC2_nfl<-predict(PCA_global_nfl)[,2]
data_ids_alltraits$PC3_nfl<-predict(PCA_global_nfl)[,3]
```

### Selection models

```{r}
sel_PCA_nfl_87<-glmmTMB(fitness_rel~PC1_nfl+PC2_nfl+PC3_nfl+(1|subplot),
                    subset(data_ids_alltraits,year==1987))
sel_PCA_nfl_88<-glmmTMB(fitness_rel~PC1_nfl+PC2_nfl+PC3_nfl+(1|subplot),
                    subset(data_ids_alltraits,year==1988))
sel_PCA_nfl_89<-glmmTMB(fitness_rel~PC1_nfl+PC2_nfl+PC3_nfl+(1|subplot),
                    subset(data_ids_alltraits,year==1989))
summary(sel_PCA_nfl_87)
summary(sel_PCA_nfl_88)
summary(sel_PCA_nfl_89)
```

# Additional: skewness as function of mean/median FD & SD/var of FD

Idea from Stemkovski et al. 2023 (Ecology).

## Models

```{r}
summary(lm(skew~avFD_std,subset(data_ids,year==1987)))
summary(lm(skew~avFD_std,subset(data_ids,year==1988)))
summary(lm(skew~avFD_std,subset(data_ids,year==1989)))

summary(lm(skew~MFD_std,subset(data_ids,year==1987)))
summary(lm(skew~MFD_std,subset(data_ids,year==1988)))
summary(lm(skew~MFD_std,subset(data_ids,year==1989)))

summary(lm(skew~SD_std,subset(data_ids,year==1987)))
summary(lm(skew~SD_std,subset(data_ids,year==1988)))
summary(lm(skew~SD_std,subset(data_ids,year==1989)))

summary(lm(skew~var_std,subset(data_ids,year==1987)))
summary(lm(skew~var_std,subset(data_ids,year==1988)))
summary(lm(skew~var_std,subset(data_ids,year==1989)))
```

Higher skewness in early-flowering in 1987 and 1988.
Higher skewness with higher SD and var in all three years.

## Plots

Preliminary, better to do with yearly models.

```{r}
plot(ggpredict(lm(skew~avFD_std*year,data_ids),terms=c("avFD_std","year")))
plot(ggpredict(lm(skew~MFD_std*year,data_ids),terms=c("MFD_std","year")))
plot(ggpredict(lm(skew~SD_std*year,data_ids),terms=c("SD_std","year")))
plot(ggpredict(lm(skew~var_std*year,data_ids),terms=c("var_std","year")))
```


# Session info

```{r}
sessionInfo()
```
