---
title: "Selection on within-individual variation in flowering time in Lathyrus vernus"
subtitle: "Analyses of relationships between phenological traits and fruit initiation and pre-dispersal seed predation, and analyses of phenotypic selection on phenological traits"
author : "Alicia Valdés"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(tibble.width = Inf)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r load packages, include=FALSE}
library(tidyverse)
library(jtools)
library(ggeffects)
library(glmmTMB)
library(DHARMa)
library(RColorBrewer)
library(gridExtra)
library(ggthemes)
library(ggfortify)
library(ggcorrplot)
library(car)
library(broom.mixed)
library(performance)
library(sjPlot)
library(lme4)
```

```{r Define ggplot themes and palettes, include=FALSE}
my_theme <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(legend.position="none")+theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
my_theme_legend <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
myPalette <- colorRampPalette(brewer.pal(11, "YlOrRd"))
```

```{r}
load(file="output/boot_sel_nfl_glmer.RData")
load(file="output/boot_sel_87_nfl_glmer.RData")
load(file="output/boot_sel_88_nfl_glmer.RData")
load(file="output/boot_sel_89_nfl_glmer.RData")
```

# Read clean data from .csv file

```{r}
data_ids <- read_csv("data/clean/data_ids.csv")
data_ids$imp_seed_preyed <- as.factor(data_ids$imp_seed_preyed)
data_ids$year <- as.factor(data_ids$year)
data_ids$subplot<-as.factor(data_ids$subplot)
```

# Correlations

I will fit models using traits representing the 4 moments of the distribution (mean: avFD, variance: var, skewness: skew and kurtosis: kurt)

Check the correlations of these 4 traits using all data:

```{r}
data_ids%>%select(year,avFD_v,var,skew,kurt) %>%
    select_if(is.numeric) %>% 
    cor(use="pairwise.complete.obs") %>%
    ggcorrplot(method = "square", type = "lower", hc.order = F, lab = T)+
  theme(legend.position="none")
```

Check the yearly correlations:

```{r}
grid.arrange(
  data_ids%>%select(year,avFD_v,var,skew,kurt) %>%
    filter(year==1987) %>%
    select_if(is.numeric) %>% 
    cor(use="pairwise.complete.obs") %>%
    ggcorrplot(method = "square", type = "lower", hc.order = F, lab = T)+
    ggtitle("1987")+theme(legend.position="none"),
  data_ids%>%select(year,avFD_v,var,skew,kurt) %>%
    filter(year==1988) %>%
    select_if(is.numeric) %>% 
    cor(use="pairwise.complete.obs") %>%
    ggcorrplot(method = "square", type = "lower", hc.order = F, lab = T)+
    ggtitle("1988")+theme(legend.position="none"),
  data_ids%>%select(year,avFD_v,var,skew,kurt) %>%
    filter(year==1989) %>%
    select_if(is.numeric) %>% 
    cor(use="pairwise.complete.obs") %>%
    ggcorrplot(method = "square", type = "lower", hc.order = F, lab = T)+
    ggtitle("1989")+theme(legend.position="none"),
  ncol=3)
```

Probaly OK? Check VIFs of each model.

# FRUIT INITIATION

Using (within-year) standardized traits and subplot as a random effect (GLMM). Also GLM without subplot.

## Global models

Including only linear effects and interactions with year.

```{r}
fr_init<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                   (avFD_std+var_std+skew_std+kurt_std)*year+
                   (1|subplot),data_ids,family="binomial")
summary(fr_init)
Anova(fr_init)
plot(check_collinearity(fr_init))
```

Differences among years in the effects of skewness and kurtosis (and of avFD, marginally significant).
Collinearity OK?

```{r}
fr_init_glm<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                   (avFD_std+var_std+skew_std+kurt_std)*year,
                 data_ids,family="binomial")
summary(fr_init_glm)
Anova(fr_init_glm)
plot(check_collinearity(fr_init_glm))
```

Differences among years in the effects of skewness and avFD (and of kurtosis, marginally significant).
Collinearity OK?

Both the GLMM and GLM show that the effect of variance does not differ among years.

Plot predictions using GLMM.

```{r}
plot(ggpredict(fr_init,terms=c("avFD_std [all]","year")))
plot(ggpredict(fr_init,terms=c("var_std [all]","year")))
plot(ggpredict(fr_init,terms=c("skew_std [all]","year")))
plot(ggpredict(fr_init,terms=c("kurt_std [all]","year")))
```

## Yearly models

Including also quadratic effects.
So far, using GLMM and not including interactions among traits

```{r}
fr_init_87<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                   (avFD_std+var_std+skew_std+kurt_std)+
                     I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                   (1|subplot),subset(data_ids,year==1987),family="binomial")
fr_init_88<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                   (avFD_std+var_std+skew_std+kurt_std)+
                     I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                   (1|subplot),subset(data_ids,year==1988),family="binomial")
fr_init_89<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                   (avFD_std+var_std+skew_std+kurt_std)+
                     I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                   (1|subplot),subset(data_ids,year==1989),family="binomial")
summary(fr_init_87)
summary(fr_init_88)
summary(fr_init_89)
Anova(fr_init_87)
Anova(fr_init_88)
Anova(fr_init_89)
plot(check_collinearity(fr_init_87))
plot(check_collinearity(fr_init_88))
plot(check_collinearity(fr_init_89))
```

Keep quadratic effects of skewness in 1987 and variance in 1988.

```{r}
fr_init_87<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                   (avFD_std+var_std+skew_std+kurt_std)+
                     I(skew_std^2)+
                   (1|subplot),subset(data_ids,year==1987),family="binomial")
fr_init_88<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                   (avFD_std+var_std+skew_std+kurt_std)+
                     I(var_std^2)+
                   (1|subplot),subset(data_ids,year==1988),family="binomial")
fr_init_89<-glmmTMB(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                   (avFD_std+var_std+skew_std+kurt_std)+
                   (1|subplot),subset(data_ids,year==1989),family="binomial")
summary(fr_init_87)
summary(fr_init_88)
summary(fr_init_89)
Anova(fr_init_87)
Anova(fr_init_88)
Anova(fr_init_89)
plot(check_collinearity(fr_init_87)) # Remove kurtosis?
plot(check_collinearity(fr_init_88))
plot(check_collinearity(fr_init_89))
```

Plot predictions using GLMM.

1987

```{r}
plot(ggpredict(fr_init_87,terms="avFD_std [all]")) # *
plot(ggpredict(fr_init_87,terms="var_std [all]")) # *
plot(ggpredict(fr_init_87,terms="skew_std [all]")) # quadratic*
plot(ggpredict(fr_init_87,terms="kurt_std [all]")) # *
```

1988

```{r}
plot(ggpredict(fr_init_88,terms="avFD_std [all]")) # *
plot(ggpredict(fr_init_88,terms="var_std [all]")) # quadratic*
plot(ggpredict(fr_init_88,terms="skew_std [all]"))
plot(ggpredict(fr_init_88,terms="kurt_std [all]"))
```

1989

```{r}
plot(ggpredict(fr_init_89,terms="avFD_std [all]")) # *
plot(ggpredict(fr_init_89,terms="var_std [all]")) 
plot(ggpredict(fr_init_89,terms="skew_std [all]")) # *
plot(ggpredict(fr_init_89,terms="kurt_std [all]"))
```

# PRE-DISPERSAL SEED PREDATION

Using (within-year) standardized traits and subplot as a random effect (GLMM). Also GLM without subplot.

## Global models

Including only linear effects and interactions with year.

```{r}
seed_pred<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~
                   (avFD_std+var_std+skew_std+kurt_std)*year+
                   (1|subplot),data_ids,family="binomial")
summary(seed_pred)
Anova(seed_pred)
plot(check_collinearity(seed_pred)) # This is because of interactions with year
plot(check_collinearity(glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~
                   (avFD_std+var_std+skew_std+kurt_std)+year+
                   (1|subplot),data_ids,family="binomial"))) # OK
```

Differences among years in the effects of average FD and skewness.
Collinearity OK.

```{r}
seed_pred_glm<-glm(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~
                   (avFD_std+var_std+skew_std+kurt_std)*year,
                   data_ids,family="binomial")
summary(seed_pred_glm)
Anova(seed_pred_glm)
plot(check_collinearity(seed_pred_glm)) # This is because of interactions with year
plot(check_collinearity(glm(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~
                   (avFD_std+var_std+skew_std+kurt_std)+year,
                   data_ids,family="binomial"))) # OK?
```

Differences among years in the effects of average FD and skewness.
Collinearity OK?

Both the GLMM and GLM show that the effect of variance does not differ among years.

Plot predictions using GLMM.

```{r}
plot(ggpredict(seed_pred,terms=c("avFD_std [all]","year")))
plot(ggpredict(seed_pred,terms=c("var_std [all]","year")))
plot(ggpredict(seed_pred,terms=c("skew_std [all]","year")))
plot(ggpredict(seed_pred,terms=c("kurt_std [all]","year")))
```

## Yearly models

Including also quadratic effects.
So far, using GLMM and not including interactions among traits

```{r}
seed_pred_87<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~
                   (avFD_std+var_std+skew_std+kurt_std)+
                     I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                   (1|subplot),subset(data_ids,year==1987),family="binomial")
seed_pred_88<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~
                   (avFD_std+var_std+skew_std+kurt_std)+
                     I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                   (1|subplot),subset(data_ids,year==1988),family="binomial")
seed_pred_89<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~
                   (avFD_std+var_std+skew_std+kurt_std)+
                     I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                   (1|subplot),subset(data_ids,year==1989),family="binomial")
summary(seed_pred_87)
summary(seed_pred_88)
summary(seed_pred_89)
Anova(seed_pred_87)
Anova(seed_pred_88)
Anova(seed_pred_89)
plot(check_collinearity(seed_pred_87))
plot(check_collinearity(seed_pred_88))
plot(check_collinearity(seed_pred_89))
```

Keep quadratic effects of skewness in 1987, average FD and variance in 1988, and average FD in 1989.

```{r}
seed_pred_87<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~
                   (avFD_std+var_std+skew_std+kurt_std)+
                     I(skew_std^2)+
                   (1|subplot),subset(data_ids,year==1987),family="binomial")
seed_pred_88<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~
                   (avFD_std+var_std+skew_std+kurt_std)+
                     I(avFD_std^2)+I(var_std^2)+
                   (1|subplot),subset(data_ids,year==1988),family="binomial")
seed_pred_89<-glmmTMB(cbind(pr_seeds=round(n_preyed_seed),
                    npr_seeds=round(n_seed)-round(n_preyed_seed))~
                   (avFD_std+var_std+skew_std+kurt_std)+
                     I(avFD_std^2)+
                   (1|subplot),subset(data_ids,year==1989),family="binomial")
summary(seed_pred_87)
summary(seed_pred_88)
summary(seed_pred_89)
Anova(seed_pred_87)
Anova(seed_pred_88)
Anova(seed_pred_89)
plot(check_collinearity(seed_pred_87))
plot(check_collinearity(seed_pred_88))
plot(check_collinearity(seed_pred_89))
```

Plot predictions using GLMM.

1987

```{r}
plot(ggpredict(seed_pred_87,terms="avFD_std [all]")) # 
plot(ggpredict(seed_pred_87,terms="var_std [all]")) # 
plot(ggpredict(seed_pred_87,terms="skew_std [all]")) # quadratic*
plot(ggpredict(seed_pred_87,terms="kurt_std [all]")) # *
```

1988

```{r}
plot(ggpredict(seed_pred_88,terms="avFD_std [all]")) # quadratic*
plot(ggpredict(seed_pred_88,terms="var_std [all]")) # quadratic*
plot(ggpredict(seed_pred_88,terms="skew_std [all]")) # *
plot(ggpredict(seed_pred_88,terms="kurt_std [all]")) # 
```

1989

```{r}
plot(ggpredict(seed_pred_89,terms="avFD_std [all]")) # quadratic*
plot(ggpredict(seed_pred_89,terms="var_std [all]")) # *
plot(ggpredict(seed_pred_89,terms="skew_std [all]")) # *
plot(ggpredict(seed_pred_89,terms="kurt_std [all]")) # 
```

# PHENOTYPIC SELECTION

Using (within-year) standardized traits and subplot as a random effect (LMM). Also LM without subplot.

## Global models

### Without n_fl

Including only linear effects and interactions with year.

```{r}
sel<-glmmTMB(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)*year+(1|subplot),
             data_ids)
summary(sel)
Anova(sel)
plot(check_collinearity(sel))
```

Differences among years in the effects of variance? Collinearity OK.

```{r}
sel_lm<-lm(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)*year,
             data_ids)
summary(sel_lm)
Anova(sel_lm)
plot(check_collinearity(sel_lm))
```

Differences among years in the effects of variance? Collinearity OK.

Plot predictions using LMM.

```{r}
plot(ggpredict(sel,terms=c("avFD_std [all]","year")))
plot(ggpredict(sel,terms=c("var_std [all]","year")))
plot(ggpredict(sel,terms=c("skew_std [all]","year")))
plot(ggpredict(sel,terms=c("kurt_std [all]","year")))
```

### With n_fl

Including only linear effects and interactions with year.

```{r}
sel_nfl<-glmmTMB(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)*year+n_fl_std+
                   (1|subplot),data_ids)
summary(sel_nfl)
Anova(sel_nfl)
plot(check_collinearity(sel_nfl))
```

Differences among years in the effects of variance (NS)? Collinearity OK.
Or maybe just say: no differences among years in any of the effects, so we do not run yearly models.

```{r}
sel_nfl_lm<-lm(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)*year+n_fl_std,
               data_ids)
summary(sel_nfl_lm)
Anova(sel_nfl_lm)
plot(check_collinearity(sel_nfl_lm))
```

Differences among years in the effects of variance (NS)? Collinearity OK.
Or maybe just say: no differences among years in any of the effects, so we do not run yearly models.

Plot predictions using LMM.

```{r}
plot(ggpredict(sel_nfl,terms=c("avFD_std [all]","year")))
plot(ggpredict(sel_nfl,terms=c("var_std [all]","year")))
plot(ggpredict(sel_nfl,terms=c("skew_std [all]","year")))
plot(ggpredict(sel_nfl,terms=c("kurt_std [all]","year")))
plot(ggpredict(sel_nfl,terms=c("n_fl_std [all]")))
```

#### BCA intervals for LMM

Refit model with lme4, otherwise bootstrap does not work.

```{r}
sel_nfl_glmer<-lmer(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)*year+
                       n_fl_std+(1|subplot),data_ids)
```

```{r eval=FALSE, include=FALSE}
FUN <- function(fit) {
    return(fixef(fit))
}
boot_sel_nfl_glmer<-bootMer(sel_nfl_glmer, FUN,nsim=10000,verbose=T)
save(boot_sel_nfl_glmer,file="output/boot_sel_nfl_glmer.RData")
```

```{r}
confint(boot_sel_nfl_glmer,level=0.95, method="boot") # Percentile method
```

## Yearly models

### Without n_fl

Including also quadratic effects.
So far, using LMM and not including interactions among traits

```{r}
sel_87<-glmmTMB(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)+
                     I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                   (1|subplot),subset(data_ids,year==1987))
sel_88<-glmmTMB(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)+
                     I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                   (1|subplot),subset(data_ids,year==1988))
sel_89<-glmmTMB(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)+
                     I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                   (1|subplot),subset(data_ids,year==1989))
summary(sel_87)
summary(sel_88)
summary(sel_89)
Anova(sel_87)
Anova(sel_88)
Anova(sel_89)
plot(check_collinearity(sel_87))
plot(check_collinearity(sel_88))
plot(check_collinearity(sel_89))
```

Keep no quadratic effects.

```{r}
sel_87<-glmmTMB(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)+
                   (1|subplot),subset(data_ids,year==1987))
sel_88<-glmmTMB(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)+
                   (1|subplot),subset(data_ids,year==1988))
sel_89<-glmmTMB(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)+
                   (1|subplot),subset(data_ids,year==1989))
summary(sel_87)
summary(sel_88)
summary(sel_89)
Anova(sel_87)
Anova(sel_88)
Anova(sel_89)
plot(check_collinearity(sel_87))
plot(check_collinearity(sel_88))
plot(check_collinearity(sel_89))
```

Plot predictions using LMM.

1987

```{r}
plot(ggpredict(sel_87,terms="avFD_std [all]")) # *
plot(ggpredict(sel_87,terms="var_std [all]")) # *
plot(ggpredict(sel_87,terms="skew_std [all]")) # 
plot(ggpredict(sel_87,terms="kurt_std [all]")) # 
```

1988

```{r}
plot(ggpredict(sel_88,terms="avFD_std [all]")) # *
plot(ggpredict(sel_88,terms="var_std [all]")) # *
plot(ggpredict(sel_88,terms="skew_std [all]")) # 
plot(ggpredict(sel_88,terms="kurt_std [all]")) # 
```

1989

```{r}
plot(ggpredict(sel_89,terms="avFD_std [all]")) # *
plot(ggpredict(sel_89,terms="var_std [all]")) # *
plot(ggpredict(sel_89,terms="skew_std [all]")) # 
plot(ggpredict(sel_89,terms="kurt_std [all]")) # 
```

### With n_fl

Including also quadratic effects.
So far, using LMM and not including interactions among traits

```{r}
sel_87_nfl<-glmmTMB(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)+n_fl_std+
                     I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                   (1|subplot),subset(data_ids,year==1987))
sel_88_nfl<-glmmTMB(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)+n_fl_std+
                     I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                   (1|subplot),subset(data_ids,year==1988))
sel_89_nfl<-glmmTMB(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)+n_fl_std+
                     I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                   (1|subplot),subset(data_ids,year==1989))
summary(sel_87_nfl)
summary(sel_88_nfl)
summary(sel_89_nfl)
Anova(sel_87_nfl)
Anova(sel_88_nfl)
Anova(sel_89_nfl)
plot(check_collinearity(sel_87_nfl))
plot(check_collinearity(sel_88_nfl))
plot(check_collinearity(sel_89_nfl))
```

Keep no quadratic effects.

```{r}
sel_87_nfl<-glmmTMB(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)+n_fl_std+
                   (1|subplot),subset(data_ids,year==1987))
sel_88_nfl<-glmmTMB(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)+n_fl_std+
                   (1|subplot),subset(data_ids,year==1988))
sel_89_nfl<-glmmTMB(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)+n_fl_std+
                   (1|subplot),subset(data_ids,year==1989))
summary(sel_87_nfl)
summary(sel_88_nfl)
summary(sel_89_nfl)
Anova(sel_87_nfl)
Anova(sel_88_nfl)
Anova(sel_89_nfl)
plot(check_collinearity(sel_87_nfl))
plot(check_collinearity(sel_88_nfl))
plot(check_collinearity(sel_89_nfl))
```

Plot predictions using LMM.

1987

```{r}
plot(ggpredict(sel_87_nfl,terms="avFD_std [all]")) #
plot(ggpredict(sel_87_nfl,terms="var_std [all]")) # *
plot(ggpredict(sel_87_nfl,terms="skew_std [all]")) # 
plot(ggpredict(sel_87_nfl,terms="kurt_std [all]")) # 
plot(ggpredict(sel_87_nfl,terms="n_fl_std [all]")) # *
```

1988

```{r}
plot(ggpredict(sel_88_nfl,terms="avFD_std [all]")) # 
plot(ggpredict(sel_88_nfl,terms="var_std [all]")) # 
plot(ggpredict(sel_88_nfl,terms="skew_std [all]")) # 
plot(ggpredict(sel_88_nfl,terms="kurt_std [all]")) # 
plot(ggpredict(sel_88_nfl,terms="n_fl_std [all]")) # *
```

1989

```{r}
plot(ggpredict(sel_89_nfl,terms="avFD_std [all]")) # 
plot(ggpredict(sel_89_nfl,terms="var_std [all]")) # 
plot(ggpredict(sel_89_nfl,terms="skew_std [all]")) # *
plot(ggpredict(sel_89_nfl,terms="kurt_std [all]")) # 
plot(ggpredict(sel_89_nfl,terms="n_fl_std [all]")) # *
```

#### BCA intervals for LMMs

Refit models with lme4, otherwise bootstrap does not work.

```{r}
sel_87_nfl_glmer<-lmer(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)+
                          n_fl_std+(1|subplot),subset(data_ids,year==1987))
sel_88_nfl_glmer<-lmer(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)+
                          n_fl_std+(1|subplot),subset(data_ids,year==1988))
sel_89_nfl_glmer<-lmer(fitness_rel~(avFD_std+var_std+skew_std+kurt_std)+
                          n_fl_std+(1|subplot),subset(data_ids,year==1989))
```

```{r eval=FALSE, include=FALSE}
boot_sel_87_nfl_glmer<-bootMer(sel_87_nfl_glmer, FUN,nsim=10000,verbose=T)
boot_sel_88_nfl_glmer<-bootMer(sel_88_nfl_glmer, FUN,nsim=10000,verbose=T)
boot_sel_89_nfl_glmer<-bootMer(sel_89_nfl_glmer, FUN,nsim=10000,verbose=T)
save(boot_sel_87_nfl_glmer,file="output/boot_sel_87_nfl_glmer.RData")
save(boot_sel_88_nfl_glmer,file="output/boot_sel_88_nfl_glmer.RData")
save(boot_sel_89_nfl_glmer,file="output/boot_sel_89_nfl_glmer.RData")
```

```{r}
confint(boot_sel_87_nfl_glmer,level=0.95, method="boot") # Percentile method
confint(boot_sel_88_nfl_glmer,level=0.95, method="boot") # Percentile method
confint(boot_sel_89_nfl_glmer,level=0.95, method="boot") # Percentile method
```

# Tables

## Global models

```{r}
tab_model(fr_init,seed_pred,sel_nfl,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation","Seed predation","Selection"),
          file="output/tables/Table_global_models.html",title="Global models")
# More options to change for getting publication-ready tables!
```

## Fruit initiation

```{r}
tab_model(fr_init_87,fr_init_88,fr_init_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          file="output/tables/Table_fr_init.html",
          title="Yearly models for fruit initiation")
```

## Seed predation

```{r}
tab_model(seed_pred_87,seed_pred_88,seed_pred_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          file="output/tables/Table_seed_pred.html",
          title="Yearly models for seed predation")
```

## Selection

```{r}
tab_model(sel_87_nfl,sel_88_nfl,sel_89_nfl,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          file="output/tables/Table_selection.html",
          title="Yearly models for selection")
```

# Plots

Extract predictions from models

```{r}
prediction_fr_init<-rbind(rbind(tibble(ggpredict(fr_init_87,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_init_88,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_init_89,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="avFD_std"), # avFD_std
                    rbind(tibble(ggpredict(fr_init_87,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_init_88,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_init_89,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="var_std"), # var_std
                    rbind(tibble(ggpredict(fr_init_87,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_init_88,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_init_89,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="skew_std"), # skew_std
                    rbind(tibble(ggpredict(fr_init_87,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_init_88,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_init_89,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="kurt_std"))%>% # kurt_std
  mutate(response="fr_init")
prediction_seed_pred<-rbind(rbind(tibble(ggpredict(seed_pred_87,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(seed_pred_88,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(seed_pred_89,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="avFD_std"), # avFD_std
                    rbind(tibble(ggpredict(seed_pred_87,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(seed_pred_88,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(seed_pred_89,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="var_std"), # var_std
                    rbind(tibble(ggpredict(seed_pred_87,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(seed_pred_88,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(seed_pred_89,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="skew_std"), # skew_std
                    rbind(tibble(ggpredict(seed_pred_87,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(seed_pred_88,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(seed_pred_89,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="kurt_std"))%>% # kurt_std
  mutate(response="prop_seed_preyed")
prediction_sel<-rbind(rbind(tibble(ggpredict(sel_87_nfl,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(sel_88_nfl,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(sel_89_nfl,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="avFD_std"), # avFD_std
                    rbind(tibble(ggpredict(sel_87_nfl,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(sel_88_nfl,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(sel_89_nfl,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="var_std"), # var_std
                    rbind(tibble(ggpredict(sel_87_nfl,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(sel_88_nfl,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(sel_89_nfl,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="skew_std"), # skew_std
                    rbind(tibble(ggpredict(sel_87_nfl,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(sel_88_nfl,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(sel_89_nfl,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="kurt_std"))%>% # kurt_std
  mutate(response="fitness_rel")
prediction_all<-rbind(prediction_fr_init,prediction_seed_pred,prediction_sel)
```

## Everything

```{r}
data_points_plots<-data_ids%>%
  select(year,fr_init,prop_seed_preyed,fitness_rel,
         avFD_std,var_std,skew_std,kurt_std)%>%
  pivot_longer(cols=avFD_std:kurt_std,
               names_to="predictor",values_to="value_predictor")%>%
  pivot_longer(cols=fr_init:fitness_rel,
               names_to="response",values_to="value_response")
ggplot()+
  geom_point(data=data_points_plots,
             aes(x=value_predictor,y=value_response,color=year),
             size=2,alpha=0.3)+
  facet_grid(cols=vars(factor(predictor,
                              levels=c("avFD_std","var_std",
                                       "skew_std","kurt_std"))),
             rows=vars(response),scales="free")+
  geom_ribbon(data=prediction_all,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=year),
              alpha=0.3)+
  geom_line(data=prediction_all,aes(x=x,y=predicted,color=year),
            linewidth=1)+
  my_theme()
```

## Fruit initiation in 3 years

```{r}
predictor.labs<-c("Average","Variance","Skewness","Kurtosis")
names(predictor.labs)<-c("avFD_std","var_std","skew_std","kurt_std")
ggplot()+
  geom_point(data=data_ids%>%
               select(year,fr_init,avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
               names_to="predictor",values_to="value_predictor"),
             aes(x=value_predictor,y=fr_init),
             size=2,alpha=0.3)+
  facet_grid(cols=vars(predictor=factor(predictor,
                              levels=c("avFD_std","var_std",
                                       "skew_std","kurt_std"))),
             rows=vars(year),scales="free",switch="x",
             labeller=labeller(predictor=predictor.labs))+
  geom_ribbon(data=prediction_fr_init,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
              alpha=0.3)+
  geom_line(data=prediction_fr_init,aes(x=x,y=predicted),
            linewidth=1)+
  ylab("Fruit intitiation")+xlab(NULL)+
  my_theme()
```

## Seed predation in 3 years

```{r}
ggplot()+
  geom_point(data=data_ids%>%
               select(year,prop_seed_preyed,avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
               names_to="predictor",values_to="value_predictor"),
             aes(x=value_predictor,y=prop_seed_preyed),
             size=2,alpha=0.3)+
  facet_grid(cols=vars(predictor=factor(predictor,
                              levels=c("avFD_std","var_std",
                                       "skew_std","kurt_std"))),
             rows=vars(year),scales="free",switch="x",
             labeller=labeller(predictor=predictor.labs))+
  geom_ribbon(data=prediction_seed_pred,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
              alpha=0.3)+
  geom_line(data=prediction_seed_pred,aes(x=x,y=predicted),
            linewidth=1)+
  ylab("Seed predation")+xlab(NULL)+
  my_theme()
```

## Selection in 3 years

```{r}
ggplot()+
  geom_point(data=data_ids%>%
               select(year,fitness_rel,avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
               names_to="predictor",values_to="value_predictor"),
             aes(x=value_predictor,y=fitness_rel),
             size=2,alpha=0.3)+
  facet_grid(cols=vars(predictor=factor(predictor,
                              levels=c("avFD_std","var_std",
                                       "skew_std","kurt_std"))),
             rows=vars(year),scales="free",switch="x",
             labeller=labeller(predictor=predictor.labs))+
  geom_ribbon(data=prediction_sel,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
              alpha=0.3)+
  geom_line(data=prediction_sel,aes(x=x,y=predicted),
            linewidth=1)+
  ylab("Relative fitness")+xlab(NULL)+
  my_theme()
```

## 1987

```{r}
response.labs<-c("Fruit initiation","Seed predation","Relative fitness")
names(response.labs)<-c("fr_init","prop_seed_preyed","fitness_rel")
data_points_plots_87<-subset(data_points_plots,year==1987)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")),
         response=factor(response,levels=c("fr_init","prop_seed_preyed",
                                       "fitness_rel")))

ggplot()+
  geom_point(data=data_points_plots_87,
             aes(x=value_predictor,y=value_response),
             size=2,alpha=0.3)+
  facet_grid(cols=vars(predictor=factor(predictor)),
             rows=vars(response=factor(response)),
             scales="free",switch="x",
             labeller=labeller(predictor=predictor.labs,
                               response=response.labs))+
  geom_ribbon(data=subset(prediction_all,year==1987),
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
              alpha=0.3)+
  geom_line(data=subset(prediction_all,year==1987),aes(x=x,y=predicted),
            linewidth=1)+
  my_theme()
```

## 1988

```{r}
data_points_plots_88<-subset(data_points_plots,year==1988)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")),
         response=factor(response,levels=c("fr_init","prop_seed_preyed",
                                       "fitness_rel")))
ggplot()+
  geom_point(data=data_points_plots_88,
             aes(x=value_predictor,y=value_response),
             size=2,alpha=0.3)+
  facet_grid(cols=vars(predictor=factor(predictor)),
             rows=vars(response=factor(response)),
             scales="free",switch="x",
             labeller=labeller(predictor=predictor.labs,
                               response=response.labs))+
  geom_ribbon(data=subset(prediction_all,year==1988),
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
              alpha=0.3)+
  geom_line(data=subset(prediction_all,year==1988),aes(x=x,y=predicted),
            linewidth=1)+
  my_theme()
```

## 1989

```{r}
data_points_plots_89<-subset(data_points_plots,year==1989)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")),
         response=factor(response,levels=c("fr_init","prop_seed_preyed",
                                       "fitness_rel")))
ggplot()+
  geom_point(data=data_points_plots_89,
             aes(x=value_predictor,y=value_response),
             size=2,alpha=0.3)+
  facet_grid(cols=vars(predictor=factor(predictor)),
             rows=vars(response=factor(response)),
             scales="free",switch="x",
             labeller=labeller(predictor=predictor.labs,
                               response=response.labs))+
  geom_ribbon(data=subset(prediction_all,year==1989),
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
              alpha=0.3)+
  geom_line(data=subset(prediction_all,year==1989),aes(x=x,y=predicted),
            linewidth=1)+
  my_theme()
```

# Session info

```{r}
sessionInfo()
```
