---
title: "Selection on within-individual variation in flowering time in Lathyrus vernus"
author: "Alicia Valdés"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  pdf_document:
    toc: yes
    toc_depth: 4
  word_document:
    toc: yes
    toc_depth: '4'
subtitle: "Analyses of relationships between phenological traits and fruit initiation
  and pre-dispersal seed predation, and analyses of phenotypic selection on phenological
  traits"
editor_options:
  chunk_output_type: inline
---
# Analyses with only mean and variance (not used)

## FRUIT INITIATION

### Yearly models

#### Linear effects

##### Same n

```{r}
fr_init_linear_87_mv2<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+var_std,
                          subset(data_ids,year==1987&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
fr_init_linear_88_mv2<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+var_std,
                    subset(data_ids,year==1988&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
fr_init_linear_89_mv2<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+var_std,
                    subset(data_ids,year==1989&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
tab_model(fr_init_linear_87_mv2,fr_init_linear_88_mv2,fr_init_linear_89_mv2,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit initiation, linear effects, mean and variance")
Anova(fr_init_linear_87_mv2)
Anova(fr_init_linear_88_mv2)
Anova(fr_init_linear_89_mv2) 
```

##### Larger n

```{r}
fr_init_linear_87_mv<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                         avFD_std+var_std,
                       subset(data_ids,year==1987),family="binomial")
fr_init_linear_88_mv<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                         avFD_std+var_std,
                    subset(data_ids,year==1988),family="binomial")
fr_init_linear_89_mv<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                         avFD_std+var_std,
                    subset(data_ids,year==1989),family="binomial")
tab_model(fr_init_linear_87_mv,fr_init_linear_88_mv,fr_init_linear_89_mv,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit initiation, linear effects, mean and variance")
Anova(fr_init_linear_87_mv)
Anova(fr_init_linear_88_mv)
Anova(fr_init_linear_89_mv) 
```

#### Non-linear effects

##### Same n

```{r}
fr_init_nonlinear_87_mv2<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                            avFD_std+var_std+
                            I(avFD_std^2)+I(var_std^2),
                          subset(data_ids,year==1987&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
fr_init_nonlinear_88_mv2<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                            avFD_std+var_std+
                            I(avFD_std^2)+I(var_std^2),
                    subset(data_ids,year==1988&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
fr_init_nonlinear_89_mv2<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                            avFD_std+var_std+
                            I(avFD_std^2)+I(var_std^2),
                    subset(data_ids,year==1989&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
tab_model(fr_init_nonlinear_87_mv2,fr_init_nonlinear_88_mv2,
          fr_init_nonlinear_89_mv2,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit initiation, nonlinear effects, mean and variance")
Anova(fr_init_nonlinear_87_mv2)
Anova(fr_init_nonlinear_88_mv2)
Anova(fr_init_nonlinear_89_mv2) 
```

##### Larger n

```{r}
fr_init_nonlinear_87_mv<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                            avFD_std+var_std+
                            I(avFD_std^2)+I(var_std^2),
                          subset(data_ids,year==1987),family="binomial")
fr_init_nonlinear_88_mv<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                            avFD_std+var_std+
                            I(avFD_std^2)+I(var_std^2),
                    subset(data_ids,year==1988),family="binomial")
fr_init_nonlinear_89_mv<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                            avFD_std+var_std+
                            I(avFD_std^2)+I(var_std^2),
                    subset(data_ids,year==1989),family="binomial")
tab_model(fr_init_nonlinear_87_mv,fr_init_nonlinear_88_mv,
          fr_init_nonlinear_89_mv,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit initiation, nonlinear effects, mean and variance")
Anova(fr_init_nonlinear_87_mv)
Anova(fr_init_nonlinear_88_mv)
Anova(fr_init_nonlinear_89_mv) 
```

## SEEDS ESCAPING PREDATION

### Yearly models

#### Linear effects

##### Same n

```{r}
seed_escpred_linear_87_mv2<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std,
                            subset(data_ids,year==1987&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
seed_escpred_linear_88_mv2<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std,
                            subset(data_ids,year==1988&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
seed_escpred_linear_89_mv2<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std,
                            subset(data_ids,year==1989&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
tab_model(seed_escpred_linear_87_mv2,seed_escpred_linear_88_mv2,
          seed_escpred_linear_89_mv2,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Seeds escaping predation, linear effects, mean and variance")
Anova(seed_escpred_linear_87_mv2)
Anova(seed_escpred_linear_88_mv2)
Anova(seed_escpred_linear_89_mv2)
```

##### Larger n

```{r}
seed_escpred_linear_87_mv<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std,
                            subset(data_ids,year==1987),family="binomial")
seed_escpred_linear_88_mv<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std,
                            subset(data_ids,year==1988),family="binomial")
seed_escpred_linear_89_mv<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std,
                            subset(data_ids,year==1989),family="binomial")
tab_model(seed_escpred_linear_87_mv,seed_escpred_linear_88_mv,
          seed_escpred_linear_89_mv,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Seeds escaping predation, linear effects, mean and variance")
Anova(seed_escpred_linear_87_mv)
Anova(seed_escpred_linear_88_mv)
Anova(seed_escpred_linear_89_mv)
```

#### Non-linear effects

##### Same n

```{r}
seed_escpred_nonlinear_87_mv2<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+
                                 I(avFD_std^2)+I(var_std^2),
                               subset(data_ids,year==1987&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
seed_escpred_nonlinear_88_mv2<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+
                                 I(avFD_std^2)+I(var_std^2),
                               subset(data_ids,year==1988&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
seed_escpred_nonlinear_89_mv2<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+
                                 I(avFD_std^2)+I(var_std^2),
                               subset(data_ids,year==1989&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
tab_model(seed_escpred_nonlinear_87_mv2,seed_escpred_nonlinear_88_mv2,
          seed_escpred_nonlinear_89_mv2,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Seeds escaping predation, nonlinear effects, mean and variance")
Anova(seed_escpred_nonlinear_87_mv2)
Anova(seed_escpred_nonlinear_88_mv2)
Anova(seed_escpred_nonlinear_89_mv2) 
```

##### Larger n

```{r}
seed_escpred_nonlinear_87_mv<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+
                                 I(avFD_std^2)+I(var_std^2),
                               subset(data_ids,year==1987),family="binomial")
seed_escpred_nonlinear_88_mv<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+
                                 I(avFD_std^2)+I(var_std^2),
                               subset(data_ids,year==1988),family="binomial")
seed_escpred_nonlinear_89_mv<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+
                                 I(avFD_std^2)+I(var_std^2),
                               subset(data_ids,year==1989),family="binomial")
tab_model(seed_escpred_nonlinear_87_mv,seed_escpred_nonlinear_88_mv,
          seed_escpred_nonlinear_89_mv,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Seeds escaping predation, nonlinear effects, mean and variance")
Anova(seed_escpred_nonlinear_87_mv)
Anova(seed_escpred_nonlinear_88_mv)
Anova(seed_escpred_nonlinear_89_mv) 
```

## PHENOTYPIC SELECTION with n_fl

### Yearly models

#### Linear effects

##### Same n

```{r}
sel_nfl_linear_87_mv2<-lm(fitness_rel~avFD_std+var_std+
                        n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)))
sel_nfl_linear_88_mv2<-lm(fitness_rel~avFD_std+var_std+
                        n_fl_log_std,
                      subset(data_ids,year==1988&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)))
sel_nfl_linear_89_mv2<-lm(fitness_rel~avFD_std+var_std+
                        n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)))
tab_model(sel_nfl_linear_87_mv2,sel_nfl_linear_88_mv2,sel_nfl_linear_89_mv2,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Selection, linear effects, mean and variance")
Anova(sel_nfl_linear_87_mv2)
Anova(sel_nfl_linear_88_mv2)
Anova(sel_nfl_linear_89_mv2)
```

###### BCA intervals

####### 1987

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_87_mv2) coef(sel_nfl_linear_87_mv2)[2]
b <- car::Boot(sel_nfl_linear_87_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_87_mv2) coef(sel_nfl_linear_87_mv2)[3]
b <- car::Boot(sel_nfl_linear_87_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_87_mv2) coef(sel_nfl_linear_87_mv2)[4]
b <- car::Boot(sel_nfl_linear_87_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_87_mv2 <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_87_mv2)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_87_mv2)<-c("avFD_std","var_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_87_mv2,file="output/BCIs_sel_nfl_linear_87_mv2.RData")
```

```{r}
BCIs_sel_nfl_linear_87_mv2
```

####### 1988

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_88_mv2) coef(sel_nfl_linear_88_mv2)[2]
b <- car::Boot(sel_nfl_linear_88_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_88_mv2) coef(sel_nfl_linear_88_mv2)[3]
b <- car::Boot(sel_nfl_linear_88_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_88_mv2) coef(sel_nfl_linear_88_mv2)[4]
b <- car::Boot(sel_nfl_linear_88_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_88_mv2 <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_88_mv2)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_88_mv2)<-c("avFD_std","var_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_88_mv2,file="output/BCIs_sel_nfl_linear_88_mv2.RData")
```

```{r}
BCIs_sel_nfl_linear_88_mv2
```

####### 1989

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_89_mv2) coef(sel_nfl_linear_89_mv2)[2]
b <- car::Boot(sel_nfl_linear_89_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_89_mv2) coef(sel_nfl_linear_89_mv2)[3]
b <- car::Boot(sel_nfl_linear_89_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_89_mv2) coef(sel_nfl_linear_89_mv2)[4]
b <- car::Boot(sel_nfl_linear_89_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_89_mv2 <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_89_mv2)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_89_mv2)<-c("avFD_std","var_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_89_mv2,file="output/BCIs_sel_nfl_linear_89_mv2.RData")
```

```{r}
BCIs_sel_nfl_linear_89_mv2
```

##### Larger n

```{r}
sel_nfl_linear_87_mv<-lm(fitness_rel~avFD_std+var_std+
                        n_fl_log_std,
                      subset(data_ids,year==1987&
                               !is.na(avFD_std)&!is.na(var_std)))
sel_nfl_linear_88_mv<-lm(fitness_rel~avFD_std+var_std+
                        n_fl_log_std,
                      subset(data_ids,year==1988&
                               !is.na(avFD_std)&!is.na(var_std)))
sel_nfl_linear_89_mv<-lm(fitness_rel~avFD_std+var_std+
                        n_fl_log_std,
                      subset(data_ids,year==1989&
                               !is.na(avFD_std)&!is.na(var_std)))
tab_model(sel_nfl_linear_87_mv,sel_nfl_linear_88_mv,sel_nfl_linear_89_mv,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Selection, linear effects, mean and variance")
Anova(sel_nfl_linear_87_mv)
Anova(sel_nfl_linear_88_mv)
Anova(sel_nfl_linear_89_mv)
```

###### BCA intervals

####### 1987

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_87_mv) coef(sel_nfl_linear_87_mv)[2]
b <- car::Boot(sel_nfl_linear_87_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_87_mv) coef(sel_nfl_linear_87_mv)[3]
b <- car::Boot(sel_nfl_linear_87_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_87_mv) coef(sel_nfl_linear_87_mv)[4]
b <- car::Boot(sel_nfl_linear_87_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_87_mv <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_87_mv)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_87_mv)<-c("avFD_std","var_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_87_mv,file="output/BCIs_sel_nfl_linear_87_mv.RData")
```

```{r}
BCIs_sel_nfl_linear_87_mv
```

####### 1988

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_88_mv) coef(sel_nfl_linear_88_mv)[2]
b <- car::Boot(sel_nfl_linear_88_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_88_mv) coef(sel_nfl_linear_88_mv)[3]
b <- car::Boot(sel_nfl_linear_88_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_88_mv) coef(sel_nfl_linear_88_mv)[4]
b <- car::Boot(sel_nfl_linear_88_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_88_mv <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_88_mv)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_88_mv)<-c("avFD_std","var_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_88_mv,file="output/BCIs_sel_nfl_linear_88_mv.RData")
```

```{r}
BCIs_sel_nfl_linear_88_mv
```

####### 1989

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_89_mv) coef(sel_nfl_linear_89_mv)[2]
b <- car::Boot(sel_nfl_linear_89_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_89_mv) coef(sel_nfl_linear_89_mv)[3]
b <- car::Boot(sel_nfl_linear_89_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_89_mv) coef(sel_nfl_linear_89_mv)[4]
b <- car::Boot(sel_nfl_linear_89_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_89_mv <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_89_mv)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_89_mv)<-c("avFD_std","var_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_89_mv,file="output/BCIs_sel_nfl_linear_89_mv.RData")
```

```{r}
BCIs_sel_nfl_linear_89_mv
```

#### Non-linear effects

##### Same n

```{r}
sel_nfl_nonlinear_87_mv2<-lm(fitness_rel~avFD_std+var_std+
                           n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+I(n_fl_log_std^2),
                         subset(data_ids,year==1987&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)))
sel_nfl_nonlinear_88_mv2<-lm(fitness_rel~avFD_std+var_std+
                           n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+I(n_fl_log_std^2),
                         subset(data_ids,year==1988&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)))
sel_nfl_nonlinear_89_mv2<-lm(fitness_rel~avFD_std+var_std+
                           n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+I(n_fl_log_std^2),
                           subset(data_ids,year==1989&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)))
tab_model(sel_nfl_nonlinear_87_mv2,sel_nfl_nonlinear_88_mv2,
          sel_nfl_nonlinear_89_mv2,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Selection, non-linear effects, mean and variance")
Anova(sel_nfl_nonlinear_87_mv2)
Anova(sel_nfl_nonlinear_88_mv2)
Anova(sel_nfl_nonlinear_89_mv2)
```

###### BCA intervals

####### 1987

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_87_mv2) coef(sel_nfl_nonlinear_87_mv2)[5]
b <- car::Boot(sel_nfl_nonlinear_87_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_87_mv2) coef(sel_nfl_nonlinear_87_mv2)[6]
b <- car::Boot(sel_nfl_nonlinear_87_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_87_mv2) coef(sel_nfl_nonlinear_87_mv2)[7]
b <- car::Boot(sel_nfl_nonlinear_87_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_87_mv2<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_87_mv2)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_87_mv2)<-c("avFD_std2","var_std2",
                                          "n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_87_mv2,
     file="output/BCIs_sel_nfl_nonlinear_87_mv2.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_87_mv2
```

####### 1988

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_88_mv2) coef(sel_nfl_nonlinear_88_mv2)[5]
b <- car::Boot(sel_nfl_nonlinear_88_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_88_mv2) coef(sel_nfl_nonlinear_88_mv2)[6]
b <- car::Boot(sel_nfl_nonlinear_88_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_88_mv2) coef(sel_nfl_nonlinear_88_mv2)[7]
b <- car::Boot(sel_nfl_nonlinear_88_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_88_mv2<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_88_mv2)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_88_mv2)<-c("avFD_std2","var_std2",
                                          "n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_88_mv2,
     file="output/BCIs_sel_nfl_nonlinear_88_mv2.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_88_mv2
```

####### 1989

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_89_mv2) coef(sel_nfl_nonlinear_89_mv2)[5]
b <- car::Boot(sel_nfl_nonlinear_89_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_89_mv2) coef(sel_nfl_nonlinear_89_mv2)[6]
b <- car::Boot(sel_nfl_nonlinear_89_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_89_mv2) coef(sel_nfl_nonlinear_89_mv2)[7]
b <- car::Boot(sel_nfl_nonlinear_89_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_89_mv2<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_89_mv2)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_89_mv2)<-c("avFD_std2","var_std2",
                                          "n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_89_mv2,
     file="output/BCIs_sel_nfl_nonlinear_89_mv2.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_89_mv2
```

##### Larger n

```{r}
sel_nfl_nonlinear_87_mv<-lm(fitness_rel~avFD_std+var_std+
                           n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+I(n_fl_log_std^2),
                         subset(data_ids,year==1987&
                                  !is.na(avFD_std)&!is.na(var_std)))
sel_nfl_nonlinear_88_mv<-lm(fitness_rel~avFD_std+var_std+
                           n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+I(n_fl_log_std^2),
                         subset(data_ids,year==1988&
                                  !is.na(avFD_std)&!is.na(var_std)))
sel_nfl_nonlinear_89_mv<-lm(fitness_rel~avFD_std+var_std+
                           n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+I(n_fl_log_std^2),
                           subset(data_ids,year==1989&
                                    !is.na(avFD_std)&!is.na(var_std)))
tab_model(sel_nfl_nonlinear_87_mv,sel_nfl_nonlinear_88_mv,
          sel_nfl_nonlinear_89_mv,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Selection, non-linear effects, mean and variance")
Anova(sel_nfl_nonlinear_87_mv)
Anova(sel_nfl_nonlinear_88_mv)
Anova(sel_nfl_nonlinear_89_mv)
```

###### BCA intervals

####### 1987

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_87_mv) coef(sel_nfl_nonlinear_87_mv)[5]
b <- car::Boot(sel_nfl_nonlinear_87_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_87_mv) coef(sel_nfl_nonlinear_87_mv)[6]
b <- car::Boot(sel_nfl_nonlinear_87_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_87_mv) coef(sel_nfl_nonlinear_87_mv)[7]
b <- car::Boot(sel_nfl_nonlinear_87_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_87_mv<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_87_mv)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_87_mv)<-c("avFD_std2","var_std2",
                                          "n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_87_mv,
     file="output/BCIs_sel_nfl_nonlinear_87_mv.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_87_mv
```

####### 1988

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_88_mv) coef(sel_nfl_nonlinear_88_mv)[5]
b <- car::Boot(sel_nfl_nonlinear_88_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_88_mv) coef(sel_nfl_nonlinear_88_mv)[6]
b <- car::Boot(sel_nfl_nonlinear_88_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_88_mv) coef(sel_nfl_nonlinear_88_mv)[7]
b <- car::Boot(sel_nfl_nonlinear_88_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_88_mv<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_88_mv)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_88_mv)<-c("avFD_std2","var_std2",
                                          "n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_88_mv,
     file="output/BCIs_sel_nfl_nonlinear_88_mv.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_88_mv
```

####### 1989

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_89_mv) coef(sel_nfl_nonlinear_89_mv)[5]
b <- car::Boot(sel_nfl_nonlinear_89_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_89_mv) coef(sel_nfl_nonlinear_89_mv)[6]
b <- car::Boot(sel_nfl_nonlinear_89_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_89_mv) coef(sel_nfl_nonlinear_89_mv)[7]
b <- car::Boot(sel_nfl_nonlinear_89_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_89_mv<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_89_mv)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_89_mv)<-c("avFD_std2","var_std2",
                                          "n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_89_mv,
     file="output/BCIs_sel_nfl_nonlinear_89_mv.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_89_mv
```

# Univariate GLMs (not used)

## FRUIT INITIATIOM

### Global models

#### Linear

```{r}
fr_init_linear_mean<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+year+ 
                           avFD_std:year,
                         data_ids,family="binomial")
fr_init_linear_var<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std+year+ 
                           var_std:year,
                         data_ids,family="binomial")
fr_init_linear_skew<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std+year+ 
                           skew_std:year,
                         data_ids,family="binomial")
fr_init_linear_kurt<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std+year+ 
                           kurt_std:year,
                         data_ids,family="binomial")
```

```{r}
tab_model(fr_init_linear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, linear effects, mean"))
Anova(fr_init_linear_mean) # Use type II (now) or III?
```

```{r}
tab_model(fr_init_linear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, linear effects, variance"))
Anova(fr_init_linear_var) # Use type II (now) or III?
```

```{r}
tab_model(fr_init_linear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, linear effects, skewness"))
Anova(fr_init_linear_skew) # Use type II (now) or III?
```

```{r}
tab_model(fr_init_linear_kurt,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, linear effects, kurtosis"))
Anova(fr_init_linear_kurt) # Use type II (now) or III?
```

#### Non-linear

```{r}
fr_init_nonlinear_mean<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+
                              I(avFD_std^2)+year+ 
                           avFD_std:year+I(avFD_std^2):year,
                         data_ids,family="binomial")
fr_init_nonlinear_var<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std+
                             I(var_std^2)+year+ 
                           var_std:year+I(var_std^2):year,
                         data_ids,family="binomial")
fr_init_nonlinear_skew<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std+
                              I(skew_std^2)+year+ 
                           skew_std:year+I(skew_std^2):year,
                         data_ids,family="binomial")
fr_init_nonlinear_kurt<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std+
                              I(kurt_std^2)+year+ 
                           kurt_std:year+I(kurt_std^2):year,
                         data_ids,family="binomial")
```

```{r}
tab_model(fr_init_nonlinear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, non-linear effects, mean"))
Anova(fr_init_nonlinear_mean) # Use type II (now) or III?
```

```{r}
tab_model(fr_init_nonlinear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, non-linear effects, variance"))
Anova(fr_init_nonlinear_var) # Use type II (now) or III?
```

```{r}
tab_model(fr_init_nonlinear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, non-linear effects, skewness"))
Anova(fr_init_nonlinear_skew) # Use type II (now) or III?
```

```{r}
tab_model(fr_init_nonlinear_kurt,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, non-linear effects, kurtosis"))
Anova(fr_init_nonlinear_kurt) # Use type II (now) or III?
```

### Yearly models

#### Linear

```{r}
# Mean
fr_init_linear_mean_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std,
                      subset(data_ids,year==1987),family="binomial")
fr_init_linear_mean_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std,
                      subset(data_ids,year==1988),family="binomial")
fr_init_linear_mean_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std,
                      subset(data_ids,year==1989),family="binomial")
# Variance
fr_init_linear_var_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std,
                      subset(data_ids,year==1987),family="binomial")
fr_init_linear_var_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std,
                      subset(data_ids,year==1988),family="binomial")
fr_init_linear_var_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std,
                      subset(data_ids,year==1989),family="binomial")
# Skewness
fr_init_linear_skew_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std,
                      subset(data_ids,year==1987),family="binomial")
fr_init_linear_skew_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std,
                      subset(data_ids,year==1988),family="binomial")
fr_init_linear_skew_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std,
                      subset(data_ids,year==1989),family="binomial")
# Kurtosis
fr_init_linear_kurt_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std,
                      subset(data_ids,year==1987),family="binomial")
fr_init_linear_kurt_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std,
                      subset(data_ids,year==1988),family="binomial")
fr_init_linear_kurt_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std,
                      subset(data_ids,year==1989),family="binomial")
```

```{r}
sdiff_fr_init_linear<-rbind(
  tidy(fr_init_linear_mean_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_linear_mean_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_linear_mean_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(fr_init_linear_var_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_linear_var_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_linear_var_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(fr_init_linear_skew_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_linear_skew_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_linear_skew_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(fr_init_linear_kurt_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_linear_kurt_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_linear_kurt_89)[2,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sdiff=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sdiff,star),predictor=term,type=as.factor("linear"))
```

#### Non-linear

```{r}
# Mean
fr_init_nonlinear_mean_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+
                                 I(avFD_std^2),
                      subset(data_ids,year==1987),family="binomial")
fr_init_nonlinear_mean_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+
                                 I(avFD_std^2),
                      subset(data_ids,year==1988),family="binomial")
fr_init_nonlinear_mean_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+
                                 I(avFD_std^2),
                      subset(data_ids,year==1989),family="binomial")
# Variance
fr_init_nonlinear_var_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std+
                                 I(var_std^2),
                      subset(data_ids,year==1987),family="binomial")
fr_init_nonlinear_var_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std+
                                 I(var_std^2),
                      subset(data_ids,year==1988),family="binomial")
fr_init_nonlinear_var_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std+
                                 I(var_std^2),
                      subset(data_ids,year==1989),family="binomial")
# Skewness
fr_init_nonlinear_skew_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std+
                                 I(skew_std^2),
                      subset(data_ids,year==1987),family="binomial")
fr_init_nonlinear_skew_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std+
                                 I(skew_std^2),
                      subset(data_ids,year==1988),family="binomial")
fr_init_nonlinear_skew_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std+
                                 I(skew_std^2),
                      subset(data_ids,year==1989),family="binomial")
# Kurtosis
fr_init_nonlinear_kurt_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std+
                                 I(kurt_std^2),
                      subset(data_ids,year==1987),family="binomial")
fr_init_nonlinear_kurt_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std+
                                 I(kurt_std^2),
                      subset(data_ids,year==1988),family="binomial")
fr_init_nonlinear_kurt_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std+
                                 I(kurt_std^2),
                      subset(data_ids,year==1989),family="binomial")
```

```{r}
sdiff_fr_init_nonlinear<-rbind(
  tidy(fr_init_nonlinear_mean_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_nonlinear_mean_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_nonlinear_mean_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(fr_init_nonlinear_var_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_nonlinear_var_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_nonlinear_var_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(fr_init_nonlinear_skew_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_nonlinear_skew_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_nonlinear_skew_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(fr_init_nonlinear_kurt_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_nonlinear_kurt_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_nonlinear_kurt_89)[3,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sdiff=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sdiff,star),
         predictor=str_extract(term, "(?<=I\\().*?(?=\\^2\\))"),
         type=as.factor("nonlinear"))
```

## SEEDS ESCAPING PREDATION

### Global models

#### Linear

```{r}
seeds_escpred_linear_mean<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~avFD_std+year+ 
                           avFD_std:year,
                         data_ids,family="binomial")
seeds_escpred_linear_var<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~var_std+year+ 
                           var_std:year,
                         data_ids,family="binomial")
seeds_escpred_linear_skew<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~skew_std+year+ 
                           skew_std:year,
                         data_ids,family="binomial")
seeds_escpred_linear_kurt<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~kurt_std+year+ 
                           kurt_std:year,
                         data_ids,family="binomial")
```

```{r}
tab_model(seeds_escpred_linear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, linear effects, mean"))
Anova(seeds_escpred_linear_mean) # Use type II (now) or III?
```

```{r}
tab_model(seeds_escpred_linear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, linear effects, variance"))
Anova(seeds_escpred_linear_var) # Use type II (now) or III?
```

```{r}
tab_model(seeds_escpred_linear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, linear effects, skewness"))
Anova(seeds_escpred_linear_skew) # Use type II (now) or III?
```

```{r}
tab_model(seeds_escpred_linear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, linear effects, kurtosis"))
Anova(seeds_escpred_linear_kurt) # Use type II (now) or III?
```

#### Non-linear

```{r}
seeds_escpred_nonlinear_mean<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~avFD_std+I(avFD_std^2)+
                                    year+ 
                           avFD_std:year+I(avFD_std^2):year,
                         data_ids,family="binomial")
seeds_escpred_nonlinear_var<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~var_std+I(var_std^2)+
                                   year+ 
                           var_std:year+I(var_std^2):year,
                         data_ids,family="binomial")
seeds_escpred_nonlinear_skew<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~skew_std+I(skew_std^2)+
                                    year+ 
                           skew_std:year+I(skew_std^2):year,
                         data_ids,family="binomial")
seeds_escpred_nonlinear_kurt<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~kurt_std+I(kurt_std^2)+
                                    year+ 
                           kurt_std:year+I(kurt_std^2):year,
                         data_ids,family="binomial")
```

```{r}
tab_model(seeds_escpred_nonlinear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, non-linear effects, mean"))
Anova(seeds_escpred_nonlinear_mean) # Use type II (now) or III?
```

```{r}
tab_model(seeds_escpred_nonlinear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, non-linear effects, variance"))
Anova(seeds_escpred_nonlinear_var) # Use type II (now) or III?
```

```{r}
tab_model(seeds_escpred_nonlinear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, non-linear effects, skewness"))
Anova(seeds_escpred_nonlinear_skew) # Use type II (now) or III?
```

```{r}
tab_model(seeds_escpred_nonlinear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, non-linear effects, kurtosis"))
Anova(seeds_escpred_nonlinear_kurt) # Use type II (now) or III?
```

### Yearly models

#### Linear

```{r}
# Mean
seeds_escpred_linear_mean_87<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),
                                        pr_seeds=round(n_preyed_seed))~
                                    avFD_std,
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_mean_88<-glm(cbind(npr_seeds=round(n_seed)-   
                                          round(n_preyed_seed),    
                                        pr_seeds=round(n_preyed_seed))~
                                    avFD_std,
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_mean_89<-glm(cbind(npr_seeds=round(n_seed)- 
                                          round(n_preyed_seed),      
                                        pr_seeds=round(n_preyed_seed))
                                  ~avFD_std,
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
# Variance
seeds_escpred_linear_var_87<-glm(cbind(npr_seeds=round(n_seed)- 
                                         round(n_preyed_seed),     
                                       pr_seeds=round(n_preyed_seed))~
                                   var_std,
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_var_88<-glm(cbind(npr_seeds=round(n_seed)-  
                                         round(n_preyed_seed),    
                                       pr_seeds=round(n_preyed_seed))~
                                   var_std,
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_var_89<-glm(cbind(npr_seeds=round(n_seed)-  
                                         round(n_preyed_seed),     
                                       pr_seeds=round(n_preyed_seed))~
                                   var_std,
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
# Skewness
seeds_escpred_linear_skew_87<-glm(cbind(npr_seeds=round(n_seed)- 
                                          round(n_preyed_seed),       
                                        pr_seeds=round(n_preyed_seed))~
                                    skew_std,
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_skew_88<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),   
                                        pr_seeds=round(n_preyed_seed))~
                                    skew_std,
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_skew_89<-glm(cbind(npr_seeds=round(n_seed)-   
                                          round(n_preyed_seed),     
                                        pr_seeds=round(n_preyed_seed))~
                                    skew_std,
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
# Kurtosis
seeds_escpred_linear_kurt_87<-glm(cbind(npr_seeds=round(n_seed)- 
                                          round(n_preyed_seed),     
                                        pr_seeds=round(n_preyed_seed))~
                                    kurt_std,
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_kurt_88<-glm(cbind(npr_seeds=round(n_seed)-     
                                          round(n_preyed_seed),       
                                        pr_seeds=round(n_preyed_seed))~
                                    kurt_std,
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_kurt_89<-glm(cbind(npr_seeds=round(n_seed)-     
                                          round(n_preyed_seed),      
                                        pr_seeds=round(n_preyed_seed))~
                                    kurt_std,
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
```

```{r}
sdiff_seeds_escpred_linear<-rbind(
  tidy(seeds_escpred_linear_mean_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_linear_mean_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_linear_mean_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(seeds_escpred_linear_var_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_linear_var_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_linear_var_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(seeds_escpred_linear_skew_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_linear_skew_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_linear_skew_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(seeds_escpred_linear_kurt_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_linear_kurt_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_linear_kurt_89)[2,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sdiff=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sdiff,star),predictor=term,type=as.factor("linear"))
```

#### Non-linear

```{r}
# Mean
seeds_escpred_nonlinear_mean_87<-glm(cbind(npr_seeds=round(n_seed)- 
                                             round(n_preyed_seed),    
                                           pr_seeds=round(n_preyed_seed))~
                                       avFD_std+I(avFD_std^2),
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_mean_88<-glm(cbind(npr_seeds=round(n_seed)-  
                                             round(n_preyed_seed), 
                                           pr_seeds=round(n_preyed_seed))~
                                       avFD_std+I(avFD_std^2),
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_mean_89<-glm(cbind(npr_seeds=round(n_seed)- 
                                             round(n_preyed_seed), 
                                           pr_seeds=round(n_preyed_seed))~
                                       avFD_std+I(avFD_std^2),
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
# Variance
seeds_escpred_nonlinear_var_87<-glm(cbind(npr_seeds=round(n_seed)- 
                                            round(n_preyed_seed),  
                                          pr_seeds=round(n_preyed_seed))~
                                      var_std+I(var_std^2),
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_var_88<-glm(cbind(npr_seeds=round(n_seed)-   
                                            round(n_preyed_seed),    
                                          pr_seeds=round(n_preyed_seed))~
                                      var_std+I(var_std^2),
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_var_89<-glm(cbind(npr_seeds=round(n_seed)- 
                                            round(n_preyed_seed),  
                                          pr_seeds=round(n_preyed_seed))~
                                      var_std+I(var_std^2),
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
# Skewness
seeds_escpred_nonlinear_skew_87<-glm(cbind(npr_seeds=round(n_seed)-  
                                             round(n_preyed_seed), 
                                           pr_seeds=round(n_preyed_seed))~
                                       skew_std+I(skew_std^2),
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_skew_88<-glm(cbind(npr_seeds=round(n_seed)-
                                             round(n_preyed_seed),   
                                           pr_seeds=round(n_preyed_seed))~
                                       skew_std+I(skew_std^2),
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_skew_89<-glm(cbind(npr_seeds=round(n_seed)- 
                                             round(n_preyed_seed),  
                                           pr_seeds=round(n_preyed_seed))~
                                       skew_std+I(skew_std^2),
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
# Kurtosis
seeds_escpred_nonlinear_kurt_87<-glm(cbind(npr_seeds=round(n_seed)- 
                                             round(n_preyed_seed),      
                                           pr_seeds=round(n_preyed_seed))~
                                       kurt_std+I(kurt_std^2),
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_kurt_88<-glm(cbind(npr_seeds=round(n_seed)- 
                                             round(n_preyed_seed),  
                                           pr_seeds=round(n_preyed_seed))~
                                       kurt_std+I(kurt_std^2),
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_kurt_89<-glm(cbind(npr_seeds=round(n_seed)-   
                                             round(n_preyed_seed),   
                                           pr_seeds=round(n_preyed_seed))~
                                       kurt_std+I(kurt_std^2),
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
```

```{r}
sdiff_seeds_escpred_nonlinear<-rbind(
  tidy(seeds_escpred_nonlinear_mean_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_nonlinear_mean_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_nonlinear_mean_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(seeds_escpred_nonlinear_var_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_nonlinear_var_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_nonlinear_var_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(seeds_escpred_nonlinear_skew_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_nonlinear_skew_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_nonlinear_skew_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(seeds_escpred_nonlinear_kurt_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_nonlinear_kurt_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_nonlinear_kurt_89)[3,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sdiff=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sdiff,star),
         predictor=str_extract(term, "(?<=I\\().*?(?=\\^2\\))"),
         type=as.factor("nonlinear"))
```

## PHENOTYPIC SELECTION

### Global models

#### Linear

```{r}
sel_linear_mean<-lm(fitness_rel~avFD_std+year+ 
                           avFD_std:year,
                         subset(data_ids,!is.na(avFD_std)))
sel_linear_var<-lm(fitness_rel~var_std+year+ 
                           var_std:year,
                         subset(data_ids,!is.na(var_std)))
sel_linear_skew<-lm(fitness_rel~skew_std+year+ 
                           skew_std:year,
                         subset(data_ids,!is.na(skew_std)))
sel_linear_kurt<-lm(fitness_rel~kurt_std+year+ 
                           kurt_std:year,
                         subset(data_ids,!is.na(kurt_std)))
```

```{r}
tab_model(sel_linear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, linear effects, mean"))
Anova(sel_linear_mean) # Use type II (now) or III?
```

```{r}
tab_model(sel_linear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, linear effects, variance"))
Anova(sel_linear_var) # Use type II (now) or III?
```

```{r}
tab_model(sel_linear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, linear effects, skewness"))
Anova(sel_linear_skew) # Use type II (now) or III?
```

```{r}
tab_model(sel_linear_kurt,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, linear effects, kurtosis"))
Anova(sel_linear_kurt) # Use type II (now) or III?
```

#### Non-linear

```{r}
sel_nonlinear_mean<-lm(fitness_rel~avFD_std+year+I(avFD_std^2)+ 
                           avFD_std:year+I(avFD_std^2):year,
                         subset(data_ids,!is.na(avFD_std)))
sel_nonlinear_var<-lm(fitness_rel~var_std+year+I(var_std^2)+  
                           var_std:year+I(var_std^2):year,
                         subset(data_ids,!is.na(var_std)))
sel_nonlinear_skew<-lm(fitness_rel~skew_std+year+I(skew_std^2)+ 
                           skew_std:year+I(skew_std^2):year,
                         subset(data_ids,!is.na(skew_std)))
sel_nonlinear_kurt<-lm(fitness_rel~kurt_std+year+I(kurt_std^2)+  
                           kurt_std:year+I(kurt_std^2):year,
                         subset(data_ids,!is.na(kurt_std)))
```

```{r}
tab_model(sel_nonlinear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, mean"))
Anova(sel_nonlinear_mean) # Use type II (now) or III?
```

```{r}
tab_model(sel_nonlinear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, variance"))
Anova(sel_nonlinear_var) # Use type II (now) or III?
```

```{r}
tab_model(sel_nonlinear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, skewness"))
Anova(sel_nonlinear_skew) # Use type II (now) or III?
```

```{r}
tab_model(sel_nonlinear_kurt,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, kurtosis"))
Anova(sel_nonlinear_kurt) # Use type II (now) or III?
```

### Yearly models

#### Linear

```{r}
# Mean
sel_linear_mean_87<-lm(fitness_rel~avFD_std,
                      subset(data_ids,year==1987&!is.na(avFD_std)))
sel_linear_mean_88<-lm(fitness_rel~avFD_std,
                      subset(data_ids,year==1989&!is.na(avFD_std)))
sel_linear_mean_89<-lm(fitness_rel~avFD_std,
                      subset(data_ids,year==1989&!is.na(avFD_std)))
# Variance
sel_linear_var_87<-lm(fitness_rel~var_std,
                      subset(data_ids,year==1987&!is.na(var_std)))
sel_linear_var_88<-lm(fitness_rel~var_std,
                      subset(data_ids,year==1989&!is.na(var_std)))
sel_linear_var_89<-lm(fitness_rel~var_std,
                      subset(data_ids,year==1989&!is.na(var_std)))
# Skewness
sel_linear_skew_87<-lm(fitness_rel~skew_std,
                      subset(data_ids,year==1987&!is.na(skew_std)))
sel_linear_skew_88<-lm(fitness_rel~skew_std,
                      subset(data_ids,year==1989&!is.na(skew_std)))
sel_linear_skew_89<-lm(fitness_rel~skew_std,
                      subset(data_ids,year==1989&!is.na(skew_std)))
# Kurtosis
sel_linear_kurt_87<-lm(fitness_rel~kurt_std,
                      subset(data_ids,year==1987&!is.na(kurt_std)))
sel_linear_kurt_88<-lm(fitness_rel~kurt_std,
                      subset(data_ids,year==1989&!is.na(kurt_std)))
sel_linear_kurt_89<-lm(fitness_rel~kurt_std,
                      subset(data_ids,year==1989&!is.na(kurt_std)))
```

```{r}
sdiff_sel_linear<-rbind(
  tidy(sel_linear_mean_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_linear_mean_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_linear_mean_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(sel_linear_var_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_linear_var_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_linear_var_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(sel_linear_skew_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_linear_skew_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_linear_skew_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(sel_linear_kurt_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_linear_kurt_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_linear_kurt_89)[2,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sdiff=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sdiff,star),predictor=term,type=as.factor("linear"))
```

#### Non-linear

```{r}
# Mean
sel_nonlinear_mean_87<-lm(fitness_rel~avFD_std+I(avFD_std^2),
                      subset(data_ids,year==1987&!is.na(avFD_std)))
sel_nonlinear_mean_88<-lm(fitness_rel~avFD_std+I(avFD_std^2),
                      subset(data_ids,year==1989&!is.na(avFD_std)))
sel_nonlinear_mean_89<-lm(fitness_rel~avFD_std+I(avFD_std^2),
                      subset(data_ids,year==1989&!is.na(avFD_std)))
# Variance
sel_nonlinear_var_87<-lm(fitness_rel~var_std+I(var_std^2),
                      subset(data_ids,year==1987&!is.na(var_std)))
sel_nonlinear_var_88<-lm(fitness_rel~var_std+I(var_std^2),
                      subset(data_ids,year==1989&!is.na(var_std)))
sel_nonlinear_var_89<-lm(fitness_rel~var_std+I(var_std^2),
                      subset(data_ids,year==1989&!is.na(var_std)))
# Skewness
sel_nonlinear_skew_87<-lm(fitness_rel~skew_std+I(skew_std^2),
                      subset(data_ids,year==1987&!is.na(skew_std)))
sel_nonlinear_skew_88<-lm(fitness_rel~skew_std+I(skew_std^2),
                      subset(data_ids,year==1989&!is.na(skew_std)))
sel_nonlinear_skew_89<-lm(fitness_rel~skew_std+I(skew_std^2),
                      subset(data_ids,year==1989&!is.na(skew_std)))
# Kurtosis
sel_nonlinear_kurt_87<-lm(fitness_rel~kurt_std+I(kurt_std^2),
                      subset(data_ids,year==1987&!is.na(kurt_std)))
sel_nonlinear_kurt_88<-lm(fitness_rel~kurt_std+I(kurt_std^2),
                      subset(data_ids,year==1989&!is.na(kurt_std)))
sel_nonlinear_kurt_89<-lm(fitness_rel~kurt_std+I(kurt_std^2),
                      subset(data_ids,year==1989&!is.na(kurt_std)))
```

```{r}
sdiff_sel_nonlinear<-rbind(
  tidy(sel_nonlinear_mean_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nonlinear_mean_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nonlinear_mean_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nonlinear_var_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nonlinear_var_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nonlinear_var_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nonlinear_skew_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nonlinear_skew_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nonlinear_skew_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nonlinear_kurt_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nonlinear_kurt_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nonlinear_kurt_89)[3,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sdiff=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sdiff,star),
         predictor=str_extract(term, "(?<=I\\().*?(?=\\^2\\))"),
         type=as.factor("nonlinear"))
```

## PHENOTYPIC SELECTION with n_fl

### Global models

#### Linear

```{r}
sel_nfl_linear_mean<-lm(fitness_rel~avFD_std+year+n_fl_log_std+
                           avFD_std:year,
                         subset(data_ids,!is.na(avFD_std)))
sel_nfl_linear_var<-lm(fitness_rel~var_std+year+n_fl_log_std+ 
                           var_std:year,
                         subset(data_ids,!is.na(var_std)))
sel_nfl_linear_skew<-lm(fitness_rel~skew_std+year+n_fl_log_std+ 
                           skew_std:year,
                         subset(data_ids,!is.na(skew_std)))
sel_nfl_linear_kurt<-lm(fitness_rel~kurt_std+year+n_fl_log_std+ 
                           kurt_std:year,
                         subset(data_ids,!is.na(kurt_std)))
```

```{r}
tab_model(sel_nfl_linear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection with nfl, linear effects, mean"))
Anova(sel_nfl_linear_mean) # Use type II (now) or III?
```

```{r}
tab_model(sel_nfl_linear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection with nfl, linear effects, variance"))
Anova(sel_nfl_linear_var) # Use type II (now) or III?
```

```{r}
tab_model(sel_nfl_linear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection with nfl, linear effects, skewness"))
Anova(sel_nfl_linear_skew) # Use type II (now) or III?
```

```{r}
tab_model(sel_nfl_linear_kurt,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection with nfl, linear effects, kurtosis"))
Anova(sel_nfl_linear_kurt) # Use type II (now) or III?
```

#### Non-linear

```{r}
sel_nfl_nonlinear_mean<-lm(fitness_rel~avFD_std+year+I(avFD_std^2)+
                             n_fl_log_std+ 
                           avFD_std:year+I(avFD_std^2):year,
                         subset(data_ids,!is.na(avFD_std)))
sel_nfl_nonlinear_var<-lm(fitness_rel~var_std+year+I(var_std^2)+
                            n_fl_log_std+  
                           var_std:year+I(var_std^2):year,
                         subset(data_ids,!is.na(var_std)))
sel_nfl_nonlinear_skew<-lm(fitness_rel~skew_std+year+I(skew_std^2)+
                             n_fl_log_std+ 
                           skew_std:year+I(skew_std^2):year,
                         subset(data_ids,!is.na(skew_std)))
sel_nfl_nonlinear_kurt<-lm(fitness_rel~kurt_std+year+I(kurt_std^2)+
                             n_fl_log_std+  
                           kurt_std:year+I(kurt_std^2):year,
                         subset(data_ids,!is.na(kurt_std)))
```

```{r}
tab_model(sel_nfl_nonlinear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, mean"))
Anova(sel_nfl_nonlinear_mean) # Use type II (now) or III?
```

```{r}
tab_model(sel_nfl_nonlinear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, variance"))
Anova(sel_nfl_nonlinear_var) # Use type II (now) or III?
```

```{r}
tab_model(sel_nfl_nonlinear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, skewness"))
Anova(sel_nfl_nonlinear_skew) # Use type II (now) or III?
```

```{r}
tab_model(sel_nfl_nonlinear_kurt,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, kurtosis"))
Anova(sel_nfl_linear_kurt) # Use type II (now) or III?
```

### Yearly models

#### Linear

```{r}
# Mean
sel_nfl_linear_mean_87<-lm(fitness_rel~avFD_std+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(avFD_std)))
sel_nfl_linear_mean_88<-lm(fitness_rel~avFD_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(avFD_std)))
sel_nfl_linear_mean_89<-lm(fitness_rel~avFD_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(avFD_std)))
# Variance
sel_nfl_linear_var_87<-lm(fitness_rel~var_std+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(var_std)))
sel_nfl_linear_var_88<-lm(fitness_rel~var_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(var_std)))
sel_nfl_linear_var_89<-lm(fitness_rel~var_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(var_std)))
# Skewness
sel_nfl_linear_skew_87<-lm(fitness_rel~skew_std+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(skew_std)))
sel_nfl_linear_skew_88<-lm(fitness_rel~skew_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(skew_std)))
sel_nfl_linear_skew_89<-lm(fitness_rel~skew_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(skew_std)))
# Kurtosis
sel_nfl_linear_kurt_87<-lm(fitness_rel~kurt_std+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(kurt_std)))
sel_nfl_linear_kurt_88<-lm(fitness_rel~kurt_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(kurt_std)))
sel_nfl_linear_kurt_89<-lm(fitness_rel~kurt_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(kurt_std)))
```

```{r}
sgrad_sel_nfl_linear<-rbind(
  tidy(sel_nfl_linear_mean_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_linear_mean_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_linear_mean_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nfl_linear_var_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_linear_var_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_linear_var_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nfl_linear_skew_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_linear_skew_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_linear_skew_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nfl_linear_kurt_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_linear_kurt_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_linear_kurt_89)[2,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sgrad=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sgrad,star),predictor=term,type=as.factor("linear"))
```

#### Non-linear

```{r}
# Mean
sel_nfl_nonlinear_mean_87<-lm(fitness_rel~avFD_std+I(avFD_std^2)+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(avFD_std)))
sel_nfl_nonlinear_mean_88<-lm(fitness_rel~avFD_std+I(avFD_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(avFD_std)))
sel_nfl_nonlinear_mean_89<-lm(fitness_rel~avFD_std+I(avFD_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(avFD_std)))
# Variance
sel_nfl_nonlinear_var_87<-lm(fitness_rel~var_std+I(var_std^2)+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(var_std)))
sel_nfl_nonlinear_var_88<-lm(fitness_rel~var_std+I(var_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(var_std)))
sel_nfl_nonlinear_var_89<-lm(fitness_rel~var_std+I(var_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(var_std)))
# Skewness
sel_nfl_nonlinear_skew_87<-lm(fitness_rel~skew_std+I(skew_std^2)+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(skew_std)))
sel_nfl_nonlinear_skew_88<-lm(fitness_rel~skew_std+I(skew_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(skew_std)))
sel_nfl_nonlinear_skew_89<-lm(fitness_rel~skew_std+I(skew_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(skew_std)))
# Kurtosis
sel_nfl_nonlinear_kurt_87<-lm(fitness_rel~kurt_std+I(kurt_std^2)+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(kurt_std)))
sel_nfl_nonlinear_kurt_88<-lm(fitness_rel~kurt_std+I(kurt_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(kurt_std)))
sel_nfl_nonlinear_kurt_89<-lm(fitness_rel~kurt_std+I(kurt_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(kurt_std)))
```

```{r}
sgrad_sel_nfl_nonlinear<-rbind(
  tidy(sel_nfl_nonlinear_mean_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_nonlinear_mean_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_nonlinear_mean_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nfl_nonlinear_var_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_nonlinear_var_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_nonlinear_var_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nfl_nonlinear_skew_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_nonlinear_skew_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_nonlinear_skew_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nfl_nonlinear_kurt_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_nonlinear_kurt_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_nonlinear_kurt_89)[3,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sgrad=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sgrad,star),
         predictor=str_extract(term, "(?<=I\\().*?(?=\\^2\\))"),
         type=as.factor("nonlinear"))
```

# Figures

## With univariate model predictions

### Extract predictions from univariate GLMs

```{r}
prediction_fr_init_linear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(fr_init_linear_mean_87,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_linear_mean_88,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_linear_mean_89,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(fr_init_linear_var_87,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_linear_var_88,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_linear_var_89,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(fr_init_linear_skew_87,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_linear_skew_88,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_linear_skew_89,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(fr_init_linear_kurt_87,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_linear_kurt_88,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_linear_kurt_89,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sdiff_fr_init_linear%>%
              dplyr::select(predictor,sdiff,year,signif,star,print,type))
```

```{r}
prediction_fr_init_nonlinear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(fr_init_nonlinear_mean_87,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_nonlinear_mean_88,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_nonlinear_mean_89,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(fr_init_nonlinear_var_87,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_nonlinear_var_88,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_nonlinear_var_89,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(fr_init_nonlinear_skew_87,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_nonlinear_skew_88,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_nonlinear_skew_89,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(fr_init_nonlinear_kurt_87,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_nonlinear_kurt_88,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_nonlinear_kurt_89,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sdiff_fr_init_nonlinear%>%
              dplyr::select(predictor,sdiff,year,signif,star,print,type))
```

```{r}
prediction_fr_init_univar<-rbind(prediction_fr_init_linear_univar,
                                 prediction_fr_init_nonlinear_univar)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")))
```

```{r}
prediction_seeds_escpred_linear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(seeds_escpred_linear_mean_87,
                         terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_linear_mean_88,
                         terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_linear_mean_89,
                         terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(seeds_escpred_linear_var_87,
                         terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_linear_var_88,
                         terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_linear_var_89,
                         terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(seeds_escpred_linear_skew_87,
                         terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_linear_skew_88,
                         terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_linear_skew_89,
                         terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(seeds_escpred_linear_kurt_87,
                         terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_linear_kurt_88,
                         terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_linear_kurt_89,
                         terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sdiff_seeds_escpred_linear%>%
              dplyr::select(predictor,sdiff,year,signif,star,print,type))
```

```{r}
prediction_seeds_escpred_nonlinear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(seeds_escpred_nonlinear_mean_87,
                         terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_nonlinear_mean_88,
                         terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_nonlinear_mean_89,
                         terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(seeds_escpred_nonlinear_var_87,
                         terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_nonlinear_var_88,
                         terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_nonlinear_var_89,
                         terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(seeds_escpred_nonlinear_skew_87,
                         terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_nonlinear_skew_88,
                         terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_nonlinear_skew_89,
                         terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(seeds_escpred_nonlinear_kurt_87,
                         terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_nonlinear_kurt_88,
                         terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_nonlinear_kurt_89,
                         terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sdiff_seeds_escpred_nonlinear%>%
              dplyr::select(predictor,sdiff,year,signif,star,print,type))
```

```{r}
prediction_seeds_escpred_univar<-rbind(prediction_seeds_escpred_linear_univar,
                                 prediction_seeds_escpred_nonlinear_univar)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")))
```

```{r}
prediction_sel_linear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(sel_linear_mean_87,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_linear_mean_88,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_linear_mean_89,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(sel_linear_var_87,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_linear_var_88,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_linear_var_89,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(sel_linear_skew_87,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_linear_skew_88,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_linear_skew_89,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(sel_linear_kurt_87,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_linear_kurt_88,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_linear_kurt_89,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sdiff_sel_linear%>%
              dplyr::select(predictor,sdiff,year,signif,star,print,type))
```

```{r}
prediction_sel_nonlinear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(sel_nonlinear_mean_87,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nonlinear_mean_88,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nonlinear_mean_89,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(sel_nonlinear_var_87,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nonlinear_var_88,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nonlinear_var_89,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(sel_nonlinear_skew_87,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nonlinear_skew_88,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nonlinear_skew_89,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(sel_nonlinear_kurt_87,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nonlinear_kurt_88,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nonlinear_kurt_89,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sdiff_sel_nonlinear%>%
              dplyr::select(predictor,sdiff,year,signif,star,print,type))
```

```{r}
prediction_sel_univar<-rbind(prediction_sel_linear_univar,
                                 prediction_sel_nonlinear_univar)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")))
```

```{r}
prediction_sel_nfl_linear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(sel_nfl_linear_mean_87,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nfl_linear_mean_88,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nfl_linear_mean_89,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(sel_nfl_linear_var_87,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nfl_linear_var_88,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nfl_linear_var_89,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(sel_nfl_linear_skew_87,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nfl_linear_skew_88,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_linear_skew_89,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(sel_nfl_linear_kurt_87,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nfl_linear_kurt_88,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nfl_linear_kurt_89,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sgrad_sel_nfl_linear%>%
              dplyr::select(predictor,sgrad,year,signif,star,print,type))
```

```{r}
prediction_sel_nfl_nonlinear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(sel_nfl_nonlinear_mean_87,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nonlinear_mean_88,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nfl_nonlinear_mean_89,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(sel_nfl_nonlinear_var_87,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nfl_nonlinear_var_88,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nfl_nonlinear_var_89,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(sel_nfl_nonlinear_skew_87,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nfl_nonlinear_skew_88,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nfl_nonlinear_skew_89,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(sel_nfl_nonlinear_kurt_87,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nfl_nonlinear_kurt_88,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nfl_nonlinear_kurt_89,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sgrad_sel_nfl_nonlinear%>%
              dplyr::select(predictor,sgrad,year,signif,star,print,type))
```

```{r}
prediction_sel_nfl_univar<-rbind(prediction_sel_nfl_linear_univar,
                                 prediction_sel_nfl_nonlinear_univar)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")))
```

### Figure 2 (not used)

Figure based on predictions of yearly univariate models (selection differentials).

```{r}
predictor.labs<-c("Mean","Variance","Skewness","Kurtosis")
names(predictor.labs)<-c("avFD_std","var_std","skew_std","kurt_std")
fig2<-ggplot()+
  geom_point(data=data_ids%>%
               dplyr::select(year,fr_init,avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
                            names_to="predictor",values_to="value_predictor")%>%
               mutate(predictor=factor(predictor,
                                       levels=c("avFD_std","var_std",
                                                "skew_std","kurt_std"))),
             aes(x=value_predictor,y=fr_init),
             size=2,alpha=0.3)+
  facet_grid2(c("year","predictor"), 
              labeller=labeller(predictor=predictor.labs), 
              scales = "free", independent = "all")+
  geom_ribbon(data=prediction_fr_init_univar,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=type),
              alpha=0.3)+
  geom_line(data=prediction_fr_init_univar,
            aes(x=x,y=predicted,linetype=signif,color=type),
            linewidth=1)+
  scale_linetype_manual(values=c("dotted", "solid"))+
  ylab("Proportion of flowers that developed to fruits")+
  xlab("Value of the moment")+
  my_theme()+
  geom_text(data=prediction_fr_init_univar%>%
              dplyr::select(year,predictor,print,type)%>%
              distinct()%>%
              pivot_wider(names_from=type,values_from=print)%>%
              mutate(print=paste("L = ",linear,"\n","NL =", nonlinear)),
            aes(x=Inf,y=Inf,label=print),
             hjust=1.05, vjust=1.2,family="serif")
fig2
#ggsave(file="output/figures/fig2.tiff", plot=fig2, width=10, height=7)
```

### Figure 3 (not used)

Figure based on predictions of yearly univariate models (selection differentials).

```{r}
fig3<-ggplot()+
  geom_point(data=data_ids%>%
               dplyr::select(year,prop_seed_preyed,
                      avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
                            names_to="predictor",values_to="value_predictor")%>%
               mutate(predictor=factor(predictor,
                                       levels=c("avFD_std","var_std",
                                                "skew_std","kurt_std")))%>%
               filter(!is.na(prop_seed_preyed)),
             aes(x=value_predictor,y=1-prop_seed_preyed),
             size=2,alpha=0.3)+
  facet_grid2(c("year","predictor"), 
              labeller=labeller(predictor=predictor.labs), 
              scales = "free", independent = "all")+
  geom_ribbon(data=prediction_seeds_escpred_univar,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=type),
              alpha=0.3)+
  geom_line(data=prediction_seeds_escpred_univar,
            aes(x=x,y=predicted,linetype=signif,color=type),
            linewidth=1)+
  scale_linetype_manual(values=c("dotted", "solid"))+
  ylab("Proportion of seeds escaping predation")+
  xlab("Value of the moment")+
  my_theme()+
  geom_text(data=prediction_seeds_escpred_univar%>%
              dplyr::select(year,predictor,print,type)%>%
              distinct()%>%
              pivot_wider(names_from=type,values_from=print)%>%
              mutate(print=paste("L = ",linear,"\n","NL =", nonlinear)),
            aes(x=Inf,y=0.25,label=print),
            hjust=1.05, vjust=1.2,family="serif")
fig3
#ggsave(file="output/figures/fig3.tiff", plot=fig3, width=10, height=7)
```

### Figure 4 (not used)

Figure based on predictions of yearly univariate models (selection differentials).

```{r}
fig4<-ggplot()+
  geom_point(data=data_ids%>%
               dplyr::select(year,fitness_rel,avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
                            names_to="predictor",values_to="value_predictor")%>%
               mutate(predictor=factor(predictor,
                                       levels=c("avFD_std","var_std",
                                                "skew_std","kurt_std"))),
             aes(x=value_predictor,y=fitness_rel),
             size=2,alpha=0.3)+
  facet_grid2(c("year","predictor"), 
              labeller=labeller(predictor=predictor.labs), 
              scales = "free", independent = "all")+
  geom_ribbon(data=prediction_sel_nfl_univar,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=type),
              alpha=0.3)+
  geom_line(data=prediction_sel_nfl_univar,
            aes(x=x,y=predicted,linetype=signif,color=type),
            linewidth=1)+
  scale_linetype_manual(values=c("dotted", "solid"))+
  ylab("Relative fitness (number of intact seeds)")+
  xlab("Value of the moment")+
  my_theme()+
  geom_text(data=prediction_sel_nfl_univar%>%
              dplyr::select(year,predictor,print,type)%>%
              distinct()%>%
              pivot_wider(names_from=type,values_from=print)%>%
              mutate(print=paste("L = ",linear,"\n","NL =", nonlinear)),
            aes(x=Inf,y=Inf,label=print),
             hjust=1.05, vjust=1.2,family="serif")
fig4
#ggsave(file="output/figures/fig4.tiff", plot=fig4, width=10, height=7)
```

### Figure 5 (not used)

Figure based on predictions of yearly univariate models (selection differentials).

```{r}
fig5<-ggplot()+
  geom_point(data=data_ids%>%
               dplyr::select(year,fitness_rel,avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
                            names_to="predictor",values_to="value_predictor")%>%
               mutate(predictor=factor(predictor,
                                       levels=c("avFD_std","var_std",
                                                "skew_std","kurt_std"))),
             aes(x=value_predictor,y=fitness_rel),
             size=2,alpha=0.3)+
  facet_grid2(c("year","predictor"), 
              labeller=labeller(predictor=predictor.labs), 
              scales = "free", independent = "all")+
  geom_ribbon(data=prediction_sel_univar,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=type),
              alpha=0.3)+
  geom_line(data=prediction_sel_univar,
            aes(x=x,y=predicted,linetype=signif,color=type),
            linewidth=1)+
  scale_linetype_manual(values=c("dotted", "solid"))+
  ylab("Relative fitness (number of intact seeds)")+
  xlab("Value of the moment")+
  my_theme()+
  geom_text(data=prediction_sel_univar%>%
              dplyr::select(year,predictor,print,type)%>%
              distinct()%>%
              pivot_wider(names_from=type,values_from=print)%>%
              mutate(print=paste("L = ",linear,"\n","NL =", nonlinear)),
            aes(x=Inf,y=Inf,label=print),
             hjust=1.05, vjust=1.2,family="serif")
fig5
#ggsave(file="output/figures/fig5.tiff", plot=fig5, width=10, height=7)
```


## Sub-figure (not used)

Sub-figure with min, mean and max of each of the moments (not used so far).

```{r}
data_ids%>%ungroup()%>%
  dplyr::select(avFD_std,var_std,skew_std,kurt_std)%>%summary()
data_ids%>%ungroup()%>%
  filter(near(avFD_std,mean(avFD_std),tol=0.001)==T)%>%dplyr::select(year,id)
data_ids%>%ungroup()%>%
  filter(avFD_std==min(avFD_std)|avFD_std==max(avFD_std))%>%
  dplyr::select(year,id)
data_ids%>%ungroup()%>%   
  filter(near(var_std,mean(var_std,na.rm=T),tol=0.006)==T)%>%
  dplyr::select(year,id)
data_ids%>%ungroup()%>%
  filter(var_std==min(var_std,na.rm=T)|var_std==max(var_std,na.rm=T))%>%
  dplyr::select(year,id)
data_ids%>%ungroup()%>%
  filter(near(skew_std,mean(skew_std,na.rm=T),tol=0.015)==T)%>%
  dplyr::select(year,id)
data_ids%>%ungroup()%>%
  filter(skew_std==min(skew_std,na.rm=T)|skew_std==max(skew_std,na.rm=T))%>%
  dplyr::select(year,id)
data_ids%>%ungroup()%>%
    filter(near(kurt_std,mean(kurt_std,na.rm=T),tol=0.001)==T)%>%
  dplyr::select(year,id)
data_ids%>%ungroup()%>%
  filter(kurt_std==min(kurt_std,na.rm=T)|kurt_std==max(kurt_std,na.rm=T))%>%
  dplyr::select(year,id)
```

```{r fig.height=2, fig.width=8}
grid.arrange(
  # Mean
  ggplot(rbind(data_id_flowers%>%filter(year==1987&id=="1:50")%>%
                 mutate(stat="2_medium"),
               data_id_flowers%>%filter(year==1987&id=="2:115")%>%
                 mutate(stat="1_high"),
               data_id_flowers%>%filter(year==1988&id=="3:59")%>%
                 mutate(stat="3_low")),
         aes(x=opening_date_v,fill=stat))+
    geom_density(color="black",alpha=0.7)+
  scale_fill_manual(values=c("#756bb1","#bcbddc","#efedf5"))+
    my_theme()+xlab(NULL)+ylab(NULL),
  # Variance
  ggplot(rbind(data_id_flowers%>%filter(year==1989&id=="1:34")%>%
               mutate(stat="3_low"),
             data_id_flowers%>%filter(year==1987&id=="1:59")%>%
               mutate(stat="2_medium"),
             data_id_flowers%>%filter(year==1987&id=="3:141")%>%
               mutate(stat="1_high")),
       aes(x=opening_date_v,fill=stat))+
  geom_density(color="black",alpha=0.7)+
  scale_fill_manual(values=c("#756bb1","#bcbddc","#efedf5"))+
  my_theme()+xlab(NULL)+ylab(NULL),
  # Skewness
  ggplot(rbind(data_id_flowers%>%filter(year==1989&id=="2:28")%>%
                 mutate(stat="2_medium"),
               data_id_flowers%>%filter(year==1987&id=="4:433")%>%
                 mutate(stat="1_high"),
               data_id_flowers%>%filter(year==1989&id=="2:16")%>%
                 mutate(stat="3_low")),
         aes(x=opening_date_v,fill=stat))+
    geom_density(color="black",alpha=0.7)+
  scale_fill_manual(values=c("#756bb1","#bcbddc","#efedf5"))+
    my_theme()+xlab(NULL)+ylab(NULL),
  # Kurtosis
  ggplot(rbind(data_id_flowers%>%filter(year==1988&id=="3:61")%>%
                 mutate(stat="2_medium"),
               data_id_flowers%>%filter(year==1988&id=="6:12")%>%
                 mutate(stat="3_low"),
               data_id_flowers%>%filter(year==1988&id=="6:13")%>%
                 mutate(stat="1_high")),
         aes(x=opening_date_v,fill=stat))+
    geom_density(color="black",alpha=0.7)+
  scale_fill_manual(values=c("#756bb1","#bcbddc","#efedf5"))+
    my_theme()+xlab(NULL)+ylab(NULL),
  ncol=4,bottom=textGrob("Opening date",just="center",
                      gp=gpar(fontsize=16,fontfamily="serif")),
  left=textGrob("Density",just="center",hjust=0.30,
                      gp=gpar(fontsize=16,fontfamily="serif"),
                      rot = 90))
```

