---
title: "Selection on within-individual variation in flowering time in Lathyrus vernus"
author: "Alicia Valdés"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  pdf_document:
    toc: yes
    toc_depth: 4
  word_document:
    toc: yes
    toc_depth: '4'
subtitle: "Analyses of relationships between phenological traits and fruit initiation
  and pre-dispersal seed predation, and analyses of phenotypic selection on phenological
  traits"
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(tibble.width = Inf)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r load packages, include=FALSE}
library(tidyverse)
library(jtools)
library(ggeffects)
library(glmmTMB)
library(DHARMa)
library(RColorBrewer)
library(gridExtra)
library(ggthemes)
library(ggfortify)
library(ggcorrplot)
library(car)
library(broom.mixed)
library(performance)
library(sjPlot)
library(lme4)
library(bcaboot)
library(purrr)
library(ggridges)
library(moments)
library(grid)
library(stringr)
library(ggh4x)
library(ggpubr)
library(multcompView)
library(multcomp)
library(brms)
library(bayesplot)
library(PearsonDS)
library(plotrix)
```

```{r Define ggplot themes and palettes, include=FALSE}
my_theme <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(legend.position="none")+theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
my_theme_legend <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
myPalette <- colorRampPalette(brewer.pal(11, "YlOrRd"))
```

```{r load previously created output}
load(file="output/BCIs_sel_linear.RData")
load(file="output/BCIs_sel_nonlinear.RData")
load(file="output/BCIs_sel_linear_87.RData")
load(file="output/BCIs_sel_nonlinear_87.RData")
load(file="output/BCIs_sel_linear_88.RData")
load(file="output/BCIs_sel_nonlinear_88.RData")
load(file="output/BCIs_sel_linear_89.RData")
load(file="output/BCIs_sel_nonlinear_89.RData")
load(file="output/BCIs_sel_nfl_linear.RData")
load(file="output/BCIs_sel_nfl_nonlinear.RData")
load(file="output/BCIs_sel_nfl_linear_87.RData")
load(file="output/BCIs_sel_nfl_linear_88.RData")
load(file="output/BCIs_sel_nfl_linear_89.RData")
load(file="output/BCIs_sel_nfl_nonlinear_87.RData")
load(file="output/BCIs_sel_nfl_nonlinear_88.RData")
load(file="output/BCIs_sel_nfl_nonlinear_89.RData")
load(file="output/BCIs_sel_nfl_linear_87_mv.RData")
load(file="output/BCIs_sel_nfl_linear_88_mv.RData")
load(file="output/BCIs_sel_nfl_linear_89_mv.RData")
load(file="output/BCIs_sel_nfl_nonlinear_87_mv.RData")
load(file="output/BCIs_sel_nfl_nonlinear_88_mv.RData")
load(file="output/BCIs_sel_nfl_nonlinear_89_mv.RData")
load(file="output/BCIs_sel_nfl_linear_87_mv2.RData")
load(file="output/BCIs_sel_nfl_linear_88_mv2.RData")
load(file="output/BCIs_sel_nfl_linear_89_mv2.RData")
load(file="output/BCIs_sel_nfl_nonlinear_87_mv2.RData")
load(file="output/BCIs_sel_nfl_nonlinear_88_mv2.RData")
load(file="output/BCIs_sel_nfl_nonlinear_89_mv2.RData")
load(file="output/BCIs_abs_nfl_linear.RData")
load(file="output/BCIs_abs_nfl_nonlinear.RData")
load(file="output/models/brms_87.rda")
load(file="output/models/brms_88.rda")
load(file="output/models/brms_89.rda")
load(file="output/BCIs_abs_nfl_linear_87.RData")
load(file="output/BCIs_abs_nfl_linear_88.RData")
load(file="output/BCIs_abs_nfl_linear_89.RData")
load(file="output/BCIs_abs_nfl_nonlinear_87.RData")
load(file="output/BCIs_abs_nfl_nonlinear_88.RData")
load(file="output/BCIs_abs_nfl_nonlinear_89.RData")
```

# Read clean data from .csv files

```{r}
data_ids <- read_csv("data/clean/data_ids.csv")
data_ids$imp_seed_preyed <- as.factor(data_ids$imp_seed_preyed)
data_ids$year <- as.factor(data_ids$year)
data_ids$subplot<-as.factor(data_ids$subplot)
data_id_flowers <- read_csv("data/clean/data_id_flowers.csv")
data_weather<-read_csv("C:/Users/alici/Dropbox/SU/Projects/lathyrus/lathyrus_ms1/data/clean/weather_GDD.csv")
```

# Figure 1 (not used)

```{r}
# Changes in mean
mean_data<-data.frame(A_early=rnorm(500000,mean=63.2,sd=0.64),
                      B_medium=rnorm(500000,mean=66.2,sd=0.64),
                      C_late=rnorm(500000,mean=69.2,sd=0.64))%>%
  pivot_longer(cols=A_early:C_late,names_to="names",values_to="values")
summary_mean_data<-mean_data%>%
  group_by(names)%>%
  summarise(mean(values),var(values),skewness(values),kurtosis(values))
summary_mean_data

# Changes in variance
var_data<-data.frame(A_low=rnorm(500000,mean=66.2,sd=0.34),
                     B_medium=rnorm(500000,mean=66.2,sd=0.64),
                     C_large=rnorm(500000,mean=66.2,sd=0.94))%>%
  pivot_longer(cols=A_low:C_large,names_to="names",values_to="values")
summary_var_data<-var_data%>%
  group_by(names)%>%
  summarise(mean(values),var(values),skewness(values),kurtosis(values))
summary_var_data


# Changes in skewness and kurtosis --> modify in Inkscape
fig1_part<-grid.arrange(
  ggplot(mean_data,aes(x=values,fill=names))+
    geom_density(alpha=0.7)+
    xlab("Opening date")+
    ylab("Density")+my_theme()+ggtitle("A) Changes in mean")+
    scale_fill_manual(values=c("#efedf5","#bcbddc","#756bb1")),
  ggplot(var_data,aes(x=values,fill=names))+geom_density(alpha=0.7)+
    xlab("Opening date")+
    ylab("Density")+my_theme()+ggtitle("B) Changes in variance")+
    scale_fill_manual(values=c("#efedf5","#bcbddc","#756bb1")),
  ncol=2)
ggsave(file="output/figures/fig1_part.svg", plot=fig1_part, width=10, height=4)
```

# Fig. 1

```{r}
curves_mean<-data.frame(
  low=rpearson(10000,
               moments=c(mean=63.2,variance=0.5,skewness=0,kurtosis=3)),
  medium=rpearson(10000,
                  moments=c(mean=66.2,variance=0.5,skewness=0,kurtosis=3)),
  high=rpearson(10000,
                moments=c(mean=69.2,variance=0.5,skewness=0,kurtosis=3)))%>%
  pivot_longer(cols=low:high,names_to="curve_id",values_to="value")%>%
  mutate(moment="Mean")
curves_var<-data.frame(
  low=rpearson(10000,
               moments=c(mean=66.2,variance=0.05,skewness=0,kurtosis=3)),
  medium=rpearson(10000,
                  moments=c(mean=66.2,variance=0.5,skewness=0,kurtosis=3)),
  high=rpearson(10000,
                moments=c(mean=66.2,variance=3,skewness=0,kurtosis=3)))%>%
  pivot_longer(cols=low:high,names_to="curve_id",values_to="value")%>%
  mutate(moment="Variance")
curves_skew<-data.frame(
  low=rpearson(10000,
               #moments=c(mean=66.2,variance=0.5,skewness=-1.3,kurtosis=3)),
               moments=c(mean=66.2,variance=0.5,skewness=-1.1,kurtosis=3)),
  medium=rpearson(10000,
                  moments=c(mean=66.2,variance=0.5,skewness=0,kurtosis=3)),
  high=rpearson(10000,
                #moments=c(mean=66.2,variance=0.5,skewness=1.3,kurtosis=3)))%>%
                moments=c(mean=66.2,variance=0.5,skewness=1.1,kurtosis=3)))%>%
  pivot_longer(cols=low:high,names_to="curve_id",values_to="value")%>%
  mutate(moment="Skewness")
curves_kurt<-data.frame(
  low=rpearson(10000,
               #moments=c(mean=66.2,variance=0.5,skewness=0,kurtosis=1.5))
               moments=c(mean=66.2,variance=0.5,skewness=0,kurtosis=2)),
  medium=rpearson(10000,
                  moments=c(mean=66.2,variance=0.5,skewness=0,kurtosis=3)),
  high=rpearson(10000,
                moments=c(mean=66.2,variance=0.5,skewness=0,kurtosis=7)))%>%
  pivot_longer(cols=low:high,names_to="curve_id",values_to="value")%>%
  mutate(moment="Kurtosis")
curves<-rbind(curves_mean,curves_var,curves_skew,curves_kurt)%>%
  mutate(moment=factor(moment,
                       levels=c("Mean","Variance","Skewness","Kurtosis")),
         curve_id=factor(curve_id,
                         levels=c("low","medium","high")))
```

```{r}
curves%>%group_by(moment,curve_id)%>%
  summarise(mean=mean(value),var=var(value),
            skew=skewness(value),kurt=kurtosis(value))
```

```{r}
fig1<-grid.arrange(
  ggplot(curves%>%filter(moment=="Mean"),aes(x=value,fill=curve_id))+
    geom_density(alpha=0.5)+my_theme_legend()+theme(legend.position="top")+
    labs(fill="Mean")+xlab("Opening date")+ylab("Density")+ggtitle("A)")+
    scale_fill_manual(values=c("#1a9641","#ffffbf","#d7191c"),
                      labels=c("63.2", "66.2", "69.2"))+
    theme(plot.title = element_text(hjust =-0.09,vjust=-6))+
    scale_x_continuous(breaks=c(60,62,64,66,68,70,72)),
  ggplot(curves%>%filter(moment=="Variance"),aes(x=value,fill=curve_id))+
    geom_density(alpha=0.5)+my_theme_legend()+theme(legend.position="top")+
    labs(fill="Variance")+xlab("Opening date")+ylab("Density")+ggtitle("B)")+
    scale_fill_manual(values=c("#1a9641","#ffffbf","#d7191c"),
                      labels=c("0.05", "0.5", "3.0"))+
    theme(plot.title = element_text(hjust =-0.09,vjust=-6))+
    scale_x_continuous(breaks=c(60,62,64,66,68,70,72)),
  ggplot(curves%>%filter(moment=="Skewness"),aes(x=value,fill=curve_id))+
    geom_density(alpha=0.5)+my_theme_legend()+theme(legend.position="top")+
    labs(fill="Skewness")+xlab("Opening date")+ylab("Density")+ggtitle("C)")+
    scale_fill_manual(values=c("#1a9641","#ffffbf","#d7191c"),
                      labels=c("-1.1", "0.0", "1.1"))+
    theme(plot.title = element_text(hjust =-0.09,vjust=-6))+
    scale_x_continuous(breaks=c(62,64,66,68,70,72)),
  ggplot(curves%>%filter(moment=="Kurtosis"),
         aes(x=value,fill=curve_id))+
    geom_density(alpha=0.5)+my_theme_legend()+theme(legend.position="top")+
    labs(fill="Kurtosis")+xlab("Opening date")+ylab("Density")+ggtitle("D)")+
    scale_fill_manual(values=c("#1a9641","#ffffbf","#d7191c"),
                      labels=c("2.0", "3.0", "6.3"))+
    theme(plot.title = element_text(hjust =-0.09,vjust=-6))+
    scale_x_continuous(breaks=c(62,64,66,68,70,72)),
  ncol=2
)
ggsave(file="output/figures/fig1.tiff", plot=fig1, width=12, height=10)
```

# Descriptive

## Flowering phenology curves of individuals

```{r}
ids_years_1_2fl<-data_id_flowers%>%group_by(year,id)%>%mutate(count=n())%>%
  filter(count==1|count==2)%>%dplyr::select(id,year)%>%distinct(id,year) 
# All ids and years with 1 or 2 fl

data_id_flowers_3fl<-data_id_flowers %>%
  anti_join(ids_years_1_2fl)%>% # Keep only ids and years with at least 3 fl
  mutate(subplot=factor(subplot,ordered=T),number=factor(number,ordered=T))%>%
  mutate(year=factor(year),
         id=factor(id,
                   levels=unique(id[order(subplot,number)]), ordered=TRUE))
# id as ordered factor based on subplot and number

# split the data into chunks of 21 subplot, number
# based on their unique id values
id_chunks <-data_id_flowers_3fl %>% 
  distinct(subplot,number) %>%
  arrange(subplot,number)%>%
  mutate(chunk = ceiling(row_number()/21)) %>%
  inner_join(data_id_flowers_3fl, by =c("subplot","number")) %>%
  split(.$chunk)

# create a list of plots, one for each chunk of ids
plot_list<-map(id_chunks,~ggplot(.x,aes(x=opening_date_v,y=id,fill=year))+
                   geom_density_ridges()+
                   theme_ridges()+theme(text=element_text(family="serif"))+
                   theme(legend.position="top")+
                   labs(x="Opening date (number of days from the vernal equinox)",
                        y="Individual")+
                   scale_fill_manual(values=c("#E69F00","#56B4E9","#009E73")))

# save the plots as TIFF files
walk2(plot_list, seq_along(plot_list), 
      ~ ggsave(paste0("output/figures/myplot_", .y, ".tiff"), 
               plot = .x, width = 6.5, height = 9, units = "in", dpi = 300))
```

## Distributions of the four moments

### All years

```{r}
histograms_SI<-grid.arrange(
  # Mean
  ggplot(data_ids,aes(x=avFD_v))+
    geom_histogram(color="black",alpha=0.6,position="identity")+
    ggtitle("A)")+
    my_theme()+xlab("Mean")+ylab("Count"),
  # Variance
  ggplot(data_ids,aes(x=var))+
    geom_histogram(color="black",alpha=0.6,position="identity")+
    ggtitle("B)")+
    my_theme()+xlab("Variance")+ylab("Count"),
  # Skewness
  ggplot(data_ids,aes(x=skew))+
    geom_histogram(color="black",alpha=0.6,position="identity")+
    ggtitle("C)")+
    my_theme()+xlab("Skewness")+ylab("Count"),
  # Kurtosis
  ggplot(data_ids,aes(x=kurt))+
    geom_histogram(color="black",alpha=0.6,position="identity")+
    ggtitle("D)")+
    my_theme()+xlab("Kurtosis")+ylab("Count"),
  ncol=2)
ggsave(histograms_SI,filename="output/figures/histograms_SI.tiff",
       device="tiff",width=20,height=15,units="cm",dpi=300,compression="lzw")
```

### By year

```{r}
histograms_SI_years<-grid.arrange(
  # Mean
  ggplot(data_ids,aes(x=avFD_v,fill=year))+
    geom_histogram(color="black",position="identity")+
    scale_fill_manual(values=c("#E69F00","#56B4E9","#009E73"))+
    facet_grid(rows=vars(year))+ggtitle("A)")+
    my_theme()+xlab("Mean")+ylab("Count"),
  # Variance
  ggplot(data_ids,aes(x=var,fill=year))+
    geom_histogram(color="black",position="identity")+
    scale_fill_manual(values=c("#E69F00","#56B4E9","#009E73"))+
    facet_grid(rows=vars(year))+ggtitle("B)")+
    my_theme()+xlab("Variance")+ylab("Count"),
  # Skewness
  ggplot(data_ids,aes(x=skew,fill=year))+
    geom_histogram(color="black",position="identity")+
    scale_fill_manual(values=c("#E69F00","#56B4E9","#009E73"))+
    facet_grid(rows=vars(year))+ggtitle("C)")+
    my_theme()+xlab("Skewness")+ylab("Count"),
  # Kurtosis
  ggplot(data_ids,aes(x=kurt,fill=year))+
    geom_histogram(color="black",position="identity")+
    scale_fill_manual(values=c("#E69F00","#56B4E9","#009E73"))+
    facet_grid(rows=vars(year))+ggtitle("D)")+
    my_theme()+xlab("Kurtosis")+ylab("Count"),
  ncol=2)
ggsave(histograms_SI_years,filename="output/figures/histograms_SI_years.tiff",
       device="tiff",width=20,height=25,units="cm",dpi=300,compression="lzw")
```

## Ranges, means and SD

```{r}
data_ids%>%
  summarise(min_mean=min(avFD_v),max_mean=max(avFD_v),
            mean_mean=mean(avFD_v),sd_mean=sd(avFD_v),
            min_var=min(var,na.rm=T),max_var=max(var,na.rm=T),
            mean_var=mean(var,na.rm=T),sd_var=sd(var,na.rm=T),
            min_skew=min(skew,na.rm=T),max_skew=max(skew,na.rm=T),
            mean_skew=mean(skew,na.rm=T),sd_skew=sd(skew,na.rm=T),
            min_kurt=min(kurt,na.rm=T),max_kurt=max(kurt,na.rm=T),
            mean_kurt=mean(kurt,na.rm=T),sd_kurt=sd(kurt,na.rm=T))
```

# Correct errors in n_fl and n_fr

```{r}
filter(data_ids,n_fl!=n_fl_a) # n_fl_a is correct
```

```{r}
filter(data_ids,n_fr!=n_mat_intact_fr) # n_mat_intact_fr is correct
```

```{r}
data_ids<-data_ids%>%
  dplyr::select(-n_fl)%>%
  rename(n_fl=n_fl_a)
```

```{r}
data_ids<-data_ids%>%
  dplyr::select(-n_fr) # Use n_mat_intact_fr 
```

# Recalculate fruit set, fruit initiation and fruit maturation

```{r}
data_ids<-data_ids%>%
  mutate(n_mat_intact_fr=ifelse(is.na(n_mat_intact_fr),0,n_mat_intact_fr))
```


```{r}
data_ids<-data_ids%>%
  mutate(fr_set=n_mat_intact_fr/n_fl,
         fr_init=n_init_fr/n_fl,
         fr_mat=ifelse(n_init_fr>0,n_mat_intact_fr/n_init_fr,NA))
```

# Differences in variables among years

```{r}
Anova(lm(avFD_v~year,data_ids))
Anova(lm(var~year,data_ids))
Anova(lm(skew~year,data_ids))
Anova(lm(kurt~year,data_ids))
# Fruit set
Anova(glm(cbind(fr_set=n_mat_intact_fr,
                fr_no_set=n_fl-n_mat_intact_fr)~year,data_ids,family="binomial")) 
Anova(lm(asin(sqrt(fr_set))~year,data_ids)) 
# Fruit initiation
Anova(glm(cbind(fr_init=n_init_fr,
                fr_no_init=n_fl-n_init_fr)~year,
          data_ids,family="binomial")) 
Anova(lm(asin(sqrt(fr_init))~year,data_ids)) 
# Fruit maturation
Anova(glm(cbind(fr_mat=n_mat_intact_fr,
                fr_no_mat=n_init_fr-n_mat_intact_fr)~year,
          data_ids,family="binomial"))
Anova(lm(asin(sqrt(fr_mat))~year,data_ids)) 
# Proportion of seeds escaping predation
Anova(glm(cbind(npr_seeds=round(n_seed)-round(n_preyed_seed),
                pr_seeds=round(n_preyed_seed))~year,
          data_ids,family="binomial"))
Anova(lm(asin(sqrt(1-prop_seed_preyed))~year,data_ids)) 
# Fitness
Anova(lm(fitness~year,data_ids))
```

```{r}
letters_mean<-as.data.frame.list(
  multcompLetters4(aov(avFD_v~year,data_ids),
                   TukeyHSD(aov(avFD_v~year,data_ids)))$year)%>%
  dplyr::select(Letters)%>%
  rownames_to_column(var="year")
letters_var<-as.data.frame.list(
  multcompLetters4(aov(var~year,data_ids),
                   TukeyHSD(aov(var~year,data_ids)))$year)%>%
  dplyr::select(Letters)%>%
  rownames_to_column(var="year")
letters_skew<-as.data.frame.list(
  multcompLetters4(aov(skew~year,data_ids),
                   TukeyHSD(aov(skew~year,data_ids)))$year)%>%
  dplyr::select(Letters)%>%
  rownames_to_column(var="year")
letters_kurt<-as.data.frame.list(
  multcompLetters4(aov(kurt~year,data_ids),
                   TukeyHSD(aov(kurt~year,data_ids)))$year)%>%
  dplyr::select(Letters)%>%
  rownames_to_column(var="year")
# Using lms with arcsine transformation for proportions
letters_fr_set<-data.frame(
  Letters=cld(glht(lm(asin(sqrt(fr_set))~year,data_ids),
                   linfc= mcp(year="Tukey")))$mcletters$Letters)%>%
  rownames_to_column(var="year")
letters_fr_init<-data.frame(
  Letters=cld(glht(lm(asin(sqrt(fr_init))~year,data_ids),
                   linfc= mcp(year="Tukey")))$mcletters$Letters)%>%
  rownames_to_column(var="year")
letters_fr_mat<-data.frame(
  Letters=cld(glht(lm(asin(sqrt(fr_mat))~year,data_ids),
                   linfc= mcp(year="Tukey")))$mcletters$Letters)%>%
  rownames_to_column(var="year")
letters_seeds_escpred<-data.frame(
  Letters=cld(glht(lm(asin(sqrt(1-prop_seed_preyed))~year,data_ids),
                   linfc= mcp(year="Tukey")))$mcletters$Letters)%>%
  rownames_to_column(var="year")
# Using lms with square root transformation for fitness
letters_sel<-data.frame(
  Letters=cld(glht(lm(sqrt(fitness)~year,data_ids),
                   linfc= mcp(year="Tukey")))$mcletters$Letters)%>%
  rownames_to_column(var="year")
```

```{r}
# diffs_moments_years_SI<-ggplot(
#   rbind(
#     left_join(data.frame(ggpredict(lm(avFD_v~year,data_ids))),
#               letters_mean,join_by(year.x==year))%>%
#       mutate(moment="Mean"),
#     left_join(data.frame(ggpredict(lm(var~year,data_ids))),
#               letters_var,join_by(year.x==year))%>%
#       mutate(moment="Variance"),
#     left_join(data.frame(ggpredict(lm(skew~year,data_ids))),
#               letters_skew,join_by(year.x==year))%>%
#       mutate(moment="Skewness"),
#     left_join(data.frame(ggpredict(lm(kurt~year,data_ids))),
#               letters_kurt,join_by(year.x==year))%>%
#       mutate(moment="Kurtosis")
#   )%>%
#     mutate(moment=factor(moment,
#                          levels=c("Mean","Variance","Skewness","Kurtosis"))),
#        aes(x=year.x,y=year.predicted,
#            ymin=year.conf.low,ymax=year.conf.high))+
#   geom_errorbar(width=.2)+geom_point()+
#   geom_text(aes(label=Letters,y=year.conf.high),
#             vjust=-0.2,family="serif")+
#   facet_wrap(~moment,scales="free",nrow=1)+
#   my_theme()+xlab(NULL)+ylab("Value of the moment")
# diffs_moments_years_SI
# ggsave(diffs_moments_years_SI,
#        filename="output/figures/diffs_moments_years_SI.tiff",
#        device="tiff",width=26,height=8,units="cm",dpi=300,compression="lzw")
# 
# diffs_vars_years_SI<-ggplot(
#   rbind(
#   left_join(data.frame(ggpredict(
#     glm(cbind(fr_set=n_mat_intact_fr,fr_no_set=n_fl-n_mat_intact_fr)~year,
#         data_ids,family="binomial"))),
#     letters_fr_set,join_by(year.x==year))%>%
#     mutate(var="Fruit set"),
#   left_join(data.frame(ggpredict(
#     glm(cbind(fr_init=n_init_fr,fr_no_init=n_fl-n_init_fr)~year,
#         data_ids,family="binomial"))),
#     letters_fr_init,join_by(year.x==year))%>%
#     mutate(var="Fruit initiation"),
#   left_join(data.frame(ggpredict(
#     glm(cbind(fr_mat=n_mat_intact_fr,fr_no_mat=n_init_fr-n_mat_intact_fr)~year,
#         data_ids,family="binomial"))),
#     letters_fr_mat,join_by(year.x==year))%>%
#     mutate(var="Fruit maturation"),
#   left_join(data.frame(ggpredict(
#     glm(cbind(npr_seeds=round(n_seed)-round(n_preyed_seed),
#               pr_seeds=round(n_preyed_seed))~year,
#         data_ids,family="binomial"))),
#     letters_seeds_escpred,join_by(year.x==year))%>%
#     mutate(var="Proportion of seeds\nescaping predation"),
#   left_join(data.frame(ggpredict(lm(fitness~year,data_ids))),
#             letters_sel,join_by(year.x==year))%>%
#     mutate(var="Fitness")
# )%>%
#   mutate(var=factor(var,
#                     levels=c("Fruit set",
#                              "Fruit initiation",
#                              "Fruit maturation",
#                              "Proportion of seeds\nescaping predation",
#                              "Fitness"))),
#   aes(x=year.x,y=year.predicted,
#       ymin=year.conf.low,ymax=year.conf.high))+
#   geom_errorbar(width=.2)+geom_point()+
#   geom_text(aes(label=Letters,y=year.conf.high),
#             vjust=-0.2,family="serif")+
#   facet_wrap(~var,scales="free",nrow=2)+
#   my_theme()+xlab(NULL)+ylab("Value of the variable")
# diffs_vars_years_SI
# ggsave(diffs_vars_years_SI,
#        filename="output/figures/diffs_vars_years_SI.tiff",
#        device="tiff",width=26,height=18,units="cm",dpi=300,compression="lzw")
```

```{r}
data_ids%>%group_by(year)%>%
  summarise(mean_fr_set=mean(fr_set),
            mean_fr_init=mean(fr_init),
            mean_fr_mat=mean(fr_mat,na.rm=T),
            mean_prop_seed_preyed=mean(prop_seed_preyed,na.rm=T),
            mean_fitness=mean(fitness))
```

Why means are different in the plots???

```{r}
ggerrorplot(data_ids,x="year",y="fr_set",combine=F,size=0.5,
            desc_stat="mean_se",error.plot = "errorbar",add = "mean",
            xlab="Year")+my_theme()+ylab("Mean")
plot(ggpredict(glm(cbind(fr_set=n_mat_intact_fr,
                fr_no_set=n_fl-n_mat_intact_fr)~year,data_ids,
                family="binomial")))
data_ids$fr_set_asin<-with(data_ids,asin(sqrt(fr_set)))
plot(ggpredict(lm(fr_set_asin~year,data_ids)))
```

```{r}
diffs_moments_years_SI<-grid.arrange(
  ggerrorplot(data_ids,x="year",y="avFD_v",combine=F,size=0.5,
              desc_stat="mean_se",error.plot = "errorbar",add = "none",
              xlab="Year")+my_theme()+ylab("Mean")+
    stat_summary(geom="point",size=2,fun.y="mean")+
    geom_text(data=data_ids%>%group_by(year)%>%
                summarize(mean_se=mean(avFD_v)+(sd(avFD_v)/sqrt(n()))),
            aes(x=year,y=mean_se+0.1,label=letters_mean$Letters),
            vjust=-0.2,family="serif")+
    ggtitle("A)")+  
    theme(plot.title=element_text(face="plain",size=16,hjust=-0.15)),
  ggerrorplot(data_ids,x="year",y="var",combine=F,size=0.5,
              desc_stat="mean_se",error.plot = "errorbar",add = "none",
              xlab="Year")+my_theme()+ylab("Variance")+
    stat_summary(geom="point",size=2,fun.y="mean")+
    geom_text(data=data_ids%>%group_by(year)%>%
                summarize(mean_se=mean(var,na.rm=T)+
                            (sd(var,na.rm=T)/sqrt(n()))),
            aes(x=year,y=mean_se+0.005,label=letters_var$Letters),
            vjust=-0.2,family="serif")+
    ggtitle("B)")+
    theme(plot.title=element_text(face="plain",size=16,hjust=-0.15)),
  ggerrorplot(data_ids,x="year",y="skew",combine=F,size=0.5,
              desc_stat="mean_se",error.plot = "errorbar",add = "none",
              xlab="Year")+my_theme()+ylab("Skewness")+
    stat_summary(geom="point",size=2,fun.y="mean")+
    geom_text(data=data_ids%>%group_by(year)%>%
                summarize(mean_se=mean(skew,na.rm=T)+
                            (sd(skew,na.rm=T)/sqrt(n()))),
            aes(x=year,y=mean_se+0.007,label=letters_skew$Letters),
            vjust=-0.2,family="serif")+
    ggtitle("C)")+
    theme(plot.title=element_text(face="plain",size=16,hjust=-0.15)),
  ggerrorplot(data_ids,x="year",y="kurt",combine=F,size=0.5,
              desc_stat="mean_se",error.plot = "errorbar",add = "none",
              xlab="Year")+my_theme()+ylab("Kurtosis")+
    stat_summary(geom="point",size=2,fun.y="mean")+
    geom_text(data=data_ids%>%group_by(year)%>%
                summarize(mean_se=mean(kurt,na.rm=T)+
                            (sd(kurt,na.rm=T)/sqrt(n()))),
            aes(x=year,y=mean_se+0.009,label=letters_kurt$Letters),
            vjust=-0.2,family="serif")+
    ggtitle("D)")+
    theme(plot.title=element_text(face="plain",size=16,hjust=-0.15)),
  ncol=2)
diffs_moments_years_SI
ggsave(diffs_moments_years_SI,
       filename="output/figures/diffs_moments_years_SI.tiff",
       device="tiff",width=20,height=20,units="cm",dpi=300,compression="lzw")
```

```{r}
data_ids$prop_seeds_escpred<-1-data_ids$prop_seed_preyed
```


```{r}
diffs_vars_years_SI<-grid.arrange(
  ggerrorplot(data_ids,x="year",y="fr_init",combine=F,size=0.5,
              desc_stat="mean_se",error.plot = "errorbar",add = "none",
              xlab="Year")+my_theme()+ylab("Fruit initiation")+
    stat_summary(geom="point",size=2,fun.y="mean")+
    geom_text(data=data_ids%>%group_by(year)%>%
                summarize(mean_se=mean(fr_init)+(sd(fr_init)/sqrt(n()))),
            aes(x=year,y=mean_se+0.001,label=letters_fr_init$Letters),
            vjust=-0.2,family="serif")+
    ggtitle("A)")+
    theme(plot.title=element_text(face="plain",size=16,hjust=-0.15)),
  ggerrorplot(data_ids,x="year",y="fr_mat",combine=F,size=0.5,
              desc_stat="mean_se",error.plot = "errorbar",add = "none",
              xlab="Year")+my_theme()+ylab("Fruit maturation")+
    stat_summary(geom="point",size=2,fun.y="mean")+
    geom_text(data=data_ids%>%group_by(year)%>%
                summarize(mean_se=mean(fr_mat,na.rm=T)+
                            (sd(fr_mat,na.rm=T)/sqrt(n()))),
            aes(x=year,y=mean_se+0.002,label=letters_fr_mat$Letters),
            vjust=-0.2,family="serif")+
    ggtitle("B)")+
    theme(plot.title=element_text(face="plain",size=16,hjust=-0.15)),
  ggerrorplot(data_ids,x="year",y="prop_seeds_escpred",combine=F,size=0.5,
              desc_stat="mean_se",error.plot = "errorbar",add = "none",
              xlab="Year")+my_theme()+
    ylab("Propotion of seeds\nescaping predation")+
    stat_summary(geom="point",size=2,fun.y="mean")+
    geom_text(data=data_ids%>%group_by(year)%>%
                summarize(mean_se=mean(prop_seeds_escpred,na.rm=T)+
                            (sd(prop_seeds_escpred,na.rm=T)/sqrt(n()))),
            aes(x=year,y=mean_se+0.008,label=letters_seeds_escpred$Letters),
            vjust=-0.2,family="serif")+
    ggtitle("C)")+
    theme(plot.title=element_text(face="plain",size=16,hjust=-0.15)),
  ggerrorplot(data_ids,x="year",y="fitness",combine=F,size=0.5,
              desc_stat="mean_se",error.plot = "errorbar",add = "none",
              xlab="Year")+my_theme()+ylab("Fitness")+
    stat_summary(geom="point",size=2,fun.y="mean")+
    geom_text(data=data_ids%>%group_by(year)%>%
                summarize(mean_se=mean(fitness)+(sd(fitness)/sqrt(n()))),
            aes(x=year,y=mean_se+0.008,label=letters_sel$Letters),
            vjust=-0.2,family="serif")+
    ggtitle("D)")+
    theme(plot.title=element_text(face="plain",size=16,hjust=-0.15)),
  ncol=2)
diffs_vars_years_SI
ggsave(diffs_vars_years_SI,
       filename="output/figures/diffs_vars_years_SI.tiff",
       device="tiff",width=20,height=20,units="cm",dpi=300,compression="lzw")
```

# Correlations

I will fit models using traits representing the 4 moments of the distribution (mean: avFD, variance: var, skewness: skew and kurtosis: kurt)

Check the correlations of these 4 traits using all data:

```{r}
data_ids%>%dplyr::select(year,avFD_v,var,skew,kurt) %>%
  rename(Mean=avFD_v,Variance=var,Skewness=skew,Kurtosis=kurt)%>%
  ungroup()%>%
  select_if(is.numeric) %>% 
  cor(use="pairwise.complete.obs") %>%
  ggcorrplot(method = "square", type = "lower", hc.order = F, lab = T)+
  theme(legend.position="none")+my_theme()+xlab(NULL)+ylab(NULL)
ggsave(filename="output/figures/corr_SI.tiff",
       device="tiff",width=10,height=8,units="cm",dpi=300,compression="lzw")
```

Check the yearly correlations:

```{r}
corr_SI_years<-grid.arrange(
  data_ids%>%dplyr::select(year,avFD_v,var,skew,kurt) %>%
    filter(year==1987) %>%
    rename(Mean=avFD_v,Variance=var,Skewness=skew,Kurtosis=kurt)%>%
    select_if(is.numeric) %>% 
    cor(use="pairwise.complete.obs") %>%
    ggcorrplot(method = "square", type = "lower", hc.order = F, lab = T)+
    ggtitle("1987")+theme(legend.position="none")+
    my_theme()+xlab(NULL)+ylab(NULL),
  data_ids%>%dplyr::select(year,avFD_v,var,skew,kurt) %>%
    filter(year==1988) %>%
    rename(Mean=avFD_v,Variance=var,Skewness=skew,Kurtosis=kurt)%>%
    select_if(is.numeric) %>% 
    cor(use="pairwise.complete.obs") %>%
    ggcorrplot(method = "square", type = "lower", hc.order = F, lab = T)+
    ggtitle("1988")+theme(legend.position="none")+
    my_theme()+xlab(NULL)+ylab(NULL),
  data_ids%>%dplyr::select(year,avFD_v,var,skew,kurt) %>%
    filter(year==1989) %>%
    rename(Mean=avFD_v,Variance=var,Skewness=skew,Kurtosis=kurt)%>%
    select_if(is.numeric) %>% 
    cor(use="pairwise.complete.obs") %>%
    ggcorrplot(method = "square", type = "lower", hc.order = F, lab = T)+
    ggtitle("1989")+theme(legend.position="none")+
    my_theme()+xlab(NULL)+ylab(NULL),
  ncol=3)
ggsave(corr_SI_years,filename="output/figures/corr_SI_years.tiff",
       device="tiff",width=25,height=10,units="cm",dpi=300,compression="lzw")
```

Probaly OK? Check VIFs of each model.

# Multivariate GLMs

## FRUIT SET (NOT USED)

Using (within-year) standardized traits.

### Global models (SI)

#### Linear effects

```{r}
fr_set_linear<-glm(cbind(fr_set=n_mat_intact_fr,
                          fr_no_set=n_fl-n_mat_intact_fr)~avFD_std+var_std+
                      skew_std+kurt_std+year+ 
                      # Include main effect of year here
                      # but not in selection models!
                      avFD_std:year+var_std:year+skew_std:year+kurt_std:year,
                    data_ids,family="binomial")
tab_model(fr_set_linear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit set, linear effects"))
Anova(fr_set_linear) # Use type II (now) or III?
check_collinearity(glm(cbind(ffr_set=n_mat_intact_fr,
                             fr_no_set=n_fl-n_mat_intact_fr)~avFD_std+var_std+
                         skew_std+kurt_std+year,
                       data_ids,family="binomial"))
```

According to Anova, differences among years in the effects of avFD, skew and kurt.

##### Plot predictions

```{r}
plot(ggpredict(fr_set_linear,
               terms=c("avFD_std [all]","year"))) # Significant diffs among years
plot(ggpredict(fr_set_linear,
               terms=c("var_std [all]"))) # Main effect signficant
plot(ggpredict(fr_set_linear,
               terms=c("skew_std [all]","year"))) # Significant diffs among years
plot(ggpredict(fr_set_linear,
               terms=c("kurt_std [all]","year"))) # Significant diffs among years
```

#### Non-linear effects

```{r}
fr_set_nonlinear<-glm(cbind(fr_set=n_mat_intact_fr,
                          fr_no_set=n_fl-n_mat_intact_fr)~
                         avFD_std+var_std+skew_std+kurt_std+year+ 
                         avFD_std:year+var_std:year+skew_std:year+kurt_std:year+
                         I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                         I(avFD_std^2):year+I(var_std^2):year+
                         I(skew_std^2):year+I(kurt_std^2):year,
                       data_ids,family="binomial")
tab_model(fr_set_nonlinear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit set, non linear effects"))
Anova(fr_set_nonlinear) # Use type II (now) or III?
```

None of the quadratic effects is significant.

Ratio of n observations to n parameters in the model:

```{r}
nobs(fr_set_nonlinear)/dim(model.matrix(fr_set_nonlinear))[2]
```

OK. If including interactions, it would be lower than 10.
Similar problem with yearly models, so not including interactions in any model so far.

### Yearly models

#### Linear effects

```{r}
fr_set_linear_87<-glm(cbind(fr_set=n_mat_intact_fr,
                          fr_no_set=n_fl-n_mat_intact_fr)~
                         avFD_std+var_std+skew_std+kurt_std,
                       subset(data_ids,year==1987),family="binomial")
fr_set_linear_88<-glm(cbind(fr_set=n_mat_intact_fr,
                          fr_no_set=n_fl-n_mat_intact_fr)~
                         avFD_std+var_std+skew_std+kurt_std,
                    subset(data_ids,year==1988),family="binomial")
fr_set_linear_89<-glm(cbind(fr_set=n_mat_intact_fr,
                          fr_no_set=n_fl-n_mat_intact_fr)~
                         avFD_std+var_std+skew_std+kurt_std,
                    subset(data_ids,year==1989),family="binomial")
tab_model(fr_set_linear_87,fr_set_linear_88,fr_set_linear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit set, linear effects")
check_collinearity(fr_set_linear_87)
check_collinearity(fr_set_linear_88)
check_collinearity(fr_set_linear_89)
Anova(fr_set_linear_87)
Anova(fr_set_linear_88)
Anova(fr_set_linear_89) 
```

##### Plot predictions

```{r}
plot(ggpredict(fr_set_linear_87,terms=c("var_std [all]"))) 
plot(ggpredict(fr_set_linear_87,terms=c("skew_std [all]"))) 
plot(ggpredict(fr_set_linear_87,terms=c("kurt_std [all]"))) 
```

```{r}
plot(ggpredict(fr_set_linear_88,terms=c("avFD_std [all]"))) 
```

```{r}
plot(ggpredict(fr_set_linear_88,terms=c("avFD_std [all]"))) 
plot(ggpredict(fr_set_linear_88,terms=c("skew_std [all]"))) 
```

#### Non-linear effects

```{r}
fr_set_nonlinear_87<-glm(cbind(fr_set=n_mat_intact_fr,
                          fr_no_set=n_fl-n_mat_intact_fr)~
                            avFD_std+var_std+skew_std+kurt_std+
                            I(avFD_std^2)+I(var_std^2)+
                            I(skew_std^2)+I(kurt_std^2),
                          subset(data_ids,year==1987),family="binomial")
fr_set_nonlinear_88<-glm(cbind(fr_set=n_mat_intact_fr,
                          fr_no_set=n_fl-n_mat_intact_fr)~
                            avFD_std+var_std+skew_std+kurt_std+
                            I(avFD_std^2)+I(var_std^2)+
                            I(skew_std^2)+I(kurt_std^2),
                    subset(data_ids,year==1988),family="binomial")
fr_set_nonlinear_89<-glm(cbind(fr_set=n_mat_intact_fr,
                          fr_no_set=n_fl-n_mat_intact_fr)~
                            avFD_std+var_std+skew_std+kurt_std+
                            I(avFD_std^2)+I(var_std^2)+
                            I(skew_std^2)+I(kurt_std^2),
                    subset(data_ids,year==1989),family="binomial")
tab_model(fr_set_nonlinear_87,fr_set_nonlinear_88,fr_set_nonlinear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit set, nonlinear effects")
Anova(fr_set_nonlinear_87)
Anova(fr_set_nonlinear_88)
Anova(fr_set_nonlinear_89) 
```

##### Plot predictions

```{r}
plot(ggpredict(fr_set_nonlinear_88,terms=c("var_std [all]"))) 
```

## FRUIT INITIATION

Using (within-year) standardized traits.

### Global models (SI)

#### Linear effects

```{r}
fr_init_linear<-glm(cbind(fr_init=n_init_fr,
                fr_no_init=n_fl-n_init_fr)~avFD_std+var_std+
                      skew_std+kurt_std+year+ 
                      # Include main effect of year here
                      # but not in selection models!
                      avFD_std:year+var_std:year+skew_std:year+kurt_std:year,
                    data_ids,family="binomial")
tab_model(fr_init_linear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, linear effects"))
Anova(fr_init_linear) # Use type II (now) or III?
check_collinearity(glm(cbind(fr_init=n_init_fr,
                fr_no_init=n_fl-n_init_fr)~avFD_std+var_std+
                         skew_std+kurt_std+year,
                       data_ids,family="binomial"))
```

#### Non-linear effects

```{r}
fr_init_nonlinear<-glm(cbind(fr_init=n_init_fr,
                fr_no_init=n_fl-n_init_fr)~
                         avFD_std+var_std+skew_std+kurt_std+year+ 
                         avFD_std:year+var_std:year+skew_std:year+kurt_std:year+
                         I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                         I(avFD_std^2):year+I(var_std^2):year+
                         I(skew_std^2):year+I(kurt_std^2):year,
                       data_ids,family="binomial")
tab_model(fr_init_nonlinear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, non linear effects"))
Anova(fr_init_nonlinear) # Use type II (now) or III?
```

### Yearly models

#### Linear effects

```{r}
fr_init_linear_87<-glm(cbind(fr_init=n_init_fr,
                fr_no_init=n_fl-n_init_fr)~
                         avFD_std+var_std+skew_std+kurt_std,
                       subset(data_ids,year==1987),family="binomial")
fr_init_linear_88<-glm(cbind(fr_init=n_init_fr,
                fr_no_init=n_fl-n_init_fr)~
                         avFD_std+var_std+skew_std+kurt_std,
                    subset(data_ids,year==1988),family="binomial")
fr_init_linear_89<-glm(cbind(fr_init=n_init_fr,
                fr_no_init=n_fl-n_init_fr)~
                         avFD_std+var_std+skew_std+kurt_std,
                    subset(data_ids,year==1989),family="binomial")
tab_model(fr_init_linear_87,fr_init_linear_88,fr_init_linear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit initiation, linear effects")
check_collinearity(fr_init_linear_87)
check_collinearity(fr_init_linear_88)
check_collinearity(fr_init_linear_89)
Anova(fr_init_linear_87)
Anova(fr_init_linear_88)
Anova(fr_init_linear_89) 
```

#### Non-linear effects

```{r}
fr_init_nonlinear_87<-glm(cbind(fr_init=n_init_fr,
                fr_no_init=n_fl-n_init_fr)~
                            avFD_std+var_std+skew_std+kurt_std+
                            I(avFD_std^2)+I(var_std^2)+
                            I(skew_std^2)+I(kurt_std^2),
                          subset(data_ids,year==1987),family="binomial")
fr_init_nonlinear_88<-glm(cbind(fr_init=n_init_fr,
                fr_no_init=n_fl-n_init_fr)~
                            avFD_std+var_std+skew_std+kurt_std+
                            I(avFD_std^2)+I(var_std^2)+
                            I(skew_std^2)+I(kurt_std^2),
                    subset(data_ids,year==1988),family="binomial")
fr_init_nonlinear_89<-glm(cbind(fr_init=n_init_fr,
                fr_no_init=n_fl-n_init_fr)~
                            avFD_std+var_std+skew_std+kurt_std+
                            I(avFD_std^2)+I(var_std^2)+
                            I(skew_std^2)+I(kurt_std^2),
                    subset(data_ids,year==1989),family="binomial")
tab_model(fr_init_nonlinear_87,fr_init_nonlinear_88,fr_init_nonlinear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit initiation, nonlinear effects")
Anova(fr_init_nonlinear_87)
Anova(fr_init_nonlinear_88)
Anova(fr_init_nonlinear_89) 
```

## FRUIT MATURATION

Using (within-year) standardized traits.

### Global models (SI)

#### Linear effects

```{r}
fr_mat_linear<-glm(cbind(fr_mat=n_mat_intact_fr,
                fr_no_mat=n_init_fr-n_mat_intact_fr)~avFD_std+var_std+
                      skew_std+kurt_std+year+ 
                      # Include main effect of year here
                      # but not in selection models!
                      avFD_std:year+var_std:year+skew_std:year+kurt_std:year,
                    data_ids,family="binomial")
tab_model(fr_mat_linear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit maturation, linear effects"))
Anova(fr_mat_linear) # Use type II (now) or III?
check_collinearity(glm(cbind(fr_mat=n_mat_intact_fr,
                fr_no_mat=n_init_fr-n_mat_intact_fr)~avFD_std+var_std+
                         skew_std+kurt_std+year,
                       data_ids,family="binomial"))
```

#### Non-linear effects

```{r}
fr_mat_nonlinear<-glm(cbind(fr_mat=n_mat_intact_fr,
                fr_no_mat=n_init_fr-n_mat_intact_fr)~
                         avFD_std+var_std+skew_std+kurt_std+year+ 
                         avFD_std:year+var_std:year+skew_std:year+kurt_std:year+
                         I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                         I(avFD_std^2):year+I(var_std^2):year+
                         I(skew_std^2):year+I(kurt_std^2):year,
                       data_ids,family="binomial")
tab_model(fr_mat_nonlinear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit maturation, non linear effects"))
Anova(fr_mat_nonlinear) # Use type II (now) or III?
```

### Yearly models

#### Linear effects

```{r}
fr_mat_linear_87<-glm(cbind(fr_mat=n_mat_intact_fr,
                fr_no_mat=n_init_fr-n_mat_intact_fr)~
                         avFD_std+var_std+skew_std+kurt_std,
                       subset(data_ids,year==1987),family="binomial")
fr_mat_linear_88<-glm(cbind(fr_mat=n_mat_intact_fr,
                fr_no_mat=n_init_fr-n_mat_intact_fr)~
                         avFD_std+var_std+skew_std+kurt_std,
                    subset(data_ids,year==1988),family="binomial")
fr_mat_linear_89<-glm(cbind(fr_mat=n_mat_intact_fr,
                fr_no_mat=n_init_fr-n_mat_intact_fr)~
                         avFD_std+var_std+skew_std+kurt_std,
                    subset(data_ids,year==1989),family="binomial")
tab_model(fr_mat_linear_87,fr_mat_linear_88,fr_mat_linear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit maturation, linear effects")
check_collinearity(fr_mat_linear_87)
check_collinearity(fr_mat_linear_88)
check_collinearity(fr_mat_linear_89)
Anova(fr_mat_linear_87)
Anova(fr_mat_linear_88)
Anova(fr_mat_linear_89) 
```

#### Non-linear effects

```{r}
fr_mat_nonlinear_87<-glm(cbind(fr_mat=n_mat_intact_fr,
                fr_no_mat=n_init_fr-n_mat_intact_fr)~
                            avFD_std+var_std+skew_std+kurt_std+
                            I(avFD_std^2)+I(var_std^2)+
                            I(skew_std^2)+I(kurt_std^2),
                          subset(data_ids,year==1987),family="binomial")
fr_mat_nonlinear_88<-glm(cbind(fr_mat=n_mat_intact_fr,
                fr_no_mat=n_init_fr-n_mat_intact_fr)~
                            avFD_std+var_std+skew_std+kurt_std+
                            I(avFD_std^2)+I(var_std^2)+
                            I(skew_std^2)+I(kurt_std^2),
                    subset(data_ids,year==1988),family="binomial")
fr_mat_nonlinear_89<-glm(cbind(fr_mat=n_mat_intact_fr,
                fr_no_mat=n_init_fr-n_mat_intact_fr)~
                            avFD_std+var_std+skew_std+kurt_std+
                            I(avFD_std^2)+I(var_std^2)+
                            I(skew_std^2)+I(kurt_std^2),
                    subset(data_ids,year==1989),family="binomial")
tab_model(fr_mat_nonlinear_87,fr_mat_nonlinear_88,fr_mat_nonlinear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit maturation, nonlinear effects")
Anova(fr_mat_nonlinear_87)
Anova(fr_mat_nonlinear_88)
Anova(fr_mat_nonlinear_89) 
```

## SEEDS ESCAPING PREDATION

Using (within-year) standardized traits.

### Global models (SI)

#### Linear effects

```{r}
seed_escpred_linear<-glm(cbind(npr_seeds=round(n_seed)-round(n_preyed_seed),
                        pr_seeds=round(n_preyed_seed))~
                          avFD_std+var_std+skew_std+kurt_std+year+ 
                          avFD_std:year+var_std:year+
                          skew_std:year+kurt_std:year,
                        data_ids,family="binomial")
tab_model(seed_escpred_linear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, linear effects"))
Anova(seed_escpred_linear)
check_collinearity(glm(cbind(npr_seeds=round(n_seed)-round(n_preyed_seed),
                        pr_seeds=round(n_preyed_seed))~
                          avFD_std+var_std+skew_std+kurt_std+year,
                        data_ids,family="binomial"))
```

According to Anova, differences among years in the effects of avFD and skew.

##### Plot predictions

```{r}
plot(ggpredict(seed_escpred_linear,terms=c("avFD_std [all]","year"))) 
# Significant diffs among years
plot(ggpredict(seed_escpred_linear,terms=c("var_std [all]"))) 
# Main effect signficant
plot(ggpredict(seed_escpred_linear,terms=c("year [all]"))) 
# Main effect signficant
plot(ggpredict(seed_escpred_linear,terms=c("skew_std [all]","year"))) 
# Significant diffs among years
```

#### Non-linear effects

```{r}
seed_escpred_nonlinear<-glm(cbind(npr_seeds=round(n_seed)-round(n_preyed_seed),
                        pr_seeds=round(n_preyed_seed))~
                          avFD_std+var_std+skew_std+kurt_std+year+ 
                          avFD_std:year+var_std:year+
                          skew_std:year+kurt_std:year+
                          I(avFD_std^2)+I(var_std^2)+
                          I(skew_std^2)+I(kurt_std^2)+
                          I(avFD_std^2):year+I(var_std^2):year+
                          I(skew_std^2):year+I(kurt_std^2):year,
                        data_ids,family="binomial")
tab_model(seed_escpred_nonlinear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, non linear effects"))
Anova(seed_escpred_nonlinear) # Use type II (now) or III?
```

Significant non-linear effects according to Anova: I(var_std^2), I(skew_std^2), year:I(avFD_std^2), year:I(skew_std^2)

##### Plot predictions

```{r}
plot(ggpredict(seed_escpred_nonlinear,terms=c("var_std [all]"))) 
# Quadratic effect
plot(ggpredict(seed_escpred_nonlinear,terms=c("skew_std [all]"))) 
# Quadratic effect
plot(ggpredict(seed_escpred_nonlinear,terms=c("avFD_std [all]","year"))) 
# Quadratic effect, differences among years
plot(ggpredict(seed_escpred_nonlinear,terms=c("skew_std [all]","year"))) 
# Quadratic effect, differences among years
```

### Yearly models

#### Linear effects

```{r}
seed_escpred_linear_87<-glm(cbind(npr_seeds=round(n_seed)-round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std+skew_std+kurt_std,
                            subset(data_ids,year==1987&n_seed>0),
                            family="binomial")
data_seed_esc_pred_88<-subset(data_ids,year==1988&n_seed>0&
                                !is.na(avFD_std)&!is.na(var_std)&
                                !is.na(skew_std)&!is.na(kurt_std))
seed_escpred_linear_88<-glm(cbind(npr_seeds=round(n_seed)-round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std+skew_std+kurt_std,
                            data_seed_esc_pred_88,
                            family="binomial")
seed_escpred_linear_89<-glm(cbind(npr_seeds=round(n_seed)-round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std+skew_std+kurt_std,
                            subset(data_ids,year==1989&n_seed>0),
                            family="binomial")
tab_model(seed_escpred_linear_87,seed_escpred_linear_88,seed_escpred_linear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Seeds escaping predation, linear effects")
check_collinearity(seed_escpred_linear_87)
check_collinearity(seed_escpred_linear_88)
check_collinearity(seed_escpred_linear_89)
Anova(seed_escpred_linear_87)
Anova(seed_escpred_linear_88)
Anova(seed_escpred_linear_89)
```

##### Plot predictions

```{r}
plot(ggpredict(seed_escpred_linear_87,terms=c("avFD_std [all]"))) 
plot(ggpredict(seed_escpred_linear_87,terms=c("var_std [all]"))) 
plot(ggpredict(seed_escpred_linear_87,terms=c("skew_std [all]"))) 
plot(ggpredict(seed_escpred_linear_87,terms=c("kurt_std [all]"))) 
```

```{r}
plot(ggpredict(seed_escpred_linear_88,terms=c("avFD_std [all]"))) 
plot(ggpredict(seed_escpred_linear_88,terms=c("var_std [all]"))) 
plot(ggpredict(seed_escpred_linear_88,terms=c("skew_std [all]"))) 
```

```{r}
plot(ggpredict(seed_escpred_linear_89,terms=c("var_std [all]"))) 
plot(ggpredict(seed_escpred_linear_89,terms=c("skew_std [all]"))) 
```

#### Non-linear effects

```{r}
seed_escpred_nonlinear_87<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+skew_std+kurt_std+
                                 I(avFD_std^2)+I(var_std^2)+
                                 I(skew_std^2)+I(kurt_std^2),
                               subset(data_ids,year==1987&n_seed>0),
                               family="binomial")
seed_escpred_nonlinear_88<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+skew_std+kurt_std+
                                 I(avFD_std^2)+I(var_std^2)+
                                 I(skew_std^2)+I(kurt_std^2),
                               subset(data_ids,year==1988&n_seed>0),
                               family="binomial")
seed_escpred_nonlinear_89<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+skew_std+kurt_std+
                                 I(avFD_std^2)+I(var_std^2)+
                                 I(skew_std^2)+I(kurt_std^2),
                               subset(data_ids,year==1989&n_seed>0),
                               family="binomial")
# nobs(seed_escpred_nonlinear_89)/
# dim(model.matrix(seed_escpred_nonlinear_89))[2] = 7.2
# Careful! Only case when this ratio is <10
tab_model(seed_escpred_nonlinear_87,seed_escpred_nonlinear_88,
          seed_escpred_nonlinear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Seeds escaping predation, nonlinear effects")
Anova(seed_escpred_nonlinear_87)
Anova(seed_escpred_nonlinear_88)
Anova(seed_escpred_nonlinear_89) 
```

##### Plot predictions

```{r}
plot(ggpredict(seed_escpred_nonlinear_87,terms=c("skew_std [all]")))
```

```{r}
plot(ggpredict(seed_escpred_nonlinear_88,terms=c("avFD_std [all]")))
```

```{r}
plot(ggpredict(seed_escpred_nonlinear_89,terms=c("avFD_std [all]")))
```

## PHENOTYPIC SELECTION with n_fl

Try with n_fl --> log --> std

```{r}
data_ids<-data_ids%>%
  mutate(n_fl_log=log(n_fl))%>%
  group_by(year)%>%
  mutate(n_fl_log_std=as.vector(scale(n_fl_log)))
```


Using (within-year) standardized traits.

### Global models  (SI)

#### Linear effects

Including only linear effects and interactions with year.

```{r}
sel_nfl_linear<-lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std+n_fl_log_std+
              avFD_std:year+var_std:year+skew_std:year+kurt_std:year,
              # Not including main effect of yr cause fitness rel within yrs
              subset(data_ids,!is.na(avFD_std)&!is.na(var_std)&
                       !is.na(skew_std)&!is.na(kurt_std)))
tab_model(sel_nfl_linear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, linear effects"))
Anova(sel_nfl_linear)
check_collinearity(lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std+n_fl_std,
              subset(data_ids,!is.na(avFD_std)&!is.na(var_std)&
                       !is.na(skew_std)&!is.na(kurt_std))))
```

According to Anova, no differences among years.

##### Plot predictions

```{r}
plot(ggpredict(sel_nfl_linear,terms=c("var_std [all]")))
plot(ggpredict(sel_nfl_linear,terms=c("skew_std [all]")))
```

##### BCA intervals

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[2]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[3]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[4]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[5]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[6]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD_std:year1988
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[7]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD_std:year1989
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[8]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std:year1988
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[9]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std:year1989
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[10]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std:year1988
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[11]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std:year1989
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[12]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std:year1988
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[13]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std:year1989
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[14]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,], skew_std_ci[1,], kurt_std_ci[1,], n_fl_log_std_ci[1,],
        avFD_std_year1988_ci[1,],avFD_std_year1989_ci[1,],var_std_year1988_ci[1,],
        var_std_year1989_ci[1,],skew_std_year1988_ci[1,],skew_std_year1989_ci[1,],
        kurt_std_year1988_ci[1,],kurt_std_year1989_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,], skew_std_ci[2,], kurt_std_ci[2,], n_fl_log_std_ci[2,],
        avFD_std_year1988_ci[2,],avFD_std_year1989_ci[2,],var_std_year1988_ci[2,],
        var_std_year1989_ci[2,],skew_std_year1988_ci[2,],skew_std_year1989_ci[2,],
        kurt_std_year1988_ci[2,],kurt_std_year1989_ci[2,])
)
colnames(BCIs_sel_nfl_linear)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear) <- c("avFD_std","var_std","skew_std","kurt_std","n_fl_log_std",
                                "avFD_std_year1988","avFD_std_year1988","var_std_year1988",
                                "var_std_year1989","skew_std_year1988","skew_std_year1989",
                                "kurt_std_year1988","kurt_std_year1989")
save(BCIs_sel_nfl_linear,file="output/BCIs_sel_nfl_linear.RData")
```

```{r}
BCIs_sel_nfl_linear
```

Similar to significances with Anova

#### Non-linear effects

```{r}
sel_nfl_nonlinear<-lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std+
                        n_fl_log_std+
                        avFD_std:year+var_std:year+skew_std:year+kurt_std:year+
                        I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                        I(n_fl_log_std^2)+
                        I(avFD_std^2):year+I(var_std^2):year+
                        I(skew_std^2):year+I(kurt_std^2):year,
                      subset(data_ids,!is.na(avFD_std)&!is.na(var_std)&
                               !is.na(skew_std)&!is.na(kurt_std)))
tab_model(sel_nfl_nonlinear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects"))
Anova(sel_nfl_nonlinear)
plot(check_collinearity(sel_nfl_nonlinear))
```

Only the quadratic effect of flower number is significant.

##### BCA intervals

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[7]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[8]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[9]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std2
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[10]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[11]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD_std2:year1988
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[20]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD_std2:year1989
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[21]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2:year1988
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[22]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2:year1989
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[23]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2:year1988
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[24]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2:year1989
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[25]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std22:year1988
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[26]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std2:year1989
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[27]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear <- cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,], skew_std2_ci[1,], kurt_std2_ci[1,],
        n_fl_log_std2_ci[1,],
        avFD_std2_year1988_ci[1,],avFD_std2_year1989_ci[1,],
        var_std2_year1988_ci[1,],var_std2_year1989_ci[1,],
        skew_std2_year1988_ci[1,],skew_std2_year1989_ci[1,],
        kurt_std2_year1988_ci[1,],kurt_std2_year1989_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,], skew_std2_ci[2,], kurt_std2_ci[2,],
        n_fl_log_std2_ci[2,],
        avFD_std2_year1988_ci[2,],avFD_std2_year1989_ci[2,],
        var_std2_year1988_ci[2,],var_std2_year1989_ci[2,],
        skew_std2_year1988_ci[2,],skew_std2_year1989_ci[2,],
        kurt_std2_year1988_ci[2,],kurt_std2_year1989_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear)<-c("avFD_std2","var_std2","skew_std2",
                                    "kurt_std2","n_fl_log_std2",
                                    "avFD_std2_year1988","avFD_std2_year1989",
                                    "var_std2_year1988","var_std2_year1989",
                                    "skew_std2_year1988","skew_std2_year1989",
                                    "kurt_std2_year1988","kurt_std2_year1989")
save(BCIs_sel_nfl_nonlinear,file="output/BCIs_sel_nfl_nonlinear.RData")
```

```{r}
BCIs_sel_nfl_nonlinear
```

### Yearly models

#### Linear effects

```{r}
sel_nfl_linear_87<-lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std+
                        n_fl_log_std,
                      subset(data_ids,year==1987&
                               !is.na(avFD_std)&!is.na(var_std)&
                               !is.na(skew_std)&!is.na(kurt_std)))
sel_nfl_linear_88<-lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std+
                        n_fl_log_std,
                      subset(data_ids,year==1988&
                               !is.na(avFD_std)&!is.na(var_std)&
                               !is.na(skew_std)&!is.na(kurt_std)))
sel_nfl_linear_89<-lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std+
                        n_fl_log_std,
                      subset(data_ids,year==1989&
                               !is.na(avFD_std)&!is.na(var_std)&
                               !is.na(skew_std)&!is.na(kurt_std)))
tab_model(sel_nfl_linear_87,sel_nfl_linear_88,sel_nfl_linear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Selection, linear effects")
check_collinearity(sel_nfl_linear_87)
check_collinearity(sel_nfl_linear_88)
check_collinearity(sel_nfl_linear_89)
Anova(sel_nfl_linear_87)
Anova(sel_nfl_linear_88)
Anova(sel_nfl_linear_89)
```

##### Plot predictions

```{r}
plot(ggpredict(sel_nfl_linear_87,terms=c("var_std [all]")))
plot(ggpredict(sel_nfl_linear_89,terms=c("skew_std [all]")))
```

##### BCA intervals

###### 1987

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_87) coef(sel_nfl_linear_87)[2]
b <- car::Boot(sel_nfl_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_87) coef(sel_nfl_linear_87)[3]
b <- car::Boot(sel_nfl_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std
slp <- function(sel_nfl_linear_87) coef(sel_nfl_linear_87)[4]
b <- car::Boot(sel_nfl_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std
slp <- function(sel_nfl_linear_87) coef(sel_nfl_linear_87)[5]
b <- car::Boot(sel_nfl_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_87) coef(sel_nfl_linear_87)[6]
b <- car::Boot(sel_nfl_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_87 <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,], skew_std_ci[1,], kurt_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,], skew_std_ci[2,], kurt_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_87)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_87)<-c("avFD_std","var_std","skew_std","kurt_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_87,file="output/BCIs_sel_nfl_linear_87.RData")
```

```{r}
BCIs_sel_nfl_linear_87
```

###### 1988

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_88) coef(sel_nfl_linear_88)[2]
b <- car::Boot(sel_nfl_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_88) coef(sel_nfl_linear_88)[3]
b <- car::Boot(sel_nfl_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std
slp <- function(sel_nfl_linear_88) coef(sel_nfl_linear_88)[4]
b <- car::Boot(sel_nfl_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std
slp <- function(sel_nfl_linear_88) coef(sel_nfl_linear_88)[5]
b <- car::Boot(sel_nfl_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_88) coef(sel_nfl_linear_88)[6]
b <- car::Boot(sel_nfl_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_88 <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,], skew_std_ci[1,], kurt_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,], skew_std_ci[2,], kurt_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_88)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_88)<-c("avFD_std","var_std","skew_std","kurt_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_88,file="output/BCIs_sel_nfl_linear_88.RData")
```

```{r}
BCIs_sel_nfl_linear_88
```

###### 1989

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_89) coef(sel_nfl_linear_89)[2]
b <- car::Boot(sel_nfl_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_89) coef(sel_nfl_linear_89)[3]
b <- car::Boot(sel_nfl_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std
slp <- function(sel_nfl_linear_89) coef(sel_nfl_linear_89)[4]
b <- car::Boot(sel_nfl_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std
slp <- function(sel_nfl_linear_89) coef(sel_nfl_linear_89)[5]
b <- car::Boot(sel_nfl_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_89) coef(sel_nfl_linear_89)[6]
b <- car::Boot(sel_nfl_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_89 <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,], skew_std_ci[1,], kurt_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,], skew_std_ci[2,], kurt_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_89)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_89)<-c("avFD_std","var_std","skew_std","kurt_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_89,file="output/BCIs_sel_nfl_linear_89.RData")
```

```{r}
BCIs_sel_nfl_linear_89
```

#### Non-linear effects

```{r}
sel_nfl_nonlinear_87<-lm(fitness_rel~avFD_std+var_std+
                           skew_std+kurt_std+n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+
                           I(skew_std^2)+I(kurt_std^2)+I(n_fl_log_std^2),
                         subset(data_ids,year==1987&
                                  !is.na(avFD_std)&!is.na(var_std)&
                                  !is.na(skew_std)&!is.na(kurt_std)))
sel_nfl_nonlinear_88<-lm(fitness_rel~avFD_std+var_std+
                           skew_std+kurt_std+n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+
                           I(skew_std^2)+I(kurt_std^2)+I(n_fl_log_std^2),
                         subset(data_ids,year==1988&
                                  !is.na(avFD_std)&!is.na(var_std)&
                                  !is.na(skew_std)&!is.na(kurt_std)))
sel_nfl_nonlinear_89<-lm(fitness_rel~avFD_std+var_std+
                           skew_std+kurt_std+n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+
                           I(skew_std^2)+I(kurt_std^2)+I(n_fl_log_std^2),
                           subset(data_ids,year==1989&
                                    !is.na(avFD_std)&!is.na(var_std)&
                                    !is.na(skew_std)&!is.na(kurt_std)))
tab_model(sel_nfl_nonlinear_87,sel_nfl_nonlinear_88,sel_nfl_nonlinear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Selection, non-linear effects")
Anova(sel_nfl_nonlinear_87)
Anova(sel_nfl_nonlinear_88)
Anova(sel_nfl_nonlinear_89)
```

##### BCA intervals

###### 1987

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_87) coef(sel_nfl_nonlinear_87)[7]
b <- car::Boot(sel_nfl_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_87) coef(sel_nfl_nonlinear_87)[8]
b <- car::Boot(sel_nfl_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2
slp <- function(sel_nfl_nonlinear_87) coef(sel_nfl_nonlinear_87)[9]
b <- car::Boot(sel_nfl_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std2
slp <- function(sel_nfl_nonlinear_87) coef(sel_nfl_nonlinear_87)[10]
b <- car::Boot(sel_nfl_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_87) coef(sel_nfl_nonlinear_87)[11]
b <- car::Boot(sel_nfl_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_87<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,], skew_std2_ci[1,], kurt_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,], skew_std2_ci[2,], kurt_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_87)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_87)<-c("avFD_std2","var_std2","skew_std2",
                                    "kurt_std2","n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_87,file="output/BCIs_sel_nfl_nonlinear_87.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_87
```

###### 1988

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_88) coef(sel_nfl_nonlinear_88)[7]
b <- car::Boot(sel_nfl_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_88) coef(sel_nfl_nonlinear_88)[8]
b <- car::Boot(sel_nfl_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2
slp <- function(sel_nfl_nonlinear_88) coef(sel_nfl_nonlinear_88)[9]
b <- car::Boot(sel_nfl_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std2
slp <- function(sel_nfl_nonlinear_88) coef(sel_nfl_nonlinear_88)[10]
b <- car::Boot(sel_nfl_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_88) coef(sel_nfl_nonlinear_88)[11]
b <- car::Boot(sel_nfl_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_88<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,], skew_std2_ci[1,], kurt_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,], skew_std2_ci[2,], kurt_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_88)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_88)<-c("avFD_std2","var_std2","skew_std2",
                                    "kurt_std2","n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_88,file="output/BCIs_sel_nfl_nonlinear_88.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_88
```

###### 1989

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_89) coef(sel_nfl_nonlinear_89)[7]
b <- car::Boot(sel_nfl_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_89) coef(sel_nfl_nonlinear_89)[8]
b <- car::Boot(sel_nfl_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2
slp <- function(sel_nfl_nonlinear_89) coef(sel_nfl_nonlinear_89)[9]
b <- car::Boot(sel_nfl_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std2
slp <- function(sel_nfl_nonlinear_89) coef(sel_nfl_nonlinear_89)[10]
b <- car::Boot(sel_nfl_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_89) coef(sel_nfl_nonlinear_89)[11]
b <- car::Boot(sel_nfl_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_89<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,], skew_std2_ci[1,], kurt_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,], skew_std2_ci[2,], kurt_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_89)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_89)<-c("avFD_std2","var_std2","skew_std2",
                                    "kurt_std2","n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_89,file="output/BCIs_sel_nfl_nonlinear_89.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_89
```

## SI: ABSOLUTE FITNESS ~ ABSOLUTE TRAITS

### Global models

#### Linear effects

Including only linear effects and interactions with year.

```{r}
abs_nfl_linear<-lm(fitness~avFD+var+skew+kurt+n_fl_log+year+
              avFD:year+var:year+skew:year+kurt:year,
              # Including main effect of yr cause fitness is not rel within yrs
              subset(data_ids,!is.na(avFD_std)&!is.na(var_std)&
                       !is.na(skew_std)&!is.na(kurt_std)))
tab_model(abs_nfl_linear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Absolute fitness and traits, linear effects"))
Anova(abs_nfl_linear)
check_collinearity(lm(fitness~avFD+var+skew+kurt+n_fl_log,
              subset(data_ids,!is.na(avFD_std)&!is.na(var_std)&
                       !is.na(skew_std)&!is.na(kurt_std))))
```

##### BCA intervals

```{r eval=FALSE, include=FALSE}
# avFD
slp <- function(abs_nfl_linear) coef(abs_nfl_linear)[2]
b <- car::Boot(abs_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var
slp <- function(abs_nfl_linear) coef(abs_nfl_linear)[3]
b <- car::Boot(abs_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew
slp <- function(abs_nfl_linear) coef(abs_nfl_linear)[4]
b <- car::Boot(abs_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt
slp <- function(abs_nfl_linear) coef(abs_nfl_linear)[5]
b <- car::Boot(abs_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log
slp <- function(abs_nfl_linear) coef(abs_nfl_linear)[6]
b <- car::Boot(abs_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# year1988
slp <- function(abs_nfl_linear) coef(abs_nfl_linear)[7]
b <- car::Boot(abs_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# year1989
slp <- function(abs_nfl_linear) coef(abs_nfl_linear)[8]
b <- car::Boot(abs_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD:year1988
slp <- function(abs_nfl_linear) coef(abs_nfl_linear)[9]
b <- car::Boot(abs_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD:year1989
slp <- function(abs_nfl_linear) coef(abs_nfl_linear)[10]
b <- car::Boot(abs_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var:year1988
slp <- function(abs_nfl_linear) coef(abs_nfl_linear)[11]
b <- car::Boot(abs_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var:year1989
slp <- function(abs_nfl_linear) coef(abs_nfl_linear)[12]
b <- car::Boot(abs_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew:year1988
slp <- function(abs_nfl_linear) coef(abs_nfl_linear)[13]
b <- car::Boot(abs_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew:year1989
slp <- function(abs_nfl_linear) coef(abs_nfl_linear)[14]
b <- car::Boot(abs_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt:year1988
slp <- function(abs_nfl_linear) coef(abs_nfl_linear)[15]
b <- car::Boot(abs_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt:year1989
slp <- function(abs_nfl_linear) coef(abs_nfl_linear)[16]
b <- car::Boot(abs_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_abs_nfl_linear <- cbind(
  rbind(avFD_ci[1,],var_ci[1,], skew_ci[1,], kurt_ci[1,], n_fl_log_ci[1,],
        year1988_ci[1,],year1989_ci[1,],
        avFD_year1988_ci[1,],avFD_year1989_ci[1,],var_year1988_ci[1,],
        var_year1989_ci[1,],skew_year1988_ci[1,],skew_year1989_ci[1,],
        kurt_year1988_ci[1,],kurt_year1989_ci[1,]),
  rbind(avFD_ci[2,],var_ci[2,], skew_ci[2,], kurt_ci[2,], n_fl_log_ci[2,],
        year1988_ci[2,],year1989_ci[2,],
        avFD_year1988_ci[2,],avFD_year1989_ci[2,],var_year1988_ci[2,],
        var_year1989_ci[2,],skew_year1988_ci[2,],skew_year1989_ci[2,],
        kurt_year1988_ci[2,],kurt_year1989_ci[2,])
)
colnames(BCIs_abs_nfl_linear)<-c("lower","upper")
rownames(BCIs_abs_nfl_linear) <- c("avFD","var","skew","kurt","n_fl_log",
                                   "year1988","year1989",
                                   "avFD_year1988","avFD_year1989",
                                   "var_year1988","var_year1989",
                                   "skew_year1988","skew_year1989",
                                   "kurt_year1988","kurt_year1989")
save(BCIs_abs_nfl_linear,file="output/BCIs_abs_nfl_linear.RData")
```

```{r}
BCIs_abs_nfl_linear
```

#### Non-linear effects

```{r}
abs_nfl_nonlinear<-lm(fitness~avFD+var+skew+kurt+
                        n_fl_log+year+
                        avFD:year+var:year+skew:year+kurt:year+
                        I(avFD^2)+I(var^2)+I(skew^2)+I(kurt^2)+
                        I(n_fl_log^2)+
                        I(avFD^2):year+I(var^2):year+
                        I(skew^2):year+I(kurt^2):year,
                      subset(data_ids,!is.na(avFD_std)&!is.na(var_std)&
                               !is.na(skew_std)&!is.na(kurt_std)))
tab_model(abs_nfl_nonlinear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Absolute fitness and traits, non-linear effects"))
Anova(abs_nfl_nonlinear)
```

##### BCA intervals

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD2
slp <- function(abs_nfl_nonlinear) coef(abs_nfl_nonlinear)[9]
b <- car::Boot(abs_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var2
slp <- function(abs_nfl_nonlinear) coef(abs_nfl_nonlinear)[10]
b <- car::Boot(abs_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew2
slp <- function(abs_nfl_nonlinear) coef(abs_nfl_nonlinear)[11]
b <- car::Boot(abs_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt2
slp <- function(abs_nfl_nonlinear) coef(abs_nfl_nonlinear)[12]
b <- car::Boot(abs_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log2
slp <- function(abs_nfl_nonlinear) coef(abs_nfl_nonlinear)[13]
b <- car::Boot(abs_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD2:year1988
slp <- function(abs_nfl_nonlinear) coef(abs_nfl_nonlinear)[22]
b <- car::Boot(abs_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD2:year1989
slp <- function(abs_nfl_nonlinear) coef(abs_nfl_nonlinear)[23]
b <- car::Boot(abs_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var2:year1988
slp <- function(abs_nfl_nonlinear) coef(abs_nfl_nonlinear)[24]
b <- car::Boot(abs_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var2:year1989
slp <- function(abs_nfl_nonlinear) coef(abs_nfl_nonlinear)[25]
b <- car::Boot(abs_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew2:year1988
slp <- function(abs_nfl_nonlinear) coef(abs_nfl_nonlinear)[26]
b <- car::Boot(abs_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew2:year1989
slp <- function(abs_nfl_nonlinear) coef(abs_nfl_nonlinear)[27]
b <- car::Boot(abs_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt2:year1988
slp <- function(abs_nfl_nonlinear) coef(abs_nfl_nonlinear)[28]
b <- car::Boot(abs_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt2:year1989
slp <- function(abs_nfl_nonlinear) coef(abs_nfl_nonlinear)[29]
b <- car::Boot(abs_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_abs_nfl_nonlinear <- cbind(
  rbind(avFD2_ci[1,],var2_ci[1,], skew2_ci[1,], kurt2_ci[1,],
        n_fl_log2_ci[1,],
        avFD2_year1988_ci[1,],avFD2_year1989_ci[1,],
        var2_year1988_ci[1,],var2_year1989_ci[1,],
        skew2_year1988_ci[1,],skew2_year1989_ci[1,],
        kurt2_year1988_ci[1,],kurt2_year1989_ci[1,]),
  rbind(avFD2_ci[2,],var2_ci[2,], skew2_ci[2,], kurt2_ci[2,],
        n_fl_log2_ci[2,],
        avFD2_year1988_ci[2,],avFD2_year1989_ci[2,],
        var2_year1988_ci[2,],var2_year1989_ci[2,],
        skew2_year1988_ci[2,],skew2_year1989_ci[2,],
        kurt2_year1988_ci[2,],kurt2_year1989_ci[2,])
)
colnames(BCIs_abs_nfl_nonlinear)<-c("lower","upper")
rownames(BCIs_abs_nfl_nonlinear)<-c("avFD2","var2","skew2",
                                    "kurt2","n_fl_log2",
                                    "avFD2_year1988","avFD2_year1989",
                                    "var2_year1988","var2_year1989",
                                    "skew2_year1988","skew2_year1989",
                                    "kurt2_year1988","kurt2_year1989")
save(BCIs_abs_nfl_nonlinear,file="output/BCIs_abs_nfl_nonlinear.RData")
```

```{r}
BCIs_abs_nfl_nonlinear
```

### Yearly models

#### Linear effects

```{r}
abs_nfl_linear_87<-lm(fitness~avFD+var+skew+kurt+
                        n_fl_log,
                      subset(data_ids,year==1987&
                               !is.na(avFD)&!is.na(var)&
                               !is.na(skew)&!is.na(kurt)))
abs_nfl_linear_88<-lm(fitness_rel~avFD+var+skew+kurt+
                        n_fl_log,
                      subset(data_ids,year==1988&
                               !is.na(avFD)&!is.na(var)&
                               !is.na(skew)&!is.na(kurt)))
abs_nfl_linear_89<-lm(fitness_rel~avFD+var+skew+kurt+
                        n_fl_log,
                      subset(data_ids,year==1989&
                               !is.na(avFD)&!is.na(var)&
                               !is.na(skew)&!is.na(kurt)))
tab_model(abs_nfl_linear_87,abs_nfl_linear_88,abs_nfl_linear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Absolute fitness and traits, linear effects")
```


##### BCA intervals

###### 1987

```{r eval=FALSE, include=FALSE}
# avFD
slp <- function(abs_nfl_linear_87) coef(abs_nfl_linear_87)[2]
b <- car::Boot(abs_nfl_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var
slp <- function(abs_nfl_linear_87) coef(abs_nfl_linear_87)[3]
b <- car::Boot(abs_nfl_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew
slp <- function(abs_nfl_linear_87) coef(abs_nfl_linear_87)[4]
b <- car::Boot(abs_nfl_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt
slp <- function(abs_nfl_linear_87) coef(abs_nfl_linear_87)[5]
b <- car::Boot(abs_nfl_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log
slp <- function(abs_nfl_linear_87) coef(abs_nfl_linear_87)[6]
b <- car::Boot(abs_nfl_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_abs_nfl_linear_87 <- cbind(
  rbind(avFD_ci[1,],var_ci[1,], skew_ci[1,], kurt_ci[1,],
        n_fl_log_ci[1,]),
  rbind(avFD_ci[2,],var_ci[2,], skew_ci[2,], kurt_ci[2,],
        n_fl_log_ci[2,])
)
colnames(BCIs_abs_nfl_linear_87)<-c("lower","upper")
rownames(BCIs_abs_nfl_linear_87)<-c("avFD","var","skew","kurt",
                                    "n_fl_log")
save(BCIs_abs_nfl_linear_87,file="output/BCIs_abs_nfl_linear_87.RData")
```

```{r}
BCIs_abs_nfl_linear_87
```

###### 1988

```{r eval=FALSE, include=FALSE}
# avFD
slp <- function(abs_nfl_linear_88) coef(abs_nfl_linear_88)[2]
b <- car::Boot(abs_nfl_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var
slp <- function(abs_nfl_linear_88) coef(abs_nfl_linear_88)[3]
b <- car::Boot(abs_nfl_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew
slp <- function(abs_nfl_linear_88) coef(abs_nfl_linear_88)[4]
b <- car::Boot(abs_nfl_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt
slp <- function(abs_nfl_linear_88) coef(abs_nfl_linear_88)[5]
b <- car::Boot(abs_nfl_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log
slp <- function(abs_nfl_linear_88) coef(abs_nfl_linear_88)[6]
b <- car::Boot(abs_nfl_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_abs_nfl_linear_88 <- cbind(
  rbind(avFD_ci[1,],var_ci[1,], skew_ci[1,], kurt_ci[1,],
        n_fl_log_ci[1,]),
  rbind(avFD_ci[2,],var_ci[2,], skew_ci[2,], kurt_ci[2,],
        n_fl_log_ci[2,])
)
colnames(BCIs_abs_nfl_linear_88)<-c("lower","upper")
rownames(BCIs_abs_nfl_linear_88)<-c("avFD","var","skew","kurt",
                                    "n_fl_log")
save(BCIs_abs_nfl_linear_88,file="output/BCIs_abs_nfl_linear_88.RData")
```

```{r}
BCIs_abs_nfl_linear_88
```

###### 1989

```{r eval=FALSE, include=FALSE}
# avFD
slp <- function(abs_nfl_linear_89) coef(abs_nfl_linear_89)[2]
b <- car::Boot(abs_nfl_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var
slp <- function(abs_nfl_linear_89) coef(abs_nfl_linear_89)[3]
b <- car::Boot(abs_nfl_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew
slp <- function(abs_nfl_linear_89) coef(abs_nfl_linear_89)[4]
b <- car::Boot(abs_nfl_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt
slp <- function(abs_nfl_linear_89) coef(abs_nfl_linear_89)[5]
b <- car::Boot(abs_nfl_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log
slp <- function(abs_nfl_linear_89) coef(abs_nfl_linear_89)[6]
b <- car::Boot(abs_nfl_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_abs_nfl_linear_89 <- cbind(
  rbind(avFD_ci[1,],var_ci[1,], skew_ci[1,], kurt_ci[1,],
        n_fl_log_ci[1,]),
  rbind(avFD_ci[2,],var_ci[2,], skew_ci[2,], kurt_ci[2,],
        n_fl_log_ci[2,])
)
colnames(BCIs_abs_nfl_linear_89)<-c("lower","upper")
rownames(BCIs_abs_nfl_linear_89)<-c("avFD","var","skew","kurt",
                                    "n_fl_log")
save(BCIs_abs_nfl_linear_89,file="output/BCIs_abs_nfl_linear_89.RData")
```

```{r}
BCIs_abs_nfl_linear_89
```

#### Non-linear effects

```{r}
abs_nfl_nonlinear_87<-lm(fitness~avFD+var+
                           skew+kurt+n_fl_log+
                           I(avFD^2)+I(var^2)+
                           I(skew^2)+I(kurt^2)+I(n_fl_log^2),
                         subset(data_ids,year==1987&
                                  !is.na(avFD)&!is.na(var)&
                                  !is.na(skew)&!is.na(kurt)))
abs_nfl_nonlinear_88<-lm(fitness~avFD+var+
                           skew+kurt+n_fl_log+
                           I(avFD^2)+I(var^2)+
                           I(skew^2)+I(kurt^2)+I(n_fl_log^2),
                         subset(data_ids,year==1988&
                                  !is.na(avFD)&!is.na(var)&
                                  !is.na(skew)&!is.na(kurt)))
abs_nfl_nonlinear_89<-lm(fitness~avFD+var+
                           skew+kurt+n_fl_log+
                           I(avFD^2)+I(var^2)+
                           I(skew^2)+I(kurt^2)+I(n_fl_log^2),
                           subset(data_ids,year==1989&
                                    !is.na(avFD)&!is.na(var)&
                                    !is.na(skew)&!is.na(kurt)))
tab_model(abs_nfl_nonlinear_87,abs_nfl_nonlinear_88,abs_nfl_nonlinear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Absolute fitness and traits, non-linear effects")
```

##### BCA intervals

###### 1987

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD2
slp <- function(abs_nfl_nonlinear_87) coef(abs_nfl_nonlinear_87)[7]
b <- car::Boot(abs_nfl_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var2
slp <- function(abs_nfl_nonlinear_87) coef(abs_nfl_nonlinear_87)[8]
b <- car::Boot(abs_nfl_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew2
slp <- function(abs_nfl_nonlinear_87) coef(abs_nfl_nonlinear_87)[9]
b <- car::Boot(abs_nfl_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt2
slp <- function(abs_nfl_nonlinear_87) coef(abs_nfl_nonlinear_87)[10]
b <- car::Boot(abs_nfl_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log2
slp <- function(abs_nfl_nonlinear_87) coef(abs_nfl_nonlinear_87)[11]
b <- car::Boot(abs_nfl_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_abs_nfl_nonlinear_87<-cbind(
  rbind(avFD2_ci[1,],var2_ci[1,], skew2_ci[1,], kurt2_ci[1,],
        n_fl_log2_ci[1,]),
  rbind(avFD2_ci[2,],var2_ci[2,], skew2_ci[2,], kurt2_ci[2,],
        n_fl_log2_ci[2,])
)
colnames(BCIs_abs_nfl_nonlinear_87)<-c("lower","upper")
rownames(BCIs_abs_nfl_nonlinear_87)<-c("avFD2","var2","skew2",
                                    "kurt2","n_fl_log2")
save(BCIs_abs_nfl_nonlinear_87,file="output/BCIs_abs_nfl_nonlinear_87.RData")
```

```{r}
BCIs_abs_nfl_nonlinear_87
```

###### 1988

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD2
slp <- function(abs_nfl_nonlinear_88) coef(abs_nfl_nonlinear_88)[7]
b <- car::Boot(abs_nfl_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var2
slp <- function(abs_nfl_nonlinear_88) coef(abs_nfl_nonlinear_88)[8]
b <- car::Boot(abs_nfl_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew2
slp <- function(abs_nfl_nonlinear_88) coef(abs_nfl_nonlinear_88)[9]
b <- car::Boot(abs_nfl_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt2
slp <- function(abs_nfl_nonlinear_88) coef(abs_nfl_nonlinear_88)[10]
b <- car::Boot(abs_nfl_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log2
slp <- function(abs_nfl_nonlinear_88) coef(abs_nfl_nonlinear_88)[11]
b <- car::Boot(abs_nfl_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_abs_nfl_nonlinear_88<-cbind(
  rbind(avFD2_ci[1,],var2_ci[1,], skew2_ci[1,], kurt2_ci[1,],
        n_fl_log2_ci[1,]),
  rbind(avFD2_ci[2,],var2_ci[2,], skew2_ci[2,], kurt2_ci[2,],
        n_fl_log2_ci[2,])
)
colnames(BCIs_abs_nfl_nonlinear_88)<-c("lower","upper")
rownames(BCIs_abs_nfl_nonlinear_88)<-c("avFD2","var2","skew2",
                                    "kurt2","n_fl_log2")
save(BCIs_abs_nfl_nonlinear_88,file="output/BCIs_abs_nfl_nonlinear_88.RData")
```

```{r}
BCIs_abs_nfl_nonlinear_88
```

###### 1989

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD2
slp <- function(abs_nfl_nonlinear_89) coef(abs_nfl_nonlinear_89)[7]
b <- car::Boot(abs_nfl_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var2
slp <- function(abs_nfl_nonlinear_89) coef(abs_nfl_nonlinear_89)[8]
b <- car::Boot(abs_nfl_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew2
slp <- function(abs_nfl_nonlinear_89) coef(abs_nfl_nonlinear_89)[9]
b <- car::Boot(abs_nfl_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt2
slp <- function(abs_nfl_nonlinear_89) coef(abs_nfl_nonlinear_89)[10]
b <- car::Boot(abs_nfl_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log2
slp <- function(abs_nfl_nonlinear_89) coef(abs_nfl_nonlinear_89)[11]
b <- car::Boot(abs_nfl_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_abs_nfl_nonlinear_89<-cbind(
  rbind(avFD2_ci[1,],var2_ci[1,], skew2_ci[1,], kurt2_ci[1,],
        n_fl_log2_ci[1,]),
  rbind(avFD2_ci[2,],var2_ci[2,], skew2_ci[2,], kurt2_ci[2,],
        n_fl_log2_ci[2,])
)
colnames(BCIs_abs_nfl_nonlinear_89)<-c("lower","upper")
rownames(BCIs_abs_nfl_nonlinear_89)<-c("avFD2","var2","skew2",
                                    "kurt2","n_fl_log2")
save(BCIs_abs_nfl_nonlinear_89,file="output/BCIs_abs_nfl_nonlinear_89.RData")
```

```{r}
BCIs_abs_nfl_nonlinear_89
```

## SI: PHENOTYPIC SELECTION without n_fl

### Global models

#### Linear effects

Including only linear effects and interactions with year.

```{r}
sel_linear<-lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std+
              avFD_std:year+var_std:year+skew_std:year+kurt_std:year,
              # Not including main effect of yr cause fitness rel within yrs
              subset(data_ids,!is.na(avFD_std)&!is.na(var_std)&
                       !is.na(skew_std)&!is.na(kurt_std)))
tab_model(sel_linear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, linear effects, without n_fl"))
Anova(sel_linear)
check_collinearity(lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std,
              subset(data_ids,!is.na(avFD_std)&!is.na(var_std)&
                       !is.na(skew_std)&!is.na(kurt_std))))
```

##### BCA intervals

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_linear) coef(sel_linear)[2]
b <- car::Boot(sel_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_linear) coef(sel_linear)[3]
b <- car::Boot(sel_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std
slp <- function(sel_linear) coef(sel_linear)[4]
b <- car::Boot(sel_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std
slp <- function(sel_linear) coef(sel_linear)[5]
b <- car::Boot(sel_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD_std:year1988
slp <- function(sel_linear) coef(sel_linear)[6]
b <- car::Boot(sel_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD_std:year1989
slp <- function(sel_linear) coef(sel_linear)[7]
b <- car::Boot(sel_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std:year1988
slp <- function(sel_linear) coef(sel_linear)[8]
b <- car::Boot(sel_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std:year1989
slp <- function(sel_linear) coef(sel_linear)[9]
b <- car::Boot(sel_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std:year1988
slp <- function(sel_linear) coef(sel_linear)[10]
b <- car::Boot(sel_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std:year1989
slp <- function(sel_linear) coef(sel_linear)[11]
b <- car::Boot(sel_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std:year1988
slp <- function(sel_linear) coef(sel_linear)[12]
b <- car::Boot(sel_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std:year1989
slp <- function(sel_linear) coef(sel_linear)[13]
b <- car::Boot(sel_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_linear <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,], skew_std_ci[1,], kurt_std_ci[1,],
        avFD_std_year1988_ci[1,],avFD_std_year1989_ci[1,],var_std_year1988_ci[1,],
        var_std_year1989_ci[1,],skew_std_year1988_ci[1,],skew_std_year1989_ci[1,],
        kurt_std_year1988_ci[1,],kurt_std_year1989_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,], skew_std_ci[2,], kurt_std_ci[2,],
        avFD_std_year1988_ci[2,],avFD_std_year1989_ci[2,],var_std_year1988_ci[2,],
        var_std_year1989_ci[2,],skew_std_year1988_ci[2,],skew_std_year1989_ci[2,],
        kurt_std_year1988_ci[2,],kurt_std_year1989_ci[2,])
)
colnames(BCIs_sel_linear)<-c("lower","upper")
rownames(BCIs_sel_linear) <- c("avFD_std","var_std","skew_std","kurt_std",
                                "avFD_std_year1988","avFD_std_year1988","var_std_year1988",
                                "var_std_year1989","skew_std_year1988","skew_std_year1989",
                                "kurt_std_year1988","kurt_std_year1989")
save(BCIs_sel_linear,file="output/BCIs_sel_linear.RData")
```

```{r}
BCIs_sel_linear
```

#### Non-linear effects

```{r}
sel_nonlinear<-lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std+
                    avFD_std:year+var_std:year+skew_std:year+kurt_std:year+
                    I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+ 
                    I(avFD_std^2):year+I(var_std^2):year+
                    I(skew_std^2):year+I(kurt_std^2):year,
                  subset(data_ids,!is.na(avFD_std)&!is.na(var_std)&
                           !is.na(skew_std)&!is.na(kurt_std)))
tab_model(sel_nonlinear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, without n_fl"))
Anova(sel_nonlinear)
plot(check_collinearity(sel_nonlinear))
```

##### BCA intervals

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nonlinear) coef(sel_nonlinear)[6]
b <- car::Boot(sel_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nonlinear) coef(sel_nonlinear)[7]
b <- car::Boot(sel_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2
slp <- function(sel_nonlinear) coef(sel_nonlinear)[8]
b <- car::Boot(sel_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std2
slp <- function(sel_nonlinear) coef(sel_nonlinear)[9]
b <- car::Boot(sel_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD_std2:year1988
slp <- function(sel_nonlinear) coef(sel_nonlinear)[18]
b <- car::Boot(sel_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD_std2:year1989
slp <- function(sel_nonlinear) coef(sel_nonlinear)[19]
b <- car::Boot(sel_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2:year1988
slp <- function(sel_nonlinear) coef(sel_nonlinear)[20]
b <- car::Boot(sel_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2:year1989
slp <- function(sel_nonlinear) coef(sel_nonlinear)[21]
b <- car::Boot(sel_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2:year1988
slp <- function(sel_nonlinear) coef(sel_nonlinear)[22]
b <- car::Boot(sel_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2:year1989
slp <- function(sel_nonlinear) coef(sel_nonlinear)[23]
b <- car::Boot(sel_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std22:year1988
slp <- function(sel_nonlinear) coef(sel_nonlinear)[24]
b <- car::Boot(sel_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std2:year1989
slp <- function(sel_nonlinear) coef(sel_nonlinear)[25]
b <- car::Boot(sel_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nonlinear <- cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,], skew_std2_ci[1,], kurt_std2_ci[1,],
        avFD_std2_year1988_ci[1,],avFD_std2_year1989_ci[1,],
        var_std2_year1988_ci[1,],var_std2_year1989_ci[1,],
        skew_std2_year1988_ci[1,],skew_std2_year1989_ci[1,],
        kurt_std2_year1988_ci[1,],kurt_std2_year1989_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,], skew_std2_ci[2,], kurt_std2_ci[2,],
        avFD_std2_year1988_ci[2,],avFD_std2_year1989_ci[2,],
        var_std2_year1988_ci[2,],var_std2_year1989_ci[2,],
        skew_std2_year1988_ci[2,],skew_std2_year1989_ci[2,],
        kurt_std2_year1988_ci[2,],kurt_std2_year1989_ci[2,])
)
colnames(BCIs_sel_nonlinear)<-c("lower","upper")
rownames(BCIs_sel_nonlinear)<-c("avFD_std2","var_std2","skew_std2",
                                    "kurt_std2",
                                    "avFD_std2_year1988","avFD_std2_year1989",
                                    "var_std2_year1988","var_std2_year1989",
                                    "skew_std2_year1988","skew_std2_year1989",
                                    "kurt_std2_year1988","kurt_std2_year1989")
save(BCIs_sel_nonlinear,file="output/BCIs_sel_nonlinear.RData")
```

```{r}
BCIs_sel_nonlinear
```

### Yearly models

#### Linear effects

```{r}
sel_linear_87<-lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std,
                      subset(data_ids,year==1987&
                               !is.na(avFD_std)&!is.na(var_std)&
                               !is.na(skew_std)&!is.na(kurt_std)))
sel_linear_88<-lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std,
                      subset(data_ids,year==1988&
                               !is.na(avFD_std)&!is.na(var_std)&
                               !is.na(skew_std)&!is.na(kurt_std)))
sel_linear_89<-lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std,
                      subset(data_ids,year==1989&
                               !is.na(avFD_std)&!is.na(var_std)&
                               !is.na(skew_std)&!is.na(kurt_std)))
tab_model(sel_linear_87,sel_linear_88,sel_linear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Selection, linear effects, without n_fl")
check_collinearity(sel_linear_87)
check_collinearity(sel_linear_88)
check_collinearity(sel_linear_89)
Anova(sel_linear_87)
Anova(sel_linear_88)
Anova(sel_linear_89)
```

##### BCA intervals

###### 1987

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_linear_87) coef(sel_linear_87)[2]
b <- car::Boot(sel_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_linear_87) coef(sel_linear_87)[3]
b <- car::Boot(sel_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std
slp <- function(sel_linear_87) coef(sel_linear_87)[4]
b <- car::Boot(sel_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std
slp <- function(sel_linear_87) coef(sel_linear_87)[5]
b <- car::Boot(sel_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_linear_87 <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,], skew_std_ci[1,], kurt_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,], skew_std_ci[2,], kurt_std_ci[2,])
)
colnames(BCIs_sel_linear_87)<-c("lower","upper")
rownames(BCIs_sel_linear_87)<-c("avFD_std","var_std","skew_std","kurt_std")
save(BCIs_sel_linear_87,file="output/BCIs_sel_linear_87.RData")
```

```{r}
BCIs_sel_linear_87
```

###### 1988

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_linear_88) coef(sel_linear_88)[2]
b <- car::Boot(sel_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_linear_88) coef(sel_linear_88)[3]
b <- car::Boot(sel_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std
slp <- function(sel_linear_88) coef(sel_linear_88)[4]
b <- car::Boot(sel_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std
slp <- function(sel_linear_88) coef(sel_linear_88)[5]
b <- car::Boot(sel_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_linear_88 <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,], skew_std_ci[1,], kurt_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,], skew_std_ci[2,], kurt_std_ci[2,])
)
colnames(BCIs_sel_linear_88)<-c("lower","upper")
rownames(BCIs_sel_linear_88)<-c("avFD_std","var_std","skew_std","kurt_std")
save(BCIs_sel_linear_88,file="output/BCIs_sel_linear_88.RData")
```

```{r}
BCIs_sel_linear_88
```

###### 1989

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_linear_89) coef(sel_linear_89)[2]
b <- car::Boot(sel_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_linear_89) coef(sel_linear_89)[3]
b <- car::Boot(sel_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std
slp <- function(sel_linear_89) coef(sel_linear_89)[4]
b <- car::Boot(sel_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std
slp <- function(sel_linear_89) coef(sel_linear_89)[5]
b <- car::Boot(sel_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_linear_89 <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,], skew_std_ci[1,], kurt_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,], skew_std_ci[2,], kurt_std_ci[2,])
)
colnames(BCIs_sel_linear_89)<-c("lower","upper")
rownames(BCIs_sel_linear_89)<-c("avFD_std","var_std","skew_std","kurt_std")
save(BCIs_sel_linear_89,file="output/BCIs_sel_linear_89.RData")
```

```{r}
BCIs_sel_linear_89
```

#### Non-linear effects

```{r}
sel_nonlinear_87<-lm(fitness_rel~avFD_std+var_std+
                           skew_std+kurt_std+
                           I(avFD_std^2)+I(var_std^2)+
                           I(skew_std^2)+I(kurt_std^2),
                         subset(data_ids,year==1987&
                                  !is.na(avFD_std)&!is.na(var_std)&
                                  !is.na(skew_std)&!is.na(kurt_std)))
sel_nonlinear_88<-lm(fitness_rel~avFD_std+var_std+
                           skew_std+kurt_std+
                           I(avFD_std^2)+I(var_std^2)+
                           I(skew_std^2)+I(kurt_std^2),
                         subset(data_ids,year==1988&
                                  !is.na(avFD_std)&!is.na(var_std)&
                                  !is.na(skew_std)&!is.na(kurt_std)))
sel_nonlinear_89<-lm(fitness_rel~avFD_std+var_std+
                           skew_std+kurt_std+
                           I(avFD_std^2)+I(var_std^2)+
                           I(skew_std^2)+I(kurt_std^2),
                           subset(data_ids,year==1989&
                                    !is.na(avFD_std)&!is.na(var_std)&
                                    !is.na(skew_std)&!is.na(kurt_std)))
tab_model(sel_nonlinear_87,sel_nonlinear_88,sel_nonlinear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Selection, non-linear effects, without n_fl")
Anova(sel_nonlinear_87)
Anova(sel_nonlinear_88)
Anova(sel_nonlinear_89)
```

##### BCA intervals

###### 1987

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nonlinear_87) coef(sel_nonlinear_87)[6]
b <- car::Boot(sel_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nonlinear_87) coef(sel_nonlinear_87)[7]
b <- car::Boot(sel_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2
slp <- function(sel_nonlinear_87) coef(sel_nonlinear_87)[8]
b <- car::Boot(sel_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std2
slp <- function(sel_nonlinear_87) coef(sel_nonlinear_87)[9]
b <- car::Boot(sel_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nonlinear_87<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,], skew_std2_ci[1,], kurt_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,], skew_std2_ci[2,], kurt_std2_ci[2,])
)
colnames(BCIs_sel_nonlinear_87)<-c("lower","upper")
rownames(BCIs_sel_nonlinear_87)<-c("avFD_std2","var_std2","skew_std2",
                                    "kurt_std2")
save(BCIs_sel_nonlinear_87,file="output/BCIs_sel_nonlinear_87.RData")
```

```{r}
BCIs_sel_nonlinear_87
```

###### 1988

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nonlinear_88) coef(sel_nonlinear_88)[6]
b <- car::Boot(sel_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nonlinear_88) coef(sel_nonlinear_88)[7]
b <- car::Boot(sel_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2
slp <- function(sel_nonlinear_88) coef(sel_nonlinear_88)[8]
b <- car::Boot(sel_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std2
slp <- function(sel_nonlinear_88) coef(sel_nonlinear_88)[9]
b <- car::Boot(sel_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nonlinear_88<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,], skew_std2_ci[1,], kurt_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,], skew_std2_ci[2,], kurt_std2_ci[2,])
)
colnames(BCIs_sel_nonlinear_88)<-c("lower","upper")
rownames(BCIs_sel_nonlinear_88)<-c("avFD_std2","var_std2","skew_std2",
                                    "kurt_std2")
save(BCIs_sel_nonlinear_88,file="output/BCIs_sel_nonlinear_88.RData")
```

```{r}
BCIs_sel_nonlinear_88
```

###### 1989

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nonlinear_89) coef(sel_nonlinear_89)[6]
b <- car::Boot(sel_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nonlinear_89) coef(sel_nonlinear_89)[7]
b <- car::Boot(sel_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2
slp <- function(sel_nonlinear_89) coef(sel_nonlinear_89)[8]
b <- car::Boot(sel_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std2
slp <- function(sel_nonlinear_89) coef(sel_nonlinear_89)[9]
b <- car::Boot(sel_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nonlinear_89<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,], skew_std2_ci[1,], kurt_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,], skew_std2_ci[2,], kurt_std2_ci[2,])
)
colnames(BCIs_sel_nonlinear_89)<-c("lower","upper")
rownames(BCIs_sel_nonlinear_89)<-c("avFD_std2","var_std2","skew_std2",
                                    "kurt_std2")
save(BCIs_sel_nonlinear_89,file="output/BCIs_sel_nonlinear_89.RData")
```

```{r}
BCIs_sel_nonlinear_89
```

# Figures

With multivariate model predictions

## Extract predictions from multivariate GLMs

### Fruit set

```{r}
coefs_fr_set_linear<-rbind(
  tidy(fr_set_linear_87)[2:5,]%>%mutate(year=as.factor("1987")),
  tidy(fr_set_linear_88)[2:5,]%>%mutate(year=as.factor("1988")),
  tidy(fr_set_linear_89)[2:5,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         coef=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(coef,star),
         predictor=term,
         type=as.factor("linear"))
coefs_fr_set_nonlinear<-rbind(
  tidy(fr_set_nonlinear_87)[6:9,]%>%mutate(year=as.factor("1987")),
  tidy(fr_set_nonlinear_88)[6:9,]%>%mutate(year=as.factor("1988")),
  tidy(fr_set_nonlinear_89)[6:9,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         coef=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(coef,star),
         predictor=str_extract(term, "(?<=I\\().*?(?=\\^2\\))"),
         type=as.factor("nonlinear"))
```


```{r}
prediction_fr_set_linear<-rbind(rbind(tibble(ggpredict(fr_set_linear_87,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_set_linear_88,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_set_linear_89,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="avFD_std"), # avFD_std
                    rbind(tibble(ggpredict(fr_set_linear_87,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_set_linear_88,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_set_linear_89,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="var_std"), # var_std
                    rbind(tibble(ggpredict(fr_set_linear_87,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_set_linear_88,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_set_linear_89,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="skew_std"), # skew_std
                    rbind(tibble(ggpredict(fr_set_linear_87,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_set_linear_88,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_set_linear_89,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="kurt_std"))%>% # kurt_std
  mutate(response="fr_set",type="linear")%>%
  left_join(coefs_fr_set_linear%>%
              dplyr::select(predictor,coef,year,signif,star,print,type))

prediction_fr_set_nonlinear<-rbind(rbind(tibble(ggpredict(fr_set_nonlinear_87,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_set_nonlinear_88,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_set_nonlinear_89,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="avFD_std"), # avFD_std
                    rbind(tibble(ggpredict(fr_set_nonlinear_87,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_set_nonlinear_88,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_set_nonlinear_89,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="var_std"), # var_std
                    rbind(tibble(ggpredict(fr_set_nonlinear_87,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_set_nonlinear_88,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_set_nonlinear_89,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="skew_std"), # skew_std
                    rbind(tibble(ggpredict(fr_set_nonlinear_87,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_set_nonlinear_88,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_set_nonlinear_89,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="kurt_std"))%>% # kurt_std
  mutate(response="fr_set",type="nonlinear")%>%
  left_join(coefs_fr_set_nonlinear%>%
              dplyr::select(predictor,coef,year,signif,star,print,type))
prediction_fr_set<-rbind(prediction_fr_set_linear,
                                 prediction_fr_set_nonlinear)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")))
```

### Fruit initiation

```{r}
coefs_fr_init_linear<-rbind(
  tidy(fr_init_linear_87)[2:5,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_linear_88)[2:5,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_linear_89)[2:5,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         coef=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(coef,star),
         predictor=term,
         type=as.factor("linear"))
coefs_fr_init_nonlinear<-rbind(
  tidy(fr_init_nonlinear_87)[6:9,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_nonlinear_88)[6:9,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_nonlinear_89)[6:9,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         coef=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(coef,star),
         predictor=str_extract(term, "(?<=I\\().*?(?=\\^2\\))"),
         type=as.factor("nonlinear"))
```

```{r}
prediction_fr_init_linear<-rbind(rbind(tibble(ggpredict(fr_init_linear_87,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_init_linear_88,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_init_linear_89,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="avFD_std"), # avFD_std
                    rbind(tibble(ggpredict(fr_init_linear_87,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_init_linear_88,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_init_linear_89,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="var_std"), # var_std
                    rbind(tibble(ggpredict(fr_init_linear_87,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_init_linear_88,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_init_linear_89,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="skew_std"), # skew_std
                    rbind(tibble(ggpredict(fr_init_linear_87,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_init_linear_88,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_init_linear_89,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="kurt_std"))%>% # kurt_std
  mutate(response="fr_init",type="linear")%>%
  left_join(coefs_fr_init_linear%>%
              dplyr::select(predictor,coef,year,signif,star,print,type))

prediction_fr_init_nonlinear<-rbind(rbind(tibble(ggpredict(fr_init_nonlinear_87,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_init_nonlinear_88,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_init_nonlinear_89,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="avFD_std"), # avFD_std
                    rbind(tibble(ggpredict(fr_init_nonlinear_87,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_init_nonlinear_88,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_init_nonlinear_89,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="var_std"), # var_std
                    rbind(tibble(ggpredict(fr_init_nonlinear_87,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_init_nonlinear_88,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_init_nonlinear_89,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="skew_std"), # skew_std
                    rbind(tibble(ggpredict(fr_init_nonlinear_87,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_init_nonlinear_88,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_init_nonlinear_89,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="kurt_std"))%>% # kurt_std
  mutate(response="fr_init",type="nonlinear")%>%
  left_join(coefs_fr_init_nonlinear%>%
              dplyr::select(predictor,coef,year,signif,star,print,type))
prediction_fr_init<-rbind(prediction_fr_init_linear,
                                 prediction_fr_init_nonlinear)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")))
```

### Fruit maturation

```{r}
coefs_fr_mat_linear<-rbind(
  tidy(fr_mat_linear_87)[2:5,]%>%mutate(year=as.factor("1987")),
  tidy(fr_mat_linear_88)[2:5,]%>%mutate(year=as.factor("1988")),
  tidy(fr_mat_linear_89)[2:5,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         coef=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(coef,star),
         predictor=term,
         type=as.factor("linear"))
coefs_fr_mat_nonlinear<-rbind(
  tidy(fr_mat_nonlinear_87)[6:9,]%>%mutate(year=as.factor("1987")),
  tidy(fr_mat_nonlinear_88)[6:9,]%>%mutate(year=as.factor("1988")),
  tidy(fr_mat_nonlinear_89)[6:9,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         coef=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(coef,star),
         predictor=str_extract(term, "(?<=I\\().*?(?=\\^2\\))"),
         type=as.factor("nonlinear"))
```


```{r}
prediction_fr_mat_linear<-rbind(rbind(tibble(ggpredict(fr_mat_linear_87,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_mat_linear_88,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_mat_linear_89,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="avFD_std"), # avFD_std
                    rbind(tibble(ggpredict(fr_mat_linear_87,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_mat_linear_88,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_mat_linear_89,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="var_std"), # var_std
                    rbind(tibble(ggpredict(fr_mat_linear_87,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_mat_linear_88,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_mat_linear_89,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="skew_std"), # skew_std
                    rbind(tibble(ggpredict(fr_mat_linear_87,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_mat_linear_88,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_mat_linear_89,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="kurt_std"))%>% # kurt_std
  mutate(response="fr_mat",type="linear")%>%
  left_join(coefs_fr_mat_linear%>%
              dplyr::select(predictor,coef,year,signif,star,print,type))

prediction_fr_mat_nonlinear<-rbind(rbind(tibble(ggpredict(fr_mat_nonlinear_87,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_mat_nonlinear_88,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_mat_nonlinear_89,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="avFD_std"), # avFD_std
                    rbind(tibble(ggpredict(fr_mat_nonlinear_87,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_mat_nonlinear_88,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_mat_nonlinear_89,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="var_std"), # var_std
                    rbind(tibble(ggpredict(fr_mat_nonlinear_87,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_mat_nonlinear_88,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_mat_nonlinear_89,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="skew_std"), # skew_std
                    rbind(tibble(ggpredict(fr_mat_nonlinear_87,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(fr_mat_nonlinear_88,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(fr_mat_nonlinear_89,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="kurt_std"))%>% # kurt_std
  mutate(response="fr_mat",type="nonlinear")%>%
  left_join(coefs_fr_mat_nonlinear%>%
              dplyr::select(predictor,coef,year,signif,star,print,type))
prediction_fr_mat<-rbind(prediction_fr_mat_linear,
                                 prediction_fr_mat_nonlinear)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")))
```

### Seeds escaping predation

```{r}
coefs_seed_escpred_linear<-rbind(
  tidy(seed_escpred_linear_87)[2:5,]%>%mutate(year=as.factor("1987")),
  tidy(seed_escpred_linear_88)[2:5,]%>%mutate(year=as.factor("1988")),
  tidy(seed_escpred_linear_89)[2:5,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         coef=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(coef,star),
         predictor=term,
         type=as.factor("linear"))
coefs_seed_escpred_nonlinear<-rbind(
  tidy(seed_escpred_nonlinear_87)[6:9,]%>%mutate(year=as.factor("1987")),
  tidy(seed_escpred_nonlinear_88)[6:9,]%>%mutate(year=as.factor("1988")),
  tidy(seed_escpred_nonlinear_89)[6:9,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         coef=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(coef,star),
         predictor=str_extract(term, "(?<=I\\().*?(?=\\^2\\))"),
         type=as.factor("nonlinear"))
```

```{r}
prediction_seed_escpred_linear<-rbind(rbind(tibble(ggpredict(seed_escpred_linear_87,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(seed_escpred_linear_88,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(seed_escpred_linear_89,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="avFD_std"), # avFD_std
                    rbind(tibble(ggpredict(seed_escpred_linear_87,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(seed_escpred_linear_88,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(seed_escpred_linear_89,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="var_std"), # var_std
                    rbind(tibble(ggpredict(seed_escpred_linear_87,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(seed_escpred_linear_88,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(seed_escpred_linear_89,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="skew_std"), # skew_std
                    rbind(tibble(ggpredict(seed_escpred_linear_87,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(seed_escpred_linear_88,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(seed_escpred_linear_89,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="kurt_std"))%>% # kurt_std
  mutate(response="seed_escpred",type="linear")%>%
  left_join(coefs_seed_escpred_linear%>%
              dplyr::select(predictor,coef,year,signif,star,print,type))

prediction_seed_escpred_nonlinear<-rbind(rbind(tibble(ggpredict(seed_escpred_nonlinear_87,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(seed_escpred_nonlinear_88,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(seed_escpred_nonlinear_89,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="avFD_std"), # avFD_std
                    rbind(tibble(ggpredict(seed_escpred_nonlinear_87,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(seed_escpred_nonlinear_88,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(seed_escpred_nonlinear_89,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="var_std"), # var_std
                    rbind(tibble(ggpredict(seed_escpred_nonlinear_87,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(seed_escpred_nonlinear_88,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(seed_escpred_nonlinear_89,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="skew_std"), # skew_std
                    rbind(tibble(ggpredict(seed_escpred_nonlinear_87,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(seed_escpred_nonlinear_88,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(seed_escpred_nonlinear_89,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="kurt_std"))%>% # kurt_std
  mutate(response="seed_escpred",type="nonlinear")%>%
  left_join(coefs_seed_escpred_nonlinear%>%
              dplyr::select(predictor,coef,year,signif,star,print,type))
prediction_seed_escpred<-rbind(prediction_seed_escpred_linear,
                                 prediction_seed_escpred_nonlinear)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")))
```

### Selection with n_fl

```{r}
coefs_sel_nfl_linear<-rbind(
  tidy(sel_nfl_linear_87)[2:5,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_linear_88)[2:5,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_linear_89)[2:5,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=ifelse(p.value>0.05,0,1),
         coef=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(coef,star),
         predictor=term,
         type=as.factor("linear"))%>%
  mutate(signif=factor(ifelse(row_number()==3,1,signif)))
# Change signif for skewness cause it is signif according to BCA intervals
coefs_sel_nfl_nonlinear<-rbind(
  tidy(sel_nfl_nonlinear_87)[7:10,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_nonlinear_88)[7:10,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_nonlinear_89)[7:10,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         coef=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(coef,star),
         predictor=str_extract(term, "(?<=I\\().*?(?=\\^2\\))"),
         type=as.factor("nonlinear"))
```

```{r}
prediction_sel_nfl_linear<-rbind(rbind(tibble(ggpredict(sel_nfl_linear_87,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(sel_nfl_linear_88,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(sel_nfl_linear_89,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="avFD_std"), # avFD_std
                    rbind(tibble(ggpredict(sel_nfl_linear_87,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(sel_nfl_linear_88,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(sel_nfl_linear_89,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="var_std"), # var_std
                    rbind(tibble(ggpredict(sel_nfl_linear_87,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(sel_nfl_linear_88,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(sel_nfl_linear_89,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="skew_std"), # skew_std
                    rbind(tibble(ggpredict(sel_nfl_linear_87,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(sel_nfl_linear_88,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(sel_nfl_linear_89,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="kurt_std"))%>% # kurt_std
  mutate(response="sel_nfl",type="linear")%>%
  left_join(coefs_sel_nfl_linear%>%
              dplyr::select(predictor,coef,year,signif,star,print,type))

prediction_sel_nfl_nonlinear<-rbind(rbind(tibble(ggpredict(sel_nfl_nonlinear_87,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(sel_nfl_nonlinear_88,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(sel_nfl_nonlinear_89,
                                           terms=c("avFD_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="avFD_std"), # avFD_std
                    rbind(tibble(ggpredict(sel_nfl_nonlinear_87,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(sel_nfl_nonlinear_88,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(sel_nfl_nonlinear_89,
                                           terms=c("var_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="var_std"), # var_std
                    rbind(tibble(ggpredict(sel_nfl_nonlinear_87,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(sel_nfl_nonlinear_88,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(sel_nfl_nonlinear_89,
                                           terms=c("skew_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="skew_std"), # skew_std
                    rbind(tibble(ggpredict(sel_nfl_nonlinear_87,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1987)),
                          tibble(ggpredict(sel_nfl_nonlinear_88,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1988)),
                          tibble(ggpredict(sel_nfl_nonlinear_89,
                                           terms=c("kurt_std [all]")))%>%
                            mutate(year=as.factor(1989)))%>%
                      mutate(predictor="kurt_std"))%>% # kurt_std
  mutate(response="sel_nfl",type="nonlinear")%>%
  left_join(coefs_sel_nfl_nonlinear%>%
              dplyr::select(predictor,coef,year,signif,star,print,type))
prediction_sel_nfl<-rbind(prediction_sel_nfl_linear,
                                 prediction_sel_nfl_nonlinear)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")))
```

## Figure 2

Figure based on predictions of yearly models.

```{r}
predictor.labs<-c("Mean","Variance","Skewness","Kurtosis")
names(predictor.labs)<-c("avFD_std","var_std","skew_std","kurt_std")
fig2<-ggplot()+
  geom_point(data=data_ids%>%
               dplyr::select(year,fr_set,avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
                            names_to="predictor",values_to="value_predictor")%>%
               mutate(predictor=factor(predictor,
                                       levels=c("avFD_std","var_std",
                                                "skew_std","kurt_std"))),
             aes(x=value_predictor,y=fr_set),
             size=2,alpha=0.3)+
  facet_grid2(c("predictor","year"), 
              labeller=labeller(predictor=predictor.labs), 
              scales = "free", independent = "all")+
  geom_ribbon(data=prediction_fr_set,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=type),
              alpha=0.3)+
  geom_line(data=prediction_fr_set,
            aes(x=x,y=predicted,linetype=signif,color=type),
            linewidth=1)+
  scale_linetype_manual(values=c("dotted", "solid"))+
  ylab("Proportion of flowers that developed to fruits")+
  xlab("Value of the moment")+
  # geom_text(data=prediction_fr_set%>%
  #             select(year,predictor,print,type)%>%
  #             distinct()%>%
  #             pivot_wider(names_from=type,values_from=print)%>%
  #             mutate(print=paste("L = ",linear,"\n","NL =", nonlinear)),
  #           aes(x=Inf,y=Inf,label=print),
  #            hjust=1.05, vjust=1.2,family="serif")+
  my_theme()
fig2
ggsave(file="output/figures/fig2.tiff", plot=fig2, width=10, height=10)
```

## Figures fruit initiation and maturation

```{r}
fig_fr_init<-ggplot()+
  geom_point(data=data_ids%>%
               dplyr::select(year,fr_init,avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
                            names_to="predictor",values_to="value_predictor")%>%
               mutate(predictor=factor(predictor,
                                       levels=c("avFD_std","var_std",
                                                "skew_std","kurt_std"))),
             aes(x=value_predictor,y=fr_init),
             size=2,alpha=0.3)+
  facet_grid2(c("predictor","year"), 
              labeller=labeller(predictor=predictor.labs), 
              scales = "free", independent = "all")+
  geom_ribbon(data=prediction_fr_init,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=type),
              alpha=0.3)+
  geom_line(data=prediction_fr_init,
            aes(x=x,y=predicted,linetype=signif,color=type),
            linewidth=1)+
  scale_linetype_manual(values=c("dotted", "solid"))+
  ylab("Fruit initiation (proportion of flowers that initiated fruits)")+
  xlab("Value of the moment")+
  my_theme()
fig_fr_init
ggsave(file="output/figures/fig_fr_init.tiff",
       plot=fig_fr_init, width=10, height=10)
```

```{r}
fig_fr_mat<-ggplot()+
  geom_point(data=data_ids%>%
               dplyr::select(year,fr_mat,avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
                            names_to="predictor",values_to="value_predictor")%>%
               mutate(predictor=factor(predictor,
                                       levels=c("avFD_std","var_std",
                                                "skew_std","kurt_std"))),
             aes(x=value_predictor,y=fr_mat),
             size=2,alpha=0.3)+
  facet_grid2(c("predictor","year"), 
              labeller=labeller(predictor=predictor.labs), 
              scales = "free", independent = "all")+
  geom_ribbon(data=prediction_fr_mat,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=type),
              alpha=0.3)+
  geom_line(data=prediction_fr_mat,
            aes(x=x,y=predicted,linetype=signif,color=type),
            linewidth=1)+
  scale_linetype_manual(values=c("dotted", "solid"))+
  ylab("Fruit maturation (proportion of initiated fruits that developed to mature fruits)")+
  xlab("Value of the moment")+
  my_theme()
fig_fr_mat
ggsave(file="output/figures/fig_fr_mat.tiff",
       plot=fig_fr_mat, width=10, height=10)
```

## Figure 3

Figure based on predictions of yearly models

```{r}
fig3<-ggplot()+
  geom_point(data=data_ids%>%
               filter(n_seed>0)%>%
               dplyr::select(year,prop_seed_preyed,
                      avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
                            names_to="predictor",values_to="value_predictor")%>%
               mutate(predictor=factor(predictor,
                                       levels=c("avFD_std","var_std",
                                                "skew_std","kurt_std")))%>%
               filter(!is.na(prop_seed_preyed)),
             aes(x=value_predictor,y=1-prop_seed_preyed),
             size=2,alpha=0.3)+
  facet_grid2(c("predictor","year"), 
              labeller=labeller(predictor=predictor.labs), 
              scales = "free", independent = "all")+
  geom_ribbon(data=prediction_seed_escpred,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=type),
              alpha=0.3)+
  geom_line(data=prediction_seed_escpred,
            aes(x=x,y=predicted,linetype=signif,color=type),
            linewidth=1)+
  scale_linetype_manual(values=c("dotted", "solid"))+
  ylab("Proportion of seeds escaping predation")+
  xlab("Value of the moment")+
  # geom_text(data=prediction_seed_escpred%>%
  #             select(year,predictor,print,type)%>%
  #             distinct()%>%
  #             pivot_wider(names_from=type,values_from=print)%>%
  #             mutate(print=paste("L = ",linear,"\n","NL =", nonlinear)),
  #           aes(x=Inf,y=Inf,label=print),
  #            hjust=1.05, vjust=1.2,family="serif")+
  my_theme()
fig3
ggsave(file="output/figures/fig3.tiff", plot=fig3, width=10, height=10)
```

## Figure 4

Figure based on predictions of yearly models

```{r}
fig4<-ggplot()+
  facet_grid2(c("predictor","year"), 
              labeller=labeller(predictor=predictor.labs), 
              scales = "free", independent = "all")+
  geom_ribbon(data=prediction_sel_nfl%>%
                filter(type=="linear"), # Showing only linear effects
              # cause none of the non-linear are significant
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high),
              alpha=0.3,fill="#CC0000")+
  geom_line(data=prediction_sel_nfl%>%
              filter(type=="linear"),
            aes(x=x,y=predicted,linetype=signif),
            linewidth=1,color="#CC0000")+
  geom_point(data=data_ids%>%
               dplyr::select(year,fitness_rel,
                      avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
                            names_to="predictor",values_to="value_predictor")%>%
               mutate(predictor=factor(predictor,
                                       levels=c("avFD_std","var_std",
                                                "skew_std","kurt_std"))),
             aes(x=value_predictor,y=fitness_rel),
             size=2,alpha=0.3)+
  scale_linetype_manual(values=c("dashed", "solid"))+
  ylab("Relative fitness")+
  xlab("Value of the moment")+
  # geom_text(data=prediction_seed_escpred%>%
  #             select(year,predictor,print,type)%>%
  #             distinct()%>%
  #             pivot_wider(names_from=type,values_from=print)%>%
  #             mutate(print=paste("L = ",linear,"\n","NL =", nonlinear)),
  #           aes(x=Inf,y=Inf,label=print),
  #            hjust=1.05, vjust=1.2,family="serif")+
  my_theme()
fig4
ggsave(file="output/figures/fig4.tiff", plot=fig4, width=10, height=10)
```

# New figure

I need to reorder and rename the figures!

```{r}
data_figure<-rbind(prediction_fr_init,
      prediction_fr_mat,
      prediction_seed_escpred)%>%
  # Remove non-significant effects
  filter(signif==1)%>%
  # Remove linear effects when quadratic effect is significant
  # for same year/response/predictor combination
  # (only plot quadratic effect in these cases)
  filter(!(year==1988&response=="fr_init"&predictor=="avFD_std"&
             type=="linear"))%>%
  filter(!(year==1988&response=="seed_escpred"&predictor=="avFD_std"&
             type=="linear"))%>%
  filter(!(year==1987&response=="seed_escpred"&predictor=="skew_std"&
             type=="linear"))
```


```{r}
fig_new<-ggplot()+
  # geom_point(data=data_ids%>%
  #              dplyr::select(year,fr_init,avFD_std,var_std,skew_std,kurt_std)%>%
  #              pivot_longer(cols=avFD_std:kurt_std,
  #                           names_to="predictor",values_to="value_predictor")%>%
  #              mutate(predictor=factor(predictor,
  #                                      levels=c("avFD_std","var_std",
  #                                               "skew_std","kurt_std"))),
  #            aes(x=value_predictor,y=fr_init),
  #            size=2,alpha=0.3)+
  facet_grid2(c("predictor","year"), 
              labeller=labeller(predictor=predictor.labs), 
              scales = "free", independent = "x")+
  geom_ribbon(data=data_figure,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=response),
              alpha=0.3)+
  geom_line(data=data_figure,
            aes(x=x,y=predicted,linetype=type,color=response),
            linewidth=1)+
  scale_linetype_manual(values=c("solid","dotted"))+
  scale_y_continuous(limits=c(0,1))+
  ylab("Proportion")+
  xlab("Value of the moment")+
  my_theme_legend()+theme(legend.position="top")+
  scale_fill_manual(values=c("#E69F00", "#56B4E9", "#009E73"),
                    name=NULL,
                       labels = c("Fruit initiation","Fruit maturation",
                                 "Seeds escaping predation"))+
  scale_color_manual(values=c("#E69F00", "#56B4E9", "#009E73"),
                     name=NULL,
                       labels = c("Fruit initiation","Fruit maturation",
                                 "Seeds escaping predation"))+
  guides(linetype=F)
fig_new
ggsave(file="output/figures/fig_new.tiff", plot=fig_new, width=10, height=12)
ggsave(file="output/figures/fig_new.svg", plot=fig_new, width=10, height=12)
```

# New figure with space to add coefficient plots

```{r}
plot_87<-ggplot()+
    facet_grid2(c("predictor"),labeller=labeller(predictor=predictor.labs), 
                scales = "free", independent = "x")+
    geom_ribbon(data=data_figure%>%filter(year==1987),
                aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=response),
                alpha=0.3)+
    geom_line(data=data_figure%>%filter(year==1987),
              aes(x=x,y=predicted,linetype=type,color=response),linewidth=1)+
    scale_linetype_manual(values=c("solid","dotted"))+
    scale_y_continuous(limits=c(0,1))+  ylab("Proportion")+
    xlab("Value of the moment")+my_theme()+
    scale_fill_manual(values=c("#E69F00", "#56B4E9", "#009E73"),name=NULL,
                      labels = c("Fruit initiation","Fruit maturation",
                                 "Seeds escaping predation"))+
    scale_color_manual(values=c("#E69F00", "#56B4E9", "#009E73"),name=NULL,
                       labels = c("Fruit initiation","Fruit maturation",
                                  "Seeds escaping predation"))+
    guides(linetype=F)+theme(plot.margin=unit(c(0.5,0.5,0.5,6),"cm"))
plot_88<-ggplot()+
    facet_grid2(c("predictor"),labeller=labeller(predictor=predictor.labs), 
                scales = "free", independent = "x")+
    geom_ribbon(data=data_figure%>%filter(year==1988),
                aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=response),
                alpha=0.3)+
    geom_line(data=data_figure%>%filter(year==1988),
              aes(x=x,y=predicted,linetype=type,color=response),linewidth=1)+
    scale_linetype_manual(values=c("solid","dotted"))+
    scale_y_continuous(limits=c(0,1))+  ylab("Proportion")+
    xlab("Value of the moment")+my_theme()+
    scale_fill_manual(values=c("#E69F00", "#56B4E9", "#009E73"),name=NULL,
                      labels = c("Fruit initiation","Fruit maturation",
                                 "Seeds escaping predation"))+
    scale_color_manual(values=c("#E69F00", "#56B4E9", "#009E73"),name=NULL,
                       labels = c("Fruit initiation","Fruit maturation",
                                  "Seeds escaping predation"))+
    guides(linetype=F)+theme(plot.margin=unit(c(0.5,0.5,7.8,6),"cm"))
plot_89<-ggplot()+
    facet_grid2(c("predictor"),labeller=labeller(predictor=predictor.labs), 
                scales = "free", independent = "x")+
    geom_ribbon(data=data_figure%>%filter(year==1989),
                aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=response),
                alpha=0.3)+
    geom_line(data=data_figure%>%filter(year==1989),
              aes(x=x,y=predicted,linetype=type,color=response),linewidth=1)+
    scale_linetype_manual(values=c("solid","dotted"))+
    scale_y_continuous(limits=c(0,1))+  ylab("Proportion")+
    xlab("Value of the moment")+my_theme()+
    scale_fill_manual(values=c("#E69F00", "#009E73"),name=NULL,
                      labels = c("Fruit initiation",
                                 "Seeds escaping predation"))+
    scale_color_manual(values=c("#E69F00","#009E73"),name=NULL,
                       labels = c("Fruit initiation",
                                  "Seeds escaping predation"))+
    guides(linetype=F)+theme(plot.margin=unit(c(0.5,0.5,0.5,6),"cm"))
fig_new_space<-grid.arrange(plot_87,plot_88,plot_89,ncol=3)
fig_new_space
ggsave(file="output/figures/fig_new_space.tiff", plot=fig_new_space, width=18, height=12)
ggsave(file="output/figures/fig_new_space.svg", plot=fig_new_space, width=18, height=12)
```


# Climatic data 87-89

```{r}
data_hline<-data_weather%>%
      filter(year==1987|year==1988|year==1989)%>%
      filter(month==4|month==5)%>%
      mutate(yday=yday(date))%>%
      group_by(month,year)%>%
      summarise(mean=mean(mean))
data_weather%>%
  filter(year==1987|year==1988|year==1989)%>%
  filter(month==4|month==5)%>%
  mutate(yday=yday(date))%>%
  ggplot(aes(x=day,y=mean))+geom_line(size=1)+
  facet_grid(rows=vars(month),cols=vars(year))+
  ggtitle("Mean temperatures")+
  geom_hline(data=data_hline,aes(yintercept=mean),
             color="blue",linetype="dashed")
```

```{r}
data_hline<-data_weather%>%
  filter(year==1987|year==1988|year==1989)%>%
  filter(month==4|month==5)%>%
  mutate(yday=yday(date))%>%
  dplyr::select(year,month,day,mean,min,max,yday)%>%
  pivot_longer(cols=mean:max,names_to="measure",values_to="value")%>%
  group_by(month,year,measure)%>%
  summarise(mean=mean(value))
data_weather%>%
  filter(year==1987|year==1988|year==1989)%>%
  filter(month==4|month==5)%>%
  mutate(yday=yday(date))%>%
  dplyr::select(year,month,day,mean,min,max,yday)%>%
  pivot_longer(cols=mean:max,names_to="measure",values_to="value")%>%
  ggplot(aes(x=day,y=value,color=measure))+geom_line(size=1)+
  facet_grid(rows=vars(month),cols=vars(year))+
  ggtitle("Temperatures")+
  geom_hline(data=data_hline,aes(yintercept=mean,color=measure),
             linetype="dashed")
```

```{r}
fig_clim_SI<-grid.arrange(
  ggplot(data=data_weather%>%filter(year==1987|year==1988|year==1989)%>%
           filter(month==4|month==5|month==6)%>%
           mutate(yday=yday(date))%>%
           dplyr::select(year,month,date,yday,mean,min,max),
         aes(x=yday,y=mean,ymin=min,ymax=max))+
    facet_grid(cols=vars(year),scales="free")+
    geom_ribbon(fill="lightskyblue1")+geom_line()+my_theme()+
    ylab("Temperature\n(ºC)")+xlab("Day of year")+ggtitle("A)")+
    theme(plot.title = element_text(hjust =-0.09,vjust=-6))+
    geom_vline(xintercept=121,linetype="dashed")+
    geom_vline(xintercept=152,linetype="dashed"),
  ggplot(data=data_weather%>%filter(year==1987|year==1988|year==1989)%>%        
           filter(month==4|month==5|month==6)%>%mutate(yday=yday(date))%>%
           dplyr::select(year,yday,month,mean,min,max)%>%
           group_by(year,month)%>%
           summarise(mean_mean=mean(mean),mean_min=mean(min),mean_max=mean(max),
                     se_mean=std.error(mean),se_min=std.error(min),
                     se_max=std.error(max))%>%
           pivot_longer(-c(year,month),names_to=c("stat","measure"),
                        names_sep="_",values_to="value")%>%
           pivot_wider(names_from="stat",values_from="value")%>%
           filter(measure=="mean"),
         aes(x=year,y=mean,ymin=mean-se,ymax=mean+se,color=factor(month)))+
    geom_jitter(position=position_dodge(width=0.75))+
    geom_errorbar(position=position_dodge(width=0.75),width=0.3)+
    my_theme_legend()+theme(legend.position="top")+
    ylab("Mean temperature (ºC)")+xlab("Year")+ggtitle("B)")+
    theme(plot.title = element_text(hjust =-0.05,vjust=-6))+
    scale_x_continuous(breaks=c(1987,1988,1989))+
    scale_color_discrete(name=NULL,labels=c("April","May","June")),
  ggplot(data=data_id_flowers%>%dplyr::select(id,opening_date_c)%>%
           mutate(year=year(opening_date_c),yday=yday(opening_date_c),
                  date=date(opening_date_c))%>%
           group_by(year,date,yday)%>%
           summarise(n_opening=n()),
         aes(x=yday,y=n_opening))+
    facet_grid(cols=vars(year),scales="free")+
    geom_col(fill="orchid")+my_theme()+
    ylab("Number offlowers\nopening")+xlab(NULL)+ggtitle("C)")+
    theme(plot.title = element_text(hjust =-0.09,vjust=-6))+
    scale_x_continuous(limits=c(90,180))+
    geom_vline(xintercept=121,linetype="dashed")+
    geom_vline(xintercept=152,linetype="dashed"),
  nrow=3
)
ggsave(file="output/figures/fig_clim_SI.tiff", plot=fig_clim_SI,
       width=10, height=12)
```



```{r}
ggerrorplot(data_weather%>%
              filter(year==1987|year==1988|year==1989)%>%
              filter(month==4|month==5),
            x="year",y=c("min","mean","max"),
            desc_stat="mean_se",error.plot = "errorbar",
            facet.by="month",add = "mean")
```

```{r}
data_weather_8789<-data_weather%>%
  filter(year==1987|year==1988|year==1989)%>%
  filter(month==4|month==5)%>%
  mutate(year=factor(year))
```

```{r}
model_april_min<-lm(min~year,subset(data_weather_8789,month==4))
model_may_min<-lm(min~year,subset(data_weather_8789,month==5))
model_april_mean<-lm(mean~year,subset(data_weather_8789,month==4))
model_may_mean<-lm(mean~year,subset(data_weather_8789,month==5))
model_april_max<-lm(max~year,subset(data_weather_8789,month==4))
model_may_max<-lm(max~year,subset(data_weather_8789,month==5))
```

```{r}
summary(model_april_min)
Anova(model_april_min) # Differences among years in April min temp (almost NS)
summary(model_may_min)
Anova(model_may_min) # Differences among years in May min temp
summary(model_april_mean)
Anova(model_april_mean) # No differences among years in April mean temp
summary(model_may_mean)
Anova(model_may_mean) # Differences among years in May mean temp
summary(model_april_max)
Anova(model_april_max) # No differences among years in April max temp
summary(model_may_max)
Anova(model_may_max) # Differences among years in May max temp
```

# Within- vs. among-individual components of variation

```{r eval=FALSE, include=FALSE}
brms_87<-brm(opening_date_v~1+(1|id),
             data = subset(data_id_flowers,year==1987),
             family = gaussian(),
             chains = 4, cores = 4, iter = 10000, warmup = 3000, thin = 5)
save(brms_87, file = "output/models/brms_87.rda")
```

```{r eval=FALSE, include=FALSE}
brms_88<-brm(opening_date_v~1+(1|id),
             data = subset(data_id_flowers,year==1988),
             family = gaussian(),
             chains = 4, cores = 4, iter = 10000, warmup = 3000, thin = 5)
save(brms_88, file = "output/models/brms_88.rda")
```

```{r eval=FALSE, include=FALSE}
brms_89<-brm(opening_date_v~1+(1|id),
             data = subset(data_id_flowers,year==1989),
             family = gaussian(),
             chains = 4, cores = 4, iter = 10000, warmup = 3000, thin = 5)
save(brms_89, file = "output/models/brms_89.rda")
```

```{r}
plot(brms_87)
plot(brms_88)
plot(brms_89)
```

```{r}
cowplot::plot_grid(mcmc_rhat_hist(brms::rhat(brms_87))+my_theme_legend()+
            theme(legend.position="top")+
            theme(legend.text=element_text(size=10)),
          mcmc_neff_hist(neff_ratio(brms_87))+my_theme_legend()+
            theme(legend.position="top")+
            theme(legend.text=element_text(size=10)),
          labels = c("A)","B)"),label_fontfamily="serif")
cowplot::plot_grid(mcmc_rhat_hist(brms::rhat(brms_88))+my_theme_legend()+
            theme(legend.position="top")+
            theme(legend.text=element_text(size=10)),
          mcmc_neff_hist(neff_ratio(brms_88))+my_theme_legend()+
            theme(legend.position="top")+
            theme(legend.text=element_text(size=10)),
          labels = c("A)","B)"),label_fontfamily="serif")
cowplot::plot_grid(mcmc_rhat_hist(brms::rhat(brms_89))+my_theme_legend()+
            theme(legend.position="top")+
            theme(legend.text=element_text(size=10)),
          mcmc_neff_hist(neff_ratio(brms_89))+my_theme_legend()+
            theme(legend.position="top")+
            theme(legend.text=element_text(size=10)),
          labels = c("A)","B)"),label_fontfamily="serif")
```

```{r}
summary(brms_87)
summary(brms_88)
summary(brms_89)
```


```{r}
v_among_87 <- (VarCorr(brms_87, summary = FALSE)$id$sd)^2
v_within_87 <- (VarCorr(brms_87, summary = FALSE)$residual$sd)^2
prop_v_among_87 <- as.mcmc(v_among_87 / (v_among_87 + v_within_87))
prop_v_within_87 <- as.mcmc(v_within_87 / (v_among_87 + v_within_87))
summary(prop_v_among_87)
summary(prop_v_within_87)
plot(prop_v_among_87)
plot(prop_v_within_87)
```

```{r}
v_among_88 <- (VarCorr(brms_88, summary = FALSE)$id$sd)^2
v_within_88 <- (VarCorr(brms_88, summary = FALSE)$residual$sd)^2
prop_v_among_88 <- as.mcmc(v_among_88 / (v_among_88 + v_within_88))
prop_v_within_88 <- as.mcmc(v_within_88 / (v_among_88 + v_within_88))
summary(prop_v_among_88)
summary(prop_v_within_88)
plot(prop_v_among_88)
plot(prop_v_within_88)
```

```{r}
v_among_89 <- (VarCorr(brms_89, summary = FALSE)$id$sd)^2
v_within_89 <- (VarCorr(brms_89, summary = FALSE)$residual$sd)^2
prop_v_among_89 <- as.mcmc(v_among_89 / (v_among_89 + v_within_89))
prop_v_within_89 <- as.mcmc(v_within_89 / (v_among_89 + v_within_89))
summary(prop_v_among_89)
summary(prop_v_within_89)
plot(prop_v_among_89)
plot(prop_v_within_89)
```

```{r}
full_join(
  data.frame(among_mean=c(summary(prop_v_among_87)$statistics[1],
                     summary(prop_v_among_88)$statistics[1],
                     summary(prop_v_among_89)$statistics[1]))%>%
    mutate(year=c(1987,1988,1989)),
  data.frame(within_mean=c(summary(prop_v_within_87)$statistics[1],
                      summary(prop_v_within_88)$statistics[1],
                      summary(prop_v_within_89)$statistics[1]))%>%
    mutate(year=c(1987,1988,1989)))%>%
    pivot_longer(cols=c("among_mean","within_mean"),
                 names_to="effect",values_to="mean")%>%
  mutate(effect=ifelse(effect=="among_mean","among","within"))%>%
  full_join(data.frame(among_lower=c(coda::HPDinterval(prop_v_among_87)[1],
                                     coda::HPDinterval(prop_v_among_88)[1],
                                     coda::HPDinterval(prop_v_among_89)[1]),
                       among_upper=c(coda::HPDinterval(prop_v_among_87)[2],
                                     coda::HPDinterval(prop_v_among_88)[2],
                                     coda::HPDinterval(prop_v_among_89)[2]),
                       within_lower=c(coda::HPDinterval(prop_v_within_87)[1],
                                      coda::HPDinterval(prop_v_within_88)[1],
                                      coda::HPDinterval(prop_v_within_89)[1]),
                       within_upper=c(coda::HPDinterval(prop_v_within_87)[2],
                                      coda::HPDinterval(prop_v_within_88)[2],
                                      coda::HPDinterval(prop_v_within_89)[2]))%>%
              mutate(year=c(1987,1988,1989))%>%
            pivot_longer(cols=c("among_lower","among_upper",
                                "within_lower","within_upper"),
                 names_to=c("effect","cat"),names_sep="_",values_to="value")%>%
              pivot_wider(names_from="cat",values_from="value"))%>%
  mutate(year=factor(year))%>%
  ggplot(aes(x=year,y=mean,ymin=lower,ymax=upper,color=effect))+
  geom_errorbar(linewidth=0.5,width=0.2,position=position_dodge(0.3))+
  geom_point(size=2,position=position_dodge(0.3))+
  my_theme()+xlab("Year")+ylab("Proportion of variance")
ggsave(file="output/figures/prop_var.tiff", width=4, height=3.5)
```

# Session info

```{r}
sessionInfo()
```
