---
title: "Selection on within-individual variation in flowering time in Lathyrus vernus"
author: "Alicia Valdés"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  pdf_document:
    toc: yes
    toc_depth: 4
  word_document:
    toc: yes
    toc_depth: '4'
subtitle: "Analyses of relationships between phenological traits and fruit initiation
  and pre-dispersal seed predation, and analyses of phenotypic selection on phenological
  traits"
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(tibble.width = Inf)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r load packages, include=FALSE}
library(tidyverse)
library(jtools)
library(ggeffects)
library(glmmTMB)
library(DHARMa)
library(RColorBrewer)
library(gridExtra)
library(ggthemes)
library(ggfortify)
library(ggcorrplot)
library(car)
library(broom.mixed)
library(performance)
library(sjPlot)
library(lme4)
library(bcaboot)
library(purrr)
library(ggridges)
library(moments)
library(grid)
library(stringr)
library(ggh4x)
```

```{r Define ggplot themes and palettes, include=FALSE}
my_theme <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(legend.position="none")+theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
my_theme_legend <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
myPalette <- colorRampPalette(brewer.pal(11, "YlOrRd"))
```

```{r load previously created output}
load(file="output/BCIs_sel_nfl_linear.RData")
load(file="output/BCIs_sel_nfl_nonlinear.RData")
load(file="output/BCIs_sel_nfl_linear_87.RData")
load(file="output/BCIs_sel_nfl_linear_88.RData")
load(file="output/BCIs_sel_nfl_linear_89.RData")
load(file="output/BCIs_sel_nfl_nonlinear_87.RData")
load(file="output/BCIs_sel_nfl_nonlinear_88.RData")
load(file="output/BCIs_sel_nfl_nonlinear_89.RData")
load(file="output/BCIs_sel_nfl_linear_87_mv.RData")
load(file="output/BCIs_sel_nfl_linear_88_mv.RData")
load(file="output/BCIs_sel_nfl_linear_89_mv.RData")
load(file="output/BCIs_sel_nfl_nonlinear_87_mv.RData")
load(file="output/BCIs_sel_nfl_nonlinear_88_mv.RData")
load(file="output/BCIs_sel_nfl_nonlinear_89_mv.RData")
load(file="output/BCIs_sel_nfl_linear_87_mv2.RData")
load(file="output/BCIs_sel_nfl_linear_88_mv2.RData")
load(file="output/BCIs_sel_nfl_linear_89_mv2.RData")
load(file="output/BCIs_sel_nfl_nonlinear_87_mv2.RData")
load(file="output/BCIs_sel_nfl_nonlinear_88_mv2.RData")
load(file="output/BCIs_sel_nfl_nonlinear_89_mv2.RData")
```

# Read clean data from .csv file

```{r}
data_ids <- read_csv("data/clean/data_ids.csv")
data_ids$imp_seed_preyed <- as.factor(data_ids$imp_seed_preyed)
data_ids$year <- as.factor(data_ids$year)
data_ids$subplot<-as.factor(data_ids$subplot)
data_id_flowers <- read_csv("data/clean/data_id_flowers.csv")
```

# Figure 1 (theoretical)

```{r}
# Changes in mean
mean_data<-data.frame(A_early=rnorm(500000,mean=63.2,sd=0.64),
                      B_medium=rnorm(500000,mean=66.2,sd=0.64),
                      C_late=rnorm(500000,mean=69.2,sd=0.64))%>%
  pivot_longer(cols=A_early:C_late,names_to="names",values_to="values")
summary_mean_data<-mean_data%>%
  group_by(names)%>%
  summarise(mean(values),var(values),skewness(values),kurtosis(values))
summary_mean_data

# Changes in variance
var_data<-data.frame(A_low=rnorm(500000,mean=66.2,sd=0.34),
                     B_medium=rnorm(500000,mean=66.2,sd=0.64),
                     C_large=rnorm(500000,mean=66.2,sd=0.94))%>%
  pivot_longer(cols=A_low:C_large,names_to="names",values_to="values")
summary_var_data<-var_data%>%
  group_by(names)%>%
  summarise(mean(values),var(values),skewness(values),kurtosis(values))
summary_var_data


# Changes in skewness and kurtosis --> modify in Inkscape
fig1_part<-grid.arrange(
  ggplot(mean_data,aes(x=values,fill=names))+
    geom_density(alpha=0.7)+
    xlab("Opening date")+
    ylab("Density")+my_theme()+ggtitle("A) Changes in mean")+
    scale_fill_manual(values=c("#efedf5","#bcbddc","#756bb1")),
  ggplot(var_data,aes(x=values,fill=names))+geom_density(alpha=0.7)+
    xlab("Opening date")+
    ylab("Density")+my_theme()+ggtitle("B) Changes in variance")+
    scale_fill_manual(values=c("#efedf5","#bcbddc","#756bb1")),
  ncol=2)
ggsave(file="output/figures/fig1_part.svg", plot=fig1_part, width=10, height=4)
```


# Descriptive

## Flowering phenology curves of individuals

```{r}
ids_years_1_2fl<-data_id_flowers%>%group_by(year,id)%>%mutate(count=n())%>%
  filter(count==1|count==2)%>%select(id,year)%>%distinct(id,year) 
# All ids and years with 1 or 2 fl

data_id_flowers_3fl<-data_id_flowers %>%
  anti_join(ids_years_1_2fl)%>% # Keep only ids and years with at least 3 fl
  mutate(subplot=factor(subplot,ordered=T),number=factor(number,ordered=T))%>%
  mutate(year=factor(year),
         id=factor(id,
                   levels=unique(id[order(subplot,number)]), ordered=TRUE))
# id as ordered factor based on subplot and number

# split the data into chunks of 21 subplot, number
# based on their unique id values
id_chunks <-data_id_flowers_3fl %>% 
  distinct(subplot,number) %>%
  arrange(subplot,number)%>%
  mutate(chunk = ceiling(row_number()/21)) %>%
  inner_join(data_id_flowers_3fl, by =c("subplot","number")) %>%
  split(.$chunk)

# create a list of plots, one for each chunk of ids
plot_list<-map(id_chunks,~ggplot(.x,aes(x=opening_date_v,y=id,fill=year))+
                   geom_density_ridges()+
                   theme_ridges()+theme(text=element_text(family="serif"))+
                   theme(legend.position="top")+
                   labs(x="Opening date (number of days from the vernal equinox)",
                        y="Individual")+
                   scale_fill_manual(values=c("#E69F00","#56B4E9","#009E73")))

# save the plots as TIFF files
walk2(plot_list, seq_along(plot_list), 
      ~ ggsave(paste0("output/figures/myplot_", .y, ".tiff"), 
               plot = .x, width = 6.5, height = 9, units = "in", dpi = 300))
```

## Distributions of the four moments

### All years

```{r}
histograms_SI<-grid.arrange(
  # Mean
  ggplot(data_ids,aes(x=avFD_v))+
    geom_histogram(color="black",alpha=0.6,position="identity")+
    ggtitle("A)")+
    my_theme()+xlab("Mean")+ylab("Count"),
  # Variance
  ggplot(data_ids,aes(x=var))+
    geom_histogram(color="black",alpha=0.6,position="identity")+
    ggtitle("B)")+
    my_theme()+xlab("Variance")+ylab("Count"),
  # Skewness
  ggplot(data_ids,aes(x=skew))+
    geom_histogram(color="black",alpha=0.6,position="identity")+
    ggtitle("C)")+
    my_theme()+xlab("Skewness")+ylab("Count"),
  # Kurtosis
  ggplot(data_ids,aes(x=kurt))+
    geom_histogram(color="black",alpha=0.6,position="identity")+
    ggtitle("D)")+
    my_theme()+xlab("Kurtosis")+ylab("Count"),
  ncol=2)
ggsave(histograms_SI,filename="output/figures/histograms_SI.tiff",
       device="tiff",width=20,height=15,units="cm",dpi=300,compression="lzw")
```

### By year

```{r}
histograms_SI_years<-grid.arrange(
  # Mean
  ggplot(data_ids,aes(x=avFD_v,fill=year))+
    geom_histogram(color="black",position="identity")+
    scale_fill_manual(values=c("#E69F00","#56B4E9","#009E73"))+
    facet_grid(rows=vars(year))+ggtitle("A)")+
    my_theme()+xlab("Mean")+ylab("Count"),
  # Variance
  ggplot(data_ids,aes(x=var,fill=year))+
    geom_histogram(color="black",position="identity")+
    scale_fill_manual(values=c("#E69F00","#56B4E9","#009E73"))+
    facet_grid(rows=vars(year))+ggtitle("B)")+
    my_theme()+xlab("Variance")+ylab("Count"),
  # Skewness
  ggplot(data_ids,aes(x=skew,fill=year))+
    geom_histogram(color="black",position="identity")+
    scale_fill_manual(values=c("#E69F00","#56B4E9","#009E73"))+
    facet_grid(rows=vars(year))+ggtitle("C)")+
    my_theme()+xlab("Skewness")+ylab("Count"),
  # Kurtosis
  ggplot(data_ids,aes(x=kurt,fill=year))+
    geom_histogram(color="black",position="identity")+
    scale_fill_manual(values=c("#E69F00","#56B4E9","#009E73"))+
    facet_grid(rows=vars(year))+ggtitle("D)")+
    my_theme()+xlab("Kurtosis")+ylab("Count"),
  ncol=2)
ggsave(histograms_SI_years,filename="output/figures/histograms_SI_years.tiff",
       device="tiff",width=20,height=25,units="cm",dpi=300,compression="lzw")
```

## Ranges, means and SD

```{r}
data_ids%>%
  summarise(min_mean=min(avFD_v),max_mean=max(avFD_v),
            mean_mean=mean(avFD_v),sd_mean=sd(avFD_v),
            min_var=min(var,na.rm=T),max_var=max(var,na.rm=T),
            mean_var=mean(var,na.rm=T),sd_var=sd(var,na.rm=T),
            min_skew=min(skew,na.rm=T),max_skew=max(skew,na.rm=T),
            mean_skew=mean(skew,na.rm=T),sd_skew=sd(skew,na.rm=T),
            min_kurt=min(kurt,na.rm=T),max_kurt=max(kurt,na.rm=T),
            mean_kurt=mean(kurt,na.rm=T),sd_kurt=sd(kurt,na.rm=T))
```


# Correlations

I will fit models using traits representing the 4 moments of the distribution (mean: avFD, variance: var, skewness: skew and kurtosis: kurt)

Check the correlations of these 4 traits using all data:

```{r}
data_ids%>%select(year,avFD_v,var,skew,kurt) %>%
  rename(Mean=avFD_v,Variance=var,Skewness=skew,Kurtosis=kurt)%>%
  select_if(is.numeric) %>% 
  cor(use="pairwise.complete.obs") %>%
  ggcorrplot(method = "square", type = "lower", hc.order = F, lab = T)+
  theme(legend.position="none")+my_theme()+xlab(NULL)+ylab(NULL)
ggsave(filename="output/figures/corr_SI.tiff",
       device="tiff",width=10,height=8,units="cm",dpi=300,compression="lzw")
```

Check the yearly correlations:

```{r}
corr_SI_years<-grid.arrange(
  data_ids%>%select(year,avFD_v,var,skew,kurt) %>%
    filter(year==1987) %>%
    rename(Mean=avFD_v,Variance=var,Skewness=skew,Kurtosis=kurt)%>%
    select_if(is.numeric) %>% 
    cor(use="pairwise.complete.obs") %>%
    ggcorrplot(method = "square", type = "lower", hc.order = F, lab = T)+
    ggtitle("1987")+theme(legend.position="none")+
    my_theme()+xlab(NULL)+ylab(NULL),
  data_ids%>%select(year,avFD_v,var,skew,kurt) %>%
    filter(year==1988) %>%
    rename(Mean=avFD_v,Variance=var,Skewness=skew,Kurtosis=kurt)%>%
    select_if(is.numeric) %>% 
    cor(use="pairwise.complete.obs") %>%
    ggcorrplot(method = "square", type = "lower", hc.order = F, lab = T)+
    ggtitle("1988")+theme(legend.position="none")+
    my_theme()+xlab(NULL)+ylab(NULL),
  data_ids%>%select(year,avFD_v,var,skew,kurt) %>%
    filter(year==1989) %>%
    rename(Mean=avFD_v,Variance=var,Skewness=skew,Kurtosis=kurt)%>%
    select_if(is.numeric) %>% 
    cor(use="pairwise.complete.obs") %>%
    ggcorrplot(method = "square", type = "lower", hc.order = F, lab = T)+
    ggtitle("1989")+theme(legend.position="none")+
    my_theme()+xlab(NULL)+ylab(NULL),
  ncol=3)
ggsave(corr_SI_years,filename="output/figures/corr_SI_years.tiff",
       device="tiff",width=25,height=10,units="cm",dpi=300,compression="lzw")
```

Probaly OK? Check VIFs of each model.

# Multivariate GLMs

## FRUIT INITIATION

Using (within-year) standardized traits.

### Global models

#### Linear effects

```{r}
fr_init_linear<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+var_std+
                      skew_std+kurt_std+year+ 
                      # Include main effect of year here
                      # but not in selection models!
                      avFD_std:year+var_std:year+skew_std:year+kurt_std:year,
                    data_ids,family="binomial")
tab_model(fr_init_linear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, linear effects"))
Anova(fr_init_linear) # Use type II (now) or III?
check_collinearity(glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+var_std+
                         skew_std+kurt_std+year,
                       data_ids,family="binomial"))
```

According to Anova, differences among years in the effects of avFD and skew.

##### Plot predictions

```{r}
plot(ggpredict(fr_init_linear,
               terms=c("avFD_std [all]","year"))) # Significant diffs among years
plot(ggpredict(fr_init_linear,
               terms=c("var_std [all]"))) # Main effect signficant
plot(ggpredict(fr_init_linear,
               terms=c("skew_std [all]","year"))) # Significant diffs among years
```

#### Non-linear effects

```{r}
fr_init_nonlinear<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                         avFD_std+var_std+skew_std+kurt_std+year+ 
                         avFD_std:year+var_std:year+skew_std:year+kurt_std:year+
                         I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                         I(avFD_std^2):year+I(var_std^2):year+
                         I(skew_std^2):year+I(kurt_std^2):year,
                       data_ids,family="binomial")
tab_model(fr_init_nonlinear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, non linear effects"))
Anova(fr_init_nonlinear) # Use type II (now) or III?
```

None of the quadratic effects is significant.

Ratio of n observations to n parameters in the model:

```{r}
nobs(fr_init_nonlinear)/dim(model.matrix(fr_init_nonlinear))[2]
```

OK. If including interactions, it would be lower than 10.
Similar problem with yearly models, so not including interactions in any model so far.

### Yearly models

#### Linear effects

```{r}
fr_init_linear_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                         avFD_std+var_std+skew_std+kurt_std,
                       subset(data_ids,year==1987),family="binomial")
fr_init_linear_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                         avFD_std+var_std+skew_std+kurt_std,
                    subset(data_ids,year==1988),family="binomial")
fr_init_linear_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                         avFD_std+var_std+skew_std+kurt_std,
                    subset(data_ids,year==1989),family="binomial")
tab_model(fr_init_linear_87,fr_init_linear_88,fr_init_linear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit initiation, linear effects")
check_collinearity(fr_init_linear_87)
check_collinearity(fr_init_linear_88)
check_collinearity(fr_init_linear_89)
Anova(fr_init_linear_87)
Anova(fr_init_linear_88)
Anova(fr_init_linear_89) 
```

##### Plot predictions

```{r}
plot(ggpredict(fr_init_linear_87,terms=c("var_std [all]"))) 
plot(ggpredict(fr_init_linear_87,terms=c("skew_std [all]"))) 
plot(ggpredict(fr_init_linear_87,terms=c("kurt_std [all]"))) 
```

```{r}
plot(ggpredict(fr_init_linear_88,terms=c("avFD_std [all]"))) 
```

```{r}
plot(ggpredict(fr_init_linear_88,terms=c("avFD_std [all]"))) 
plot(ggpredict(fr_init_linear_88,terms=c("skew_std [all]"))) 
```

#### Non-linear effects

```{r}
fr_init_nonlinear_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                            avFD_std+var_std+skew_std+kurt_std+
                            I(avFD_std^2)+I(var_std^2)+
                            I(skew_std^2)+I(kurt_std^2),
                          subset(data_ids,year==1987),family="binomial")
fr_init_nonlinear_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                            avFD_std+var_std+skew_std+kurt_std+
                            I(avFD_std^2)+I(var_std^2)+
                            I(skew_std^2)+I(kurt_std^2),
                    subset(data_ids,year==1988),family="binomial")
fr_init_nonlinear_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                            avFD_std+var_std+skew_std+kurt_std+
                            I(avFD_std^2)+I(var_std^2)+
                            I(skew_std^2)+I(kurt_std^2),
                    subset(data_ids,year==1989),family="binomial")
tab_model(fr_init_nonlinear_87,fr_init_nonlinear_88,fr_init_nonlinear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit initiation, nonlinear effects")
Anova(fr_init_nonlinear_87)
Anova(fr_init_nonlinear_88)
Anova(fr_init_nonlinear_89) 
```

##### Plot predictions

```{r}
plot(ggpredict(fr_init_nonlinear_88,terms=c("var_std [all]"))) 
```

## SEEDS ESCAPING PREDATION

Using (within-year) standardized traits.

### Global models

#### Linear effects

```{r}
seed_escpred_linear<-glm(cbind(npr_seeds=round(n_seed)-round(n_preyed_seed),
                        pr_seeds=round(n_preyed_seed))~
                          avFD_std+var_std+skew_std+kurt_std+year+ 
                          avFD_std:year+var_std:year+
                          skew_std:year+kurt_std:year,
                        data_ids,family="binomial")
tab_model(seed_escpred_linear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, linear effects"))
Anova(seed_escpred_linear)
check_collinearity(glm(cbind(npr_seeds=round(n_seed)-round(n_preyed_seed),
                        pr_seeds=round(n_preyed_seed))~
                          avFD_std+var_std+skew_std+kurt_std+year,
                        data_ids,family="binomial"))
```

According to Anova, differences among years in the effects of avFD and skew.

##### Plot predictions

```{r}
plot(ggpredict(seed_escpred_linear,terms=c("avFD_std [all]","year"))) 
# Significant diffs among years
plot(ggpredict(seed_escpred_linear,terms=c("var_std [all]"))) 
# Main effect signficant
plot(ggpredict(seed_escpred_linear,terms=c("year [all]"))) 
# Main effect signficant
plot(ggpredict(seed_escpred_linear,terms=c("skew_std [all]","year"))) 
# Significant diffs among years
```

#### Non-linear effects

```{r}
seed_escpred_nonlinear<-glm(cbind(npr_seeds=round(n_seed)-round(n_preyed_seed),
                        pr_seeds=round(n_preyed_seed))~
                          avFD_std+var_std+skew_std+kurt_std+year+ 
                          avFD_std:year+var_std:year+
                          skew_std:year+kurt_std:year+
                          I(avFD_std^2)+I(var_std^2)+
                          I(skew_std^2)+I(kurt_std^2)+
                          I(avFD_std^2):year+I(var_std^2):year+
                          I(skew_std^2):year+I(kurt_std^2):year,
                        data_ids,family="binomial")
tab_model(seed_escpred_nonlinear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, non linear effects"))
Anova(seed_escpred_nonlinear) # Use type II (now) or III?
```

Significant non-linear effects according to Anova: I(var_std^2), I(skew_std^2), year:I(avFD_std^2), year:I(skew_std^2)

##### Plot predictions

```{r}
plot(ggpredict(seed_escpred_nonlinear,terms=c("var_std [all]"))) 
# Quadratic effect
plot(ggpredict(seed_escpred_nonlinear,terms=c("skew_std [all]"))) 
# Quadratic effect
plot(ggpredict(seed_escpred_nonlinear,terms=c("avFD_std [all]","year"))) 
# Quadratic effect, differences among years
plot(ggpredict(seed_escpred_nonlinear,terms=c("skew_std [all]","year"))) 
# Quadratic effect, differences among years
```

### Yearly models

#### Linear effects

```{r}
seed_escpred_linear_87<-glm(cbind(npr_seeds=round(n_seed)-round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std+skew_std+kurt_std,
                            subset(data_ids,year==1987),family="binomial")
seed_escpred_linear_88<-glm(cbind(npr_seeds=round(n_seed)-round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std+skew_std+kurt_std,
                            subset(data_ids,year==1988),family="binomial")
seed_escpred_linear_89<-glm(cbind(npr_seeds=round(n_seed)-round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std+skew_std+kurt_std,
                            subset(data_ids,year==1989),family="binomial")
tab_model(seed_escpred_linear_87,seed_escpred_linear_88,seed_escpred_linear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Seeds escaping predation, linear effects")
check_collinearity(seed_escpred_linear_87)
check_collinearity(seed_escpred_linear_88)
check_collinearity(seed_escpred_linear_89)
Anova(seed_escpred_linear_87)
Anova(seed_escpred_linear_88)
Anova(seed_escpred_linear_89)
```

##### Plot predictions

```{r}
plot(ggpredict(seed_escpred_linear_87,terms=c("avFD_std [all]"))) 
plot(ggpredict(seed_escpred_linear_87,terms=c("var_std [all]"))) 
plot(ggpredict(seed_escpred_linear_87,terms=c("skew_std [all]"))) 
plot(ggpredict(seed_escpred_linear_87,terms=c("kurt_std [all]"))) 
```

```{r}
plot(ggpredict(seed_escpred_linear_88,terms=c("avFD_std [all]"))) 
plot(ggpredict(seed_escpred_linear_88,terms=c("var_std [all]"))) 
plot(ggpredict(seed_escpred_linear_88,terms=c("skew_std [all]"))) 
```

```{r}
plot(ggpredict(seed_escpred_linear_89,terms=c("var_std [all]"))) 
plot(ggpredict(seed_escpred_linear_89,terms=c("skew_std [all]"))) 
```

#### Non-linear effects

```{r}
seed_escpred_nonlinear_87<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+skew_std+kurt_std+
                                 I(avFD_std^2)+I(var_std^2)+
                                 I(skew_std^2)+I(kurt_std^2),
                               subset(data_ids,year==1987),family="binomial")
seed_escpred_nonlinear_88<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+skew_std+kurt_std+
                                 I(avFD_std^2)+I(var_std^2)+
                                 I(skew_std^2)+I(kurt_std^2),
                               subset(data_ids,year==1988),family="binomial")
seed_escpred_nonlinear_89<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+skew_std+kurt_std+
                                 I(avFD_std^2)+I(var_std^2)+
                                 I(skew_std^2)+I(kurt_std^2),
                               subset(data_ids,year==1989),family="binomial")
# nobs(seed_escpred_nonlinear_89)/
# dim(model.matrix(seed_escpred_nonlinear_89))[2] = 7.2
# Careful! Only case when this ratio is <10
tab_model(seed_escpred_nonlinear_87,seed_escpred_nonlinear_88,
          seed_escpred_nonlinear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Seeds escaping predation, nonlinear effects")
Anova(seed_escpred_nonlinear_87)
Anova(seed_escpred_nonlinear_88)
Anova(seed_escpred_nonlinear_89) 
```

##### Plot predictions

```{r}
plot(ggpredict(seed_escpred_nonlinear_87,terms=c("skew_std [all]")))
```

```{r}
plot(ggpredict(seed_escpred_nonlinear_88,terms=c("avFD_std [all]")))
```

```{r}
plot(ggpredict(seed_escpred_nonlinear_89,terms=c("avFD_std [all]")))
```

## PHENOTYPIC SELECTION with n_fl

Try with n_fl --> log --> std

```{r}
data_ids<-data_ids%>%
  mutate(n_fl_log=log(n_fl))%>%
  group_by(year)%>%
  mutate(n_fl_log_std=as.vector(scale(n_fl_log)))
```


Using (within-year) standardized traits.

### Global models

#### Linear effects

Including only linear effects and interactions with year.

```{r}
sel_nfl_linear<-lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std+n_fl_log_std+
              avFD_std:year+var_std:year+skew_std:year+kurt_std:year,
              # Not including main effect of yr cause fitness rel within yrs
              subset(data_ids,!is.na(avFD_std)&!is.na(var_std)&
                       !is.na(skew_std)&!is.na(kurt_std)))
tab_model(sel_nfl_linear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, linear effects"))
Anova(sel_nfl_linear)
check_collinearity(lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std+n_fl_std,
              subset(data_ids,!is.na(avFD_std)&!is.na(var_std)&
                       !is.na(skew_std)&!is.na(kurt_std))))
```

According to Anova, no differences among years.

##### Plot predictions

```{r}
plot(ggpredict(sel_nfl_linear,terms=c("var_std [all]")))
plot(ggpredict(sel_nfl_linear,terms=c("skew_std [all]")))
```

##### BCA intervals

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[2]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[3]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[4]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[5]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[6]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD_std:year1988
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[7]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD_std:year1989
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[8]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std:year1988
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[9]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std:year1989
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[10]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std:year1988
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[11]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std:year1989
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[12]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std:year1988
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[13]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std:year1989
slp <- function(sel_nfl_linear) coef(sel_nfl_linear)[14]
b <- car::Boot(sel_nfl_linear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,], skew_std_ci[1,], kurt_std_ci[1,], n_fl_log_std_ci[1,],
        avFD_std_year1988_ci[1,],avFD_std_year1989_ci[1,],var_std_year1988_ci[1,],
        var_std_year1989_ci[1,],skew_std_year1988_ci[1,],skew_std_year1989_ci[1,],
        kurt_std_year1988_ci[1,],kurt_std_year1989_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,], skew_std_ci[2,], kurt_std_ci[2,], n_fl_log_std_ci[2,],
        avFD_std_year1988_ci[2,],avFD_std_year1989_ci[2,],var_std_year1988_ci[2,],
        var_std_year1989_ci[2,],skew_std_year1988_ci[2,],skew_std_year1989_ci[2,],
        kurt_std_year1988_ci[2,],kurt_std_year1989_ci[2,])
)
colnames(BCIs_sel_nfl_linear)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear) <- c("avFD_std","var_std","skew_std","kurt_std","n_fl_log_std",
                                "avFD_std_year1988","avFD_std_year1988","var_std_year1988",
                                "var_std_year1989","skew_std_year1988","skew_std_year1989",
                                "kurt_std_year1988","kurt_std_year1989")
save(BCIs_sel_nfl_linear,file="output/BCIs_sel_nfl_linear.RData")
```

```{r}
BCIs_sel_nfl_linear
```

Similar to significances with Anova

#### Non-linear effects

```{r}
sel_nfl_nonlinear<-lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std+
                        n_fl_log_std+
                        avFD_std:year+var_std:year+skew_std:year+kurt_std:year+
                        I(avFD_std^2)+I(var_std^2)+I(skew_std^2)+I(kurt_std^2)+
                        I(n_fl_log_std^2)+
                        I(avFD_std^2):year+I(var_std^2):year+
                        I(skew_std^2):year+I(kurt_std^2):year,
                      subset(data_ids,!is.na(avFD_std)&!is.na(var_std)&
                               !is.na(skew_std)&!is.na(kurt_std)))
tab_model(sel_nfl_nonlinear,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects"))
Anova(sel_nfl_nonlinear)
plot(check_collinearity(sel_nfl_nonlinear))
```

Only the quadratic effect of flower number is significant.

##### BCA intervals

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[7]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[8]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[9]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std2
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[10]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[11]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD_std2:year1988
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[20]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# avFD_std2:year1989
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[21]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2:year1988
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[22]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2:year1989
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[23]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2:year1988
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[24]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2:year1989
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[25]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std22:year1988
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[26]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_year1988_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std2:year1989
slp <- function(sel_nfl_nonlinear) coef(sel_nfl_nonlinear)[27]
b <- car::Boot(sel_nfl_nonlinear,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_year1989_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear <- cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,], skew_std2_ci[1,], kurt_std2_ci[1,],
        n_fl_log_std2_ci[1,],
        avFD_std2_year1988_ci[1,],avFD_std2_year1989_ci[1,],
        var_std2_year1988_ci[1,],var_std2_year1989_ci[1,],
        skew_std2_year1988_ci[1,],skew_std2_year1989_ci[1,],
        kurt_std2_year1988_ci[1,],kurt_std2_year1989_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,], skew_std2_ci[2,], kurt_std2_ci[2,],
        n_fl_log_std2_ci[2,],
        avFD_std2_year1988_ci[2,],avFD_std2_year1989_ci[2,],
        var_std2_year1988_ci[2,],var_std2_year1989_ci[2,],
        skew_std2_year1988_ci[2,],skew_std2_year1989_ci[2,],
        kurt_std2_year1988_ci[2,],kurt_std2_year1989_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear)<-c("avFD_std2","var_std2","skew_std2",
                                    "kurt_std2","n_fl_log_std2",
                                    "avFD_std2_year1988","avFD_std2_year1989",
                                    "var_std2_year1988","var_std2_year1989",
                                    "skew_std2_year1988","skew_std2_year1989",
                                    "kurt_std2_year1988","kurt_std2_year1989")
save(BCIs_sel_nfl_nonlinear,file="output/BCIs_sel_nfl_nonlinear.RData")
```

```{r}
BCIs_sel_nfl_nonlinear
```

### Yearly models

#### Linear effects

```{r}
sel_nfl_linear_87<-lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std+
                        n_fl_log_std,
                      subset(data_ids,year==1987&
                               !is.na(avFD_std)&!is.na(var_std)&
                               !is.na(skew_std)&!is.na(kurt_std)))
sel_nfl_linear_88<-lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std+
                        n_fl_log_std,
                      subset(data_ids,year==1988&
                               !is.na(avFD_std)&!is.na(var_std)&
                               !is.na(skew_std)&!is.na(kurt_std)))
sel_nfl_linear_89<-lm(fitness_rel~avFD_std+var_std+skew_std+kurt_std+
                        n_fl_log_std,
                      subset(data_ids,year==1989&
                               !is.na(avFD_std)&!is.na(var_std)&
                               !is.na(skew_std)&!is.na(kurt_std)))
tab_model(sel_nfl_linear_87,sel_nfl_linear_88,sel_nfl_linear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Selection, linear effects")
check_collinearity(sel_nfl_linear_87)
check_collinearity(sel_nfl_linear_88)
check_collinearity(sel_nfl_linear_89)
Anova(sel_nfl_linear_87)
Anova(sel_nfl_linear_88)
Anova(sel_nfl_linear_89)
```

##### Plot predictions

```{r}
plot(ggpredict(sel_nfl_linear_87,terms=c("var_std [all]")))
plot(ggpredict(sel_nfl_linear_89,terms=c("skew_std [all]")))
```

##### BCA intervals

###### 1987

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_87) coef(sel_nfl_linear_87)[2]
b <- car::Boot(sel_nfl_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_87) coef(sel_nfl_linear_87)[3]
b <- car::Boot(sel_nfl_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std
slp <- function(sel_nfl_linear_87) coef(sel_nfl_linear_87)[4]
b <- car::Boot(sel_nfl_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std
slp <- function(sel_nfl_linear_87) coef(sel_nfl_linear_87)[5]
b <- car::Boot(sel_nfl_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_87) coef(sel_nfl_linear_87)[6]
b <- car::Boot(sel_nfl_linear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_87 <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,], skew_std_ci[1,], kurt_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,], skew_std_ci[2,], kurt_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_87)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_87)<-c("avFD_std","var_std","skew_std","kurt_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_87,file="output/BCIs_sel_nfl_linear_87.RData")
```

```{r}
BCIs_sel_nfl_linear_87
```

###### 1988

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_88) coef(sel_nfl_linear_88)[2]
b <- car::Boot(sel_nfl_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_88) coef(sel_nfl_linear_88)[3]
b <- car::Boot(sel_nfl_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std
slp <- function(sel_nfl_linear_88) coef(sel_nfl_linear_88)[4]
b <- car::Boot(sel_nfl_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std
slp <- function(sel_nfl_linear_88) coef(sel_nfl_linear_88)[5]
b <- car::Boot(sel_nfl_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_88) coef(sel_nfl_linear_88)[6]
b <- car::Boot(sel_nfl_linear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_88 <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,], skew_std_ci[1,], kurt_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,], skew_std_ci[2,], kurt_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_88)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_88)<-c("avFD_std","var_std","skew_std","kurt_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_88,file="output/BCIs_sel_nfl_linear_88.RData")
```

```{r}
BCIs_sel_nfl_linear_88
```

###### 1989

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_89) coef(sel_nfl_linear_89)[2]
b <- car::Boot(sel_nfl_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_89) coef(sel_nfl_linear_89)[3]
b <- car::Boot(sel_nfl_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std
slp <- function(sel_nfl_linear_89) coef(sel_nfl_linear_89)[4]
b <- car::Boot(sel_nfl_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std
slp <- function(sel_nfl_linear_89) coef(sel_nfl_linear_89)[5]
b <- car::Boot(sel_nfl_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_89) coef(sel_nfl_linear_89)[6]
b <- car::Boot(sel_nfl_linear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_89 <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,], skew_std_ci[1,], kurt_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,], skew_std_ci[2,], kurt_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_89)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_89)<-c("avFD_std","var_std","skew_std","kurt_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_89,file="output/BCIs_sel_nfl_linear_89.RData")
```

```{r}
BCIs_sel_nfl_linear_89
```

#### Non-linear effects

```{r}
sel_nfl_nonlinear_87<-lm(fitness_rel~avFD_std+var_std+
                           skew_std+kurt_std+n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+
                           I(skew_std^2)+I(kurt_std^2)+I(n_fl_log_std^2),
                         subset(data_ids,year==1987&
                                  !is.na(avFD_std)&!is.na(var_std)&
                                  !is.na(skew_std)&!is.na(kurt_std)))
sel_nfl_nonlinear_88<-lm(fitness_rel~avFD_std+var_std+
                           skew_std+kurt_std+n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+
                           I(skew_std^2)+I(kurt_std^2)+I(n_fl_log_std^2),
                         subset(data_ids,year==1988&
                                  !is.na(avFD_std)&!is.na(var_std)&
                                  !is.na(skew_std)&!is.na(kurt_std)))
sel_nfl_nonlinear_89<-lm(fitness_rel~avFD_std+var_std+
                           skew_std+kurt_std+n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+
                           I(skew_std^2)+I(kurt_std^2)+I(n_fl_log_std^2),
                           subset(data_ids,year==1989&
                                    !is.na(avFD_std)&!is.na(var_std)&
                                    !is.na(skew_std)&!is.na(kurt_std)))
tab_model(sel_nfl_nonlinear_87,sel_nfl_nonlinear_88,sel_nfl_nonlinear_89,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Selection, non-linear effects")
Anova(sel_nfl_nonlinear_87)
Anova(sel_nfl_nonlinear_88)
Anova(sel_nfl_nonlinear_89)
```

##### BCA intervals

###### 1987

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_87) coef(sel_nfl_nonlinear_87)[7]
b <- car::Boot(sel_nfl_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_87) coef(sel_nfl_nonlinear_87)[8]
b <- car::Boot(sel_nfl_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2
slp <- function(sel_nfl_nonlinear_87) coef(sel_nfl_nonlinear_87)[9]
b <- car::Boot(sel_nfl_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std2
slp <- function(sel_nfl_nonlinear_87) coef(sel_nfl_nonlinear_87)[10]
b <- car::Boot(sel_nfl_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_87) coef(sel_nfl_nonlinear_87)[11]
b <- car::Boot(sel_nfl_nonlinear_87,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_87<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,], skew_std2_ci[1,], kurt_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,], skew_std2_ci[2,], kurt_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_87)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_87)<-c("avFD_std2","var_std2","skew_std2",
                                    "kurt_std2","n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_87,file="output/BCIs_sel_nfl_nonlinear_87.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_87
```

###### 1988

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_88) coef(sel_nfl_nonlinear_88)[7]
b <- car::Boot(sel_nfl_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_88) coef(sel_nfl_nonlinear_88)[8]
b <- car::Boot(sel_nfl_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2
slp <- function(sel_nfl_nonlinear_88) coef(sel_nfl_nonlinear_88)[9]
b <- car::Boot(sel_nfl_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std2
slp <- function(sel_nfl_nonlinear_88) coef(sel_nfl_nonlinear_88)[10]
b <- car::Boot(sel_nfl_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_88) coef(sel_nfl_nonlinear_88)[11]
b <- car::Boot(sel_nfl_nonlinear_88,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_88<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,], skew_std2_ci[1,], kurt_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,], skew_std2_ci[2,], kurt_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_88)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_88)<-c("avFD_std2","var_std2","skew_std2",
                                    "kurt_std2","n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_88,file="output/BCIs_sel_nfl_nonlinear_88.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_88
```

###### 1989

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_89) coef(sel_nfl_nonlinear_89)[7]
b <- car::Boot(sel_nfl_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_89) coef(sel_nfl_nonlinear_89)[8]
b <- car::Boot(sel_nfl_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# skew_std2
slp <- function(sel_nfl_nonlinear_89) coef(sel_nfl_nonlinear_89)[9]
b <- car::Boot(sel_nfl_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
skew_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# kurt_std2
slp <- function(sel_nfl_nonlinear_89) coef(sel_nfl_nonlinear_89)[10]
b <- car::Boot(sel_nfl_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
kurt_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_89) coef(sel_nfl_nonlinear_89)[11]
b <- car::Boot(sel_nfl_nonlinear_89,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_89<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,], skew_std2_ci[1,], kurt_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,], skew_std2_ci[2,], kurt_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_89)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_89)<-c("avFD_std2","var_std2","skew_std2",
                                    "kurt_std2","n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_89,file="output/BCIs_sel_nfl_nonlinear_89.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_89
```

## SI: PHENOTYPIC SELECTION without n_fl

### Global models

#### Linear effects

##### BCA intervals (TO DO)

#### Non-linear effects

##### BCA intervals (TO DO)

### Yearly models

#### Linear effects

##### BCA intervals (TO DO)

#### Non-linear effects

##### BCA intervals (TO DO)

# SI? Analyses with only mean and variance

## FRUIT INITIATION

### Yearly models

#### Linear effects

##### Same n

```{r}
fr_init_linear_87_mv2<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+var_std,
                          subset(data_ids,year==1987&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
fr_init_linear_88_mv2<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+var_std,
                    subset(data_ids,year==1988&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
fr_init_linear_89_mv2<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+var_std,
                    subset(data_ids,year==1989&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
tab_model(fr_init_linear_87_mv2,fr_init_linear_88_mv2,fr_init_linear_89_mv2,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit initiation, linear effects, mean and variance")
Anova(fr_init_linear_87_mv2)
Anova(fr_init_linear_88_mv2)
Anova(fr_init_linear_89_mv2) 
```

##### Larger n

```{r}
fr_init_linear_87_mv<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                         avFD_std+var_std,
                       subset(data_ids,year==1987),family="binomial")
fr_init_linear_88_mv<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                         avFD_std+var_std,
                    subset(data_ids,year==1988),family="binomial")
fr_init_linear_89_mv<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                         avFD_std+var_std,
                    subset(data_ids,year==1989),family="binomial")
tab_model(fr_init_linear_87_mv,fr_init_linear_88_mv,fr_init_linear_89_mv,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit initiation, linear effects, mean and variance")
Anova(fr_init_linear_87_mv)
Anova(fr_init_linear_88_mv)
Anova(fr_init_linear_89_mv) 
```

#### Non-linear effects

##### Same n

```{r}
fr_init_nonlinear_87_mv2<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                            avFD_std+var_std+
                            I(avFD_std^2)+I(var_std^2),
                          subset(data_ids,year==1987&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
fr_init_nonlinear_88_mv2<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                            avFD_std+var_std+
                            I(avFD_std^2)+I(var_std^2),
                    subset(data_ids,year==1988&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
fr_init_nonlinear_89_mv2<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                            avFD_std+var_std+
                            I(avFD_std^2)+I(var_std^2),
                    subset(data_ids,year==1989&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
tab_model(fr_init_nonlinear_87_mv2,fr_init_nonlinear_88_mv2,
          fr_init_nonlinear_89_mv2,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit initiation, nonlinear effects, mean and variance")
Anova(fr_init_nonlinear_87_mv2)
Anova(fr_init_nonlinear_88_mv2)
Anova(fr_init_nonlinear_89_mv2) 
```

##### Larger n

```{r}
fr_init_nonlinear_87_mv<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                            avFD_std+var_std+
                            I(avFD_std^2)+I(var_std^2),
                          subset(data_ids,year==1987),family="binomial")
fr_init_nonlinear_88_mv<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                            avFD_std+var_std+
                            I(avFD_std^2)+I(var_std^2),
                    subset(data_ids,year==1988),family="binomial")
fr_init_nonlinear_89_mv<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~
                            avFD_std+var_std+
                            I(avFD_std^2)+I(var_std^2),
                    subset(data_ids,year==1989),family="binomial")
tab_model(fr_init_nonlinear_87_mv,fr_init_nonlinear_88_mv,
          fr_init_nonlinear_89_mv,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Fruit initiation, nonlinear effects, mean and variance")
Anova(fr_init_nonlinear_87_mv)
Anova(fr_init_nonlinear_88_mv)
Anova(fr_init_nonlinear_89_mv) 
```

## SEEDS ESCAPING PREDATION

### Yearly models

#### Linear effects

##### Same n

```{r}
seed_escpred_linear_87_mv2<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std,
                            subset(data_ids,year==1987&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
seed_escpred_linear_88_mv2<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std,
                            subset(data_ids,year==1988&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
seed_escpred_linear_89_mv2<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std,
                            subset(data_ids,year==1989&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
tab_model(seed_escpred_linear_87_mv2,seed_escpred_linear_88_mv2,
          seed_escpred_linear_89_mv2,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Seeds escaping predation, linear effects, mean and variance")
Anova(seed_escpred_linear_87_mv2)
Anova(seed_escpred_linear_88_mv2)
Anova(seed_escpred_linear_89_mv2)
```

##### Larger n

```{r}
seed_escpred_linear_87_mv<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std,
                            subset(data_ids,year==1987),family="binomial")
seed_escpred_linear_88_mv<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std,
                            subset(data_ids,year==1988),family="binomial")
seed_escpred_linear_89_mv<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                  pr_seeds=round(n_preyed_seed))~
                              avFD_std+var_std,
                            subset(data_ids,year==1989),family="binomial")
tab_model(seed_escpred_linear_87_mv,seed_escpred_linear_88_mv,
          seed_escpred_linear_89_mv,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Seeds escaping predation, linear effects, mean and variance")
Anova(seed_escpred_linear_87_mv)
Anova(seed_escpred_linear_88_mv)
Anova(seed_escpred_linear_89_mv)
```

#### Non-linear effects

##### Same n

```{r}
seed_escpred_nonlinear_87_mv2<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+
                                 I(avFD_std^2)+I(var_std^2),
                               subset(data_ids,year==1987&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
seed_escpred_nonlinear_88_mv2<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+
                                 I(avFD_std^2)+I(var_std^2),
                               subset(data_ids,year==1988&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
seed_escpred_nonlinear_89_mv2<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+
                                 I(avFD_std^2)+I(var_std^2),
                               subset(data_ids,year==1989&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)),family="binomial")
tab_model(seed_escpred_nonlinear_87_mv2,seed_escpred_nonlinear_88_mv2,
          seed_escpred_nonlinear_89_mv2,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Seeds escaping predation, nonlinear effects, mean and variance")
Anova(seed_escpred_nonlinear_87_mv2)
Anova(seed_escpred_nonlinear_88_mv2)
Anova(seed_escpred_nonlinear_89_mv2) 
```

##### Larger n

```{r}
seed_escpred_nonlinear_87_mv<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+
                                 I(avFD_std^2)+I(var_std^2),
                               subset(data_ids,year==1987),family="binomial")
seed_escpred_nonlinear_88_mv<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+
                                 I(avFD_std^2)+I(var_std^2),
                               subset(data_ids,year==1988),family="binomial")
seed_escpred_nonlinear_89_mv<-glm(cbind(npr_seeds=round(n_seed)-
                                       round(n_preyed_seed),
                                     pr_seeds=round(n_preyed_seed))~
                                 avFD_std+var_std+
                                 I(avFD_std^2)+I(var_std^2),
                               subset(data_ids,year==1989),family="binomial")
tab_model(seed_escpred_nonlinear_87_mv,seed_escpred_nonlinear_88_mv,
          seed_escpred_nonlinear_89_mv,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Seeds escaping predation, nonlinear effects, mean and variance")
Anova(seed_escpred_nonlinear_87_mv)
Anova(seed_escpred_nonlinear_88_mv)
Anova(seed_escpred_nonlinear_89_mv) 
```

## PHENOTYPIC SELECTION with n_fl

### Yearly models

#### Linear effects

##### Same n

```{r}
sel_nfl_linear_87_mv2<-lm(fitness_rel~avFD_std+var_std+
                        n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)))
sel_nfl_linear_88_mv2<-lm(fitness_rel~avFD_std+var_std+
                        n_fl_log_std,
                      subset(data_ids,year==1988&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)))
sel_nfl_linear_89_mv2<-lm(fitness_rel~avFD_std+var_std+
                        n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)))
tab_model(sel_nfl_linear_87_mv2,sel_nfl_linear_88_mv2,sel_nfl_linear_89_mv2,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Selection, linear effects, mean and variance")
Anova(sel_nfl_linear_87_mv2)
Anova(sel_nfl_linear_88_mv2)
Anova(sel_nfl_linear_89_mv2)
```

###### BCA intervals

####### 1987

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_87_mv2) coef(sel_nfl_linear_87_mv2)[2]
b <- car::Boot(sel_nfl_linear_87_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_87_mv2) coef(sel_nfl_linear_87_mv2)[3]
b <- car::Boot(sel_nfl_linear_87_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_87_mv2) coef(sel_nfl_linear_87_mv2)[4]
b <- car::Boot(sel_nfl_linear_87_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_87_mv2 <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_87_mv2)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_87_mv2)<-c("avFD_std","var_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_87_mv2,file="output/BCIs_sel_nfl_linear_87_mv2.RData")
```

```{r}
BCIs_sel_nfl_linear_87_mv2
```

####### 1988

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_88_mv2) coef(sel_nfl_linear_88_mv2)[2]
b <- car::Boot(sel_nfl_linear_88_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_88_mv2) coef(sel_nfl_linear_88_mv2)[3]
b <- car::Boot(sel_nfl_linear_88_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_88_mv2) coef(sel_nfl_linear_88_mv2)[4]
b <- car::Boot(sel_nfl_linear_88_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_88_mv2 <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_88_mv2)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_88_mv2)<-c("avFD_std","var_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_88_mv2,file="output/BCIs_sel_nfl_linear_88_mv2.RData")
```

```{r}
BCIs_sel_nfl_linear_88_mv2
```

####### 1989

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_89_mv2) coef(sel_nfl_linear_89_mv2)[2]
b <- car::Boot(sel_nfl_linear_89_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_89_mv2) coef(sel_nfl_linear_89_mv2)[3]
b <- car::Boot(sel_nfl_linear_89_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_89_mv2) coef(sel_nfl_linear_89_mv2)[4]
b <- car::Boot(sel_nfl_linear_89_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_89_mv2 <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_89_mv2)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_89_mv2)<-c("avFD_std","var_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_89_mv2,file="output/BCIs_sel_nfl_linear_89_mv2.RData")
```

```{r}
BCIs_sel_nfl_linear_89_mv2
```

##### Larger n

```{r}
sel_nfl_linear_87_mv<-lm(fitness_rel~avFD_std+var_std+
                        n_fl_log_std,
                      subset(data_ids,year==1987&
                               !is.na(avFD_std)&!is.na(var_std)))
sel_nfl_linear_88_mv<-lm(fitness_rel~avFD_std+var_std+
                        n_fl_log_std,
                      subset(data_ids,year==1988&
                               !is.na(avFD_std)&!is.na(var_std)))
sel_nfl_linear_89_mv<-lm(fitness_rel~avFD_std+var_std+
                        n_fl_log_std,
                      subset(data_ids,year==1989&
                               !is.na(avFD_std)&!is.na(var_std)))
tab_model(sel_nfl_linear_87_mv,sel_nfl_linear_88_mv,sel_nfl_linear_89_mv,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Selection, linear effects, mean and variance")
Anova(sel_nfl_linear_87_mv)
Anova(sel_nfl_linear_88_mv)
Anova(sel_nfl_linear_89_mv)
```

###### BCA intervals

####### 1987

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_87_mv) coef(sel_nfl_linear_87_mv)[2]
b <- car::Boot(sel_nfl_linear_87_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_87_mv) coef(sel_nfl_linear_87_mv)[3]
b <- car::Boot(sel_nfl_linear_87_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_87_mv) coef(sel_nfl_linear_87_mv)[4]
b <- car::Boot(sel_nfl_linear_87_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_87_mv <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_87_mv)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_87_mv)<-c("avFD_std","var_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_87_mv,file="output/BCIs_sel_nfl_linear_87_mv.RData")
```

```{r}
BCIs_sel_nfl_linear_87_mv
```

####### 1988

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_88_mv) coef(sel_nfl_linear_88_mv)[2]
b <- car::Boot(sel_nfl_linear_88_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_88_mv) coef(sel_nfl_linear_88_mv)[3]
b <- car::Boot(sel_nfl_linear_88_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_88_mv) coef(sel_nfl_linear_88_mv)[4]
b <- car::Boot(sel_nfl_linear_88_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_88_mv <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_88_mv)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_88_mv)<-c("avFD_std","var_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_88_mv,file="output/BCIs_sel_nfl_linear_88_mv.RData")
```

```{r}
BCIs_sel_nfl_linear_88_mv
```

####### 1989

```{r eval=FALSE, include=FALSE}
# avFD_std
slp <- function(sel_nfl_linear_89_mv) coef(sel_nfl_linear_89_mv)[2]
b <- car::Boot(sel_nfl_linear_89_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std
slp <- function(sel_nfl_linear_89_mv) coef(sel_nfl_linear_89_mv)[3]
b <- car::Boot(sel_nfl_linear_89_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std
slp <- function(sel_nfl_linear_89_mv) coef(sel_nfl_linear_89_mv)[4]
b <- car::Boot(sel_nfl_linear_89_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_linear_89_mv <- cbind(
  rbind(avFD_std_ci[1,],var_std_ci[1,],
        n_fl_log_std_ci[1,]),
  rbind(avFD_std_ci[2,],var_std_ci[2,],
        n_fl_log_std_ci[2,])
)
colnames(BCIs_sel_nfl_linear_89_mv)<-c("lower","upper")
rownames(BCIs_sel_nfl_linear_89_mv)<-c("avFD_std","var_std",
                                    "n_fl_log_std")
save(BCIs_sel_nfl_linear_89_mv,file="output/BCIs_sel_nfl_linear_89_mv.RData")
```

```{r}
BCIs_sel_nfl_linear_89_mv
```

#### Non-linear effects

##### Same n

```{r}
sel_nfl_nonlinear_87_mv2<-lm(fitness_rel~avFD_std+var_std+
                           n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+I(n_fl_log_std^2),
                         subset(data_ids,year==1987&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)))
sel_nfl_nonlinear_88_mv2<-lm(fitness_rel~avFD_std+var_std+
                           n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+I(n_fl_log_std^2),
                         subset(data_ids,year==1988&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)))
sel_nfl_nonlinear_89_mv2<-lm(fitness_rel~avFD_std+var_std+
                           n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+I(n_fl_log_std^2),
                           subset(data_ids,year==1989&!is.na(avFD_std)&
                                   !is.na(var_std)&!is.na(skew_std)&
                                   !is.na(kurt_std)))
tab_model(sel_nfl_nonlinear_87_mv2,sel_nfl_nonlinear_88_mv2,
          sel_nfl_nonlinear_89_mv2,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Selection, non-linear effects, mean and variance")
Anova(sel_nfl_nonlinear_87_mv2)
Anova(sel_nfl_nonlinear_88_mv2)
Anova(sel_nfl_nonlinear_89_mv2)
```

###### BCA intervals

####### 1987

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_87_mv2) coef(sel_nfl_nonlinear_87_mv2)[5]
b <- car::Boot(sel_nfl_nonlinear_87_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_87_mv2) coef(sel_nfl_nonlinear_87_mv2)[6]
b <- car::Boot(sel_nfl_nonlinear_87_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_87_mv2) coef(sel_nfl_nonlinear_87_mv2)[7]
b <- car::Boot(sel_nfl_nonlinear_87_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_87_mv2<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_87_mv2)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_87_mv2)<-c("avFD_std2","var_std2",
                                          "n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_87_mv2,
     file="output/BCIs_sel_nfl_nonlinear_87_mv2.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_87_mv2
```

####### 1988

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_88_mv2) coef(sel_nfl_nonlinear_88_mv2)[5]
b <- car::Boot(sel_nfl_nonlinear_88_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_88_mv2) coef(sel_nfl_nonlinear_88_mv2)[6]
b <- car::Boot(sel_nfl_nonlinear_88_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_88_mv2) coef(sel_nfl_nonlinear_88_mv2)[7]
b <- car::Boot(sel_nfl_nonlinear_88_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_88_mv2<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_88_mv2)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_88_mv2)<-c("avFD_std2","var_std2",
                                          "n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_88_mv2,
     file="output/BCIs_sel_nfl_nonlinear_88_mv2.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_88_mv2
```

####### 1989

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_89_mv2) coef(sel_nfl_nonlinear_89_mv2)[5]
b <- car::Boot(sel_nfl_nonlinear_89_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_89_mv2) coef(sel_nfl_nonlinear_89_mv2)[6]
b <- car::Boot(sel_nfl_nonlinear_89_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_89_mv2) coef(sel_nfl_nonlinear_89_mv2)[7]
b <- car::Boot(sel_nfl_nonlinear_89_mv2,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_89_mv2<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_89_mv2)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_89_mv2)<-c("avFD_std2","var_std2",
                                          "n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_89_mv2,
     file="output/BCIs_sel_nfl_nonlinear_89_mv2.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_89_mv2
```

##### Larger n

```{r}
sel_nfl_nonlinear_87_mv<-lm(fitness_rel~avFD_std+var_std+
                           n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+I(n_fl_log_std^2),
                         subset(data_ids,year==1987&
                                  !is.na(avFD_std)&!is.na(var_std)))
sel_nfl_nonlinear_88_mv<-lm(fitness_rel~avFD_std+var_std+
                           n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+I(n_fl_log_std^2),
                         subset(data_ids,year==1988&
                                  !is.na(avFD_std)&!is.na(var_std)))
sel_nfl_nonlinear_89_mv<-lm(fitness_rel~avFD_std+var_std+
                           n_fl_log_std+
                           I(avFD_std^2)+I(var_std^2)+I(n_fl_log_std^2),
                           subset(data_ids,year==1989&
                                    !is.na(avFD_std)&!is.na(var_std)))
tab_model(sel_nfl_nonlinear_87_mv,sel_nfl_nonlinear_88_mv,
          sel_nfl_nonlinear_89_mv,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("1987","1988","1989"),
          title="Selection, non-linear effects, mean and variance")
Anova(sel_nfl_nonlinear_87_mv)
Anova(sel_nfl_nonlinear_88_mv)
Anova(sel_nfl_nonlinear_89_mv)
```

###### BCA intervals

####### 1987

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_87_mv) coef(sel_nfl_nonlinear_87_mv)[5]
b <- car::Boot(sel_nfl_nonlinear_87_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_87_mv) coef(sel_nfl_nonlinear_87_mv)[6]
b <- car::Boot(sel_nfl_nonlinear_87_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_87_mv) coef(sel_nfl_nonlinear_87_mv)[7]
b <- car::Boot(sel_nfl_nonlinear_87_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_87_mv<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_87_mv)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_87_mv)<-c("avFD_std2","var_std2",
                                          "n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_87_mv,
     file="output/BCIs_sel_nfl_nonlinear_87_mv.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_87_mv
```

####### 1988

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_88_mv) coef(sel_nfl_nonlinear_88_mv)[5]
b <- car::Boot(sel_nfl_nonlinear_88_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_88_mv) coef(sel_nfl_nonlinear_88_mv)[6]
b <- car::Boot(sel_nfl_nonlinear_88_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_88_mv) coef(sel_nfl_nonlinear_88_mv)[7]
b <- car::Boot(sel_nfl_nonlinear_88_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_88_mv<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_88_mv)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_88_mv)<-c("avFD_std2","var_std2",
                                          "n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_88_mv,
     file="output/BCIs_sel_nfl_nonlinear_88_mv.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_88_mv
```

####### 1989

Only for non-linear terms

```{r eval=FALSE, include=FALSE}
# avFD_std2
slp <- function(sel_nfl_nonlinear_89_mv) coef(sel_nfl_nonlinear_89_mv)[5]
b <- car::Boot(sel_nfl_nonlinear_89_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
avFD_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# var_std2
slp <- function(sel_nfl_nonlinear_89_mv) coef(sel_nfl_nonlinear_89_mv)[6]
b <- car::Boot(sel_nfl_nonlinear_89_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
var_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# n_fl_log_std2
slp <- function(sel_nfl_nonlinear_89_mv) coef(sel_nfl_nonlinear_89_mv)[7]
b <- car::Boot(sel_nfl_nonlinear_89_mv,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
n_fl_log_std2_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)
```

```{r eval=FALSE, include=FALSE}
# Save confidence intervals as a table
BCIs_sel_nfl_nonlinear_89_mv<-cbind(
  rbind(avFD_std2_ci[1,],var_std2_ci[1,],
        n_fl_log_std2_ci[1,]),
  rbind(avFD_std2_ci[2,],var_std2_ci[2,],
        n_fl_log_std2_ci[2,])
)
colnames(BCIs_sel_nfl_nonlinear_89_mv)<-c("lower","upper")
rownames(BCIs_sel_nfl_nonlinear_89_mv)<-c("avFD_std2","var_std2",
                                          "n_fl_log_std2")
save(BCIs_sel_nfl_nonlinear_89_mv,
     file="output/BCIs_sel_nfl_nonlinear_89_mv.RData")
```

```{r}
BCIs_sel_nfl_nonlinear_89_mv
```

# SI: Mutlivariate GLMMs (TO DO)

Using subplot as a random effect.

# Univariate GLMs

## FRUIT INITIATIOM

### Global models

#### Linear

```{r}
fr_init_linear_mean<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+year+ 
                           avFD_std:year,
                         data_ids,family="binomial")
fr_init_linear_var<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std+year+ 
                           var_std:year,
                         data_ids,family="binomial")
fr_init_linear_skew<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std+year+ 
                           skew_std:year,
                         data_ids,family="binomial")
fr_init_linear_kurt<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std+year+ 
                           kurt_std:year,
                         data_ids,family="binomial")
```

```{r}
tab_model(fr_init_linear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, linear effects, mean"))
Anova(fr_init_linear_mean) # Use type II (now) or III?
```

```{r}
tab_model(fr_init_linear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, linear effects, variance"))
Anova(fr_init_linear_var) # Use type II (now) or III?
```

```{r}
tab_model(fr_init_linear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, linear effects, skewness"))
Anova(fr_init_linear_skew) # Use type II (now) or III?
```

```{r}
tab_model(fr_init_linear_kurt,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, linear effects, kurtosis"))
Anova(fr_init_linear_kurt) # Use type II (now) or III?
```

#### Non-linear

```{r}
fr_init_nonlinear_mean<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+
                              I(avFD_std^2)+year+ 
                           avFD_std:year+I(avFD_std^2):year,
                         data_ids,family="binomial")
fr_init_nonlinear_var<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std+
                             I(var_std^2)+year+ 
                           var_std:year+I(var_std^2):year,
                         data_ids,family="binomial")
fr_init_nonlinear_skew<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std+
                              I(skew_std^2)+year+ 
                           skew_std:year+I(skew_std^2):year,
                         data_ids,family="binomial")
fr_init_nonlinear_kurt<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std+
                              I(kurt_std^2)+year+ 
                           kurt_std:year+I(kurt_std^2):year,
                         data_ids,family="binomial")
```

```{r}
tab_model(fr_init_nonlinear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, non-linear effects, mean"))
Anova(fr_init_nonlinear_mean) # Use type II (now) or III?
```

```{r}
tab_model(fr_init_nonlinear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, non-linear effects, variance"))
Anova(fr_init_nonlinear_var) # Use type II (now) or III?
```

```{r}
tab_model(fr_init_nonlinear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, non-linear effects, skewness"))
Anova(fr_init_nonlinear_skew) # Use type II (now) or III?
```

```{r}
tab_model(fr_init_nonlinear_kurt,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Fruit initiation, non-linear effects, kurtosis"))
Anova(fr_init_nonlinear_kurt) # Use type II (now) or III?
```

### Yearly models

#### Linear

```{r}
# Mean
fr_init_linear_mean_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std,
                      subset(data_ids,year==1987),family="binomial")
fr_init_linear_mean_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std,
                      subset(data_ids,year==1988),family="binomial")
fr_init_linear_mean_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std,
                      subset(data_ids,year==1989),family="binomial")
# Variance
fr_init_linear_var_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std,
                      subset(data_ids,year==1987),family="binomial")
fr_init_linear_var_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std,
                      subset(data_ids,year==1988),family="binomial")
fr_init_linear_var_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std,
                      subset(data_ids,year==1989),family="binomial")
# Skewness
fr_init_linear_skew_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std,
                      subset(data_ids,year==1987),family="binomial")
fr_init_linear_skew_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std,
                      subset(data_ids,year==1988),family="binomial")
fr_init_linear_skew_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std,
                      subset(data_ids,year==1989),family="binomial")
# Kurtosis
fr_init_linear_kurt_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std,
                      subset(data_ids,year==1987),family="binomial")
fr_init_linear_kurt_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std,
                      subset(data_ids,year==1988),family="binomial")
fr_init_linear_kurt_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std,
                      subset(data_ids,year==1989),family="binomial")
```

```{r}
sdiff_fr_init_linear<-rbind(
  tidy(fr_init_linear_mean_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_linear_mean_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_linear_mean_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(fr_init_linear_var_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_linear_var_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_linear_var_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(fr_init_linear_skew_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_linear_skew_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_linear_skew_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(fr_init_linear_kurt_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_linear_kurt_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_linear_kurt_89)[2,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sdiff=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sdiff,star),predictor=term,type=as.factor("linear"))
```

#### Non-linear

```{r}
# Mean
fr_init_nonlinear_mean_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+
                                 I(avFD_std^2),
                      subset(data_ids,year==1987),family="binomial")
fr_init_nonlinear_mean_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+
                                 I(avFD_std^2),
                      subset(data_ids,year==1988),family="binomial")
fr_init_nonlinear_mean_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~avFD_std+
                                 I(avFD_std^2),
                      subset(data_ids,year==1989),family="binomial")
# Variance
fr_init_nonlinear_var_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std+
                                 I(var_std^2),
                      subset(data_ids,year==1987),family="binomial")
fr_init_nonlinear_var_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std+
                                 I(var_std^2),
                      subset(data_ids,year==1988),family="binomial")
fr_init_nonlinear_var_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~var_std+
                                 I(var_std^2),
                      subset(data_ids,year==1989),family="binomial")
# Skewness
fr_init_nonlinear_skew_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std+
                                 I(skew_std^2),
                      subset(data_ids,year==1987),family="binomial")
fr_init_nonlinear_skew_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std+
                                 I(skew_std^2),
                      subset(data_ids,year==1988),family="binomial")
fr_init_nonlinear_skew_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~skew_std+
                                 I(skew_std^2),
                      subset(data_ids,year==1989),family="binomial")
# Kurtosis
fr_init_nonlinear_kurt_87<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std+
                                 I(kurt_std^2),
                      subset(data_ids,year==1987),family="binomial")
fr_init_nonlinear_kurt_88<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std+
                                 I(kurt_std^2),
                      subset(data_ids,year==1988),family="binomial")
fr_init_nonlinear_kurt_89<-glm(cbind(fr=n_fr,nofr=n_fl-n_fr)~kurt_std+
                                 I(kurt_std^2),
                      subset(data_ids,year==1989),family="binomial")
```

```{r}
sdiff_fr_init_nonlinear<-rbind(
  tidy(fr_init_nonlinear_mean_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_nonlinear_mean_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_nonlinear_mean_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(fr_init_nonlinear_var_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_nonlinear_var_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_nonlinear_var_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(fr_init_nonlinear_skew_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_nonlinear_skew_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_nonlinear_skew_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(fr_init_nonlinear_kurt_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(fr_init_nonlinear_kurt_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(fr_init_nonlinear_kurt_89)[3,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sdiff=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sdiff,star),
         predictor=str_extract(term, "(?<=I\\().*?(?=\\^2\\))"),
         type=as.factor("nonlinear"))
```

## SEEDS ESCAPING PREDATION

### Global models

#### Linear

```{r}
seeds_escpred_linear_mean<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~avFD_std+year+ 
                           avFD_std:year,
                         data_ids,family="binomial")
seeds_escpred_linear_var<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~var_std+year+ 
                           var_std:year,
                         data_ids,family="binomial")
seeds_escpred_linear_skew<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~skew_std+year+ 
                           skew_std:year,
                         data_ids,family="binomial")
seeds_escpred_linear_kurt<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~kurt_std+year+ 
                           kurt_std:year,
                         data_ids,family="binomial")
```

```{r}
tab_model(seeds_escpred_linear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, linear effects, mean"))
Anova(seeds_escpred_linear_mean) # Use type II (now) or III?
```

```{r}
tab_model(seeds_escpred_linear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, linear effects, variance"))
Anova(seeds_escpred_linear_var) # Use type II (now) or III?
```

```{r}
tab_model(seeds_escpred_linear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, linear effects, skewness"))
Anova(seeds_escpred_linear_skew) # Use type II (now) or III?
```

```{r}
tab_model(seeds_escpred_linear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, linear effects, kurtosis"))
Anova(seeds_escpred_linear_kurt) # Use type II (now) or III?
```

#### Non-linear

```{r}
seeds_escpred_nonlinear_mean<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~avFD_std+I(avFD_std^2)+
                                    year+ 
                           avFD_std:year+I(avFD_std^2):year,
                         data_ids,family="binomial")
seeds_escpred_nonlinear_var<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~var_std+I(var_std^2)+
                                   year+ 
                           var_std:year+I(var_std^2):year,
                         data_ids,family="binomial")
seeds_escpred_nonlinear_skew<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~skew_std+I(skew_std^2)+
                                    year+ 
                           skew_std:year+I(skew_std^2):year,
                         data_ids,family="binomial")
seeds_escpred_nonlinear_kurt<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),                                        pr_seeds=round(n_preyed_seed))~kurt_std+I(kurt_std^2)+
                                    year+ 
                           kurt_std:year+I(kurt_std^2):year,
                         data_ids,family="binomial")
```

```{r}
tab_model(seeds_escpred_nonlinear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, non-linear effects, mean"))
Anova(seeds_escpred_nonlinear_mean) # Use type II (now) or III?
```

```{r}
tab_model(seeds_escpred_nonlinear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, non-linear effects, variance"))
Anova(seeds_escpred_nonlinear_var) # Use type II (now) or III?
```

```{r}
tab_model(seeds_escpred_nonlinear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, non-linear effects, skewness"))
Anova(seeds_escpred_nonlinear_skew) # Use type II (now) or III?
```

```{r}
tab_model(seeds_escpred_nonlinear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Seeds escaping predation, non-linear effects, kurtosis"))
Anova(seeds_escpred_nonlinear_kurt) # Use type II (now) or III?
```

### Yearly models

#### Linear

```{r}
# Mean
seeds_escpred_linear_mean_87<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),
                                        pr_seeds=round(n_preyed_seed))~
                                    avFD_std,
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_mean_88<-glm(cbind(npr_seeds=round(n_seed)-   
                                          round(n_preyed_seed),    
                                        pr_seeds=round(n_preyed_seed))~
                                    avFD_std,
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_mean_89<-glm(cbind(npr_seeds=round(n_seed)- 
                                          round(n_preyed_seed),      
                                        pr_seeds=round(n_preyed_seed))
                                  ~avFD_std,
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
# Variance
seeds_escpred_linear_var_87<-glm(cbind(npr_seeds=round(n_seed)- 
                                         round(n_preyed_seed),     
                                       pr_seeds=round(n_preyed_seed))~
                                   var_std,
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_var_88<-glm(cbind(npr_seeds=round(n_seed)-  
                                         round(n_preyed_seed),    
                                       pr_seeds=round(n_preyed_seed))~
                                   var_std,
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_var_89<-glm(cbind(npr_seeds=round(n_seed)-  
                                         round(n_preyed_seed),     
                                       pr_seeds=round(n_preyed_seed))~
                                   var_std,
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
# Skewness
seeds_escpred_linear_skew_87<-glm(cbind(npr_seeds=round(n_seed)- 
                                          round(n_preyed_seed),       
                                        pr_seeds=round(n_preyed_seed))~
                                    skew_std,
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_skew_88<-glm(cbind(npr_seeds=round(n_seed)-
                                          round(n_preyed_seed),   
                                        pr_seeds=round(n_preyed_seed))~
                                    skew_std,
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_skew_89<-glm(cbind(npr_seeds=round(n_seed)-   
                                          round(n_preyed_seed),     
                                        pr_seeds=round(n_preyed_seed))~
                                    skew_std,
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
# Kurtosis
seeds_escpred_linear_kurt_87<-glm(cbind(npr_seeds=round(n_seed)- 
                                          round(n_preyed_seed),     
                                        pr_seeds=round(n_preyed_seed))~
                                    kurt_std,
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_kurt_88<-glm(cbind(npr_seeds=round(n_seed)-     
                                          round(n_preyed_seed),       
                                        pr_seeds=round(n_preyed_seed))~
                                    kurt_std,
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_linear_kurt_89<-glm(cbind(npr_seeds=round(n_seed)-     
                                          round(n_preyed_seed),      
                                        pr_seeds=round(n_preyed_seed))~
                                    kurt_std,
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
```

```{r}
sdiff_seeds_escpred_linear<-rbind(
  tidy(seeds_escpred_linear_mean_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_linear_mean_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_linear_mean_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(seeds_escpred_linear_var_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_linear_var_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_linear_var_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(seeds_escpred_linear_skew_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_linear_skew_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_linear_skew_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(seeds_escpred_linear_kurt_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_linear_kurt_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_linear_kurt_89)[2,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sdiff=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sdiff,star),predictor=term,type=as.factor("linear"))
```

#### Non-linear

```{r}
# Mean
seeds_escpred_nonlinear_mean_87<-glm(cbind(npr_seeds=round(n_seed)- 
                                             round(n_preyed_seed),    
                                           pr_seeds=round(n_preyed_seed))~
                                       avFD_std+I(avFD_std^2),
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_mean_88<-glm(cbind(npr_seeds=round(n_seed)-  
                                             round(n_preyed_seed), 
                                           pr_seeds=round(n_preyed_seed))~
                                       avFD_std+I(avFD_std^2),
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_mean_89<-glm(cbind(npr_seeds=round(n_seed)- 
                                             round(n_preyed_seed), 
                                           pr_seeds=round(n_preyed_seed))~
                                       avFD_std+I(avFD_std^2),
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
# Variance
seeds_escpred_nonlinear_var_87<-glm(cbind(npr_seeds=round(n_seed)- 
                                            round(n_preyed_seed),  
                                          pr_seeds=round(n_preyed_seed))~
                                      var_std+I(var_std^2),
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_var_88<-glm(cbind(npr_seeds=round(n_seed)-   
                                            round(n_preyed_seed),    
                                          pr_seeds=round(n_preyed_seed))~
                                      var_std+I(var_std^2),
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_var_89<-glm(cbind(npr_seeds=round(n_seed)- 
                                            round(n_preyed_seed),  
                                          pr_seeds=round(n_preyed_seed))~
                                      var_std+I(var_std^2),
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
# Skewness
seeds_escpred_nonlinear_skew_87<-glm(cbind(npr_seeds=round(n_seed)-  
                                             round(n_preyed_seed), 
                                           pr_seeds=round(n_preyed_seed))~
                                       skew_std+I(skew_std^2),
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_skew_88<-glm(cbind(npr_seeds=round(n_seed)-
                                             round(n_preyed_seed),   
                                           pr_seeds=round(n_preyed_seed))~
                                       skew_std+I(skew_std^2),
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_skew_89<-glm(cbind(npr_seeds=round(n_seed)- 
                                             round(n_preyed_seed),  
                                           pr_seeds=round(n_preyed_seed))~
                                       skew_std+I(skew_std^2),
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
# Kurtosis
seeds_escpred_nonlinear_kurt_87<-glm(cbind(npr_seeds=round(n_seed)- 
                                             round(n_preyed_seed),      
                                           pr_seeds=round(n_preyed_seed))~
                                       kurt_std+I(kurt_std^2),
                      subset(data_ids,year==1987&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_kurt_88<-glm(cbind(npr_seeds=round(n_seed)- 
                                             round(n_preyed_seed),  
                                           pr_seeds=round(n_preyed_seed))~
                                       kurt_std+I(kurt_std^2),
                      subset(data_ids,year==1988&!is.na(prop_seed_preyed)),
                      family="binomial")
seeds_escpred_nonlinear_kurt_89<-glm(cbind(npr_seeds=round(n_seed)-   
                                             round(n_preyed_seed),   
                                           pr_seeds=round(n_preyed_seed))~
                                       kurt_std+I(kurt_std^2),
                      subset(data_ids,year==1989&!is.na(prop_seed_preyed)),
                      family="binomial")
```

```{r}
sdiff_seeds_escpred_nonlinear<-rbind(
  tidy(seeds_escpred_nonlinear_mean_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_nonlinear_mean_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_nonlinear_mean_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(seeds_escpred_nonlinear_var_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_nonlinear_var_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_nonlinear_var_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(seeds_escpred_nonlinear_skew_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_nonlinear_skew_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_nonlinear_skew_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(seeds_escpred_nonlinear_kurt_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(seeds_escpred_nonlinear_kurt_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(seeds_escpred_nonlinear_kurt_89)[3,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sdiff=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sdiff,star),
         predictor=str_extract(term, "(?<=I\\().*?(?=\\^2\\))"),
         type=as.factor("nonlinear"))
```

## PHENOTYPIC SELECTION

### Global models

#### Linear

```{r}
sel_linear_mean<-lm(fitness_rel~avFD_std+year+ 
                           avFD_std:year,
                         subset(data_ids,!is.na(avFD_std)))
sel_linear_var<-lm(fitness_rel~var_std+year+ 
                           var_std:year,
                         subset(data_ids,!is.na(var_std)))
sel_linear_skew<-lm(fitness_rel~skew_std+year+ 
                           skew_std:year,
                         subset(data_ids,!is.na(skew_std)))
sel_linear_kurt<-lm(fitness_rel~kurt_std+year+ 
                           kurt_std:year,
                         subset(data_ids,!is.na(kurt_std)))
```

```{r}
tab_model(sel_linear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, linear effects, mean"))
Anova(sel_linear_mean) # Use type II (now) or III?
```

```{r}
tab_model(sel_linear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, linear effects, variance"))
Anova(sel_linear_var) # Use type II (now) or III?
```

```{r}
tab_model(sel_linear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, linear effects, skewness"))
Anova(sel_linear_skew) # Use type II (now) or III?
```

```{r}
tab_model(sel_linear_kurt,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, linear effects, kurtosis"))
Anova(sel_linear_kurt) # Use type II (now) or III?
```

#### Non-linear

```{r}
sel_nonlinear_mean<-lm(fitness_rel~avFD_std+year+I(avFD_std^2)+ 
                           avFD_std:year+I(avFD_std^2):year,
                         subset(data_ids,!is.na(avFD_std)))
sel_nonlinear_var<-lm(fitness_rel~var_std+year+I(var_std^2)+  
                           var_std:year+I(var_std^2):year,
                         subset(data_ids,!is.na(var_std)))
sel_nonlinear_skew<-lm(fitness_rel~skew_std+year+I(skew_std^2)+ 
                           skew_std:year+I(skew_std^2):year,
                         subset(data_ids,!is.na(skew_std)))
sel_nonlinear_kurt<-lm(fitness_rel~kurt_std+year+I(kurt_std^2)+  
                           kurt_std:year+I(kurt_std^2):year,
                         subset(data_ids,!is.na(kurt_std)))
```

```{r}
tab_model(sel_nonlinear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, mean"))
Anova(sel_nonlinear_mean) # Use type II (now) or III?
```

```{r}
tab_model(sel_nonlinear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, variance"))
Anova(sel_nonlinear_var) # Use type II (now) or III?
```

```{r}
tab_model(sel_nonlinear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, skewness"))
Anova(sel_nonlinear_skew) # Use type II (now) or III?
```

```{r}
tab_model(sel_nonlinear_kurt,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, kurtosis"))
Anova(sel_nonlinear_kurt) # Use type II (now) or III?
```

### Yearly models

#### Linear

```{r}
# Mean
sel_linear_mean_87<-lm(fitness_rel~avFD_std,
                      subset(data_ids,year==1987&!is.na(avFD_std)))
sel_linear_mean_88<-lm(fitness_rel~avFD_std,
                      subset(data_ids,year==1989&!is.na(avFD_std)))
sel_linear_mean_89<-lm(fitness_rel~avFD_std,
                      subset(data_ids,year==1989&!is.na(avFD_std)))
# Variance
sel_linear_var_87<-lm(fitness_rel~var_std,
                      subset(data_ids,year==1987&!is.na(var_std)))
sel_linear_var_88<-lm(fitness_rel~var_std,
                      subset(data_ids,year==1989&!is.na(var_std)))
sel_linear_var_89<-lm(fitness_rel~var_std,
                      subset(data_ids,year==1989&!is.na(var_std)))
# Skewness
sel_linear_skew_87<-lm(fitness_rel~skew_std,
                      subset(data_ids,year==1987&!is.na(skew_std)))
sel_linear_skew_88<-lm(fitness_rel~skew_std,
                      subset(data_ids,year==1989&!is.na(skew_std)))
sel_linear_skew_89<-lm(fitness_rel~skew_std,
                      subset(data_ids,year==1989&!is.na(skew_std)))
# Kurtosis
sel_linear_kurt_87<-lm(fitness_rel~kurt_std,
                      subset(data_ids,year==1987&!is.na(kurt_std)))
sel_linear_kurt_88<-lm(fitness_rel~kurt_std,
                      subset(data_ids,year==1989&!is.na(kurt_std)))
sel_linear_kurt_89<-lm(fitness_rel~kurt_std,
                      subset(data_ids,year==1989&!is.na(kurt_std)))
```

```{r}
sdiff_sel_linear<-rbind(
  tidy(sel_linear_mean_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_linear_mean_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_linear_mean_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(sel_linear_var_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_linear_var_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_linear_var_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(sel_linear_skew_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_linear_skew_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_linear_skew_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(sel_linear_kurt_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_linear_kurt_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_linear_kurt_89)[2,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sdiff=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sdiff,star),predictor=term,type=as.factor("linear"))
```

#### Non-linear

```{r}
# Mean
sel_nonlinear_mean_87<-lm(fitness_rel~avFD_std+I(avFD_std^2),
                      subset(data_ids,year==1987&!is.na(avFD_std)))
sel_nonlinear_mean_88<-lm(fitness_rel~avFD_std+I(avFD_std^2),
                      subset(data_ids,year==1989&!is.na(avFD_std)))
sel_nonlinear_mean_89<-lm(fitness_rel~avFD_std+I(avFD_std^2),
                      subset(data_ids,year==1989&!is.na(avFD_std)))
# Variance
sel_nonlinear_var_87<-lm(fitness_rel~var_std+I(var_std^2),
                      subset(data_ids,year==1987&!is.na(var_std)))
sel_nonlinear_var_88<-lm(fitness_rel~var_std+I(var_std^2),
                      subset(data_ids,year==1989&!is.na(var_std)))
sel_nonlinear_var_89<-lm(fitness_rel~var_std+I(var_std^2),
                      subset(data_ids,year==1989&!is.na(var_std)))
# Skewness
sel_nonlinear_skew_87<-lm(fitness_rel~skew_std+I(skew_std^2),
                      subset(data_ids,year==1987&!is.na(skew_std)))
sel_nonlinear_skew_88<-lm(fitness_rel~skew_std+I(skew_std^2),
                      subset(data_ids,year==1989&!is.na(skew_std)))
sel_nonlinear_skew_89<-lm(fitness_rel~skew_std+I(skew_std^2),
                      subset(data_ids,year==1989&!is.na(skew_std)))
# Kurtosis
sel_nonlinear_kurt_87<-lm(fitness_rel~kurt_std+I(kurt_std^2),
                      subset(data_ids,year==1987&!is.na(kurt_std)))
sel_nonlinear_kurt_88<-lm(fitness_rel~kurt_std+I(kurt_std^2),
                      subset(data_ids,year==1989&!is.na(kurt_std)))
sel_nonlinear_kurt_89<-lm(fitness_rel~kurt_std+I(kurt_std^2),
                      subset(data_ids,year==1989&!is.na(kurt_std)))
```

```{r}
sdiff_sel_nonlinear<-rbind(
  tidy(sel_nonlinear_mean_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nonlinear_mean_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nonlinear_mean_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nonlinear_var_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nonlinear_var_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nonlinear_var_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nonlinear_skew_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nonlinear_skew_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nonlinear_skew_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nonlinear_kurt_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nonlinear_kurt_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nonlinear_kurt_89)[3,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sdiff=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sdiff,star),
         predictor=str_extract(term, "(?<=I\\().*?(?=\\^2\\))"),
         type=as.factor("nonlinear"))
```

## PHENOTYPIC SELECTION with n_fl

### Global models

#### Linear

```{r}
sel_nfl_linear_mean<-lm(fitness_rel~avFD_std+year+n_fl_log_std+
                           avFD_std:year,
                         subset(data_ids,!is.na(avFD_std)))
sel_nfl_linear_var<-lm(fitness_rel~var_std+year+n_fl_log_std+ 
                           var_std:year,
                         subset(data_ids,!is.na(var_std)))
sel_nfl_linear_skew<-lm(fitness_rel~skew_std+year+n_fl_log_std+ 
                           skew_std:year,
                         subset(data_ids,!is.na(skew_std)))
sel_nfl_linear_kurt<-lm(fitness_rel~kurt_std+year+n_fl_log_std+ 
                           kurt_std:year,
                         subset(data_ids,!is.na(kurt_std)))
```

```{r}
tab_model(sel_nfl_linear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection with nfl, linear effects, mean"))
Anova(sel_nfl_linear_mean) # Use type II (now) or III?
```

```{r}
tab_model(sel_nfl_linear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection with nfl, linear effects, variance"))
Anova(sel_nfl_linear_var) # Use type II (now) or III?
```

```{r}
tab_model(sel_nfl_linear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection with nfl, linear effects, skewness"))
Anova(sel_nfl_linear_skew) # Use type II (now) or III?
```

```{r}
tab_model(sel_nfl_linear_kurt,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection with nfl, linear effects, kurtosis"))
Anova(sel_nfl_linear_kurt) # Use type II (now) or III?
```

#### Non-linear

```{r}
sel_nfl_nonlinear_mean<-lm(fitness_rel~avFD_std+year+I(avFD_std^2)+
                             n_fl_log_std+ 
                           avFD_std:year+I(avFD_std^2):year,
                         subset(data_ids,!is.na(avFD_std)))
sel_nfl_nonlinear_var<-lm(fitness_rel~var_std+year+I(var_std^2)+
                            n_fl_log_std+  
                           var_std:year+I(var_std^2):year,
                         subset(data_ids,!is.na(var_std)))
sel_nfl_nonlinear_skew<-lm(fitness_rel~skew_std+year+I(skew_std^2)+
                             n_fl_log_std+ 
                           skew_std:year+I(skew_std^2):year,
                         subset(data_ids,!is.na(skew_std)))
sel_nfl_nonlinear_kurt<-lm(fitness_rel~kurt_std+year+I(kurt_std^2)+
                             n_fl_log_std+  
                           kurt_std:year+I(kurt_std^2):year,
                         subset(data_ids,!is.na(kurt_std)))
```

```{r}
tab_model(sel_nfl_nonlinear_mean,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, mean"))
Anova(sel_nfl_nonlinear_mean) # Use type II (now) or III?
```

```{r}
tab_model(sel_nfl_nonlinear_var,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, variance"))
Anova(sel_nfl_nonlinear_var) # Use type II (now) or III?
```

```{r}
tab_model(sel_nfl_nonlinear_skew,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, skewness"))
Anova(sel_nfl_nonlinear_skew) # Use type II (now) or III?
```

```{r}
tab_model(sel_nfl_nonlinear_kurt,
          transform=NULL,show.ci=F,show.se=T,show.stat=T,digits=3,
          dv.labels=c("Selection, non-linear effects, kurtosis"))
Anova(sel_nfl_linear_kurt) # Use type II (now) or III?
```

### Yearly models

#### Linear

```{r}
# Mean
sel_nfl_linear_mean_87<-lm(fitness_rel~avFD_std+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(avFD_std)))
sel_nfl_linear_mean_88<-lm(fitness_rel~avFD_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(avFD_std)))
sel_nfl_linear_mean_89<-lm(fitness_rel~avFD_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(avFD_std)))
# Variance
sel_nfl_linear_var_87<-lm(fitness_rel~var_std+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(var_std)))
sel_nfl_linear_var_88<-lm(fitness_rel~var_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(var_std)))
sel_nfl_linear_var_89<-lm(fitness_rel~var_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(var_std)))
# Skewness
sel_nfl_linear_skew_87<-lm(fitness_rel~skew_std+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(skew_std)))
sel_nfl_linear_skew_88<-lm(fitness_rel~skew_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(skew_std)))
sel_nfl_linear_skew_89<-lm(fitness_rel~skew_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(skew_std)))
# Kurtosis
sel_nfl_linear_kurt_87<-lm(fitness_rel~kurt_std+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(kurt_std)))
sel_nfl_linear_kurt_88<-lm(fitness_rel~kurt_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(kurt_std)))
sel_nfl_linear_kurt_89<-lm(fitness_rel~kurt_std+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(kurt_std)))
```

```{r}
sgrad_sel_nfl_linear<-rbind(
  tidy(sel_nfl_linear_mean_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_linear_mean_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_linear_mean_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nfl_linear_var_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_linear_var_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_linear_var_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nfl_linear_skew_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_linear_skew_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_linear_skew_89)[2,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nfl_linear_kurt_87)[2,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_linear_kurt_88)[2,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_linear_kurt_89)[2,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sgrad=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sgrad,star),predictor=term,type=as.factor("linear"))
```

#### Non-linear

```{r}
# Mean
sel_nfl_nonlinear_mean_87<-lm(fitness_rel~avFD_std+I(avFD_std^2)+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(avFD_std)))
sel_nfl_nonlinear_mean_88<-lm(fitness_rel~avFD_std+I(avFD_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(avFD_std)))
sel_nfl_nonlinear_mean_89<-lm(fitness_rel~avFD_std+I(avFD_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(avFD_std)))
# Variance
sel_nfl_nonlinear_var_87<-lm(fitness_rel~var_std+I(var_std^2)+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(var_std)))
sel_nfl_nonlinear_var_88<-lm(fitness_rel~var_std+I(var_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(var_std)))
sel_nfl_nonlinear_var_89<-lm(fitness_rel~var_std+I(var_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(var_std)))
# Skewness
sel_nfl_nonlinear_skew_87<-lm(fitness_rel~skew_std+I(skew_std^2)+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(skew_std)))
sel_nfl_nonlinear_skew_88<-lm(fitness_rel~skew_std+I(skew_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(skew_std)))
sel_nfl_nonlinear_skew_89<-lm(fitness_rel~skew_std+I(skew_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(skew_std)))
# Kurtosis
sel_nfl_nonlinear_kurt_87<-lm(fitness_rel~kurt_std+I(kurt_std^2)+n_fl_log_std,
                      subset(data_ids,year==1987&!is.na(kurt_std)))
sel_nfl_nonlinear_kurt_88<-lm(fitness_rel~kurt_std+I(kurt_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(kurt_std)))
sel_nfl_nonlinear_kurt_89<-lm(fitness_rel~kurt_std+I(kurt_std^2)+n_fl_log_std,
                      subset(data_ids,year==1989&!is.na(kurt_std)))
```

```{r}
sgrad_sel_nfl_nonlinear<-rbind(
  tidy(sel_nfl_nonlinear_mean_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_nonlinear_mean_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_nonlinear_mean_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nfl_nonlinear_var_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_nonlinear_var_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_nonlinear_var_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nfl_nonlinear_skew_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_nonlinear_skew_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_nonlinear_skew_89)[3,]%>%mutate(year=as.factor("1989")),
  tidy(sel_nfl_nonlinear_kurt_87)[3,]%>%mutate(year=as.factor("1987")),
  tidy(sel_nfl_nonlinear_kurt_88)[3,]%>%mutate(year=as.factor("1988")),
  tidy(sel_nfl_nonlinear_kurt_89)[3,]%>%mutate(year=as.factor("1989"))
  )%>%
  mutate(signif=as.factor(ifelse(p.value>0.05,0,1)),
         sgrad=format(round(estimate,3),nsmall=3),
         star=ifelse(signif==1,"*","  "),
         print=paste(sgrad,star),
         predictor=str_extract(term, "(?<=I\\().*?(?=\\^2\\))"),
         type=as.factor("nonlinear"))
```

# Figures

## Extract predictions from univariate GLMs

```{r}
prediction_fr_init_linear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(fr_init_linear_mean_87,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_linear_mean_88,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_linear_mean_89,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(fr_init_linear_var_87,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_linear_var_88,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_linear_var_89,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(fr_init_linear_skew_87,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_linear_skew_88,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_linear_skew_89,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(fr_init_linear_kurt_87,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_linear_kurt_88,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_linear_kurt_89,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sdiff_fr_init_linear%>%
              select(predictor,sdiff,year,signif,star,print,type))
```

```{r}
prediction_fr_init_nonlinear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(fr_init_nonlinear_mean_87,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_nonlinear_mean_88,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_nonlinear_mean_89,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(fr_init_nonlinear_var_87,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_nonlinear_var_88,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_nonlinear_var_89,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(fr_init_nonlinear_skew_87,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_nonlinear_skew_88,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_nonlinear_skew_89,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(fr_init_nonlinear_kurt_87,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(fr_init_nonlinear_kurt_88,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(fr_init_nonlinear_kurt_89,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sdiff_fr_init_nonlinear%>%
              select(predictor,sdiff,year,signif,star,print,type))
```

```{r}
prediction_fr_init_univar<-rbind(prediction_fr_init_linear_univar,
                                 prediction_fr_init_nonlinear_univar)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")))
```

```{r}
prediction_seeds_escpred_linear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(seeds_escpred_linear_mean_87,
                         terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_linear_mean_88,
                         terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_linear_mean_89,
                         terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(seeds_escpred_linear_var_87,
                         terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_linear_var_88,
                         terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_linear_var_89,
                         terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(seeds_escpred_linear_skew_87,
                         terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_linear_skew_88,
                         terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_linear_skew_89,
                         terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(seeds_escpred_linear_kurt_87,
                         terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_linear_kurt_88,
                         terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_linear_kurt_89,
                         terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sdiff_seeds_escpred_linear%>%
              select(predictor,sdiff,year,signif,star,print,type))
```

```{r}
prediction_seeds_escpred_nonlinear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(seeds_escpred_nonlinear_mean_87,
                         terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_nonlinear_mean_88,
                         terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_nonlinear_mean_89,
                         terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(seeds_escpred_nonlinear_var_87,
                         terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_nonlinear_var_88,
                         terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_nonlinear_var_89,
                         terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(seeds_escpred_nonlinear_skew_87,
                         terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_nonlinear_skew_88,
                         terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_nonlinear_skew_89,
                         terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(seeds_escpred_nonlinear_kurt_87,
                         terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(seeds_escpred_nonlinear_kurt_88,
                         terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(seeds_escpred_nonlinear_kurt_89,
                         terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sdiff_seeds_escpred_nonlinear%>%
              select(predictor,sdiff,year,signif,star,print,type))
```

```{r}
prediction_seeds_escpred_univar<-rbind(prediction_seeds_escpred_linear_univar,
                                 prediction_seeds_escpred_nonlinear_univar)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")))
```

```{r}
prediction_sel_linear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(sel_linear_mean_87,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_linear_mean_88,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_linear_mean_89,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(sel_linear_var_87,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_linear_var_88,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_linear_var_89,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(sel_linear_skew_87,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_linear_skew_88,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_linear_skew_89,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(sel_linear_kurt_87,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_linear_kurt_88,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_linear_kurt_89,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sdiff_sel_linear%>%
              select(predictor,sdiff,year,signif,star,print,type))
```

```{r}
prediction_sel_nonlinear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(sel_nonlinear_mean_87,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nonlinear_mean_88,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nonlinear_mean_89,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(sel_nonlinear_var_87,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nonlinear_var_88,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nonlinear_var_89,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(sel_nonlinear_skew_87,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nonlinear_skew_88,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nonlinear_skew_89,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(sel_nonlinear_kurt_87,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nonlinear_kurt_88,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nonlinear_kurt_89,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sdiff_sel_nonlinear%>%
              select(predictor,sdiff,year,signif,star,print,type))
```

```{r}
prediction_sel_univar<-rbind(prediction_sel_linear_univar,
                                 prediction_sel_nonlinear_univar)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")))
```

```{r}
prediction_sel_nfl_linear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(sel_nfl_linear_mean_87,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nfl_linear_mean_88,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nfl_linear_mean_89,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(sel_nfl_linear_var_87,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nfl_linear_var_88,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nfl_linear_var_89,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(sel_nfl_linear_skew_87,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nfl_linear_skew_88,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_linear_skew_89,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(sel_nfl_linear_kurt_87,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nfl_linear_kurt_88,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nfl_linear_kurt_89,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sgrad_sel_nfl_linear%>%
              select(predictor,sgrad,year,signif,star,print,type))
```

```{r}
prediction_sel_nfl_nonlinear_univar<-rbind(
  # Mean
  rbind(tibble(ggpredict(sel_nfl_nonlinear_mean_87,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nonlinear_mean_88,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nfl_nonlinear_mean_89,terms=c("avFD_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="avFD_std"),
  # Var
  rbind(tibble(ggpredict(sel_nfl_nonlinear_var_87,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nfl_nonlinear_var_88,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nfl_nonlinear_var_89,terms=c("var_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="var_std"),
  # Skew
  rbind(tibble(ggpredict(sel_nfl_nonlinear_skew_87,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nfl_nonlinear_skew_88,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nfl_nonlinear_skew_89,terms=c("skew_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="skew_std"),
  # Kurt
  rbind(tibble(ggpredict(sel_nfl_nonlinear_kurt_87,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1987)),
        tibble(ggpredict(sel_nfl_nonlinear_kurt_88,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1988)),
        tibble(ggpredict(sel_nfl_nonlinear_kurt_89,terms=c("kurt_std [all]")))%>%
          mutate(year=as.factor(1989)))%>%
    mutate(predictor="kurt_std")
)%>%
  left_join(sgrad_sel_nfl_nonlinear%>%
              select(predictor,sgrad,year,signif,star,print,type))
```

```{r}
prediction_sel_nfl_univar<-rbind(prediction_sel_nfl_linear_univar,
                                 prediction_sel_nfl_nonlinear_univar)%>%
  mutate(predictor=factor(predictor,
                          levels=c("avFD_std","var_std","skew_std","kurt_std")))
```

## Figure 2 (new)

Figure based on predictions of yearly univariate models (selection differentials).

```{r}
predictor.labs<-c("Mean","Variance","Skewness","Kurtosis")
names(predictor.labs)<-c("avFD_std","var_std","skew_std","kurt_std")
fig2<-ggplot()+
  geom_point(data=data_ids%>%
               select(year,fr_init,avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
                            names_to="predictor",values_to="value_predictor")%>%
               mutate(predictor=factor(predictor,
                                       levels=c("avFD_std","var_std",
                                                "skew_std","kurt_std"))),
             aes(x=value_predictor,y=fr_init),
             size=2,alpha=0.3)+
  facet_grid2(c("year","predictor"), 
              labeller=labeller(predictor=predictor.labs), 
              scales = "free", independent = "all")+
  geom_ribbon(data=prediction_fr_init_univar,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=type),
              alpha=0.3)+
  geom_line(data=prediction_fr_init_univar,
            aes(x=x,y=predicted,linetype=signif,color=type),
            linewidth=1)+
  scale_linetype_manual(values=c("dotted", "solid"))+
  ylab("Proportion of flowers that developed to fruits")+
  xlab("Value of the moment")+
  my_theme()+
  geom_text(data=prediction_fr_init_univar%>%
              select(year,predictor,print,type)%>%
              distinct()%>%
              pivot_wider(names_from=type,values_from=print)%>%
              mutate(print=paste("L = ",linear,"\n","NL =", nonlinear)),
            aes(x=Inf,y=Inf,label=print),
             hjust=1.05, vjust=1.2,family="serif")
fig2
ggsave(file="output/figures/fig2.tiff", plot=fig2, width=10, height=7)
```

## Figure 3 (new)

Figure based on predictions of yearly univariate models (selection differentials).

```{r}
fig3<-ggplot()+
  geom_point(data=data_ids%>%
               select(year,prop_seed_preyed,
                      avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
                            names_to="predictor",values_to="value_predictor")%>%
               mutate(predictor=factor(predictor,
                                       levels=c("avFD_std","var_std",
                                                "skew_std","kurt_std")))%>%
               filter(!is.na(prop_seed_preyed)),
             aes(x=value_predictor,y=1-prop_seed_preyed),
             size=2,alpha=0.3)+
  facet_grid2(c("year","predictor"), 
              labeller=labeller(predictor=predictor.labs), 
              scales = "free", independent = "all")+
  geom_ribbon(data=prediction_seeds_escpred_univar,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=type),
              alpha=0.3)+
  geom_line(data=prediction_seeds_escpred_univar,
            aes(x=x,y=predicted,linetype=signif,color=type),
            linewidth=1)+
  scale_linetype_manual(values=c("dotted", "solid"))+
  ylab("Proportion of seeds escaping predation")+
  xlab("Value of the moment")+
  my_theme()+
  geom_text(data=prediction_seeds_escpred_univar%>%
              select(year,predictor,print,type)%>%
              distinct()%>%
              pivot_wider(names_from=type,values_from=print)%>%
              mutate(print=paste("L = ",linear,"\n","NL =", nonlinear)),
            aes(x=Inf,y=0.25,label=print),
            hjust=1.05, vjust=1.2,family="serif")
fig3
ggsave(file="output/figures/fig3.tiff", plot=fig3, width=10, height=7)
```

## Figure 4 (new)

Figure based on predictions of yearly univariate models (selection differentials).

```{r}
fig4<-ggplot()+
  geom_point(data=data_ids%>%
               select(year,fitness_rel,avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
                            names_to="predictor",values_to="value_predictor")%>%
               mutate(predictor=factor(predictor,
                                       levels=c("avFD_std","var_std",
                                                "skew_std","kurt_std"))),
             aes(x=value_predictor,y=fitness_rel),
             size=2,alpha=0.3)+
  facet_grid2(c("year","predictor"), 
              labeller=labeller(predictor=predictor.labs), 
              scales = "free", independent = "all")+
  geom_ribbon(data=prediction_sel_nfl_univar,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=type),
              alpha=0.3)+
  geom_line(data=prediction_sel_nfl_univar,
            aes(x=x,y=predicted,linetype=signif,color=type),
            linewidth=1)+
  scale_linetype_manual(values=c("dotted", "solid"))+
  ylab("Relative fitness (number of intact seeds)")+
  xlab("Value of the moment")+
  my_theme()+
  geom_text(data=prediction_sel_nfl_univar%>%
              select(year,predictor,print,type)%>%
              distinct()%>%
              pivot_wider(names_from=type,values_from=print)%>%
              mutate(print=paste("L = ",linear,"\n","NL =", nonlinear)),
            aes(x=Inf,y=Inf,label=print),
             hjust=1.05, vjust=1.2,family="serif")
fig4
ggsave(file="output/figures/fig4.tiff", plot=fig4, width=10, height=7)
```

## Figure 5

Figure based on predictions of yearly univariate models (selection differentials).

```{r}
fig5<-ggplot()+
  geom_point(data=data_ids%>%
               select(year,fitness_rel,avFD_std,var_std,skew_std,kurt_std)%>%
               pivot_longer(cols=avFD_std:kurt_std,
                            names_to="predictor",values_to="value_predictor")%>%
               mutate(predictor=factor(predictor,
                                       levels=c("avFD_std","var_std",
                                                "skew_std","kurt_std"))),
             aes(x=value_predictor,y=fitness_rel),
             size=2,alpha=0.3)+
  facet_grid2(c("year","predictor"), 
              labeller=labeller(predictor=predictor.labs), 
              scales = "free", independent = "all")+
  geom_ribbon(data=prediction_sel_univar,
              aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high,fill=type),
              alpha=0.3)+
  geom_line(data=prediction_sel_univar,
            aes(x=x,y=predicted,linetype=signif,color=type),
            linewidth=1)+
  scale_linetype_manual(values=c("dotted", "solid"))+
  ylab("Relative fitness (number of intact seeds)")+
  xlab("Value of the moment")+
  my_theme()+
  geom_text(data=prediction_sel_univar%>%
              select(year,predictor,print,type)%>%
              distinct()%>%
              pivot_wider(names_from=type,values_from=print)%>%
              mutate(print=paste("L = ",linear,"\n","NL =", nonlinear)),
            aes(x=Inf,y=Inf,label=print),
             hjust=1.05, vjust=1.2,family="serif")
fig5
ggsave(file="output/figures/fig5.tiff", plot=fig5, width=10, height=7)
```

## Sub-figure (not used)

Sub-figure with min, mean and max of each of the moments (not used so far).

```{r}
data_ids%>%ungroup()%>%
  select(avFD_std,var_std,skew_std,kurt_std)%>%summary()
data_ids%>%ungroup()%>%
  filter(near(avFD_std,mean(avFD_std),tol=0.001)==T)%>%select(year,id)
data_ids%>%ungroup()%>%
  filter(avFD_std==min(avFD_std)|avFD_std==max(avFD_std))%>%select(year,id)
data_ids%>%ungroup()%>%   
  filter(near(var_std,mean(var_std,na.rm=T),tol=0.006)==T)%>%select(year,id)
data_ids%>%ungroup()%>%
  filter(var_std==min(var_std,na.rm=T)|var_std==max(var_std,na.rm=T))%>%
  select(year,id)
data_ids%>%ungroup()%>%
  filter(near(skew_std,mean(skew_std,na.rm=T),tol=0.015)==T)%>%
  select(year,id)
data_ids%>%ungroup()%>%
  filter(skew_std==min(skew_std,na.rm=T)|skew_std==max(skew_std,na.rm=T))%>%
  select(year,id)
data_ids%>%ungroup()%>%
    filter(near(kurt_std,mean(kurt_std,na.rm=T),tol=0.001)==T)%>%
  select(year,id)
data_ids%>%ungroup()%>%
  filter(kurt_std==min(kurt_std,na.rm=T)|kurt_std==max(kurt_std,na.rm=T))%>%
  select(year,id)
```

```{r fig.height=2, fig.width=8}
grid.arrange(
  # Mean
  ggplot(rbind(data_id_flowers%>%filter(year==1987&id=="1:50")%>%
                 mutate(stat="2_medium"),
               data_id_flowers%>%filter(year==1987&id=="2:115")%>%
                 mutate(stat="1_high"),
               data_id_flowers%>%filter(year==1988&id=="3:59")%>%
                 mutate(stat="3_low")),
         aes(x=opening_date_v,fill=stat))+
    geom_density(color="black",alpha=0.7)+
  scale_fill_manual(values=c("#756bb1","#bcbddc","#efedf5"))+
    my_theme()+xlab(NULL)+ylab(NULL),
  # Variance
  ggplot(rbind(data_id_flowers%>%filter(year==1989&id=="1:34")%>%
               mutate(stat="3_low"),
             data_id_flowers%>%filter(year==1987&id=="1:59")%>%
               mutate(stat="2_medium"),
             data_id_flowers%>%filter(year==1987&id=="3:141")%>%
               mutate(stat="1_high")),
       aes(x=opening_date_v,fill=stat))+
  geom_density(color="black",alpha=0.7)+
  scale_fill_manual(values=c("#756bb1","#bcbddc","#efedf5"))+
  my_theme()+xlab(NULL)+ylab(NULL),
  # Skewness
  ggplot(rbind(data_id_flowers%>%filter(year==1989&id=="2:28")%>%
                 mutate(stat="2_medium"),
               data_id_flowers%>%filter(year==1987&id=="4:433")%>%
                 mutate(stat="1_high"),
               data_id_flowers%>%filter(year==1989&id=="2:16")%>%
                 mutate(stat="3_low")),
         aes(x=opening_date_v,fill=stat))+
    geom_density(color="black",alpha=0.7)+
  scale_fill_manual(values=c("#756bb1","#bcbddc","#efedf5"))+
    my_theme()+xlab(NULL)+ylab(NULL),
  # Kurtosis
  ggplot(rbind(data_id_flowers%>%filter(year==1988&id=="3:61")%>%
                 mutate(stat="2_medium"),
               data_id_flowers%>%filter(year==1988&id=="6:12")%>%
                 mutate(stat="3_low"),
               data_id_flowers%>%filter(year==1988&id=="6:13")%>%
                 mutate(stat="1_high")),
         aes(x=opening_date_v,fill=stat))+
    geom_density(color="black",alpha=0.7)+
  scale_fill_manual(values=c("#756bb1","#bcbddc","#efedf5"))+
    my_theme()+xlab(NULL)+ylab(NULL),
  ncol=4,bottom=textGrob("Opening date",just="center",
                      gp=gpar(fontsize=16,fontfamily="serif")),
  left=textGrob("Density",just="center",hjust=0.30,
                      gp=gpar(fontsize=16,fontfamily="serif"),
                      rot = 90))
```

<!-- ## Figure 2 -->

<!-- Figure based on predictions of yearly models. -->
<!-- Predictions for mean and variance based on models with only mean and variance. -->

<!-- ```{r} -->
<!-- predictor.labs<-c("Mean","Variance","Skewness","Kurtosis") -->
<!-- names(predictor.labs)<-c("avFD_std","var_std","skew_std","kurt_std") -->
<!-- fig2<-ggplot()+ -->
<!--   geom_point(data=data_ids%>% -->
<!--                select(year,fr_init,avFD_std,var_std,skew_std,kurt_std)%>% -->
<!--                pivot_longer(cols=avFD_std:kurt_std, -->
<!--                names_to="predictor",values_to="value_predictor"), -->
<!--              aes(x=value_predictor,y=fr_init), -->
<!--              size=2,alpha=0.3)+ -->
<!--   facet_grid(cols=vars(predictor=factor(predictor, -->
<!--                               levels=c("avFD_std","var_std", -->
<!--                                        "skew_std","kurt_std"))), -->
<!--              rows=vars(year),scales="free", -->
<!--              labeller=labeller(predictor=predictor.labs))+ -->
<!--   geom_ribbon(data=prediction_fr_init, -->
<!--               aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--               alpha=0.3)+ -->
<!--   geom_line(data=prediction_fr_init,aes(x=x,y=predicted,linetype=signif), -->
<!--             linewidth=1)+ -->
<!--   scale_linetype_manual(values=c("dotted", "solid"))+ -->
<!--   ylab("Proportion of flowers that developed to fruits")+ -->
<!--   xlab("Value of the moment")+ -->
<!--   my_theme() -->
<!-- fig2 -->
<!-- ggsave(file="output/figures/fig2.tiff", plot=fig2, width=10, height=7) -->
<!-- ``` -->

<!-- ## Figure 3 -->

<!-- Figure based on predictions of yearly models -->

<!-- ```{r} -->
<!-- fig3<-ggplot()+ -->
<!--   geom_point(data=data_ids%>% -->
<!--                select(year,prop_seed_preyed, -->
<!--                       avFD_std,var_std,skew_std,kurt_std)%>% -->
<!--                pivot_longer(cols=avFD_std:kurt_std, -->
<!--                names_to="predictor",values_to="value_predictor"), -->
<!--              aes(x=value_predictor,y=1-prop_seed_preyed), -->
<!--              size=2,alpha=0.3)+ -->
<!--   facet_grid(cols=vars(predictor=factor(predictor, -->
<!--                               levels=c("avFD_std","var_std", -->
<!--                                        "skew_std","kurt_std"))), -->
<!--              rows=vars(year),scales="free", -->
<!--              labeller=labeller(predictor=predictor.labs))+ -->
<!--   geom_ribbon(data=prediction_seed_escpred, -->
<!--               aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--               alpha=0.3)+ -->
<!--   geom_line(data=prediction_seed_escpred,aes(x=x,y=predicted,linetype=signif), -->
<!--             linewidth=1)+ -->
<!--   scale_linetype_manual(values=c("dotted", "solid"))+ -->
<!--   ylab("Proportion of seeds escaping predation")+xlab("Value of the moment")+ -->
<!--   my_theme() -->
<!-- fig3 -->
<!-- ggsave(file="output/figures/fig3.tiff", plot=fig3, width=10, height=7) -->
<!-- ``` -->

<!-- ## Figure 4 -->

<!-- Figure based on predictions of yearly models -->

<!-- ```{r} -->
<!-- fig4<-ggplot()+ -->
<!--   geom_point(data=data_ids%>% -->
<!--                select(year,fitness_rel, -->
<!--                       avFD_std,var_std,skew_std,kurt_std)%>% -->
<!--                pivot_longer(cols=avFD_std:kurt_std, -->
<!--                names_to="predictor",values_to="value_predictor"), -->
<!--              aes(x=value_predictor,y=fitness_rel), -->
<!--              size=2,alpha=0.3)+ -->
<!--   facet_grid(cols=vars(predictor=factor(predictor, -->
<!--                               levels=c("avFD_std","var_std", -->
<!--                                        "skew_std","kurt_std"))), -->
<!--              rows=vars(year),scales="free", -->
<!--              labeller=labeller(predictor=predictor.labs))+ -->
<!--   geom_ribbon(data=prediction_sel_nfl, -->
<!--               aes(x=x,y=predicted,ymin=conf.low,ymax=conf.high), -->
<!--               alpha=0.3)+ -->
<!--   geom_line(data=prediction_sel_nfl,aes(x=x,y=predicted,linetype=signif), -->
<!--             linewidth=1)+ -->
<!--   scale_linetype_manual(values=c("dotted", "solid"))+ -->
<!--   ylab("Relative fitness (number of intact seeds)")+xlab("Value of the moment")+ -->
<!--   my_theme() -->
<!-- fig4 -->
<!-- ggsave(file="output/figures/fig4.tiff", plot=fig4, width=10, height=7) -->
<!-- ``` -->

# TO DO: Climatic data 87-89

# Session info

```{r}
sessionInfo()
```
